---
title: "The 'Sneaky' Tournament Report (n°1)"
description: |
  Mastering Runeterra - EU edition #04 - 2021-10-02
base_url: https://www.llorr-stats.com
preview:
author:
  - name: Valentino (Legna) Vazzoler
date: 10-04-2021
output:
 distill::distill_article:
    toc: true
    toc_float: true
    toc_depth: 3
    self_contained: false
citation: false
draft: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE,
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  comment = NA,
  R.options = list(width = 140,
                   digits.secs=6),
  dev.args = list(bg = 'transparent'), # make graphics with transparent background
  fig.align = 'center',
  fig.width=9,
  fig.height=6,
  engine.path = list(
    python = 'C:/anaconda/'   # -> use_python("C:/anaconda/")
  ),
  #'distill options
  layout="l-page",
  preview=FALSE
)

#' R Option
source(file.path("C:","LlorR","scripts","lor_main.R" ))

# require(Hmisc)    # provides knitrSet and other functions
xaringanExtra::use_panelset()
```


```{r panelset-style}
xaringanExtra::style_panelset_tabs(font_family = "Roboto",
                                   active_foreground = "white",
                                   hover_foreground = "black",
                                   hover_border_color = "black",
                                   active_background = "#007fff"
                                   )
```
```{r raw-data}
#' load account of only the players 
#' who took plays in the tournament
#'#################################
LoR.Account.RMD <- fread(file.path("C:","LlorR","data","clean","MREU04_Account.csv"),na.strings = c("",NA))
#' load names of the matches pairs
#'################################
LoR.Pair.Matches <- fread(file.path("C:","LlorR","data","clean","MREU04_namesMatches.csv"),na.strings = c("",NA))
#' load the melt matches
#'######################
Match.DT <- fread(file.path("C:","LlorR","data","clean","MREU04_MatchDT.csv"), header = T, na.strings = c("", NA))
#' load DeckDT
#'############
LoR.Deck        <- fread(file.path("C:","LlorR","data","raw","LoR_DECK.csv"),na.strings = c("",NA))

#' tournament starting time
tournament.start <- as.POSIXlt("2021-10-02 15:00:00", tz = "UTC")
```

# Data {.unnumbered}

```{r previous-week}
#' load gameDT
#'############
file.DT <- file.path("C:","LlorR","data","raw","LoR_MatchDT.csv")
header        <- fread(file.DT, header = FALSE, na.strings = c("",NA), nrows = 1, stringsAsFactors = FALSE)
LoR.Match.RMD <- fread(file.DT, header = FALSE, na.strings = c("",NA), skip = 3*10^6 )
colnames(LoR.Match.RMD) <- unlist(header,use.names = F)

LoR.Melt.Matches.RMD <- LoR.Match.RMD %>%
  #' Base filters
  filter( game_type=="Ranked" ) %>%
  filter( game_start_time_utc >= tournament.start-lubridate::days(7) & game_start_time_utc < tournament.start ) %>%
  #' 'process' data
  left_join(.,LoR.Deck[,.(deck_code,archetype)] %>% setnames(old = "archetype", new = "player_1")   ,by=c("deck_code_1"="deck_code")) %>%
  left_join(.,LoR.Deck[,.(deck_code,archetype)] %>% setnames(old = "archetype", new = "opponent_1") ,by=c("deck_code_2"="deck_code")) %>%
  mutate( player_2 = opponent_1, opponent_2 = player_1 ) %>%
  select( match_key,server,game_start_time_utc,
          ends_with("_1"),ends_with("_2"),-ends_with("_3"),-ends_with("_4"),-contains("order_of_play"),-contains("deck_code"),-contains("deck_id"),-contains("participants") ) %>%
  #' melt data
  melt(id.vars=c("match_key","server","game_start_time_utc"), measure.vars=patterns(
    str_sub(
      names(select(.,ends_with("_1")))
      ,end = -3)
  ),
  value.name = str_sub(
    names(select(.,ends_with("_1")))
    ,end = -3)
  ) %>%
  # filter(is.na(player))
  select(-variable,-puuid,-match_key)

#' WR tbl
#'#######
ladder.WR.DT <- LoR.Melt.Matches.RMD %>%
  filter(game_outcome!="tie") %>%
  select( player,opponent,game_outcome ) %>%
  group_by(player) %>%
  summarise( nWin   = sum(game_outcome=="win"),
             nGames = n(),
             WR=mean(game_outcome=="win")
  ) %>%
  ungroup() %>%
  mutate( playrate = nGames/sum(nGames) )

#' MU tbl the date is already filtered
#'####################################
ladder.MUtbl <- LoR.Melt.Matches.RMD %>%
  filter( game_outcome != "tie" ) %>%
  select( player,opponent,game_outcome,server,factions ) %>%
  # mutate( factions = str_replace_all(factions, pattern="faction_",replacement = "") %>% str_replace_all(.,pattern="_Name",replacement = "") %>% factor() ) %>%
  group_by(player,opponent) %>%
  summarise( muWin   = sum(game_outcome=="win"),
             muGames = n(),
             muWR=mean(game_outcome=="win"),
             factions = unique(str_replace_all(factions, pattern="faction_",replacement = "") %>% str_replace_all(.,pattern="_Name",replacement = "") ) ) %>%
  ungroup() %>%
  mutate( CI   = map2_df(.x=muWin,.y = muGames, .f = ~binom::binom.confint(.x,.y,0.95,methods="exact")[,c("lower","upper")] ) ) %>%
  chop(CI) %>%
  unnest(CI) %>%
  mutate( okCI = map2_lgl(.x = lower,.y = upper, ~ !between(0.50,.x,.y) ) ) %>%
  mutate( direction = ifelse(muWR>0.50,"POS","NEG") ) %>%
  mutate( direction = replace(direction,direction==0.50,"TIE") ) %>%
  mutate( CI := glue::glue("({scales::percent(lower,accuracy = 0.1)}-{scales::percent(upper,accuracy = 0.1)})" ) ) %>%
  # removing ~extra variables
  select(-lower,-upper) %>%
  left_join(.,ladder.WR.DT[,c("player","playrate")],by="player")
```

```{r create-gt-summary}
namesBracket <- LoR.Pair.Matches|>
  distinct(player)|>
  filter(player!="BYE")

tibble( partecipant = Match.DT|>distinct(player)|>filter(player!="BYE")|>NROW(),
        matches = NROW(Match.DT|>distinct(player,opponent)) ,
        games = NROW(Match.DT) ) |>
  gt() |>
  text_transform(
    locations = cells_body(
      columns = partecipant
    ),
    fn = function(x) {
      glue::glue("{x}/{NROW(namesBracket)}")
    }) |>
  cols_label(
    partecipant   = md("**Partecipants**"),
    matches = md("**Matches**"),
    games = md("**Games**")
    ) |>
  gt::tab_header(
    title = glue::glue("Mastering Runeterra \n EU04")
    ) |>
 tab_options(
    table.background.color = "transparent",
    table.font.color = "black",
    table.font.color.light = "black"
   )
```

```{r create-lineUp-DT}
LineUp.DT <- Match.DT %>% 
  select(playerID,player,server,playerDeck,deck_code) %>%
  group_by(playerID,player) %>%
  summarise( listDeck=list(unique(playerDeck)),listCode=list(unique(deck_code)) )

LineUp.DT <- LineUp.DT %>%
  cbind(.,map_df(.x = LineUp.DT$listCode, .f = ~assignLineUp(.x) )) %>%
  rename("code_1"="deck_1","code_2"="deck_2","code_3"="deck_3" ) %>%
  left_join( .,LoR.Deck %>% select(deck_code,deck_1=archetype),by=c("code_1"="deck_code") ) %>%
  left_join( .,LoR.Deck %>% select(deck_code,deck_2=archetype),by=c("code_2"="deck_code") ) %>%
  left_join( .,LoR.Deck %>% select(deck_code,deck_3=archetype),by=c("code_3"="deck_code") ) %>%
  filter( !is.na(playerID) ) %>%
  # LineUp.DT %>%
  dplyr::mutate(LU = purrr::pmap_chr(list(x = deck_1,y = deck_2,z = deck_3), ~  glue::glue_collapse(na.omit(sort(c(..1,..2,..3))), sep = " - ")   )  ) %>%
  ungroup()
```

```{r compute-MU}
playRates.byLU <- LineUp.DT |>
  select(contains("deck_")) |>
  unlist(use.names = F) %>%
  tabyl(.,show_na = F) |>
  arrange(desc(n))  |>
  #' account for the presence of 3 decks
  mutate(percent = 3*percent ) |>
  rename( 'playerDeck'=1 )


#' WR tbl
#'#######
WR.DT <- Match.DT |>
  filter(game_outcome!="tie") |>
  select(playerDeck,opponentDeck,game_outcome ) |>
  group_by(playerDeck) |>
  summarise( nWin   = sum(game_outcome=="win"),
             nGames = n(),
             WR=mean(game_outcome=="win")
  ) |>
  ungroup() |>
  left_join(playRates.byLU, by="playerDeck" ) |>
  rename( "playrate"="percent" )

#' MU tbl the date is already filtered
#'####################################
MUtbl <- Match.DT %>%
  filter( game_outcome != "tie" ) %>%
  select( playerDeck,opponentDeck,game_outcome,server,factions ) %>%
  group_by(playerDeck,opponentDeck) %>%
  summarise( muWin   = sum(game_outcome=="win"),
             muGames = n(),
             muWR=mean(game_outcome=="win"),
             factions = unique(str_replace_all(factions, pattern="faction_",replacement = "") %>% str_replace_all(.,pattern="_Name",replacement = "") ) ) %>%
  ungroup() %>%
  mutate( CI   = map2_df(.x=muWin,.y = muGames, .f = ~binom::binom.confint(.x,.y,0.95,methods="exact")[,c("lower","upper")] ) ) %>%
  chop(CI) %>%
  unnest(CI) %>%
  mutate( okCI = map2_lgl(.x = lower,.y = upper, ~ !between(0.50,.x,.y) ) ) %>%
  mutate( direction = ifelse(muWR>0.50,"POS","NEG") ) %>%
  mutate( direction = replace(direction,direction==0.50,"TIE") ) %>%
  mutate( CI := glue::glue("({scales::percent(lower,accuracy = 0.1)}-{scales::percent(upper,accuracy = 0.1)})" ) ) %>%
  # removing ~extra variables
  select(-lower,-upper) %>%
  left_join(.,WR.DT[,c("playerDeck","playrate")],by="playerDeck")


# MUtbl|>
#   group_by(playerDeck)|>
#   summarise( Games = sum(muGames) )|>
#   filter( Games <= 3 )
```


```{r compute-games-americas}
Game.Result <- Match.DT |>
  # As the players and opponents plays each other only in a single match group them and the min of their game_start can identify the round they are playing in
  group_by( player,opponent,round ) |>
  arrange( player,opponent,game_start_time_utc ) |>
  summarise( result = paste(game_outcome,collapse = "," ), ldeck  = list(playerDeck) ) |>
  # number of won games in the match
  mutate( nWin = str_count(result,"win") ) |>
  # is the match won?
  mutate( matchWin = ifelse(nWin==2 | result =="BYE" ,1,0) ) |>
  ungroup() |>
  group_by(player) |>
  # sum of ALL matches won
  mutate( cumWin = cumsum(nWin)) |>
  # sum of ALL games won
  mutate( cumMatchWin = cumsum(matchWin)) |>
  left_join(LineUp.DT,by=c("player"))

Game.Result$ban <- lapply( 1:NROW(Game.Result), function(x) (setdiff( Game.Result$listDeck[x] %>% unlist(),Game.Result$ldeck[x] %>% unlist() )) %>% ifelse(length(.)==1,.,NA ) ) %>% unlist(use.names = F)
```

```{r table-ban}
#' all deck for bans
deckForBan <- LineUp.DT %>%
  # filter(!is.na(deck_3) ) %>%
  # filter(!is.na(deck_3) & server!="asia") %>%
  select(contains("deck")) %>%
  unlist(.,use.names = F) %>% unique() %>% sort()
        
#' create Ban DT      
################
ban.tbl <- Game.Result |>
  # filter(!is.na(deck_3) ) |>
  group_by( ban ) |>
  count(ban) |>
  filter( !is.na(ban) )

ban.DT <- tibble( deck = deckForBan ) |>
  left_join(ban.tbl |> select(deck = ban,nBan=n) ,by = "deck") |>
  as.data.table()

for (i in 1:NROW(ban.DT) ) {
  deck <- pull(ban.DT[i,"deck"])
  
  whichLU <- Game.Result %>%
    # filter(!is.na(deck_3) ) %>%
    filter( deck_1 == deck | deck_2 == deck | deck_3 == deck ) %>%
    pull(LU)
  
  ban.DT[i,maxBan := Game.Result |>
    filter( LU %in% whichLU ) |>
    filter( !is.na(ban) ) |>
    NROW() ]
}

full.ban.DT <- ban.DT |>  # start with ban.DT as it contains the list of all decks that theoretically can appears
  left_join(WR.DT,by=c("deck"="playerDeck")) |> # add the Seasonal data
  mutate(across(c(nBan,nWin, nGames,playrate), ~replace_na(.x, 0)) ) |>
  # mutate(across(everything(), ~replace_na(.x, 0)) ) |> # fill the missing values
  mutate( meanBan = nBan/maxBan ) |>   # since the number of ban considers all the cases with ban information it is some to impute 0
  left_join(ladder.WR.DT |> select(deck=player,lplayrate=playrate,lWR=WR),by=c("deck"))
```

```{r compute-LMI}
LMI.DT <- full.ban.DT %>%
  filter( complete.cases(.) ) |>
  filter( nGames >= 5 ) |>
  # select(playrate,WR,lWR,meanBan ) |>
  # mutate(across(everything(), ~replace_na(.x, 0)) ) |> 
  mutate( PR_ind = scale_quantile(playrate),
          WR_ind = scale_quantile(WR),
          lWR_ind = scale_quantile(lWR),
          meanBan_ind = scale_quantile(meanBan)
          ) |>
  mutate( WIN_ind    = map2_dbl(.x = WR_ind, .y = lWR_ind, ~weighted.mean(x = c(.x,.y),w = c(0.5,0.5) )) ) |>
  mutate( WIN_ind = scale_quantile(WIN_ind) ) |>
  mutate( str_dim = map2_dbl(.x = WIN_ind, .y = meanBan_ind, ~weighted.mean(x = c(.x,.y),w = c(0.5,0.5) )) ) |>
  mutate( str_dim = scale_quantile(str_dim) ) |>
  mutate( str_dim = map2_dbl(.x = WIN_ind, .y = meanBan_ind, ~weighted.mean(x = c(.x,.y),w = c(0.5,0.5) )) ) |>
  mutate( str_dim = scale_quantile(str_dim) ) |>
  mutate( LMI = map2_dbl(.x = str_dim, .y = PR_ind, ~weighted.mean(x = c(.x,.y),w = c(0.5,0.5) )) ) |>
  mutate( LMI = scale_quantile(LMI) ) |> 
  mutate( tooltip = glue::glue("{deck}
                               LMI {round(LMI*100,1)}
                               WinRate {scales::percent(WR,accuracy = 0.1)}
                               PlayRate {scales::percent(playrate,accuracy = 0.1)}
                               mean BanRate {scales::percent(meanBan,accuracy = 0.1)}") ) |>
  mutate( tooltip_mini = glue::glue("{deck}
                               LMI {round(LMI*100,1)}") ) |>
  mutate(tier = case_when( 
     LMI >= 0.9 ~ "Tier1",
     # 0.90 <= LMI & LMI < 0.975 ~ "Tier1",
     0.60 <= LMI & LMI < 0.90 ~ "Tier2",
     0.30 <= LMI & LMI < 0.60 ~ "Tier3",
     LMI < 03.0 ~ "Tier4 or lower",
    ) 
  )
```

# Players Info

::: l-page
::::: {.panelset}

::: {.panel}
### Top 8 {.panel-name}

```{r player-results}
# remotes::install_github("jthomasmock/gtExtras")
library(gtExtras)

Game.Result |> 
  group_by(player) |>
  slice_max(cumMatchWin,n=1) |>
  ungroup() |>
  arrange(desc(cumMatchWin)) |>
  slice_max(cumMatchWin,n=8) |>
  select( player, cumWin, cumMatchWin, LU ) |>
  add_column( rank = c(1:4,rep("5/8",4)), .before = "cumWin" ) |>
  gt() |>
  gt_theme_538() |>
  gt_highlight_rows(
    row = 1:4,
    fill = "whitesmoke",
    bold_target_only = TRUE,
    target_col = "player"
  ) |>
  cols_align(
    align = c("center"),
    columns = 3:5
    ) |>
  tab_header(
    title = "Top8 Players",
    subtitle = "from Mastering Runeterra - EU04"
  ) |>
  tab_source_note(
    source_note = "Metadata of games collected with RiotGames API."
  ) |>
  cols_label(
    player   = md("**Player**"),
    rank     = md("**Result**"),
    cumWin   = md("**Games Won**"),
    cumMatchWin = md("**Matches Won**"),
    LU = md("**Line Up**")
    ) |>
  tab_options(
    table.background.color = "transparent",
    table.font.color = "black",
    table.font.color.light = "black"
   )
```
:::

::: {.panel}
### All Player Line-Ups {.panel-name}

As some decks have not being played I don't have complete information

```{r table-LineUps}
LineUp.DT %>%
  select(player,LU,contains("deck_"),contains("code_") ) %>%
  # pivot_longer( cols = c(contains("deck_"),contains("code_")) ) |>
  pivot_longer(cols = c(contains("deck_"),contains("code_")),
               names_to=c(".value", "index"),
               names_sep = "_") |>
  relocate(LU,.after = code) |>
  select(-index) |>
  reactable(
    # wrap = FALSE,
    bordered = TRUE,
    highlight = TRUE,
    striped = TRUE,
    searchable = TRUE,
    compact = TRUE, # compact the table
    # fullWidth = FALSE, # don't fill the page
    defaultPageSize = 30,
    defaultColDef = colDef(
      style = list(fontWeight = 500, color = "black",
                   fontFamily = "Helvetica", fontSize = "12px"),
      align = "center",
      headerStyle = list(background = "steelblue",color="white",fontFamily = "Work Sans, sans-serif", fontSize = "14px" )
      ),
    columns = list(
      # deck_1 = colDef(name = "Deck 1", style = list(color = "red", fontFamily = "Work Sans, sans-serif", fontSize = "12px"  ) ),
      # deck_2 = colDef(name = "Deck 2", style = list(color = "green", fontFamily = "Work Sans, sans-serif", fontSize = "12px") ),
      # deck_3 = colDef(name = "Deck 3", style = list(color = "blue", fontFamily = "Work Sans, sans-serif", fontSize = "12px" ) ),
      LU = colDef( show = F ),
      # LU = colDef(name = "Line Up",minWidth = 200 ),
      deck = colDef(name = "Deck",minWidth = 200 ),
      code = colDef(name = "DeckCode", cell = function(value, index) {
        # Render as a link
        if (!is.na(value) ) {
          url <- glue::glue("{urlruneterraAR}{urldeck}{value}")
          htmltools::tags$a(href = url, target = "_blank", as.character(value))
        } } ,minWidth = 400, style = list(fontSize = "10px") )
      )
    ) |>
  reactablefmtr::add_title("Player's LineUps", background_color = "transparent" ) |>
  reactablefmtr::add_subtitle("from Mastering Runeterra - EU04", background_color = "transparent") |>
  reactablefmtr::add_source("Decks for each player who took part at the tournament.
                            Missing values are from the lack of games with other decks.
                            Metadata of games collected with RiotGames API.", background_color = "transparent")
```
:::
:::::

:::

# Deck

PingCity (TF/GP Bandle) and Nami/Zoe both performed way worse compared to the ladder. In the case of Fizz/Nami it may be because the results are split with Fizz/Nami (BW/MT) which is pretty much the same deck. (Simposon Paradox?)

Other notable results are BandleCity-Poppy/Demacia decks that performed better better than the Noxus version and even if the data is small and sparse among several decks the direction remain the same.

Akshan/Sivir (Demacia) and Lee/Zoe are confirmed as usual staple tournament decks with the first still being tier1 choice

::: {.l-page}
::::: {.panelset}

::: {.panel}
### Deck's Statistics {.panel-name}

```{r table-overall}
LMI.DT %>%
  select(deck,nGames,WR,playrate,meanBan,lWR) %>%
  mutate( diffLadder = WR-lWR ) |>
  arrange(desc(nGames)) %>%
  reactable(.,
            # wrap = FALSE,
            bordered = TRUE,
            highlight = TRUE,
            striped = TRUE,
            searchable = TRUE,
            compact = TRUE, # compact the table
            # fullWidth = FALSE, # don't fill the page
            defaultPageSize = 15,
            defaultColDef = colDef(
               style = list(fontWeight = 500, color = "black",
                       fontFamily = "Work Sans, sans-serif", fontSize = "12px"),
               # header = function(value) str_to_title(value),
               #  cell = function(value) format(value, nsmall = 1),
               align = "center",
               headerStyle = list(background = "steelblue",color="white",fontFamily = "Work Sans, sans-serif", fontSize = "14px" )
            ),
            columns = list(
                deck = colDef(name="Deck", align = "left" ),
                nGames = colDef(name="#Games"),
                WR = colDef(name="Win Rate", format = colFormat(percent = TRUE, digits = 2) ),
                playrate = colDef(name="Play Rate", format = colFormat(percent = TRUE, digits = 2) ),
                meanBan = colDef(name="Ban Rate", format = colFormat(percent = TRUE, digits = 2) ),
                lWR = colDef(show=F),
                diffLadder = colDef(name=("WinRate diff \n vs Ladder"),format = colFormat(percent = TRUE, digits = 2) )
              )
            ) |>
  reactablefmtr::add_title("Deck's Statistics", background_color = "transparent") |>
  reactablefmtr::add_subtitle("from Mastering Runeterra - EU04" , background_color = "transparent") |>
  reactablefmtr::add_source("BanRate from matches whose I can deduce the banned deck.
                            Playrates from all lineUps data so including also incomplete lineUps.
                            Metadata of games collected with RiotGames API." , background_color = "transparent")
```

- **Ban Rate**: ratio between the number of bans and the number of matches of a deck.

\begin{equation}

BanRate = \frac{\#ban}{\#match}

\end{equation}

Example: 2 Line-Ups contained a Teemo/Ezreal deck, both played all 9 matches and Teemo/Ezreal was banned respectively 3 and 6 times; the ban rate would be $\frac{(3+6)}{(9+9)} = 50\%$

- **PlayRate**:  ratio between the number of times a deck appears among all lineUps (including incomplete information cases) and the number of all decks in all lineUps.

:::

::: {.panel}
### Single Decks PlayRate {.panel-name}

How the results change is I consider only lineUps with complete information or not.

```{r table-deck, echo=FALSE}
left_join(
LineUp.DT %>%
  select(contains("deck_")) %>%
  unlist(.,use.names = F) %>%
  tabyl(.,show_na = F) %>% 
  arrange(desc(n))  %>% 
  #' account for the presence of 3 decks
  mutate(percent = 3*percent ) %>%
  rename( 'Deck'=1 ),
LineUp.DT  %>%
  select(contains("deck_")) %>%
  filter(!is.na(deck_3)) %>%
  select(contains("deck")) %>%
  unlist(.,use.names = F) %>%
  tabyl(.,show_na = F) %>% 
  arrange(desc(n))  %>% 
  #' account for the presence of 3 decks
  mutate(percent = 3*percent ) %>%
  rename( 'Deck'=1,"n_full"="n","percent_full"="percent" ),
by="Deck"
) %>%
  reactable(.,
            # wrap = FALSE,
            bordered = TRUE,
            highlight = TRUE,
            striped = TRUE,
            searchable = TRUE,
            compact = TRUE, # compact the table
            # fullWidth = FALSE, # don't fill the page
            defaultPageSize = 20,
            defaultColDef = colDef(
               style = list(fontWeight = 500, color = "black",
                       fontFamily = "Work Sans, sans-serif", fontSize = "12px"),
               # header = function(value) str_to_title(value),
               #  cell = function(value) format(value, nsmall = 1),
               align = "center",
               headerStyle = list(background = "steelblue",color="white",fontFamily = "Work Sans, sans-serif", fontSize = "14px" )
            ),
            columns = list(
              deck = colDef(name = "Deck", style = list(fontWeight = "bold",color = "black",fontFamily = "Work Sans, sans-serif", fontSize = "13px") ),
              n = colDef(name = "N", footer = function(values) sprintf("%.0f", sum(values,na.rm = T))),
              n_full = colDef(name = "N (only full Line-Ups)",footer = function(values) sprintf("%.0f", sum(values,na.rm = T))),
              percent = colDef(name = "Overall PlayRate",format = colFormat(percent = TRUE,digits = 2) ),
              percent_full = colDef(name = "Overall PlayRate (only full Line-Ups)",format = colFormat(percent = TRUE,digits = 2) )
            )
    ) |>
  reactablefmtr::add_title("Deck's Playrates", background_color = "transparent") |>
  reactablefmtr::add_subtitle("from Mastering Runeterra - EU04", background_color = "transparent") |>
  reactablefmtr::add_source("Relative frequencies from all data or only line-ups with full information.
                            Metadata of games collected with RiotGames API.", background_color = "transparent")


# MUtbl|>distinct(playerDeck) #59 Deck
```
:::
:::::
:::


# Deck Performance

Usually the play-rates and win-rates on the ladder are highly predictable of performances on a tournament, yet this time the correlation among tournament play-rate and ladder play-rates. There is a change part of it is because of the smaller sample pool of decks or also high likely that people aren't confident if abusing the most popular deck this time as they could be more easily handled with bans and counter-lineUps.

The correlation of play-rates is also interesting as there is almost none of it, while all the win-rates are indeed more unstable the data seems to suggest that certain decks are to be re-evaluated for a Bo3 setting meaning there may be more dark horses and some "overhyped" decks (like Ping City)

Please be aware that I use several variable to compute the LMI and not just the win-rate, this is because the LMI wants to evaluate the "overall" performance and while J4/Poppy for example has the highest win-rate the other values like ban-rate and play-rate are among the worst.

::: {.l-page}
::::: {.panelset}

::: {.panel}
### Top10 Decks {.panel-name}

```{r LMIxJason, fig.width=12, fig.height=8, layout="l-page", preview=TRUE}
plot.LMIbasic <- LMI.DT |>
  slice_max(LMI,n = 10,with_ties = F) %>%
  mutate_if(is.numeric, funs(round(., 4)) ) |>
  mutate( LMI = LMI*100 ) |>
  ggplot( aes(x=WR, y=playrate, size = LMI, color = tier, text=tooltip_mini)) +
  geom_point(alpha=0.6) +
  scale_size(range = c(1, 15), name="LMI") +
  theme_539() + 
  guides(colour = guide_legend(override.aes = list(size=10)),
         size = FALSE ) +
  geom_text_repel( 
    aes(label=tooltip_mini),
    color = "grey25",
    family = "Roboto",
    # fontface = "bold",
    size = 3,
    fill = NA
  ) +
  theme( legend.position = "top",
         # legend.margin = element_blank(),
         legend.background = element_blank(),
         legend.title = element_text(size=9, lineheight = 1.3),
         legend.justification = "right"
         ) +
  labs(
    title = "Top10 Decks at the Mastering Runeterra Tournament EU #04",
    x = "WinRate",
    y = "PlayRate",
    caption = element_text(glue::glue("LMI computed with the improved version which included banrate and ladder win rates
                                      Metadata of games collected with RiotGames API
                                      by Legna"))
    )
  # xlim(0, 0.40) +
  # ylim(0.30, 0.70)

plot.LMIbasic
  
ggsave("./images/MREU04-LMI-basic.png")
```

- **Tier0** with LMI >= 97.5

- **Tier1** with LMI $\in$ [85,97.5)

- **Tier2** with LMI $\in$ [60,85)

- **Tier3 or lower** with LMI < 60

`r kableExtra::text_spec("Note:", color = "red")`Hovering over a circle will display a deck values.

> The LMI [^3] [^4] is an Index I developed to measure the performance of decks in the metagame. For those who are familiar with basic statistical concept I wrote a document to explain the theory behind it: , it's very similar to [vicioussyndicate](https://www.vicioussyndicate.com) (vS) Meta Score from their data reaper report. The score of each deck ***is not*** just their "strength", it takes in consideration both play rates and win rates that's why I prefer to say it measure the "performance". The values range from 0 to 100 and the higher the value, the higher is the performance.

[^3]: [LMI - Early Theory](https://llorr-stats.com/analysis/lmi/)

[^4]: [LMI - Adding a Ban Index](https://www.llorr-stats.com/analysis/lmi-02-tentative-expansion/)

:::

::: {.panel}
### Playrate vs Ladder {.panel-name}

```{r compute-cor-PR, fig.width=12, fig.height=8}
CC.table.Ladder <- LoR.Melt.Matches.RMD |>
  select(playerDeck=player) |>
  tabyl(playerDeck) |> 
  rename("ladderPlayrate"="percent","ladderN"="n")
  # slice_head(n = 30)

plot.corPR <- LMI.DT |>
  # tabyl(playerDeck) |>
  # slice_max(playrate,n=20) |>
  rename( "playerDeck"="deck"  ) |>
  # select(playerDeck=deck,tournamentPercent=playrate,WR,meanBan) |>
  left_join(CC.table.Ladder, 
            by=c("playerDeck")
            ) %>%
  filter(complete.cases(.) ) |>
  ggplot(aes(ladderPlayrate,playrate)) +
  geom_point() +
  geom_label_repel( 
    aes(label=playerDeck),
    family = "Helvetica",
    # fontface = "bold",
    size = 3,
  )+
  stat_smooth(method="lm",se=FALSE,geom="line", alpha=0.8, color = "steelblue") +
  geom_abline(intercept = 0, alpha=0.8, color = "grey75") +
  # stat_smooth(method="lm",se=FALSE,aes(alpha=0.6)) +
  ggpubr::stat_regline_equation(aes(label = ..rr.label..),size=5,show.legend = FALSE) +
  labs(x = "Ladder Play Rate",
       y = "Tournament Play Rate",
       title = "Comparison of Play Rates",
       subtitle = "Mastering Runeterra EU #04 - Comparing Ladder and Tournament PlayRates",
       caption = element_text(glue::glue("Playrates from {tournament.start-lubridate::days(7)} to {tournament.start}, one week before the start of the tournament
                                         Blue line is fitted values with a univariate linear model
                                         Gray line is the diagonal for the first quadrant
                                         Metadata of games collected with RiotGames API") )
       ) +
  theme_539()

plot.corPR  

ggsave("images/MREU04-PRcor.png")
```

:::

::: {.panel}
### WinRate vs Ladder {.panel-name}

```{r compute-cor-WR}
deck.to.remove <- c("Jarvan IV / Poppy (BC/DE)","Fizz / Nami (BW/MT)")

plot.corWR <- WR.DT |>
  # slice_max(playrate,n=20) |>
  filter( nGames > 5 ) |>
  select(playerDeck,tournamentWR=WR,nGames) |>
  left_join(ladder.WR.DT |>
              select(playerDeck=player,ladderWR=WR), by="playerDeck") %>%
  filter(complete.cases(.) ) |>
  filter( playerDeck %!in% deck.to.remove  ) |>
  ggplot(aes(ladderWR,tournamentWR)) +
  geom_point() +
  geom_label_repel( 
    aes(label=playerDeck),
    family = "Helvetica",
    # fontface = "bold",
    size = 3,
  ) +
  stat_smooth(method="lm",se=FALSE,geom="line", alpha=0.6, color = "steelblue") +
  geom_abline(intercept = 0, alpha=0.8, color = "grey75") +
  ggpubr::stat_regline_equation(aes(label = ..rr.label..),size=5,show.legend = FALSE) +
  labs(title = "Scatter plot of Win Rates",
       x = "Ladder Win Rate",
       y = "Tournament Win Rate",
       caption = element_text(glue::glue("Playrates from {tournament.start-lubridate::days(7)} to {tournament.start} one week before the start of the tournament
                                         Decks with at least 5 games
                                         Decks removed for being outlier: {str_flatten(deck.to.remove, collapse=' & ')} that vastly outperformed the ladder winrate
                                         Blue line is fitted values with a univariate linear model
                                         Gray line is the diagonal for the first quadrant
                                         Metadata of games collected with RiotGames API"))
       ) +
  theme_539()  +
  xlim(0.30, 0.70) +
  ylim(0.30, 0.70)

plot.corWR

ggsave("images/cor.ladder.png")
```

:::

::: {.panel}

### LMI (full) {.panel-name}

```{r plot-LMI, fig.width=12, fig.height=8, layout="l-page", preview=TRUE}
plot.LMIfull <- LMI.DT |>
  mutate_if(is.numeric, funs(round(., 4)) ) |>
  mutate( LMI = LMI*100 ) |>
  ungroup() |>
  ggplot( aes(x=WR_ind, y=PR_ind, size = LMI, color = tier, text=tooltip)) +
  geom_point(alpha=0.6) +
  scale_size(range = c(1, 15), name="LMI") +
  theme_539() +
  geom_label_repel( 
    aes(label=tooltip),
    family = "Roboto",
    color = "grey50",
    fontface = "bold",
    size = 3,
    fill = NA,
    vjust = "outward",
    label.padding = unit(0.8, "mm"),
    label.size = unit(0.25, "mm"),
    label.r = unit(0.5, "mm"),
    min.segment.length = 0,
    segment.linetype = 2
  ) + 
  guides(colour = guide_legend(override.aes = list(size=10)),
         size = FALSE ) +
  theme( legend.position = "top",
         # legend.margin = element_blank(),
         legend.background = element_blank(),
         legend.title = element_text(size=9, lineheight = 1.3),
         legend.justification = "right"
         ) +
  labs(
    title = "LMI at Mastering Runeterra Tournament EU #04",
    x = "Win Index",
    y = "Freq Index",
    caption = element_text(glue::glue("LMI computed with the improved version which included banrate and ladder win rates
                                      Metadata of games collected with RiotGames API
                                      by Legna"))
    )

plot.LMIfull

ggsave("./images/MREU04-LMI-full.png")
```

```{r}
# downloadthis::download_this(
#   plot.LMIfull,
#   button_label = "Download (full) LMI plot as .png",
#   button_type = "primary",
#   has_icon = TRUE,
#   icon = "fa fa-save",
#   self_contained = FALSE
# )
```


```{r plot-LMI-plotly, fig.width=12, fig.height=8, layout="l-page", preview=TRUE}
# fig <- LMI.DT |> 
#   # slice_max(LMI,n = 50,with_ties = F) %>%
#   mutate_if(is.numeric, funs(round(., 4)) ) |>
#   ggplot( aes(x=PR_ind, y=WR_ind, size = LMI^2, color = tier, text=tooltip)) +
#   geom_point(alpha=0.6) +
#   scale_size(range = c(1, 15), name="LMI") + 
#   theme_minimal() +
#   labs( title = "LoR-Meta Index (LMI)",
#         caption = "top50 highest LMI values, with a min amount of 100 games.",
#         x = "WR Index",
#         y = "Freq Index"
#         )
# 
# ggplotly(fig, tooltip="text")
```
:::

:::::
:::

# Regions

## Play Rate

```{r process-tableFreq}
Region.Freq <- Match.DT %>%
  select(factions) %>%
  separate_rows(factions,sep=",") %>%
  tabyl(factions,show_na=F) %>%
  tibble() %>% 
  rename_all(~c("region","n","freq")) %>%
  mutate(region = str_replace_all(region, set_names(data_regions$nameRef, data_regions$factions)) ) %>% 
  add_column(., icon = data_regions$icon )
```

::: l-page
::::: {.panelset}
::: {.panel}
### Plot {.panel-name}

```{r plot-Region, fig.width=12, fig.height=8}
sxLabel_card <- format(Region.Freq$freq*100,2)
dxLabel_card <- format(Region.Freq$freq*100,2)
sxLabel_card <- ifelse(as.numeric(sxLabel_card) > 4,  sxLabel_card , "") |> as.numeric() %>% scales::number(., accuracy = 0.01)
dxLabel_card <- ifelse(as.numeric(dxLabel_card) <= 4, dxLabel_card , "") |> as.numeric() %>% scales::number(., accuracy = 0.01)

RegionByRegion <- Region.Freq |>
  ggplot(aes(x = reorder(region, freq), y = freq)) +
  geom_bar(stat="identity") +
  geom_bar_pattern(
    aes(
      pattern_filename = region,
    ),
    stat            = 'identity',
    pattern         = 'image',
    pattern_type    = 'none',
    fill            = data_regions$colorRegion,
    colour          = 'black',
    pattern_scale   = -2,
    pattern_filter  = 'point',
    pattern_gravity = 'east'
  ) +
  # theme_void() +
  labs(
    title = "Regions Play Rate",
    subtitle = "number of times a region is included in a deck",
    x = "Region",
    y = "Play Rate"
    # caption = "number of times a region is included in a deck" 
  ) +
  annotate(geom = 'text', 
         x = 1.0, 
         y = 0.15, 
         hjust = 0.5,
         label = glue::glue('n = {NROW(Match.DT)}\nGini Index = {round(DescTools::Gini(Region.Freq$freq,na.rm = T),3)}'), 
         fontface = 'bold') +
  coord_flip() +
  scale_pattern_filename_discrete(choices = data_regions$iconsPath ) +
  scale_pattern_discrete(guide = guide_legend(nrow = 1)) +
  scale_fill_manual("legend", values = data_regions$colorRegion ) +
  scale_y_continuous(limits = c(0, round(max(Region.Freq$freq+0.04 ),3) ),
                     breaks = seq(0,0.5,0.04),
                     expand = c(-0.001,0.02),
                     labels = scales::percent_format(accuracy = 1) ) +
  guides(fill = "none") +
  #' Adding the text of the frequencies
  geom_text(aes(label = sxLabel_card), hjust = 2.5, size = 5,position = position_dodge(width = 1)) +
  geom_text(aes(label = dxLabel_card), hjust = -0.5, size = 5,position = position_dodge(width = 1)) +
  theme_539() +
  theme( legend.position = "none",
         axis.text = element_text(face = "bold", color = "grey25"),
         panel.grid.major.y = element_blank()
         )
  
RegionByRegion
```

The Gini Index is a measure of heterogeneity so, in this case and in simpler terms, how much the play rates are similar. The Index goes (when normalized like here) $in$ [0,1] and it's equal to 1 when there's a single value with 100% play rate or 0 when all play rates are equal. Of course a Gini Index of 1 needs to be avoided but it's not like the aim should be 0. As said, it's just to add some additional tools.
:::


::: {.panel}
### Regions combination ocurrances {.panel-name}

```{r double-faction}
tibble( faction_1 = rep(data_regions$nameRef,each = 9),
        faction_2 = rep(data_regions$nameRef,time = 9)
        ) %>%
  left_join(.,
Match.DT |>
  select(factions) |>
  mutate(factions = str_replace_all(factions,"faction_","")) |>
  mutate(factions = str_replace_all(factions,"_Name","")) |>
  separate(factions,into = c("faction_1","faction_2"),sep = ",") |>
  mutate(across(contains("faction"),~factor(.,levels = data_regions$nameRef ))) |>
  rowwise() |>
  mutate(faction_2 = replace_na(faction_2, faction_1)) |>
  ungroup() |>
  count(faction_1,faction_2), by = c("faction_1","faction_2") ) %>%
  filter( !(is.na(n) & faction_2 != faction_1) ) |>
  mutate(n = replace_na(n, 0)) |>
  ggplot(aes(faction_1, faction_2, fill=n)) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "steelblue") +
  geom_text(aes(label=n)) +
  theme_void(base_size = 12) +
  labs(x = "", y = "") +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) +
  theme(
        legend.position = "none",
        axis.text.x = element_text(size = 10 * 0.8, angle = 0, hjust = 0.25, colour = "black"),
        axis.text.y = element_text(size = 10 * 0.8, angle = 0, hjust = 0, colour = "black"),
        axis.ticks = element_blank()
        )
```
:::

::: {.panel}
### Table {.panel-name}

```{r print-tableFreq-gt}
Region.Freq.tbl <- Region.Freq |>
  select(region,n,freq) |>
  arrange(desc(freq)) |>
  gt() |>
  tab_header(
    title = "Region Play Rate",
    subtitle = "Relative Frequencies by Inclusion Rate of a Region"
  ) %>%
  fmt_percent(
    columns = c(3),
    decimals = 2
  ) %>%
  cols_align(
    align = "left",
    columns = 1
  ) %>%
  cols_align(
    align = "center",
    columns = c(2:3)
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = 1,
    )
  ) %>%
  cols_label(
    region   = md("**Region**"),
    n        = md("**N**"),
    freq     = md("**Freq**")
  ) %>%
   tab_options(
    table.background.color = "transparent",
    table.font.color = "black",
    table.font.color.light = "black"
   )

Region.Freq.tbl

# Region.Freq.tbl <- gtsave(
#     "images/reg_freq.png",
# )
```
:::
:::::
:::

```{r twitter-meta, echo = FALSE}
# library(metathis)
metathis::meta() |>
  metathis::meta_description(
    "Mastering Runeterra - EU edition #04 - 2021-10-02"
  ) |> 
  metathis::meta_viewport() |> 
  metathis::meta_social(
    title = "THE SNEAKY TOURNAMENT REPORT (n°1)",
    url = "https://www.llorr-stats.com",
    image = "images/MREU04.png",
    image_alt = "MREU04-LMI.png",
    og_type = "website",
    og_author = "Legna",
    twitter_card_type = "summary",
    twitter_creator = "@Maou_Legna"
  )
```

# Legal bla bla {.unnumbered}

This content was created under Riot Games' "Legal Jibber Jabber" policy using assets owned by Riot Games. Riot Games does not endorse or sponsor this project.
