---
title: "THE META REPORT NAME IS TOO LONG, TOO DAMN LONG (n°16)"
description: |
  First week of patch 2.12 / Ruination Event.
base_url: https://llorr-stats.netlify.app
preview: "https://static.wikia.nocookie.net/leagueoflegends/images/d/df/03NX007T1_Sentinel-full.png"
author:
  - name: Valentino (Legna) Vazzoler
date: 07-21-2021
output:
 distill::distill_article:
    toc: true
    toc_float: true
    toc_depth: 3
    self_contained: false
citation: false
draft: false
twitter:
  site: "@Maou_Legna"
  creator: "@Maou_Legna"
params:
  prev:  "2021-07-07 21:00:00" #UTC tz / 'previous' week start
  start: "2021-07-14 21:00:00" #UTC tz / 'current' week start
  end:   "2021-07-21 21:00:00" #UTC tz / 'current' week end
  skip:  1888233  # Patch 2.11 - after removing a few games
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE,
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  comment = NA,
  R.options = list(width = 140,
                   digits.secs=6),
  dev.args = list(bg = 'transparent'), # make graphics with transparent background
  fig.align = 'center',
  fig.width=9,
  fig.height=6,
  engine.path = list(
    python = 'C:/anaconda/'   # -> use_python("C:/anaconda/")
  ),
  #'distill options
  layout="l-body-outset",
  preview=FALSE
)

#' R Option
source(file.path("C:","LlorR","scripts","lor_main.R" ))

# require(Hmisc)    # provides knitrSet and other functions
xaringanExtra::use_panelset()
#' Python
py_run_string("print('Hello World')")
lor_deckcodes <- import("lor_deckcodes")
py_module_available("lor_deckcodes")
```

```{r panelset-style}
xaringanExtra::style_panelset_tabs(font_family = "Roboto",
                                   active_foreground = "white",
                                   hover_foreground = "black",
                                   hover_border_color = "black",
                                   active_background = "#007fff"
                                   )
```

```{r raw-data}
#' load gameDT
#'############
file.DT <- file.path("C:","LlorR","data","raw","LoR_MatchDT.csv")
header        <- fread(file.DT, header = FALSE, na.strings = c("",NA), nrows = 1, stringsAsFactors = FALSE)
LoR.Match.RMD <- fread(file.DT, header = FALSE, na.strings = c("",NA), skip = params$skip )
colnames(LoR.Match.RMD) <- unlist(header,use.names = F)

#' load Account
#'#############
file.Account <- file.path("C:","LlorR","data","raw","LoR_ACCOUNT.csv")
LoR.Account.RMD <- fread(file.Account, header=T, na.strings = c("",NA), encoding = 'UTF-8') %>%
  mutate( RiotID = paste(gameName,tagLine),refID = puuid_4 ) %>%
  pivot_longer(
  cols = c("puuid_1","puuid_2","puuid_3","puuid_4"),
  names_to = "origin",
  values_to = "puuid"
)

#' load DeckDT
#'############
LoR.Deck        <- fread(file.path("C:","LlorR","data","raw","LoR_DECK.csv"),na.strings = c("",NA))
```

# Data {.unnumbered}

```{r account-info}
masterEU   <- LoR.Account.RMD %>% filter(activeShard=="europe"   & master=="master") %>% count()/4
masterNA   <- LoR.Account.RMD %>% filter(activeShard=="americas" & master=="master") %>% count()/4
masterASIA <- LoR.Account.RMD %>% filter(activeShard=="asia"     & master=="master") %>% count()/4

namesList.EU.RMD     <- fread(file.path("C:","LlorR","data","raw","LoR_LADDER_EU.csv"))$name
namesList.NA.RMD     <- fread(file.path("C:","LlorR","data","raw","LoR_LADDER_NA.csv"))$name
namesList.ASIA.RMD   <- fread(file.path("C:","LlorR","data","raw","LoR_LADDER_ASIA.csv"))$name
```

```{r nGames-data}
minrow_live <- min(which(LoR.Match.RMD[,game_start_time_utc >= as.POSIXct(params$start)]))
maxrow_live <- max(which(LoR.Match.RMD[,game_start_time_utc  < as.POSIXct(params$end)]  ))
max_time <- LoR.Match.RMD %>%
  filter( game_start_time_utc >= as.POSIXct(params$start, tz = "UTC") & game_start_time_utc < as.POSIXct(params$end, tz = "UTC") & game_type=="Ranked") %>%
  slice_max(game_start_time_utc) %>% 
  pull(game_start_time_utc) 
```

```{r process-weeekly-data-info}
nGames_live <- LoR.Match.RMD %>% 
  slice(minrow_live:maxrow_live) %>%
  mutate( game_type = case_when(
    status==404   ~ "Friendly",
    is.na(status) ~ "to Scrap",
    TRUE ~ as.character(game_type)
    )) %>%
  mutate( game_type = fct_other(factor(game_type),keep = c("Ranked","Friendly","to Scrap")) %>% fct_infreq() ) %>%
  filter( status==404 | is.na(status) | (game_start_time_utc >= as.POSIXct(params$start, tz = "UTC") & game_start_time_utc < as.POSIXct(params$end, tz = "UTC") & str_detect(game_version, '2_12') ) ) %>% 
  tabyl(game_type)

nGames <- nGames_live[nGames_live$game_type=="Ranked","n"]
```

Number of (Ranked) games analyzed: **`r nGames %>% format(.,scientific = F)`**

```{r table-nGames-data, layout="l-body"}
nGames_tbl <- nGames_live %>%
  rename_all(
      funs(
        stringr::str_to_title(.) %>%
        stringr::str_replace_all(., '\\.', '_')
      )
  ) %>%
  rename( "Status"="Game_type" ) %>%
  gt() %>%
  tab_header(
    title = "by the Numbers",
    subtitle = "Patch 2.12 first week / Master players"
    # subtitle = glue::glue("Data for games in {params$start}")
  ) %>%
  tab_footnote(
    footnote = md(glue::glue("Max datetime recovered: {max_time} UTC from {params$start} to {params$end} UTC" )),
    locations = cells_title(groups = c("subtitle"))
    )%>%
  tab_footnote(
    footnote = md(glue::glue("Metadata from Friendly Matches (that aren't Bo3) is not recoverable, \n the value may not be perfect since I lack the starting time of the game. The amount of Games to still scrap is also an estimation based on the 'position' of the game" )),
    locations = cells_body(columns = Status,
                           rows = c(3,4))
    ) %>%
  fmt_percent(
    columns = 3,
    decimals = 2
  ) %>%
  tab_footnote(
    footnote = md(glue::glue("EU Master players in the ladder: {NROW(namesList.EU.RMD)} while number of possible Master players recovered is: {masterEU} \n
                              NA Master players in the ladder: {NROW(namesList.NA.RMD)} while number of possible Master players recovered is: {masterNA} \n
                              ASIA Master players in the ladder: {NROW(namesList.ASIA.RMD)} while number of possible Master players recovered is: {masterASIA}" )),
    locations = cells_title(groups = c("subtitle"))
  ) %>%
  summary_rows(
    columns = c(N),
    fns = list(Total = ~sum(.)),
    missing_text = "---",
    formatter = fmt_markdown
  ) %>%
  summary_rows(
    columns = c(Percent),
    fns = list(Total = ~sum(.)),
    missing_text = "Match Id recovered",
    formatter = fmt_percent
  ) %>%
   tab_options(
    table.background.color = "transparent",
    table.font.color = "black",
    table.font.color.light = "black"
   )

nGames_tbl

# gtsave(nGames_tbl,
#     "images/rep_data.png"
# )
```

```{r prepare-data}
LoR.Melt.Matches.RMD <- LoR.Match.RMD %>%
  #' Base filters
  filter( game_type=="Ranked" ) %>%
  filter( str_detect(game_version, '2_12') ) %>%
  filter( game_start_time_utc >= as.POSIXct(params$start, tz = "UTC") & game_start_time_utc < as.POSIXct(params$end, tz = "UTC") ) %>%
  #' 'process' data
  left_join(.,LoR.Deck[,.(deck_code,archetype)] %>% setnames(old = "archetype", new = "player_1")   ,by=c("deck_code_1"="deck_code")) %>%
  left_join(.,LoR.Deck[,.(deck_code,archetype)] %>% setnames(old = "archetype", new = "opponent_1") ,by=c("deck_code_2"="deck_code")) %>%
  mutate( player_2 = opponent_1, opponent_2 = player_1, oppoppuid_1 = puuid_2, oppoppuid_2 = puuid_1 ) %>%
  select( match_key,server,game_start_time_utc,game_version,total_turn_count,
          ends_with("_1"),ends_with("_2"),-ends_with("_3"),-ends_with("_4"),-contains("deck_id"),-contains("participants") ) %>%
  #' melt data
  melt(id.vars=c("match_key","server","game_start_time_utc","game_version","total_turn_count"), measure.vars=patterns(
    str_sub(
      names(select(.,ends_with("_1")))
      ,end = -3)
  ),
  value.name = str_sub(
    names(select(.,ends_with("_1")))
    ,end = -3)
  ) %>%
  #' finish 'process' data
  left_join(. , LoR.Account.RMD[,c("puuid","RiotID","refID")] %>% setnames(old = "RiotID", new = "userID")     ,by=c("puuid"="puuid")) %>%
  left_join(. , LoR.Account.RMD[,c("puuid","RiotID")] %>% setnames(old = "RiotID", new = "opponentID") ,by=c("oppoppuid"="puuid")) %>%
  left_join(.,LoR.Deck %>% select(!archetype),by=c("deck_code","factions")) %>%
  select(-ends_with("puuid"),-refID)

nGames <- NROW(LoR.Melt.Matches.RMD)/2
```

```{r prepare-old-data}
LoR.Old.Matches.RMD <- LoR.Match.RMD %>%
  #' Base filters
  filter( game_type=="Ranked" ) %>%
  filter( game_start_time_utc >= as.POSIXct(params$prev, tz = "UTC") & game_start_time_utc < as.POSIXct(params$start, tz = "UTC") ) %>%
  #' 'process' data
  left_join(.,LoR.Deck[,.(deck_code,archetype)] %>% setnames(old = "archetype", new = "player_1")   ,by=c("deck_code_1"="deck_code")) %>%
  left_join(.,LoR.Deck[,.(deck_code,archetype)] %>% setnames(old = "archetype", new = "opponent_1") ,by=c("deck_code_2"="deck_code")) %>%
  mutate( player_2 = opponent_1, opponent_2 = player_1, oppoppuid_1 = puuid_2, oppoppuid_2 = puuid_1 ) %>%
  select( match_key,server,game_start_time_utc,game_version,total_turn_count,
          ends_with("_1"),ends_with("_2"),-ends_with("_3"),-ends_with("_4"),-contains("deck_id"),-contains("participants") ) %>%
  #' melt data
  melt(id.vars=c("match_key","server","game_start_time_utc","game_version","total_turn_count"), measure.vars=patterns(
    str_sub(
      names(select(.,ends_with("_1")))
      ,end = -3)
  ),
  value.name = str_sub(
    names(select(.,ends_with("_1")))
    ,end = -3)
  ) %>%
  #' finish 'process' data
  left_join(. , LoR.Account.RMD[,c("puuid","RiotID","refID")] %>% setnames(old = "RiotID", new = "userID")     ,by=c("puuid"="puuid")) %>%
  left_join(. , LoR.Account.RMD[,c("puuid","RiotID")] %>% setnames(old = "RiotID", new = "opponentID") ,by=c("oppoppuid"="puuid")) %>%
  left_join(.,LoR.Deck %>% select(!archetype),by=c("deck_code","factions")) %>%
  select(-ends_with("puuid"),-refID)
```

`r kableExtra::text_spec("Note:", color = "red")` While I'll use the site more, some may prefer the format I use in RPubs (mainly the better toc) so I'll try to also create an RPub version or provide more tools / pages for an easier search of the data.

# Regions

## Play Rate
::: l-body-outset

```{r process-tableFreq}
Region.Freq <- LoR.Melt.Matches.RMD %>%
  select(factions) %>%
  separate_rows(factions,sep=",") %>%
  tabyl(factions,show_na=F) %>%
  tibble() %>% 
  rename_all(~c("region","n","freq")) %>%
  mutate(region = fct_recode(region,!!!recodeRegLevels)) %>% 
  add_column(., icon = list.levels$iconRegion)

Region.Freq.Server <- LoR.Melt.Matches.RMD %>%
  select(server,factions) %>%
  separate_rows(factions,sep=",") %>%
  tabyl(factions,server, show_na = F) %>%
  adorn_percentages("col") %>%
  mutate(region = fct_recode(factions,!!!recodeRegLevels),.keep = "unused")

Region.Freq <- full_join(Region.Freq,Region.Freq.Server,by="region")
```

```{r process-tableFreq-old}
# Old.Region.Freq <- LoR.Old.Matches.RMD %>%
#   select(factions) %>%
#   separate_rows(factions,sep=",") %>%
#   tabyl(factions,show_na=F) %>%
#   tibble() %>%
#   rename_all(~c("region","n","freq")) %>%
#   mutate(region = fct_recode(region,!!!recodeRegLevels)) %>%
#   add_column(., icon = list.levels$iconRegion)
# 
# Old.Region.Freq.Server <- LoR.Old.Matches.RMD %>%
#   select(server,factions) %>%
#   separate_rows(factions,sep=",") %>%
#   tabyl(factions,server, show_na = F) %>%
#   adorn_percentages("col") %>%
#   mutate(region = fct_recode(factions,!!!recodeRegLevels),.keep = "unused")
# 
# Old.Region.Freq <- full_join(Old.Region.Freq,Old.Region.Freq.Server,by="region")
```
::::: {.panelset}
::: {.panel}

### Plot {.panel-name}

```{r plot-Region}
# sxLabel <- round(Region.Freq$freq*100,2) / # sxLabel <- ifelse(as.numeric(sxLabel) > 4,  sxLabel , "")
# dxLabel <- round(Region.Freq$freq*100,2) / # dxLabel <- ifelse(as.numeric(dxLabel) <= 4, dxLabel , "")
RegionByRegion <- Region.Freq %>%
  ggplot(aes(x = reorder(region, freq), y = freq)) +
  geom_bar_pattern(
    aes(
      pattern_filename = region,
    ),
    stat            = 'identity',
    pattern         = 'image',
    pattern_type    = 'none',
    fill            = list.levels$colorRegion.Balco,
    colour          = 'black',
    pattern_scale   = -2,
    pattern_filter  = 'point',
    pattern_gravity = 'east'
  ) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    title = "Regions Play Rate",
    subtitle = "number of times a region is included in a deck",
    x = "Region",
    y = "Play Rate"
    # caption = "number of times a region is included in a deck"

  ) +
  theme( plot.title    = element_text(face = "bold", size = 15),
         plot.subtitle = element_text(size = 12),
         axis.title.x  = element_text(face = "bold", size = 12),
         axis.title.y  = element_text(face = "bold", size = 12),
         axis.text.x   = element_text(size = 8)
         ) +
  annotate(geom="text", x=1, y=0.15, col="black",label = paste("n =",nGames)) +
  coord_flip() +

  scale_pattern_filename_discrete(choices = regionIcons) +
  scale_pattern_discrete(guide = guide_legend(nrow = 1)) +
  scale_fill_manual("legend", values = list.levels$colorRegion.Balco) +
  scale_y_continuous(limits = c(0, round(max(Region.Freq$freq+0.04 ),3) ),
                     breaks = seq(0,0.5,0.04),
                     expand = c(-0.001,0.02),
                     labels = scales::percent_format(accuracy = 1) ) +
  guides(fill = "none") +
  #' Adding the text of the frequencies
  geom_text(aes(label = round(Region.Freq$freq*100,2) %>% ifelse(. >= 4,  . , "")),
            hjust = 2.2, size = 5,position = position_dodge(width = 1)) +
  geom_text(aes(label = round(Region.Freq$freq*100,2) %>% ifelse(. <  4,  . , "")),
            hjust = -0.5, size = 5,position = position_dodge(width = 1))

RegionByRegion
```
:::

::: {.panel}
### Table {.panel-name}

```{r print-tableFreq-gt}
Region.Freq.tbl <- Region.Freq %>%
  select(-n,-icon) %>%
  arrange(desc(freq)) %>%
  gt( ) %>%
  tab_header(
    title = "Region Play Rate",
    subtitle = "Relative Frequencies by Inclusion Rate of a Region"
  ) %>%
  tab_spanner(
    label = "Shard",
    columns = c(americas, asia, europe)
  ) %>%
  fmt_percent(
    columns = c(2:5),
    decimals = 2
  ) %>%
  cols_align(
    align = "left",
    columns = 1
  ) %>%
  cols_align(
    align = "center",
    columns = c(2:5)
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = 1,
    )
  ) %>%
  cols_label(
    region   = md("**Region**"),
    freq     = md("**Freq**"),
    americas = md("**America**"),
    asia     = md("**Asia**"),
    europe   = md("**Europe**")
  ) %>%
   tab_options(
    table.background.color = "transparent",
    table.font.color = "black",
    table.font.color.light = "black"
   )

Region.Freq.tbl

# Region.Freq.tbl <- gtsave(
#     "images/reg_freq.png",
# )
```
:::
:::::
<!-- Close Region 1 panelset -->
:::

## Play Rate by number of Cards
::: l-body-outset

```{r process-tableFreq_byCard}
Card.Subset <- LoR.Melt.Matches.RMD %>%
  select( starts_with( "Card" ) )

Regions.Freq.byCards <- LoR.Melt.Matches.RMD %>%
  select( starts_with( "Card") ) %>% 
  map_df(.,~str_sub(.x, start=3,end=4) ) %>%
  mutate_all(~fct_recode(.,!!!recodeRegShort)) %>%
  unlist(use.names = FALSE) %>% 
  tabyl(., show_na = F) %>% 
  rename_all(~c("region","n","freq")) %>% 
  mutate(.,region := as.character(region))
  
setorderv(Regions.Freq.byCards, c("region"), c(1))

# Regions.Freq.byCards <- as.tibble(Regions.Freq.byCards)
Regions.Freq.byCards$freq <- round(Regions.Freq.byCards$freq,4)
Regions.Freq.byCards$icon <- list.levels$iconRegion

Regions.Freq.byCards.Server <- LoR.Melt.Matches.RMD %>%
  select( starts_with( "Card") ) %>% 
  map_df(.,~str_sub(.x, start=3,end=4) ) %>%
  mutate_all(~fct_recode(.,!!!recodeRegShort)) %>%
  add_column(server = LoR.Melt.Matches.RMD$server) %>%
  melt(id.var=c("server")) %>%
  select(value,server) %>%
  tabyl(value,server, show_na = F) %>%
  adorn_percentages("col") %>%
  select(c(2,3,4))  

Card.tableByRegPlot <- LoR.Melt.Matches.RMD %>%
  select( starts_with( "Card") ) %>% 
  map_df(.,~str_sub(.x, start=3,end=4) ) %>%
  mutate_all(~fct_recode(.,!!!recodeRegShort)) %>%
  add_column(server = LoR.Melt.Matches.RMD$server) %>%
  melt(id.var=c("server")) %>%
  select(value,server) %>% table() %>% prop.table(.,margin = 2) %>% as.data.table()
```

::::: {.panelset}
::: {.panel}
### Plot {.panel-name}

```{r plotRegion_byCards}
Regions.Freq.byCards$text <- format(Region.Freq$freq*100,2)

sxLabel_card <- format(Regions.Freq.byCards$freq*100,2)
dxLabel_card <- format(Regions.Freq.byCards$freq*100,2)
sxLabel_card <- ifelse(as.numeric(sxLabel_card) > 4,  sxLabel_card , "")
dxLabel_card <- ifelse(as.numeric(dxLabel_card) <= 4, dxLabel_card , "")

RegionByCards <- Regions.Freq.byCards %>%
  ggplot(aes(x = reorder(region, freq), y = freq)) +
  geom_bar_pattern(
    aes(
      pattern_filename = region,
    ),
    stat            = 'identity',
    pattern         = 'image',
    pattern_type    = 'none',
    fill            = list.levels$colorRegion.Balco,
    colour          = 'black',
    pattern_scale   = -2,
    pattern_filter  = 'point',
    pattern_gravity = 'east'
  ) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    title = "Regions Play Rate",
    subtitle = "number of times a card within a region is included in a deck",
    x = "Region",
    y = "Play Rate"
    # caption = "number of times a region is included in a deck
  ) +
  theme( plot.title    = element_text(face = "bold", size = 15),
         plot.subtitle = element_text(size = 12),
         axis.title.x  = element_text(face = "bold", size = 12),
         axis.title.y  = element_text(face = "bold", size = 12),
         axis.text.x   = element_text(size = 8)
         ) +
  annotate(geom="text", x=1, y=0.15, col="black",label = paste("n =",nGames)) +
  coord_flip() +

  scale_pattern_filename_discrete(choices = regionIcons) +
  scale_pattern_discrete(guide = guide_legend(nrow = 1)) +
  scale_fill_manual("legend", values = list.levels$colorRegion.Balco) +
  # nome of the table
  scale_y_continuous(limits = c(0, round(max(Regions.Freq.byCards$freq+0.04 ),3) ),
                     breaks = seq(0,0.5,0.04),
                     expand = c(-0.001,0.02),
                     labels = scales::percent_format(accuracy = 1) ) +
  # geom_text(aes(label=format(freq*100,2)),
  #           hjust = 2, size = 5,position = position_dodge(width = 1)) +
  geom_text(aes(label=sxLabel_card),
            hjust = 2.2, size = 5,position = position_dodge(width = 1)) +
  geom_text(aes(label=dxLabel_card),
            hjust = -0.5, size = 5,position = position_dodge(width = 1)) +
  guides(fill = "none")

RegionByCards
```
:::

::: {.panel}
### Table {.panel-name}

```{r print-tableFreq_byCard-gt}
Region.Freq.byCards.tbl <- Regions.Freq.byCards[,c("region","freq")] %>%
  cbind(.,Regions.Freq.byCards.Server) %>%
  arrange(desc(freq)) %>%
  gt( ) %>%
  tab_header(
    title = "Region Play Rate",
    subtitle = "Relative Frequencies by number of times a Card within a Region is included in a Deck"
  ) %>%
  tab_spanner(
    label = "Shard",
    columns = c(americas, asia, europe)
  ) %>%
  fmt_percent(
    columns = c(2:5),
    decimals = 2
  ) %>%
  cols_align(
    align = "left",
    columns = 1
  ) %>%
  cols_align(
    align = "center",
    columns = c(2:5)
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = 1,
    )
  ) %>%
  cols_label(
    region   = md("**Region**"),
    freq     = md("**Freq**"),
    americas = md("**America**"),
    asia     = md("**Asia**"),
    europe   = md("**Europe**")
  ) %>%
   tab_options(
    table.background.color = "transparent",
    table.font.color = "black",
    table.font.color.light = "black"
   )

Region.Freq.byCards.tbl

# Region.Freq.tbl <- gtsave(
#     "images/reg_freq.png",
# )
```
:::
:::::
<!-- Close Region 2 panelset -->
:::

# Champions Combinations

```{r process-tableChampion}
CC.tableByReg <- LoR.Melt.Matches.RMD %>%
  tabyl(player,server) %>%
  adorn_percentages("col")

CC.table <- LoR.Melt.Matches.RMD %>%
  tabyl(player) %>%
  rename_all(~c("player","n","freq")) %>%
  left_join(.,CC.tableByReg,by="player")
```

## Play Rates

In this section I provide the play rate of which combinations of champions (plus the regions) are used in a deck. The champions showed right before a game starts for example. Right now it's a simple approximation of the archetypes played in the ladder as such information is not restrictive enough.

::: l-body-outset

::::: {.panelset}
::: {.panel}
### Plot {.panel-name}

```{r plot-Champion-PR}
nrowPlot <- 20

ChampionCombo.plot <- CC.table %>%
  arrange(desc(freq)) %>%
  slice_head(.,n = 20) %>%
  ggplot(aes(x = reorder(player, freq), y = freq))  +

  geom_bar( stat = "identity",fill="steelblue" ) +
  coord_flip() +
  guides(fill = "none")  +
  theme_bw() +
  geom_text(aes(label=round(freq*100,2)),
            # face = "bold",
            hjust = -0.5, size = 4,
            # vjust=-0.25
            # position = position_dodge(width = 1)
            position = position_dodge(0.9)
            ) +

  # scale_fill_manual("legend", values = list.levels$colorRegion.Balco) +
  scale_y_continuous(limits = c(0, round(max(CC.table$freq+0.04 ),3) ),
                     breaks = seq(0,0.20,0.02),
                     expand = c(-0.001,0.02),
                     labels = scales::percent_format(accuracy = 1) ) +

  theme( plot.title = element_text(face = "bold", size = 12, hjust = 0.6),
         axis.title.x = element_text(face = "bold"),
         axis.title.y = element_text(face = "bold"),
         legend.position = "none") +

  labs(x = "Champions", y = "Play Rate",
       caption = paste0("Relative frequencies of the top ",nrowPlot," combination of champions in a deck")
       ) +
  annotate(geom="text", x=3, y=0.08, col="black",label = paste("n =",nGames,"\n"," cumulative frequence \n ",
                                                               paste0(CC.table %>% arrange(desc(freq)) %>% slice_head(.,n = 20) %>% select(freq) %>% sum() %>% round(.,4)*100 ,"%") )
           )

ChampionCombo.plot
```
:::

::: {.panel}
### Table {.panel-name}

```{r table-Champion-PR}
CC.table %>%
  arrange(desc(freq)) %>%
  # filter(nGames>100) %>%
  select(player,freq,americas,asia,europe) %>%
  datatable(., rownames = FALSE, colnames = c('Champions'='player','Play Rate'='freq','America'='americas','Asia'='asia','Europe'='europe')
            # options = list(order = list(list(3, 'desc'))
  ) %>%
  formatStyle('Play Rate', fontWeight = 'bold') %>%
  formatPercentage('Play Rate', 2) %>%
  formatPercentage('America', 2)   %>%
  formatPercentage('Asia', 2)      %>%
  formatPercentage('Europe', 2)
```
:::
:::::
<!-- Close CC lay Rate panelset -->
:::

## Day by Day

Highlisting the top10 most played decks (at the moment of the last game played).

```{r champion-freq-by-date}
m = 10

Champion.deck.daily <- (LoR.Melt.Matches.RMD %>%
  rename(.,"champions"="player") %>%
  arrange(game_start_time_utc) %>%
  select(game_start_time_utc,champions) %>%
  mutate( num_cc = factor(champions) %>% as.numeric() ))[ , cumFreq := (cumsum(num_cc)/num_cc)/.I , by=champions ] %>%
  select(!num_cc) %>%
  mutate( champions = factor(champions) %>% fct_infreq() )

fct_values <- LoR.Melt.Matches.RMD %>%
  # mutate( top5 = fct_lump(champions, n = m, w = tot, ties.method = "max") ) %>%
 mutate( top5 = fct_lump_n(player,n = m) %>% fct_infreq() ) %>%
 pull(top5) %>% levels()
```

```{r plot-date-by-date}
meta_evo <- ggplot(
   # The ggplot object has associated the data for the highlighted countries
  data = Champion.deck.daily %>% filter(champions %in% fct_values[-1]),
  aes(game_start_time_utc, cumFreq, group = champions)
  ) +
  ## Lines for the non-highlighted countries
  geom_line(
    data = Champion.deck.daily %>% filter(champions %!in% fct_values[-1]),
    color = "grey75",
    size = .6,
    alpha = .5
  ) +
  ## Lines for the highlighted countries.
  # It's important to put them after the grey lines
  # so the colored ones are on top
  geom_line(
    aes(color = champions),
    size = .9
  ) +
  # geom_text(aes(label=champions,color = champions))
  geom_text_repel(
    data = Champion.deck.daily %>% filter(champions %in% fct_values[-1]) %>% group_by(champions) %>% slice_max(game_start_time_utc,n=1),
    aes(label=str_to_upper(champions),color = champions),
    # aes(color = champions, label = champions),
    family = "Lato",
    fontface = "bold",
    size = 3,
    direction = "y",
    xlim = c(as.POSIXct(max(Champion.deck.daily$game_start_time_utc) + hours(24)), NA),
    force = 3,
    hjust = 1,
    segment.size = .7,
    segment.alpha = .5,
    segment.linetype = "dotted",
    box.padding = .4,
    segment.curvature = -0.1,
    segment.ncp = 3,
    segment.angle = 15
  ) +
  scale_x_datetime(
    # expand = c(0.02,0.01),
    date_minor_breaks = "1 day",
    limits = c(as.POSIXct(params$start, tz="UTC"), as.POSIXct(params$end, tz="UTC")+hours(24))
    # limits = c(as.POSIXct(params$start, tz="UTC"), as.POSIXct(params$end, tz="UTC"))
  )  +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0,0.20),
    breaks = seq(0,0.20,0.02),
    labels = scales::percent_format(accuracy = 1) # glue::glue("{format(seq(0, 0.20, by = 0.05), nsmall = 2)}%")
  ) +
  scale_color_manual(
    values = c(rcartocolor::carto_pal(n = 10, name = "Vivid")[1:10-1], "grey50")
  ) +
  labs(x = "Date",
       y = "Percent",
       title = "Evolution of Play Rate over time"
       # caption = glue::glue("Data from Riot API • Ranked games from Master players • ... ")
  ) +
  # tab_footnote(
  #   footnote = md(glue::glue("Max datetime recovered: {max_time} UTC from {params$start} to {params$end} UTC" )),
  #      ) + 
  theme_bw() +
  theme(
    plot.title    = element_text(face = "bold", size = 15),
    axis.title.x  = element_text(face = "bold", size = 12),
    axis.title.y  = element_text(face = "bold", size = 12),
    axis.text.x   = element_text(size = 8),
    legend.position = "none"
  )

meta_evo

```

## Win Rates

Tie games are excluded

`r kableExtra::text_spec("Update:", color = "red")` Since I'm tidying the code and site it would be better to better define some rules and one of them is the criteria I use for displaying "Meta decks" Win Rates and "Underdogs" Win Rates. Defining "Meta decks" as everything above 1% Play Rate seems fine and it's also used by other analyst. "Underdog" decks are less obvious, surely they needs to be below 1% but with with which condition to be eligible? Aside for a positive Win Rate of course. If they are "Underdog" they probably can't be too many so in the report I opted to show as "Underdog" decks the top10 decks (by Win Rate) with Play Rate in [0.1%,1%)

```{r get-muWR}
MUtbl <- LoR.Melt.Matches.RMD %>%
  
  filter(game_outcome!="tie") %>%
  select( player,opponent,game_outcome,server ) %>%
  group_by(player,opponent) %>%
  summarise( muWin   = sum(game_outcome=="win"),
             muGames = n(),
             muWR=mean(game_outcome=="win") ) %>%
  setDT()

MUtbl[, c("LCI","UCI") := binom.confint(muWin,muGames,0.95,methods="exact")[5:6] ]
MUtbl[, okCI:=(!between(0.50,LCI,UCI)) ]
MUtbl[, direction:=ifelse(muWR>0.50,"POS","NEG")  ]

MUtbl <- MUtbl %>%
  mutate( CI := glue("({percent(LCI,accuracy = 0.1)} - {percent(UCI,accuracy = 0.1)})" ) )
```

```{r process-winRate}
WR.DT <- MUtbl[, .(nWIN = sum(muWin),nGames = sum(muGames) ), by=player ]
WR.DT[ , WR:=nWIN/nGames ]
WR.DT[ , playrate:= nGames/sum(nGames) ]
```

::::: {.panelset}
::: {.panel}
### Meta Decks {.panel-name}

Win rates of the most played combination of champions. Play Rate \>= 1%

```{r print-tableWinRate}
WR.DT %>%
  arrange(desc(WR)) %>%
  # filter(nGames > 1000) %>%
  filter(playrate >= 0.01) %>%
  select(player,WR,nWIN,nGames,playrate) %>%
  datatable(., rownames = FALSE, colnames = c('Champions'='player','Win Rate'='WR','#Wins'='nWIN','#Games'='nGames','Play Rate'='playrate')) %>%
  formatPercentage('Win Rate', 1) %>%
  formatPercentage('Play Rate', 1)
```
:::

::: {.panel}
### Underdog {.panel-name}

Top Win rates of the least played combination of champions. Play rate $\in$ [0.1%,1%)[^1].

```{r print-under-tableWinRate}
WR.DT %>%
  arrange(desc(WR)) %>%
  filter(nGames >= 50 & WR >= 0.50 & playrate >= 0.001 & playrate < 0.01) %>%
  select(player,WR,nWIN,nGames,playrate) %>%
  slice_max(WR,n = 10) %>%
  datatable(., rownames = FALSE, colnames = c('Champions'='player','Win Rate'='WR','#Wins'='nWIN','#Games'='nGames','Play Rate'='playrate')
            # options = list(order = list(list(3, 'desc'))
  ) %>%
  formatPercentage('Win Rate', 1) %>%
  formatPercentage('Play Rate', 1)
```
:::
:::::
<!-- Close Win Rate panelset -->


[^1]: Min number of games 50, during the times a meta/ladder just changed.

# Match Ups

```{r get-WR-Top10}
Top10CC <- CC.table %>% arrange(desc(freq)) %>% slice_head(.,n = 10) %>% select(player) %>% pull() %>% sort()

WRTop10 <- MUtbl[ player %in% Top10CC & opponent %in% Top10CC, ]
WRTop10 <- setorderv(WRTop10, c("player","opponent"), c(1,1))
```

::: l-body-outset
::::: {.panelset}
::: {.panel}
## Match-up Grid {.panel-name}

Just a different way to print the table of the MU grid, more an experimentation

```{r prepare-flex}
require(flextable)
require(officer)

big_border   = fp_border(color="darkgray", width = 2)
small_border = fp_border(color="gray", width = 1)

dummy_fun <- function(x){
  ifelse( !is.na(x),sprintf( "%.0f%%", x*100 ),NA )
}
```

```{r prepare-flex-grid}
grid <- matrix(WRTop10$muWR, nrow = 10, ncol = 10, byrow = T)
diag(grid) <- NA

colnames(grid) <- Top10CC
colourer <- col_numeric(
  palette = c("#D73027", # red
          # "#f9ccac", # red/orange
          "white",
          # "#e3eaa7", # green
          "#1A9850" # darker green
          ),
  domain = c(0, 1))

funs <- setNames(rep(list(dummy_fun), 10), Top10CC)
```

```{r print-flex}
ft <- grid %>% 
  as_tibble() %>%
  # mutate(across(everything(),~scales::percent(.x, accuracy = 0.1 ))) %>%
  add_column(.,Top10CC,.before = Top10CC[1]) %>%
  rename("MatchUps"="Top10CC") %>%
  flextable::flextable(.) %>% 
  theme_vanilla( ) %>%
  # theme_booktabs(bold_header = TRUE) %>% 
  flextable::align(.,align = "center", part = "all") %>%
  flextable::bg(.,
    bg = colourer,
    j = ~ . -MatchUps,
    part = "body") %>% 
  border_remove(x = .) %>%
  border_outer(., part="all", border = big_border ) %>%
  border_inner_h(., part="all", border = small_border ) %>%
  border_inner_v(., part="all", border = small_border ) %>%
  set_formatter(values = funs) %>%
  fontsize(., size = 8, part = "header") %>%
  fontsize(., j=1, size = 8) %>%
  bg(., part = "header", bg = "white"  ) %>%
  bg(., j = 1, bg = "white"  ) %>%
  autofit() 

ft
```
:::

::: {.panel}
## Match-up Grid v2 {.panel-name}

The win rates on the grid are among the 10 most played champion combination.

```{r tablesGrid}
grid <- matrix(WRTop10$muWR, nrow = 10, ncol = 10, byrow = T)
diag(grid) <- NA

# unique(WRTop10$opponent) == sort(Top10CC)

grid <- data.frame(grid)
```

```{r print-huxGrid, layout="l-body"}
brks <- c(0.4, 0.5, 0.5000001,0.6)
# clrs <- round(seq(255, 40, length.out = length(brks) + 1), 0) %>%
#   {paste0("rgb(255,", ., ",", ., ")")}

clrs = c( "#eca1a6", # red
          "#f9ccac", # red/orange
          "#ffe599", # orange (50)
          "#e3eaa7", # green
          "#b5e7a0" # darker green
          )

datatable(grid,
           colnames = Top10CC,
           rownames = Top10CC,
           options = list(
            columnDefs = list(list(className = 'dt-center', targets = "_all")),
            dom = 't', ordering=F,
            headerCallback = DT::JS("function(thead) {","  $(thead).css('font-size', '8pt');","}" )

            )
          ) %>%
  formatStyle(names(grid), backgroundColor = styleInterval(brks,clrs )) %>%
  formatPercentage(names(grid), 1) %>%
  formatStyle(names(grid), fontWeight = 'bold') %>%
  formatStyle(0, fontWeight = 'bold', fontSize = "8pt")
```
:::
:::::
<!-- Close MU panelset -->
:::

## Match-up Table

Filtered cases with less than 100 games

```{r print-tableGrid, layout="l-body-outset"}
MUtbl %>%
  filter(muGames>100) %>%
  mutate( player = factor(player) ) %>%
  mutate( opponent = factor(opponent) ) %>%
  # arrange(desc(games)) %>%
  select(player,opponent,muWR,muWin,muGames,CI) %>%
  datatable(., rownames = FALSE, colnames = c('Player'='player','Opponent'='opponent','Win Rate'='muWR','#Wins'='muWin','#Games'='muGames'),
            options = list(search = list(regex = TRUE, caseInsensitive = FALSE)),
            filter = list(position = 'top', clear = FALSE)
  ) %>%
  formatPercentage('Win Rate', 1)
```



# Deck Structure of the week {.tabset .tabset-fade .tabset-pills}

Akshan? Viego? Akshan Lee? Those are all boring choices and don't need any help to add more spice to the meta. This week I wasn't sure what to choose but then I saw a strange combination with "Sivir / Twisted Fate" so I guess this is what I'll highlist.


::::: {.panelset}
::: {.panel}
## Sivir / Twisted Fate

`r kableExtra::text_spec("Update:", color = "red")` Modified the color to be more uniform with the rest of the report and site.

```{r deck-structure}
SubDeck_deck_code <- LoR.Melt.Matches.RMD %>%
  filter( player == "Sivir / Twisted Fate" ) %>%
  pull(deck_code)

brks <- c(0.50,0.55,0.60,0.65,0.70,0.75,0.80,0.85,0.90,0.95)
clrs = colorRampPalette( c("white","steelblue") )(length(brks)+1)

get_deck_structure(SubDeck_deck_code) %>%
    datatable(.,
              colnames = c("Card","Play Rate","3","2","1"),
              options = list(
                columnDefs = list(list(className = 'dt-center', targets = "_all")),
                # dom = 't',
                headerCallback = DT::JS("function(thead) {","  $(thead).css('font-size', '8pt');","}" )
              )) %>%
    formatStyle(c("playrate","3","2","1"), backgroundColor = styleInterval(brks,clrs )) %>%
    formatPercentage(c("playrate","3","2","1"), 1) %>%
    formatStyle(1, fontWeight = 'bold', fontSize = "10pt") %>%
    formatStyle(0, fontWeight = 'bold', fontSize = "10pt")
```

> How to read the table: <br> - Play rate: How often a card is included in this class of decks / the table is order by this column. <br> - 3/2/1 is the relative and absolute frequency of the number of copies in the decks that plays them <br> - Frequencies from 50% to 100% are colored from shades of green to white to identify more easily the highest values

:::
:::::
<!-- Close Deck Structure panelset -->

# What's the deal with Akshan/Lee?

When discussing about the performance about Akshan / Lee Sin decks a player told me that even in Master there's a difference in performance from top players compared to the others so I decided to take a little look at the data.

```{r print-table-akLee}
rbind(
(LoR.Melt.Matches.RMD %>%
  filter( game_outcome != "tie" & !is.na(userID) ) %>%
  filter( player == "Akshan / Lee Sin") %>%
  #' only top32
  filter( userID %in% 
            c(
(LoR.Account.RMD %>% filter(activeShard=="europe" & master=="master" & gameName   %in% namesList.EU.RMD[1:100]) %>%  pull(RiotID) %>% unique()),
(LoR.Account.RMD %>% filter(activeShard=="americas" & master=="master" & gameName %in% namesList.NA.RMD[1:100]) %>%  pull(RiotID) %>% unique())
)) %>% mutate(userID = "Top100_Master") %>% select(userID,game_outcome)),

(LoR.Melt.Matches.RMD %>%
  filter( game_outcome != "tie" & !is.na(userID) ) %>%
  filter( player == "Akshan / Lee Sin") %>%
  #' only top32
  filter( userID %in% 
            c(
(LoR.Account.RMD %>% filter(activeShard=="europe" & master=="master" & gameName   %in% namesList.EU.RMD[101:length(namesList.EU.RMD)] ) %>%  pull(RiotID) %>% unique()),
(LoR.Account.RMD %>% filter(activeShard=="americas" & master=="master" & gameName %in% namesList.EU.RMD[101:length(namesList.EU.RMD)] ) %>%  pull(RiotID) %>% unique())
)) %>% mutate(userID = "notTop100_Master") %>% select(userID,game_outcome))
) %>%
  gtsummary::tbl_summary(.,by = userID) %>%
  gtsummary::add_n()
```

At a first look it seems that there's indeed a difference and the top100 players are indeed better. But why? I opted to look at their "mastery" with the deck

```{r}
require(hrbrthemes)
AkLeeWR <- WR.DT[ player == "Akshan / Lee Sin", WR ]

LoR.Melt.Matches.RMD %>%
  filter( game_outcome != "tie" & !is.na(userID) ) %>%
  filter( player == "Akshan / Lee Sin") %>%
  #' only top32
  filter( userID %in% 
            c(
(LoR.Account.RMD %>% filter(activeShard=="europe" & master=="master" & gameName   %in% namesList.EU.RMD[1:100]) %>%  pull(RiotID) %>% unique()),
(LoR.Account.RMD %>% filter(activeShard=="americas" & master=="master" & gameName %in% namesList.NA.RMD[1:100]) %>%  pull(RiotID) %>% unique())
)
          ) %>%
  select( userID,game_start_time_utc,game_outcome) %>%
  arrange(userID,game_start_time_utc) %>%
  mutate( game_outcome = (factor(game_outcome) %>% as.numeric()-1) ) %>%
  group_by(userID) %>%
  mutate( nGames = row_number() ) %>%
  arrange(userID,game_start_time_utc) %>%
  mutate( nWin = cumsum(game_outcome)) %>%
  ungroup() %>%
  mutate( meanWR = nWin/nGames ) %>%
  group_by(userID) %>%
  slice_max(nGames) %>%
  ungroup() %>%
  # group_by( nGames ) %>%
  # # mutate( nWin = sum(nWin), totPlayer=n(), meanWR = nWin/(totPlayer*nGames) ) %>% distinct(nGames,meanWR) %>% 
  # summarise(meanWR = mean(meanWR), .groups = "drop") %>%
  ggplot(aes(x = nGames, y = meanWR)) +
  geom_point() +
  geom_smooth(method = "loess", formula = 'y ~ x + x^2') +
  geom_hline(yintercept = AkLeeWR, color="red") +
  # geom_segment(aes( x=200, y=0.82,xend=200,yend=0.52 ),arrow = arrow( length = unit(0.03,"npc") ) ) +
  # geom_label(aes(x=200,y=0.82,alpha="semitransparent"),label="Mean Win Rate \n of (Akshan/Lee) \n in patch \n 2.12",size=2.5,fill="#FDCE2A" ) +
  labs(x="Total Games", y="Win Rate",subtitle = "Top100 Master EU/NA",caption = "loess fit") +
  theme_ipsum_rc(axis_title_face = "bold",plot_title_face = "bold",plot_title_size = 12,subtitle_size = 10,axis_text_size = 5) +
  theme( legend.position = "none" ) +
  ylim(0, 1 ) +
  xlim(0,150) +

LoR.Melt.Matches.RMD %>%
  filter( game_outcome != "tie" & !is.na(userID) ) %>%
  filter( player == "Akshan / Lee Sin") %>%
  #' only top32
  filter( userID %in% 
            c(
(LoR.Account.RMD %>% filter(activeShard=="europe" & master=="master" & gameName   %in% namesList.EU.RMD[101:length(namesList.EU.RMD)] ) %>%  pull(RiotID) %>% unique()),
(LoR.Account.RMD %>% filter(activeShard=="americas" & master=="master" & gameName %in% namesList.EU.RMD[101:length(namesList.EU.RMD)] ) %>%  pull(RiotID) %>% unique())
)
          ) %>%
  select( userID,game_start_time_utc,game_outcome) %>%
  arrange(userID,game_start_time_utc) %>%
  mutate( game_outcome = (factor(game_outcome) %>% as.numeric()-1) ) %>%
  group_by(userID) %>%
  mutate( nGames = row_number() ) %>%
  arrange(userID,game_start_time_utc) %>%
  mutate( nWin = cumsum(game_outcome)) %>%
  ungroup() %>%
  mutate( meanWR = nWin/nGames ) %>%
  group_by(userID) %>%
  slice_max(nGames) %>%
  ungroup() %>%
  # group_by( nGames ) %>%
  # # mutate( nWin = sum(nWin), totPlayer=n(), meanWR = nWin/(totPlayer*nGames) ) %>% distinct(nGames,meanWR) %>% 
  # summarise(meanWR = mean(meanWR), .groups = "drop") %>%
  ggplot(aes(x = nGames, y = meanWR)) +
  geom_point() +
  geom_smooth(method = "loess", formula = 'y ~ x + x^2') +
  geom_hline(yintercept = AkLeeWR, color="red") +
  geom_segment(aes( x=100, y=0.82,xend=100,yend=0.52 ),arrow = arrow( length = unit(0.03,"npc") ) ) +
  geom_label(aes(x=100,y=0.82,alpha="semitransparent"),label="Mean Win Rate \n of (Akshan/Lee) \n in patch \n 2.12",size=2.5,fill="#FDCE2A" ) +
  labs(x="Total Games", y="Win Rate",subtitle = "Master rank [101,N] Master EU/NA",caption = "loess fit") +
  theme_ipsum_rc(axis_title_face = "bold",plot_title_face = "bold",plot_title_size = 12,subtitle_size = 10,axis_text_size = 5) +
  theme( legend.position = "none" ) +
  ylim(0, 1 ) +
  xlim(0,150) +  

plot_annotation(title = 'Akshan Lee Mastery Curve')    
```

From here it seems that "one of" the reasons why there's a difference is also because of the dedication to play the deck that rewards dedication. How much is probably overestimated for the top100 and underestimated because of the few points for the other Masters players.

The conclusion? Well, I guess it can differ for different point of views. Indeed maybe Akshan/Lee is not as bad as it looks at first glance but one may also ask if it's worth the time since it's performance on the ladder is still mediocre but if it's done while aiming at tournaments again it's another context. You (players) decide.

# LoR-Meta Index (LMI)

> The LMI [^2] is an Index I developed to measure the performance of decks in the metagame. For those who are familiar with basic statistical concept I wrote a document to explain the theory behind it: , it's very similar to [vicioussyndicate](https://www.vicioussyndicate.com) (vS) Meta Score from their data reaper report. The score of each deck ***is not*** just their "strength", it takes in consideration both play rates and win rates that's why I prefer to say it measure the "performance". The values range from 0 to 100 and the higher the value, the higher is the performance.

[^2]: [LMI - Early Theory](https://llorr-stats.netlify.app/analysis/lmi/)

```{r data-aggregation}
DT.Aggreation <- WR.DT %>%
  filter( nGames > 200 ) %>%
  # filter( playrate > 0.01 ) %>%
  mutate( freq_ind    = scale_quantile(playrate) ) %>%
  mutate( wr_ind      = scale_quantile(WR) ) %>%
  mutate( hmeta_ind   = apply(WR.DT[,.(freq_ind,wr_ind)],  1,function(x) harm.mean(x) ) )
```

```{r ggplotly-LMI,echo=FALSE}
textWRPR <- function(Deck,WR, playrate){
  glue("Deck: {Deck}\nWin Rate: {scales::percent(WR,accuracy = 0.1)}\nPlay Rate: {scales::percent(playrate,accuracy = 0.1)}")
}

f <- list(
  family = "Courier New, monospace",
  size = 18,
  color = "#7f7f7f"
)

fig <- DT.Aggreation %>%
  select(player,WR,playrate,wr_ind,freq_ind,hmeta_ind) %>%
  mutate_if(is.numeric, funs(round(., 4)) ) %>%
  mutate( tooltip = textWRPR(player,WR,playrate) ) %>%
  rename("Deck"="player","Win_Rate"="WR","Play_Rate"="playrate","WR Index"="wr_ind","Freq Index"="freq_ind","LMI"="hmeta_ind") %>%
  plot_ly(
    type = 'scatter',
    mode = 'markers',
    x = ~`WR Index`,
    y = ~`Freq Index`,
    marker = list(size = ~LMI*100, sizeref = 0.1, sizemode = 'area'),
    color = ~LMI,
    text = ~tooltip,
    hovertemplate = paste(
      "LMI:<b>%{marker.size:,}<br>",
      "<b>%{text}</b><br><extra></extra>",sep = ""
      # "%{yaxis.title.text}: %{y:$,.0f}<br>",
      # "%{xaxis.title.text}: %{x:.0%}<br>",
      # "Number Employed: %{marker.size:,}",
      # "<extra></extra>"
      )
    ) %>% layout(xaxis = list(title = "WR Index",titlefont = f),
                 yaxis = list(title = "Freq Index",titlefont = f),
                 title = 'LoR-Meta Index (LMI)'
                 ) %>% suppressWarnings()

fig
```


# Cards Presence

```{r process-UniqueCards}
allCards            <- unlist(apply(Card.Subset, 1, unique),use.names = F)
TableAllCards       <- table(allCards)
RegionShortAllCards <- str_sub(names(TableAllCards),3,4)
TableCardsDT        <- data.table(TableAllCards)
setnames(TableCardsDT,old = "allCards",new = "card")

TableCardsDT[ ,region    := str_sub(card,3,4) ]
TableCardsDT[ ,regionID  := fct_recode(region,!!!recodeRegPosition) ]
TableCardsDT[ ,nGamesReg := Region.Freq$n[as.numeric(as.character(regionID))] ]
# Region.Freq contain the frequencies of appearence of each region in the decks
TableCardsDT[ ,p.byReg   := round(N/nGamesReg,3) ]
# Frequence of a card appearing in a deck within its own region

TableCardsDT[ ,card    :=fct_recode(card,   !!!recodeCardsCode)]
TableCardsDT[ ,region  :=fct_recode(region, !!!recodeRegShort)]
```
::::: {.panelset}
::: {.panel}
## Play Rate {.panel-name}

`r kableExtra::text_spec("Twin Disciplines is closing in against Sharpsight! Will be able to see a new top auto-include?", color = "red")`

```{r print-CardsTable-1}
MostPlayed <- TableCardsDT %>%
  arrange(desc(p.byReg)) %>%
  setNames(., c("Card","# Decks with that card ","Region","RegionID","Games of X Region","Play Rate")) %>%
  select(c(1,3,6,2)) %>%
  datatable(., rownames = FALSE) %>%
  formatStyle('Card', fontWeight = 'bold') %>%
  formatStyle('Play Rate', fontWeight = 'bold') %>%
  formatStyle('Play Rate', fontWeight = 'bold') %>% formatStyle(
    'Region',
    target = 'row',
    backgroundColor = styleEqual(list.levels$factions.clean, list.levels$colorRegion.Balco)
  ) %>%
  formatPercentage('Play Rate', 1)
  # formatStyle('Card',  color = 'red', backgroundColor = 'orange', fontWeight = 'bold')

MostPlayed
```
:::

::: {.panel}
## Top 3 Play Rates by Region {.panel-name}

```{r print-CardsTable-3}
TopPlayed.PbyReg <- TableCardsDT %>%
  group_by(region) %>%
  arrange(desc(p.byReg)) %>%
  top_n(3) %>%
  arrange(region) %>%
  setNames(., c("Card","N","Region","RegionID","Games of X Region","Play Rate")) %>%
  select(c(1,3,6,2,5)) %>%
  datatable( ., rownames = FALSE, options = list(
    searching = FALSE,
    lengthChange = FALSE,
    pageLength = 4*9,
    info = FALSE)) %>%
  formatStyle('Card', fontWeight = 'bold') %>%
  formatStyle('Play Rate', fontWeight = 'bold') %>%
  formatStyle('Play Rate', fontWeight = 'bold') %>% formatStyle(
    'Region',
    target = 'row',
    backgroundColor = styleEqual(list.levels$factions.clean, list.levels$colorRegion.Balco)
  ) %>%
  formatPercentage('Play Rate', 1)

TopPlayed.PbyReg
```
:::

::: {.panel}
## Forgotten Cards {.panel-name}

Cards that couldn't find place even in a meme deck.

```{r missingCards, results='asis'}
missingCards <- unname(recodeCardsCode)[unname(recodeCardsCode) %!in% names(TableAllCards)]
missingCards.DT <- data.table( Card = as.character(fct_recode(missingCards,!!!recodeCardsCode)),
                               Code = missingCards,
                               Region = str_sub(missingCards,3,4)
                              )

# missingCards.DT <- setorderv(missingCards.DT, c("Region","Card"), c(1,1))

missColNames <- c("Region",list.levels$factions.clean[list.levels$regionShort %in% missingCards.DT$Region])

missingTable <- t(missingCards.DT[,c(1,3)] %>%
              group_by(Region) %>%
              mutate(n = row_number()) %>%
              spread(n, Card) %>%
              mutate(across(everything(), .fns = ~replace_na(.,""))) %>%
              mutate(Region = list.levels$factions.clean[list.levels$regionShort %in% Region]  )  
              ) %>%
              # setnames(.,list.levels$factions.clean) %>%
  kable("html", escape = F ) %>%
  # kable("html", escape = F, col.names = missColNames ) %>%
  kable_styling(bootstrap_options = c("hover"))

row.names(missingTable) <- NULL
missingTable
```
:::
:::::
<!-- Close Card Presence panelset -->

# Legal bla bla {.unnumbered}

This Meta Report was created under Riot Games' "Legal Jibber Jabber" policy using assets owned by Riot Games. Riot Games does not endorse or sponsor this project.
