---
params:
  ind: "MR064"
  patch: "Patch 3.9 - Week 2"
  title: "THE META REPORT NAME IS TOO LONG, TOO DAMN LONG (n°64)"
  description: "Featuring the new meta as special guest"
  cardlurl: "https://dd.b.pvp.net/latest/set6/en_us/img/cards/02BW028-full.png"
  start: "2022-06-22 18:00:00" #UTC tz / 'current' week start
  end:   "2022-06-29 18:00:00" #UTC tz / 'current' week end
  nGrid: 10
  nDeck_cc:  20
  nDeck_day: 12
  min_games: 50

title: | 
  `r params$title`
description: |
  `r params$patch` - `r params$description`
base_url: https://www.llorr-stats.com
preview: |
  `r params$cardlurl`
author:
  - name: Valentino (Legna) Vazzoler
date: 2022-06-29
output:
 distill::distill_article:
    toc: true
    toc_float: true
    toc_depth: 3
    self_contained: false
citation: FALSE
draft: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo       = FALSE, 
  eval       = TRUE, 
  warning    = FALSE, 
  error      = FALSE, 
  message    = FALSE, 
  comment    = NA, 
  R.options  = list(width = 140, digits.secs=6), 
  dev.args   = list(bg = 'whitesmoke'), 
  fig.align  = 'center', 
  fig.width  = 12, 
  fig.height = 8, 
  # fig.path   = "figures/prefix-"
  fig.path   = glue::glue("images/{params$ind}-"), 
  layout     = "l-page", 
  preview    = TRUE
)

#' R Option
options(scipen = 999)
source(file.path("C:", "LlorR", "scripts", "lor_main.R" ))
source(file.path("C:", "LlorR", "scripts", "functions", "lor_constants.R"))
source(file.path("C:", "LlorR", "scripts", "functions", "lor_functions.R"))
xaringanExtra::use_panelset()
```

```{r panelset-style}
xaringanExtra::style_panelset_tabs(
  font_family        = "Helvetica", 
  active_foreground  = "white", 
  hover_foreground   = "black", 
  hover_border_color = "black", 
  active_background  = "#007fff"
  )
```

```{r constant}
general_caption <- glue::glue("{params$patch}
                              Ranked games from {params$start} UTC to {params$end} UTC
                              Source: Metadata of games collected with RiotGames API
                              Last Update: {now(tzone='UTC')}")
```

```{r load-data}
# load DeckDT
LoR_Deck_RMD       <- fread(file.path("C:", "LlorR", "data", "raw", "LoR_DECK.csv"), na.strings = c("", NA), colClasses = "character")

# load Games DT
LoR_Match_DT_RMD <- list.files(path = file.path("C:", "LlorR", "data", "raw"), pattern = glue("^(.*)Match_DT_S13(.*)csv$"), full.names = T) |>
  map_dfr(data.table::fread, header = T, na.strings = c("", NA), encoding = "UTF-8") |>
  mutate(server = if_else(server %in% c("sea", "asia"), "apac", server) )

LoR_Diamond_DT_RMD <- list.files(path = file.path("C:", "LlorR", "data", "raw"), pattern = glue("^(.*)Diamond_DT_S13(.*)csv$"), full.names = T) |>
  map_dfr(data.table::fread, header = T, na.strings = c("", NA), encoding = "UTF-8") |>
  mutate(server = if_else(server %in% c("sea", "asia"), "apac", server) )

LoR_Account_RMD <- list.files(path = file.path("C:", "LlorR", "data", "raw"), pattern = glue("^(.*)ACCOUNT(.*)csv$"), full.names = T) |>
  map_dfr(data.table::fread, colClasses = "character", header = T, na.strings = c("", NA), encoding = "UTF-8") |>
  mutate(activeShard = if_else(activeShard %in% c("sea", "asia"), "apac", activeShard) ) |>
  mutate(RiotID = glue::glue("{gameName}#{tagLine}")) |>
  # to be safe
  distinct(puuid, .keep_all = T)
```

```{r deck-fix}
LoR_Deck_RMD <- update_and_save_deck(LoR_Deck_RMD,LoR_Match_DT_RMD |>
                                       bind_rows(LoR_Diamond_DT_RMD))
LoR_Deck_RMD[ !is.na(archetype_pretty), archetype:=archetype_pretty ]
```

```{r prepare-data}
LoR_Melt_Master_RMD <- LoR_Match_DT_RMD |>
  filter(game_type == "Ranked") |>
  filter(game_start_time_utc %within% interval(as.POSIXct(params$start, "UTC"), as.POSIXct(params$end, "UTC")) ) |>
  melt_match(LoR_Deck_RMD, LoR_Account_RMD)

LoR_Melt_Diamond_RMD <- LoR_Diamond_DT_RMD |>
  filter(game_type == "Ranked") |>
  filter(game_start_time_utc %within% interval(as.POSIXct(params$start, "UTC"), as.POSIXct(params$end, "UTC")) ) |>
  melt_match(LoR_Deck_RMD, LoR_Account_RMD)
```

# Data

```{r nGames-data}
nGames_master  <- LoR_Melt_Master_RMD |>
  filter(game_start_time_utc %within% interval(as.POSIXct(params$start, "UTC"), as.POSIXct(params$end, "UTC")-days(1) ) ) |>
  NROW()

nMaster   <- LoR_Account_RMD[master=="master", .N]

nGames_diamond  <- LoR_Melt_Diamond_RMD |>
  filter(game_start_time_utc %within% interval(as.POSIXct(params$start, "UTC"), as.POSIXct(params$end, "UTC")-days(1) ) ) |>
  NROW()

nDiamond  <- LoR_Account_RMD[master=="diamond", .N]
```

Number of Master Players: **`r nMaster`**

Number of HighDiamond [^1] Players: **`r nDiamond`**

[^1]: HighDiamond are defined as "players who played against Master player in a Ranked games but **are not** Master themselves"

Number of (Ranked) **Master** matches analysed **`r format(nGames_master/2, scientific = F)`** or **`r format(nGames_master, scientific = F)`** games.

Number of (Ranked) **\~HighDiamond** matches analysed **`r format(nGames_diamond/2, scientific = F)`** or **`r format(nGames_diamond, scientific = F)`** games.

Last Update: `r format(Sys.time(), format = "%Y-%m-%d %H:%M")`

::: l-page
::::: panelset
::: panel
### Games {.panel-name}

```{r table-nGames-data}
#| layout="l-body"

nGames_tbl <- table_by_the_numbers_double(LoR_Match_DT_RMD, LoR_Diamond_DT_RMD, LoR_Account_RMD)

nGames_tbl |> #
  tab_options(
    data_row.padding = px(1.2), 
    table.background.color = "whitesmoke", 
    table.font.color = "black", 
    table.font.color.light = "black"
   )

gtsave(nGames_tbl, glue::glue("images/{params$ind}-bytheNumbers.png")) |> invisible()
```
:::

::: panel
### Account {.panel-name}

```{r players-by-the-numbers}
#| layout="l-body"

nPlayers <- table_accounts(LoR_Account_RMD,"rank")
  
nPlayers

gtsave(nPlayers, glue::glue("images/{params$ind}-nPlayers.png")) |> invisible()
```

:::
:::::
:::

# Regions

## Play Rate

```{r compute-region-freq}
region_freq <- LoR_Melt_Master_RMD |>
  filter(game_start_time_utc %within% interval(as.POSIXct(params$start, "UTC"), as.POSIXct(params$end, "UTC")-days(1) ) ) |>
  freq_by_faction()

region_freq_new <- LoR_Melt_Master_RMD |>
  filter(game_start_time_utc %within% interval(as.POSIXct(params$end, "UTC")-days(1), as.POSIXct(params$end, "UTC") ) ) |>
  freq_by_faction()
```

::: l-page
::::: panelset
::: panel
### Plot {.panel-name}

```{r reg-freq-plot, fig.width=12, fig.height=8}
plot_freq(
  region_freq, 
  nGames_master, 
  subtitle = "number of times a region is included in a deck", 
  caption = general_caption
  )
```

The Gini Index is a measure of heterogeneity so, in this case and in simpler terms, how much the play rates are similar. The Index goes (when normalized like here) $\in [0, 1]$ and it's equal to 1 when there's a single value with 100% play rate or 0 when all play rates are equal. Of course a Gini Index of 1 needs to be avoided but it's not like the aim should be 0. As said, it's just to add some additional tools.
:::

::: panel
### Table {.panel-name}

```{r}
table_freq_gt(region_freq) |>
  tab_header(
    title    = "Region Play Rate", 
    subtitle = "Relative Frequencies by Inclusion Rate of a Region"
  ) |>
  tab_source_note( source_note = general_caption ) 
```
:::

::: panel
### Plot (New Patch) {.panel-name}

```{r reg-freq-plot-new, fig.width=12, fig.height=8}
region_freq_new |>
  plot_freq(
    subtitle = "number of times a region is included in a deck", 
    caption = general_caption
  )
```
:::

::: panel
### Table (New Patch) {.panel-name}

```{r}
region_freq_new |>
  table_freq_gt() |>
  tab_header(
    title    = "Region Play Rate", 
    subtitle = "Relative Frequencies by Inclusion Rate of a Region"
  ) |>
  tab_source_note( source_note = general_caption ) 
```
:::

:::::
:::

## Play Rate by number of Cards

```{r compute-region-freq-bycards}
region_freq_by_cards <- LoR_Melt_Master_RMD |>
  filter(game_start_time_utc %within% interval(as.POSIXct(params$start, "UTC"), as.POSIXct(params$end, "UTC")-days(1) ) ) |>
  freq_by_cards()

region_freq_by_cards_new <- LoR_Melt_Master_RMD |>
  filter(game_start_time_utc %within% interval(as.POSIXct(params$end, "UTC")-days(1), as.POSIXct(params$end, "UTC") ) ) |>
  freq_by_cards()
```


::: l-page
::::: panelset

::: panel
### Plot {.panel-name}

```{r reg-freq-bycards-plot, fig.width=12, fig.height=8}
plot_freq(
  region_freq_by_cards, 
  nGames_master, 
  subtitle = "number of times a card within a region is included in a deck", 
  # caption = general_caption
  caption = glue::glue("{params$patch}
                       Ranked games from {params$start} UTC to {params$end} UTC - Master Rank
                       DualRegions cards are counted based by the region that matters in the deck
                       Source: Metadata of games collected with RiotGames API
                       Last Update: {now(tzone='UTC')}")
  )
```
:::

::: panel
### Table {.panel-name}

```{r}
region_freq_by_cards |>
  table_freq_gt() |>
  tab_header(
    title    = "Region Play Rate", 
    subtitle = "Relative Frequencies by number of times a Card within a Region is included in a Deck"
  ) |>
  tab_source_note( source_note = general_caption )
```
:::

::: panel
### Plot (New Patch) {.panel-name}

```{r reg-freq-bycards-plot-new, fig.width=12, fig.height=8}
region_freq_by_cards_new |>
  plot_freq(
    subtitle = "number of times a card within a region is included in a deck", 
    # caption = general_caption
    caption = glue::glue("{params$patch}
                       Ranked games from {params$start} UTC to {params$end} UTC - Master Rank
                       DualRegions cards are counted based by the region that matters in the deck
                       Source: Metadata of games collected with RiotGames API
                       Last Update: {now(tzone='UTC')}")
  )
```
:::

::: panel
### Table (New Patch) {.panel-name}

```{r}
region_freq_by_cards_new |>
  table_freq_gt() |>
  tab_header(
    title    = "Region Play Rate", 
    subtitle = "Relative Frequencies by number of times a Card within a Region is included in a Deck"
  ) |>
  tab_source_note( source_note = general_caption )
```
:::

:::::
:::

# Champions Combinations (~Old Patch)

```{r process-tableChampion}
cc_table_master <- LoR_Melt_Master_RMD |>
  filter(game_start_time_utc %within% interval(as.POSIXct(params$start, "UTC"), as.POSIXct(params$end, "UTC")-days(1) ) ) |>
  tabyl(playerDeck, show_na = F) |>
  left_join(LoR_Melt_Master_RMD |>
              tabyl(playerDeck, server) |>
              adorn_percentages("col"), by="playerDeck") |>
  as.data.table()

cc_table_diamond <- LoR_Melt_Diamond_RMD |>
  filter(game_start_time_utc %within% interval(as.POSIXct(params$start, "UTC"), as.POSIXct(params$end, "UTC")-days(1) ) ) |>
  tabyl(playerDeck, show_na = F) |>
  left_join(LoR_Melt_Diamond_RMD |>
              tabyl(playerDeck, server) |>
              adorn_percentages("col"), by="playerDeck") |>
  as.data.table()

top_deck <- union(
  cc_table_master[ order(-percent) ][1:params$nDeck_cc, playerDeck], 
  cc_table_diamond[ order(-percent) ][1:params$nDeck_cc, playerDeck]
)

champion_combination <- tibble( playerDeck = top_deck ) |>
  left_join(cc_table_master[, c("playerDeck", "percent")], by ="playerDeck" ) |>
  left_join(cc_table_diamond[, c("playerDeck", "percent")], by ="playerDeck" ) |>
  rename_all(~c("playerDeck", "Master", "Diamond")) |>
  pivot_longer( cols = c("Master", "Diamond"), names_to = "master", values_to = "freq" )
```

## Play Rates

::: l-page
::::: panelset
::: panel
### Plot {.panel-name}

```{r champion-playrate-plot}
#| fig.width=12, 
#| fig.height=8

champion_combination |>
  mutate(
    playerDeck = factor(playerDeck), 
    playerDeck = fct_reorder(playerDeck, freq, mean, .desc = F )
  ) |>
  ggplot(aes(x = playerDeck, y = freq, group = master, fill = master))  +
  geom_bar(stat = "identity", position=position_dodge(0.5), width=.5 ) +
  coord_flip() +
  theme_bw() +
  geom_text(
    aes(label=round(freq*100, 2)), 
    size = 3, 
    face = "bold", 
    color = "grey50", 
    hjust = -0.5, size = 4, 
    position = position_dodge(0.9), 
  ) +
  scale_y_continuous(
    limits = c(0, round(max(champion_combination$freq+0.04 ), 3) ), 
    breaks = seq(0, 0.20, 0.02), 
    labels = scales::percent_format(accuracy = 1) ) +
  annotate(
    geom="text", 
    x=3, y=0.07, 
    col="black", 
    label = glue::glue("#Games (Master) = {nGames_master}
                       #Games (HighDiamond) = {nGames_diamond}
                       Cumulative Frequence (Master) = {scales::percent(cc_table_master[ order(-percent) ][1:params$nDeck_cc, sum(percent)], accuracy = 0.1)}
                       Cumulative Frequence (HighDiamond) = {scales::percent(cc_table_diamond[ order(-percent) ][1:params$nDeck_cc, sum(percent)], accuracy = 0.1)}")
  ) +
  theme_539() +
  labs(
    x = "Champions", 
    y = "Play Rate", 
    title = "Champions Combination Play Rates", 
    subtitle = glue::glue("Play-Rates of the top {params$nDeck_cc} most played combination of champions/regions"), 
    caption = glue::glue("{params$patch}
                         Ranked games from {params$start} UTC to {params$end} UTC
                         Decks are chosen from the union of top {params$nDeck_cc} from Last-Seasononal player and ~HighDiamond resulting in {length(top_deck)} displayed
                         Source: Metadata of games collected with RiotGames API
                         Last Update: {now(tzone='UTC')}")
  ) +
  theme( 
    axis.text = element_text(size = 9, face = "bold", color = "grey25", family = "Helvetica"), 
    panel.grid.major.y = element_blank(), 
    plot.title = element_text(face = "bold", size = 12, hjust = 0.6), 
    axis.title.x = element_text(face = "bold"), 
    axis.title.y = element_text(face = "bold"), 
    legend.position = "none"
  )
```
:::

::: panel
### from Master {.panel-name}

```{r table-Champion-PR}
cc_table_master |>
  rename(freq = percent) |>
  arrange(desc(freq)) |>
  # filter(nGames>100) |>
  select(playerDeck, freq, americas, apac, europe) |>
  reactable(
    bordered = TRUE, 
    highlight = TRUE, 
    striped = TRUE, 
    searchable = TRUE, 
    compact = TRUE, # compact the table height
    fullWidth = TRUE, # don't fill the page
    defaultPageSize = 20, 
    wrap = TRUE, 
    defaultColDef = colDef(
      style = list(fontFamily = "Helvetica", fontSize = "13px"), align = "center"
      # minWidth = 120, 
      ), 
    columns = list(
      playerDeck = colDef(name = "Champions", minWidth = 120, style = list(fontSize = "11px", fontWeight = "bold", color="black") ), 
      freq     = colDef(name = "Play Rate", format = colFormat(percent = TRUE, digits = 1), style = list( fontSize = "13px") ), 
      americas = colDef(name = "America", format = colFormat(percent = TRUE, digits = 1), style = list( fontSize = "13px") ), 
      apac     = colDef(name = "Apac", format = colFormat(percent = TRUE, digits = 1), style = list( fontSize = "13px") ), 
      europe   = colDef(name = "Europe", format = colFormat(percent = TRUE, digits = 1), style = list( fontSize = "13px") )
      )
    ) |>
  reactablefmtr::add_source(element_text(glue::glue("Source: Metadata of games collected with RiotGames API.
                                                    Last Update: {now(tzone='UTC')}")), background_color = "whitesmoke")
```
:::

::: panel
### from Diamond {.panel-name}

```{r}
cc_table_diamond |>
  rename(freq = percent) |>
  arrange(desc(freq)) |>
  # filter(nGames>100) |>
  select(playerDeck, freq, americas, apac, europe) |>
  reactable(
    bordered = TRUE, 
    highlight = TRUE, 
    striped = TRUE, 
    searchable = TRUE, 
    compact = TRUE, # compact the table height
    fullWidth = TRUE, # don't fill the page
    defaultPageSize = 20, 
    wrap = TRUE, 
    defaultColDef = colDef(
      style = list(fontFamily = "Helvetica", fontSize = "13px"), align = "center"
      # minWidth = 120, 
      ), 
    columns = list(
      playerDeck = colDef(name = "Champions", minWidth = 120, style = list(fontSize = "11px", fontWeight = "bold", color="black") ), 
      freq     = colDef(name = "Play Rate", format = colFormat(percent = TRUE, digits = 1), style = list( fontSize = "13px") ), 
      americas = colDef(name = "America", format = colFormat(percent = TRUE, digits = 1), style = list( fontSize = "13px") ), 
      apac     = colDef(name = "Apac", format = colFormat(percent = TRUE, digits = 1), style = list( fontSize = "13px") ), 
      europe   = colDef(name = "Europe", format = colFormat(percent = TRUE, digits = 1), style = list( fontSize = "13px") )
      )
    ) |>
  reactablefmtr::add_source(element_text(glue::glue("Source: Metadata of games collected with RiotGames API.
                                                    Last Update: {now(tzone='UTC')}")), background_color = "whitesmoke")
```
:::

:::::
:::

## Day by day

::: l-page
::::: panelset

::: panel
### Hourly/Dialy lines {.panel-name}

```{r day-by-day-playrate, fig.width=12, fig.height=8}
hourly_meta_plot_line <- LoR_Melt_Master_RMD |>
  filter(game_start_time_utc %within% interval(as.POSIXct(params$start, "UTC"), as.POSIXct(params$end, "UTC")-days(1) ) ) |>
  plot_playrate_by_time(prev_days = 6,max_top_pr = 12)

hourly_meta_plot_line
```

An "updated" version of the old format. I don't really find it useful (a bit cool, but not useful) and still most likely leave it

It display both daily aggregated data and hourly (background) data
:::

::: panel
### Stacked Playrates {.panel-name}

```{r day-by-day-stacked, fig.width=12, fig.height=8}
hourly_meta_plot <- LoR_Melt_Master_RMD |>
  plot_hourly_meta_deck(prev_days = 7,max_top_pr = 12, label_shift_hrs=18)

hourly_meta_plot
```

Each playrate is stacked upon the other with the decks with the highest overall play-rate (the written value) being at the bottom.

:::

::: panel
### Stacked Games {.panel-name}

```{r day-by-day-games, fig.width=12, fig.height=8}
hourly_meta_plot_abs <- LoR_Melt_Master_RMD |>
  plot_hourly_meta_deck(prev_days = 7,max_top_pr = 12,absolute = T, label_shift_hrs=18)

hourly_meta_plot_abs
```

The stacked plots are "more interesting" this week as they easily show the shift from the "old meta to the new one" but in term of absolute number of games being played and regarding with which decks.

:::

:::::
:::

## Win Rates

For the rest of the report only the data pre-patch will be used

```{r process-winRate}
LoR_Melt_Master_RMD <- LoR_Melt_Master_RMD |>
  filter(game_start_time_utc %within% interval(as.POSIXct(params$start, "UTC"), as.POSIXct(params$end, "UTC")-days(1) ) )

WR_tbl     <- win_rates(LoR_Melt_Master_RMD, server = F)
WR_tbl_Reg <- win_rates(LoR_Melt_Master_RMD, server = T)
```

::: l-page
::::: panelset
::: panel
### Meta Decks {.panel-name}

Win rates of the most played combination of champions. Play Rate $\geq 1\%$ in at least one of the servers.

Format changed to replicate the one used in the [Meta - page](https://www.llorr-stats.com/static/meta.html)

```{r print-tableWinRate}
reactable_report(data = LoR_Melt_Master_RMD,group = "meta")
```
:::

::: panel
### Underdog {.panel-name}

Top Win rates of the top10 best performing least played combination of champions. Play rate $\in [0.1%, 1%)$

```{r print-under-tableWinRate}
reactable_report(data = LoR_Melt_Master_RMD,group = "underdog")
```
:::
:::::
:::

# Match Ups

Regarding MU, this is not the most accurate estimation you can get from my data. If you want a better picture of the current meta it would be better to look at the dedicated MU-page where I use all "Ranked" games with the current sets of buffs and nerfs. While one may object I don't account for optimizations and differences in skills acquired during the weeks, the overall number of games / sample size makes them a better source of information. So, in case, please refer to the [MU - page](https://www.llorr-stats.com/static/mu.html) for a better "meta-investigation".

## Match-up Grid

The win rates on the grid are among the `r params$nGrid` most played champion combination.


```{r match-ups, layout="l-screen-inset shaded", fig.width=12, fig.height=10}
MU_tbl <- match_ups(LoR_Melt_Master_RMD)

grid_source_note <- md(glue::glue("MatchUp values from Ranked games of the player who attended the last Seasonal Tournament
                                  Order of the Archetypes based on the playrate.
                                  Source: Metadata of games collected with RiotGames API") )

gtMU_grid <- mu_grid(mu_data = MU_tbl, dim_grid = params$nGrid, 
                     games_data = LoR_Melt_Master_RMD, prev_days = 7, 
                     grid_source_note = grid_source_note, div_1 = 12, div_2 = 12, font_upper = 14, font_lower = 10)

gtMU_grid |>
  tab_options(
    data_row.padding = px(8), 
    table.font.size = px(13), 
    column_labels.font.size = px(10)
  ) |>
  cols_width(
    -1 ~ px(90), 
     1 ~ px(150), 
  ) 

gtsave(gtMU_grid, glue::glue("images/{params$ind}-mugrid-gt.png"), vwidth = 1500, vheight = 1000) |> invisible()
```

```{r download-grid}
downloadthis::download_file(
  path = file.path(glue("images/{params$ind}-mugrid-gt.png")), 
  output_name = glue("MatchUps Grid - {params$ind}"), 
  button_label = "Download MU grid as .png", 
  button_type = "danger", 
  has_icon = TRUE, 
  icon = "fa fa-save", 
  self_contained = FALSE
)
```

# LoR-Meta Index (LMI)

`r kableExtra::text_spec("Note:", color = "red")` Games from Master Rank only

**Tier0** with LMI $\geq$ 97.5 **Tier1** with LMI $\in [85, 97.5)$ **Tier2** with LMI $\in [60, 85)$ **Tier3-** with LMI $<$ 60

```{r LMI}
#| fig.width=12, 
#| fig.height=8

WR_tbl |>
  # filter( nGames > 200 ) |>
  slice_max( nGames, n = 50 ) |>
  # filter( playrate > 0.01 ) |>
  mutate( PR_ind    = scale_quantile(playrate) ) |>
  mutate( WR_ind    = scale_quantile(WR) ) |>
  mutate( LMI = map2_dbl(PR_ind, WR_ind, ~harm_mean(c(.x, .y))) ) |>
  mutate(tier = case_when( 
     LMI >= 0.975 ~ "Tier0", 
     0.85 <= LMI & LMI < 0.975 ~ "Tier1", 
     0.60 <= LMI & LMI < 0.85 ~ "Tier2", 
     LMI < 0.60 ~ "Tier3-"
    ) 
  ) |>
  slice_max(LMI, n = 15, with_ties = F) |>
  mutate_if(is.numeric, funs(round(., 4)) ) |>
  mutate( LMI = LMI*100 ) |>
  mutate( tooltip = glue("{playerDeck}
                         LMI {round(LMI, 1)}
                         WinRate {scales::percent(WR, accuracy = 0.1)}
                         PlayRate {scales::percent(playrate, accuracy = 0.1)}
                         #Games {nGames}") ) |>
  ggplot( aes(x=WR_ind, y=PR_ind, size = LMI, color = tier, text=tooltip)) +
  geom_point(alpha=0.6) +
  scale_size(range = c(1, 15), name="LMI") +
  scale_color_manual(breaks = c("Tier0", "Tier1", "Tier2", "Tier3-"), values=rcartocolor::carto_pal(4, "Bold") ) +
  theme_539() +
  geom_label_repel( 
    aes(label=tooltip), 
    family = "Roboto", 
    color = "grey40", 
    fontface = "bold", 
    size = 3, 
    fill = NA, 
    vjust = "outward", 
    label.padding = unit(0.8, "mm"), 
    label.size = unit(0.25, "mm"), 
    label.r = unit(0.5, "mm"), 
    min.segment.length = 0, 
    segment.linetype = 2, 
    segment.color = 'grey50'
  ) + 
  guides(colour = guide_legend(override.aes = list(size=10)), size = FALSE ) +
  theme(
    legend.position = "top", 
    legend.background = element_blank(), 
    legend.title = element_text(size=9, lineheight = 1.3), 
    legend.justification = "right") +
  labs(
    title = "Top15 Deck Peformances", 
    subtitle = "Deck's Peformances by highest value of LMI", 
    x = "Win Index", 
    y = "Freq Index", 
    caption = general_caption)
```

> The LMI [^4] [^5] is an Index I developed to measure the performance of decks in the metagame. For those who are familiar with basic statistical concept I wrote a document to explain the theory behind it: , it's very similar to [vicioussyndicate](https://www.vicioussyndicate.com) (vS) Meta Score from their data reaper report. The score of each deck ***is not*** just their "strength", it takes in consideration both play rates and win rates that's why I prefer to say it measure the "performance". The values range from 0 to 100 and the higher the value, the higher is the performance.

[^4]: [LMI - Early Theory](https://llorr-stats.com/analysis/lmi/)

[^5]: [LMI - Adding a Ban Index](https://www.llorr-stats.com/analysis/lmi-02-tentative-expansion/)

# Win Marathons Leaders

Top3 Players (or more in case of ties) from each server that had the highest amount of consecutive wins with the same archetype. The provided deckcode is the one played in the last win found.

```{r win-marathon}
#| layout="l-page"

gt_winning <- table_winning_streak(LoR_Melt_Master_RMD, LoR_Account_RMD, "master")

gt_winning |>
 tab_options(
    table.background.color = "whitesmoke", 
    column_labels.background.color = "whitesmoke", 
    table.font.color = "black", 
    table.font.color.light = "black"
   )

gtsave(gt_winning, glue::glue("images/{params$ind}-top_win.png")   ) |> invisible()
```

# Cards Presence (at Master)

```{r process-UniqueCards}
LoR_Melt_Master_RMD[ !is.na(cards_region_fix), cards:=cards_fix  ]

DeckWeight <- LoR_Melt_Master_RMD |>
  tabyl(deck_code) |>
  select(-percent) |>
  rename(ndeck = n)

LoR_Card <- LoR_Card |>
  select(name, cardCode) |>
  bind_rows(
    LoR_DualRegion |>
      select(name, cardCode = cardCode_fix )
  ) |>
  bind_rows(
    map_dfr(
      names(LoR_Runeterra_Champion), ~LoR_Runeterra_Champion |>
        pluck(.x) |>
        select(name, cardCode = cardCode_fix)
    )
  )

TableAllCards <- LoR_Melt_Master_RMD |>
  # slice(1:10) |>
  distinct(deck_code, cards) |>
  separate_rows(cards, sep = " ") |>
  group_by(deck_code) |>
  distinct(cards) |>
  ungroup() |>
  left_join(DeckWeight, by = "deck_code") |>
  group_by(cards) |>
  summarise(ncard = sum(ndeck)) |>
  ungroup() |>
  mutate(abbreviation = str_sub(cards, 3, 4) ) |>
  # I have the region playrate by the region_freq obtained earlier
  left_join(
    data_regions |>
      select(abbreviation, nameRef) |>
      left_join(
        region_freq |>
          group_by(group) |>
          summarise(n = sum(n)) |>
          select(nameRef=group,n)
      ) |>
      select(-nameRef), by = "abbreviation"
  ) |>
  rename(region = abbreviation, card = cards) |>
  mutate(p_by_reg = ncard/n, 
         card    = str_replace_all(card, set_names(LoR_Card$name, LoR_Card$cardCode)), 
         region  = str_replace_all(region, set_names(data_regions$nameRef, data_regions$abbreviation)) )
```

::: l-page
::: panelset
::: panel
## Play Rate {.panel-name}

```{r print-CardsTable-1}
MostPlayed <- TableAllCards |>
  arrange(desc(p_by_reg)) |>
  rename_with(~c("Card", 
                "#Decks with that card", 
                "Region", 
                "Games of X Region", 
                "Play Rate")) |>
  # select(c(1, 3, 6, 2)) |>
  DT::datatable(rownames = FALSE) |>
  DT::formatStyle('Card', fontWeight = 'bold') |>
  DT::formatStyle('Play Rate', fontWeight = 'bold') |>
  DT::formatStyle(
    'Region', 
    target = 'row', 
    backgroundColor = DT::styleEqual(data_regions$nameRef, data_regions$colorRegion)
  ) |>
  DT::formatPercentage('Play Rate', 1)

MostPlayed
```
:::

::: panel
## Top 3 Play Rates by Region {.panel-name}

```{r print-CardsTable-3}
TopPlayed.PbyReg <- TableAllCards |>
  group_by(region) |>
  arrange(desc(p_by_reg)) |>
  top_n(3) |>
  arrange(region) |>
  rename_with(~c("Card", "N", "Region", "Games of X Region", "Play Rate")) |>
  ungroup() |>
  DT::datatable(rownames = FALSE, 
            options = list(
              searching = FALSE, 
              pageLength = 3*10, 
              info = FALSE)
            ) |>
  DT::formatStyle('Card', fontWeight = 'bold') |>
  DT::formatStyle('Play Rate', fontWeight = 'bold') |>
  DT::formatStyle(
    'Region', 
    target = 'row', 
    backgroundColor = DT::styleEqual(data_regions$nameRef, data_regions$colorRegion)
  ) |>
  DT::formatPercentage('Play Rate', 1) |>
  suppressMessages()

TopPlayed.PbyReg
```
:::

::: panel
## Forgotten Cards {.panel-name}

Cards that couldn't find place even in a meme deck.

```{r missingCards}
LoR_Card |>
  as.data.table() |>
  filter( cardCode %in% LoR_Card$cardCode[LoR_Card$name %!in% TableAllCards$card] ) |>
  mutate( Region = str_sub(cardCode, 3, 4) ) |>
  group_by(Region) |>
  mutate(n = row_number(), 
         l = n() ) |>
  ungroup() |>
  arrange(desc(l)) |>
  select(-l, -cardCode) |>
  pivot_wider( names_from = n, values_from = name  ) |>
  mutate(across(everything(), .fns = ~replace_na(., ""))) |>
  t() |>
  as.data.table() |>
  {\(x) rename_all(x, ~unlist(x[1, ], use.names = F ) )  }() |>
  slice(-1) |>
  reactable(
    bordered = TRUE, 
    highlight = TRUE, 
    wrap = T, 
    sortable = F, 
    searchable = TRUE, 
    defaultPageSize = 10, 
    style = list(fontFamily = "Chivo", fontSize = "12px"), 
    # minRows = 10, 
    columns = list(
      BC = colDef( style = list ( background = data_regions$colorRegion[1], fontWeight = "bold", color  = "#404040" ) ), 
      BW = colDef( style = list ( background = data_regions$colorRegion[2], fontWeight = "bold", color  = "#404040" ) ), 
      DE = colDef( style = list ( background = data_regions$colorRegion[3], fontWeight = "bold", color  = "#404040" ) ), 
      FR = colDef( style = list ( background = data_regions$colorRegion[4], fontWeight = "bold", color  = "#404040" ) ), 
      IO = colDef( style = list ( background = data_regions$colorRegion[5], fontWeight = "bold", color  = "#404040" ) ), 
      MT = colDef( style = list ( background = data_regions$colorRegion[6], fontWeight = "bold", color  = "#404040" ) ), 
      NX = colDef( style = list ( background = data_regions$colorRegion[7], fontWeight = "bold", color  = "#404040" ) ), 
      PZ = colDef( style = list ( background = data_regions$colorRegion[8], fontWeight = "bold", color  = "#404040" ) ), 
      RU = colDef( style = list ( background = data_regions$colorRegion[9], fontWeight = "bold", color  = "#404040" ) ), 
      SI = colDef( style = list ( background = data_regions$colorRegion[10], fontWeight = "bold", color  = "#404040" ) ), #grey90
      SH = colDef( style = list ( background = data_regions$colorRegion[11], fontWeight = "bold", color = "#404040" ) )
    ), 
    defaultColDef = colDef( minWidth = 125 ) 
  )
```
:::
:::
:::

# Not-Standard Archetype Names

Names and rules for the "non standard archetypes" which are not defined by Champion+Regions

```{r gt-archetype}
tbl_archetype |>
  tab_options(
    table.background.color = "whitesmoke", 
    column_labels.background.color = "whitesmoke"
   )
```

# Legal bla bla

This content was created under Riot Games 'Legal Jibber Jabber' policy using assets owned by Riot Games. Riot Games does not endorse or sponsor this project.

```{r twitter-meta}
#| echo=FALSE

metathis::meta() |>
  metathis::meta_description(
    glue::glue("{params$patch} - {params$description}")
  ) |>
  metathis::meta_viewport() |>
  metathis::meta_social(
    title = params$title, 
    url = "https://www.llorr-stats.com/", 
    image = params$cardlurl, 
    og_type = "website", 
    og_author = "Legna", 
    twitter_card_type = "summary", 
    twitter_creator = "@Maou_Legna"
  )
```
