---
title: "Resources"
description: |
  Link to the tools I made
---

```{r, echo=FALSE,warning=FALSE}
suppressPackageStartupMessages({
  library(dplyr)
  library(reactable)
})
data_in <- tibble::tribble(
  ~Project, ~url, ~Description,
  "MatchUps", "https://llorr-stats.netlify.app/static/mu.html", "Match Ups data that cover the same (current) cycle of buff/nerfs.",
  "Bo3-Helper", "https://legnavv.shinyapps.io/Bo3-helper/", "Helper for Bo3. Using mostly the most played archetypes (still for 2.12/2.13)."
  "Meta Stats", "https://llorr-stats.netlify.app/static/meta.html", "Dashboard with Meta Stats for the current patch and recent days.",
  
) 
data_in %>%
  reactable::reactable(
    # searchable = TRUE,
    pagination = FALSE,
    columns = list(
      Project = colDef(
        minWidth = 150,
        cell = function(value, index) {
          url_in <- data_in$url[index]
          htmltools::a(href = url_in, value)
        }
      ),
      url = colDef(show = FALSE),
      # Type = colDef(minWidth = 115),
      Description = colDef(minWidth = 250)
    ),
    theme = reactableTheme(
      backgroundColor = "whitesmoke",
      borderColor = "#dfe2e5",
      stripedColor = "#f6f8fa",
      highlightColor = "#f0f5f9",
      cellPadding = "8px 12px",
      style = list(fontFamily = "-apple-system, Lato, sans-serif"),
    )
  )
```
Credits to <a href="https://themockup.blog/resources.html">Tom Mock</a> for showing how to fully bring out the distill package potential.

Regarding the Bo3-Helper, as it requires a server to work and the one I'm using have limited of available hrs it may not be always up. To solve this I would need to pay for a server and yeah it may be a problem... in case if I have enough support...I can invest on it. There's a buymeacofee (~patreon) link in the menu if one wants to help me.

```{r,echo=FALSE, eval=FALSE}

### [`MatchUps`](https://llorr-stats.netlify.app/static/mu.html)
Match Ups data that cover the same (current) cycle of buff/nerfs.
### [`Bo3-Helper`](https://legnavv.shinyapps.io/Bo3-helper/)
Helper for Bo3. Using mostly the most played archetypes (still for 2.12/2.13).
### [`Meta Stats`](https://llorr-stats.netlify.app/static/meta.html)
Dashboard with Meta Stats for the current patch and recent days.
```