---
params:
  ind: "MR033"
  patch: "Patch 2.19 - Week 2"
  title: "THE META REPORT NAME IS TOO LONG, TOO DAMN LONG (n°33)"
  description: "BETWEEN WORLDS - Seasonal Tournament Open Rounds Waiting Room"
  cardlurl: "https://dd.b.pvp.net/latest/set5/en_us/img/cards/05PZ022T1-full.png"
  prev:  "2021-11-10 17:00:00" #UTC tz / 'current' previous week start
  start: "2021-11-17 17:00:00" #UTC tz / 'current' week start
  end:   "2021-11-24 17:00:00" #UTC tz / 'current' week end
  nGrid: 15
  # skip:  3300000  # ~ Patch 2.16

title: | 
  `r params$title`
description: |
  `r params$patch` - `r params$description`
base_url: https://www.llorr-stats.com
preview: |
  `r params$cardlurl`
author:
  - name: Valentino (Legna) Vazzoler
date: 11-17-2021
output:
 distill::distill_article:
    toc: true
    toc_float: true
    toc_depth: 3
    self_contained: false
citation: false
draft: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE,
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  comment = NA,
  R.options = list(width = 140,
                   digits.secs=6),
  dev.args = list(bg = 'whitesmoke'), # make graphics with whitesmoke background
  fig.align = 'center',
  fig.width=12,
  fig.height=8,
  engine.path = list(
    python = 'C:/anaconda/'   # -> use_python("C:/anaconda/")
  ),
  #'distill options
  layout="l-page",
  preview=FALSE
)

#' R Option
options(scipen = 999)
source(file.path("C:","LlorR","scripts","lor_main.R" ))
xaringanExtra::use_panelset()
```

```{r panelset-style}
xaringanExtra::style_panelset_tabs(
  font_family = "Helvetica",
  active_foreground = "white",
  hover_foreground = "black",
  hover_border_color = "black",
  active_background = "#007fff"
  )
```

```{r raw-data}
# skip.dt <-fread(file.path("C:","LlorR","data","raw","skip_row.csv")  )
# skip.dt

#' load gameDT
#'############
# file.DT <- file.path("C:","LlorR","data","raw","LoR_MatchDT.csv")
# header        <- fread(file.DT, header = FALSE, na.strings = c("",NA), nrows = 1, stringsAsFactors = FALSE)
# LoR.Match.RMD <- fread(file.DT, header = FALSE, na.strings = c("",NA), skip = params$skip )
# colnames(LoR.Match.RMD) <- unlist(header,use.names = F)

#' Read gamesDT
###############
LoR.Match.RMD <- fread(file.path("C:","LlorR","data","raw","LoR_MatchDT.csv"), header = T, na.strings = c("", NA))

#' Read Temp
###############
Temp.Match.RMD <- fread(file.path("C:","LlorR","data","raw","LoR_TempDT.csv"), header = T, na.strings = c("", NA))

#' load Account
#'#############
LoR.Account.RMD <- fread(file.path("C:","LlorR","data","raw","LoR_ACCOUNT.csv"),
                         header=T, na.strings = c("",NA), encoding = 'UTF-8') |>
  mutate( RiotID = sprintf("%s#%s",gameName,tagLine) )

#' load DeckDT
#'############
LoR.Deck.RMD        <- fread(file.path("C:","LlorR","data","raw","LoR_DECK.csv"),na.strings = c("",NA))
```

```{r archetype-fix}
#' Limit the Deck DT to make the fixes much faster
deck_filter <- rbind(LoR.Match.RMD,Temp.Match.RMD) |>
  distinct() |>
# deck_filter <- LoR.Match.RMD |>
  #' Base filters
  # filter( game_type=="Ranked" ) |>
  filter( game_start_time_utc >= as.POSIXct(params$start, tz = "UTC") & game_start_time_utc < as.POSIXct(params$end, tz = "UTC") ) |>
  select(deck_code_1,deck_code_2) |>
  pivot_longer( cols = contains("deck_code"),values_to = "decks" ) |>
  filter(decks!="") |>
  distinct(decks)

LoR.Deck.RMD <- LoR.Deck.RMD[deck_code %in% deck_filter$decks]

#' Archetype-Fix
#'##############
source(file.path("C:","LlorR","scripts","functions","lor_archetype_rmd.R"))

LoR.Deck.RMD[ !is.na(archetype_pretty), archetype:=archetype_pretty ]
```

```{r prepare-data-temp}
#' Melt tbl
#'#########
LoR.Melt.Matches.RMD <- Temp.Match.RMD |>
  filter( game_type == "Ranked"  ) |>
  filter( game_start_time_utc >= as.POSIXct(params$start,"UTC") & game_start_time_utc < as.POSIXct(params$end,"UTC") ) |>
  select( -ends_with("_3"),-ends_with("_4")  ) |>
  left_join(LoR.Deck.RMD[,.(deck_code,playerDeck_1=archetype)],  by=c("deck_code_1"="deck_code")) |>
  left_join(LoR.Deck.RMD[,.(deck_code,opponentDeck_1=archetype)],by=c("deck_code_2"="deck_code")) |>
  rename( playerPuuid_1 = puuid_1, playerPuuid_2 = puuid_2 ) |>
  mutate( playerDeck_2 = opponentDeck_1, opponentDeck_2 = playerDeck_1, opponentPuuid_1 = playerPuuid_2, opponentPuuid_2 = playerPuuid_1 ) |>
  pivot_longer(cols = c(ends_with("_1"),ends_with("_2")),
               names_to = c(".value"),
               names_pattern = "(.*)_[0-9]"
               ) |>
  #' finish 'process' data
  left_join(LoR.Account.RMD[,.(puuid,playerID=RiotID)]   ,by=c("playerPuuid"="puuid")) |>
  left_join(LoR.Account.RMD[,.(puuid,opponentID=RiotID)] ,by=c("opponentPuuid"="puuid")) |>
  left_join(LoR.Deck.RMD |> select(!archetype),by=c("deck_code","factions")) |>
  as.data.table()
```

```{r prepare-data}
#' Melt tbl
#'#########
LoR.Melt.Master.RMD <- LoR.Match.RMD |>
  filter( game_type == "Ranked"  ) |>
  filter( game_start_time_utc >= as.POSIXct(params$start,"UTC") & game_start_time_utc < as.POSIXct(params$end,"UTC") ) |>
  select( -ends_with("_3"),-ends_with("_4")  ) |>
  left_join(LoR.Deck.RMD[,.(deck_code,playerDeck_1=archetype)],  by=c("deck_code_1"="deck_code")) |>
  left_join(LoR.Deck.RMD[,.(deck_code,opponentDeck_1=archetype)],by=c("deck_code_2"="deck_code")) |>
  rename( playerPuuid_1 = puuid_1, playerPuuid_2 = puuid_2 ) |>
  mutate( playerDeck_2 = opponentDeck_1, opponentDeck_2 = playerDeck_1, opponentPuuid_1 = playerPuuid_2, opponentPuuid_2 = playerPuuid_1 ) |>
  pivot_longer(cols = c(ends_with("_1"),ends_with("_2")),
               names_to = c(".value"),
               names_pattern = "(.*)_[0-9]"
               ) |>
  #' finish 'process' data
  left_join(LoR.Account.RMD[,.(puuid,playerID=RiotID)]   ,by=c("playerPuuid"="puuid")) |>
  left_join(LoR.Account.RMD[,.(puuid,opponentID=RiotID)] ,by=c("opponentPuuid"="puuid")) |>
  left_join(LoR.Deck.RMD |> select(!archetype),by=c("deck_code","factions"))
```

# Data

```{r account-info}
masterEU   <- LoR.Account.RMD |> filter(activeShard=="europe"   & master=="master") |> distinct(gameName,tagLine) |> count() |> pull()
masterNA   <- LoR.Account.RMD |> filter(activeShard=="americas" & master=="master") |> distinct(gameName,tagLine) |> count() |> pull()
masterASIA <- LoR.Account.RMD |> filter(activeShard=="asia"     & master=="master") |> distinct(gameName,tagLine) |> count() |> pull()

old.masterEU   <- LoR.Account.RMD |> filter(activeShard=="europe"   & note=="master") |> distinct(gameName,tagLine) |> count() |> pull()
old.masterNA   <- LoR.Account.RMD |> filter(activeShard=="americas" & note=="master") |> distinct(gameName,tagLine) |> count() |> pull()
old.masterASIA <- LoR.Account.RMD |> filter(activeShard=="asia"     & note=="master") |> distinct(gameName,tagLine) |> count() |> pull()

namesList.EU.RMD   <- lor_leaderboard("europe")$name
namesList.NA.RMD   <- lor_leaderboard("americas")$name
namesList.ASIA.RMD <- lor_leaderboard("asia")$name
```

```{r nGames-data}
minrow_live <- min(which(LoR.Match.RMD[,game_start_time_utc >= as.POSIXct(params$start)]))
maxrow_live <- max(which(LoR.Match.RMD[,game_start_time_utc  < as.POSIXct(params$end)]  ))

max_time <- LoR.Match.RMD |>
  filter( game_start_time_utc >= as.POSIXct(params$start, tz = "UTC") & game_start_time_utc < as.POSIXct(params$end, tz = "UTC") & game_type=="Ranked") |>
  slice_max(game_start_time_utc) |> 
  pull(game_start_time_utc) |>
  format(format = "%Y-%m-%d %H:%M:%S")

nMatches.extra <- LoR.Match.RMD |>
  filter( game_start_time_utc >= as.POSIXct(params$start, tz = "UTC") & game_start_time_utc < as.POSIXct(params$end, tz = "UTC") & game_type=="Ranked") |>
  tabyl(game_type) |>
  filter( game_type=="Ranked" ) |>
  pull(n)

tbl1 <- LoR.Match.RMD |>
  #' Stay only 'among' the row with the games in the time-frame I want
  ####################################################################
  slice(minrow_live:maxrow_live) |>
  #' Extrapolate Friendly and 'to Scrap' matches
  ##############################################
  mutate( game_type = case_when(
    status==404   ~ "Friendly",
    is.na(status) ~ "to Scrap",
    TRUE ~ as.character(game_type)
    )) |>
  #' Give to the new game_types a game_start_time_utc among the timeframe on interest
  #' so it can be used a filter without worrying about other parameter like status and so on
  ##########################################################################################
  mutate( game_start_time_utc = replace( game_start_time_utc, game_type %in% c("Friendly","to Scrap"),  as.POSIXct(params$start, tz = "UTC")+days(3) ) ) |>
  filter( game_start_time_utc >= as.POSIXct(params$start, tz = "UTC") & game_start_time_utc < as.POSIXct(params$end, tz = "UTC") ) |>
  mutate( game_type = fct_other(factor(game_type),keep = c("Ranked","Friendly","to Scrap")) |> fct_infreq() ) |>
  select(Status=game_type,Server=server) |>
  #' Create tbl
  #############
  tbl_summary()

tbl2 <- LoR.Match.RMD |>
  filter( game_start_time_utc >= as.POSIXct(params$start, tz = "UTC") & game_start_time_utc < as.POSIXct(params$end, tz = "UTC") ) |>
  filter( game_type == "Ranked" ) |>
  select(Server=server) |>
  tbl_summary()

# tbl1
# tbl2

merge.tbl <- tbl_merge(
    tbls = list(tbl1, tbl2),
    tab_spanner = c("**All Games**", "**Ranked**")
  )
```

```{r nGames-data-temp}
minrow_live <- min(which(Temp.Match.RMD[,game_start_time_utc >= as.POSIXct(params$start)]))
maxrow_live <- max(which(Temp.Match.RMD[,game_start_time_utc  < as.POSIXct(params$end)]  ))

max_time <- Temp.Match.RMD |>
  filter( game_start_time_utc >= as.POSIXct(params$start, tz = "UTC") & game_start_time_utc < as.POSIXct(params$end, tz = "UTC") & game_type=="Ranked") |>
  slice_max(game_start_time_utc) |> 
  pull(game_start_time_utc) |>
  format(format = "%Y-%m-%d %H:%M:%S")

nGames <- Temp.Match.RMD |>
  filter( game_start_time_utc >= as.POSIXct(params$start, tz = "UTC") & game_start_time_utc < as.POSIXct(params$end, tz = "UTC") & game_type=="Ranked") |>
  tabyl(game_type) |>
  filter( game_type=="Ranked" ) |>
  pull(n)

tbl1.temp <- Temp.Match.RMD |>
  #' Stay only 'among' the row with the games in the time-frame I want
  ####################################################################
  slice(minrow_live:maxrow_live) |>
  #' Extrapolate Friendly and 'to Scrap' matches
  ##############################################
  mutate( game_type = case_when(
    status==404   ~ "Friendly",
    is.na(status) ~ "to Scrap",
    TRUE ~ as.character(game_type)
    )) |>
  #' Give to the new game_types a game_start_time_utc among the timeframe on interest
  #' so it can be used a filter without worrying about other parameter like status and so on
  ##########################################################################################
  mutate( game_start_time_utc = replace( game_start_time_utc, game_type %in% c("Friendly","to Scrap"),  as.POSIXct(params$start, tz = "UTC")+days(3) ) ) |>
  filter( game_start_time_utc >= as.POSIXct(params$start, tz = "UTC") & game_start_time_utc < as.POSIXct(params$end, tz = "UTC") ) |>
  mutate( game_type = fct_other(factor(game_type),keep = c("Ranked","Friendly","to Scrap")) |> fct_infreq() ) |>
  select(Status=game_type,Server=server) |>
  #' Create tbl
  #############
  tbl_summary()

tbl2.temp <- Temp.Match.RMD |>
  filter( game_start_time_utc >= as.POSIXct(params$start, tz = "UTC") & game_start_time_utc < as.POSIXct(params$end, tz = "UTC") ) |>
  filter( game_type == "Ranked" ) |>
  select(Server=server) |>
  tbl_summary()

# tbl1.temp
# tbl2.temp

merge.tbl.temp <- tbl_merge( 
    tbls = list(tbl1.temp, tbl2.temp),
    tab_spanner = c("**All Games**", "**Ranked**")
  )

nMatches <- nGames
nGames <- NROW(LoR.Melt.Matches.RMD)
```

Number of (Ranked) matches analysed **`r format(nMatches.extra,scientific = F)`** or **`r format(nMatches.extra*2,scientific = F)`** games. / Master

Number of (Ranked) matches analysed **`r format(nMatches,scientific = F)`** or **`r format(nGames,scientific = F)`** games. / ~Plat+

Last Update: `r format(Sys.time(),format = "%Y-%m-%d %H:%M")`

```{r table-nGames-data, layout="l-body"}
nGames_tbl <- tbl_merge( 
  tbls = list(merge.tbl, merge.tbl.temp),
    tab_spanner = c("**Current Master**", "**Last-Season Master**")
  ) |>
  modify_footnote(
    update = label ~
      md(glue::glue("Metadata from Friendly Matches (that aren't Bo3) is not recoverable, \n the value may not be perfect since I lack the starting time of the game. The amount of Games to still scrap is also an estimation based on the 'position' of the game" ))
  ) |> # show_header_names()
  modify_footnote(
    # row_type, variable, var_label
    update = contains("stat_") ~
      md(glue::glue("n(%) took from the number of matches. When the data is analysed the size is double since we account each different player" ))
  ) |>
  # modify_header(label ~ "**Variable**") |>
  bold_labels() |>
  as_gt() |>
  tab_header(
    title = glue::glue("{params$patch} - by the Numbers")
  ) |>
  tab_footnote(
    footnote = md(glue::glue("Max datetime recovered: {max_time} UTC from {params$start} to {params$end} UTC" )),
    locations = cells_title(groups = c("title"))
    ) |>
  tab_footnote(
    footnote = md(glue::glue(
      "EU Master playerDecks in the ladder {length(namesList.EU.RMD)} while number of possible Master playerDecks recovered is {masterEU}, Number of Last-Season EU Master used {old.masterEU}
      NA Master playerDecks in the ladder {length(namesList.NA.RMD)} while number of possible Master playerDecks recovered is {masterNA}, Number of Last-Season NA Master used {old.masterNA}
      ASIA Master playerDecks in the ladder {length(namesList.ASIA.RMD)} while number of possible Master playerDecks recovered is {masterASIA}, Number of Last-Season ASIA Master used {old.masterASIA}"
      )),
    locations = cells_column_spanners(spanners = everything())
  ) 

nGames_tbl |> #
  tab_options(
    data_row.padding = px(1.2),
    table.background.color = "whitesmoke",
    table.font.color = "black",
    table.font.color.light = "black"
   )

gtsave(nGames_tbl,glue::glue("./images/meta-report/{params$ind}-bytheNumbers.png")) |> invisible()
```

# Regions

Switching back to Master as this report is supposed to be

## Play Rate

::: {.l-page}
```{r process-tableFreq}
Region.Freq <- LoR.Melt.Master.RMD |>
  select(factions) |>
  separate_rows(factions,sep=",") |>
  tabyl(factions,show_na=F) |>
  tibble() |> 
  rename_all(~c("region","n","freq")) |>
  mutate( region = map_chr(.x = region, ~str_remove_all(.x, paste(c("_Name","faction_", ""), collapse = "|") ) ) ) |>
  add_column(icon = data_regions$iconsPath)

Region.Freq.Server <- LoR.Melt.Master.RMD |>
  select(server,factions) |>
  separate_rows(factions,sep=",") |>
  tabyl(factions,server, show_na = F) |>
  adorn_percentages("col") |>
  mutate( region = map_chr(.x = factions, ~str_remove_all(.x, paste(c("_Name","faction_", ""), collapse = "|") ) ) )

Region.Freq <- full_join(Region.Freq,Region.Freq.Server,by="region")
```

::: {.panelset}
::: {.panel}
### Plot {.panel-name}

```{r plot-Region}
sxLabel_card <- format(Region.Freq$freq*100,2)
dxLabel_card <- format(Region.Freq$freq*100,2)
sxLabel_card <- ifelse(as.numeric(sxLabel_card) > 4,  sxLabel_card , "") |> as.numeric() |> {\(x) scales::number(x, accuracy = 0.01)}()
dxLabel_card <- ifelse(as.numeric(dxLabel_card) <= 4, dxLabel_card , "") |> as.numeric() |> {\(x) scales::number(x, accuracy = 0.01)}()

RegionByRegion <- Region.Freq |>
  ggplot(aes(x = reorder(region, freq), y = freq)) +
  geom_bar(stat="identity") +
  geom_bar_pattern(
    aes(
      pattern_filename = region,
    ),
    stat            = 'identity',
    pattern         = 'image',
    pattern_type    = 'none',
    fill            = data_regions$colorRegion,
    colour          = 'black',
    pattern_scale   = -2,
    pattern_filter  = 'point',
    pattern_gravity = 'east'
  ) +
  # theme_void() +
  labs(
    x = "Region",
    y = "Play Rate",
    title = "Regions Play Rate",
    subtitle = "number of times a region is included in a deck",
    caption = glue::glue("{params$patch}
                         Ranked games from {params$start} UTC to {params$end} UTC
                         Metadata of games collected with RiotGames API")
    ) +
  annotate(
    geom = 'text', 
    color = "grey50",
    x = 1.0, 
    y = 0.15, 
    hjust = 0.5,
    label = glue::glue('n = {nGames}\nGini Index = {round(DescTools::Gini(Region.Freq$freq,na.rm = T),3)}'), 
    fontface = 'bold') +
  coord_flip() +
  scale_pattern_filename_discrete(choices = data_regions$iconsPath ) +
  scale_pattern_discrete(guide = guide_legend(nrow = 1)) +
  scale_fill_manual("legend", values = data_regions$colorRegion) +
  scale_y_continuous(limits = c(0, round(max(Region.Freq$freq+0.04 ),3) ),
                     breaks = seq(0,0.5,0.04),
                     expand = c(-0.001,0.02),
                     labels = scales::percent_format(accuracy = 1) ) +
  guides(fill = "none") +
  #' Adding the text of the frequencies
  geom_text(aes(label = sxLabel_card), hjust = 2.5, size = 5,position = position_dodge(width = 1)) +
  geom_text(aes(label = dxLabel_card), hjust = -0.5, size = 5,position = position_dodge(width = 1)) +
  theme_539() +
  theme( 
    legend.position = "none",
    axis.text = element_text(face = "bold", color = "grey50"),
    panel.grid.major.y = element_blank()
    )
  
RegionByRegion
```

The Gini Index is a measure of heterogeneity so, in this case and in simpler terms, how much the play rates are similar. The Index goes (when normalized like here) $in$ [0,1] and it's equal to 1 when there's a single value with 100% play rate or 0 when all play rates are equal. Of course a Gini Index of 1 needs to be avoided but it's not like the aim should be 0. As said, it's just to add some additional tools.
:::

```{r create-gif-data}
require(gganimate)

Region.freq.master.prev <- LoR.Match.RMD |>
  filter( game_type == "Ranked"  ) |>
  filter( game_start_time_utc >= as.POSIXct(params$prev,"UTC") & game_start_time_utc < as.POSIXct(params$start,"UTC") ) |>
  select( starts_with("factions") ) |>
  pivot_longer(cols = everything(), values_to = "factions") |>
  drop_na() |>
  select(factions) |>
  separate_rows(factions,sep=",") |>
  tabyl(factions,show_na=F) |>
  tibble() |>
  rename_all(~c("region","n","freq")) |>
  mutate( region = map_chr(.x = region, ~str_remove_all(.x, paste(c("_Name","faction_", ""), collapse = "|") ) ) ) |>
  # add_column(icon = data_regions$iconsPath) |>
  select( -n ) |>
  add_column(label = "Master") |>
  add_column(time = "Previous") |>
  mutate(rank = rank(-freq))

Region.freq.master.current <- LoR.Match.RMD |>
  filter( game_type == "Ranked"  ) |>
  filter( game_start_time_utc >= as.POSIXct(params$start,"UTC") & game_start_time_utc < as.POSIXct(params$end,"UTC") ) |>
  select( starts_with("factions") ) |>
  pivot_longer(cols = everything(), values_to = "factions") |>
  drop_na() |>
  select(factions) |>
  separate_rows(factions,sep=",") |>
  tabyl(factions,show_na=F) |>
  tibble() |>
  rename_all(~c("region","n","freq")) |>
  mutate( region = map_chr(.x = region, ~str_remove_all(.x, paste(c("_Name","faction_", ""), collapse = "|") ) ) ) |>
  # add_column(icon = data_regions$iconsPath) |>
  select( -n ) |>
  add_column(label = "Master") |>
  add_column(time = "Current") |>
  mutate(rank = rank(-freq))

Region.freq.extra.prev <- Temp.Match.RMD |>
  filter( game_type == "Ranked"  ) |>
  filter( game_start_time_utc >= as.POSIXct(params$prev,"UTC") & game_start_time_utc < as.POSIXct(params$start,"UTC") ) |>
  select( starts_with("factions") ) |>
  pivot_longer(cols = everything(), values_to = "factions") |>
  drop_na() |>
  select(factions) |>
  separate_rows(factions,sep=",") |>
  tabyl(factions,show_na=F) |>
  tibble() |>
  rename_all(~c("region","n","freq")) |>
  mutate( region = map_chr(.x = region, ~str_remove_all(.x, paste(c("_Name","faction_", ""), collapse = "|") ) ) ) |>
  # add_column(icon = data_regions$iconsPath) |>
  select( -n ) |>
  add_column(label = "~Plat+") |>
  add_column(time = "Previous") |>
  mutate(rank = rank(-freq))

Region.freq.extra.current <- Temp.Match.RMD |>
  filter( game_type == "Ranked"  ) |>
  filter( game_start_time_utc >= as.POSIXct(params$start,"UTC") & game_start_time_utc < as.POSIXct(params$end,"UTC") ) |>
  select( starts_with("factions") ) |>
  pivot_longer(cols = everything(), values_to = "factions") |>
  drop_na() |>
  select(factions) |>
  separate_rows(factions,sep=",") |>
  tabyl(factions,show_na=F) |>
  tibble() |>
  rename_all(~c("region","n","freq")) |>
  mutate( region = map_chr(.x = region, ~str_remove_all(.x, paste(c("_Name","faction_", ""), collapse = "|") ) ) ) |>
  # add_column(icon = data_regions$iconsPath) |>
  select( -n ) |>
  add_column(label = "~Plat+") |>
  add_column(time = "Current") |>
  mutate(rank = rank(-freq))

static.Region.Freq <- rbind(Region.freq.master.prev,Region.freq.master.current,Region.freq.extra.prev,Region.freq.extra.current)

static.Region.Freq <- static.Region.Freq |>
  mutate( freq = ifelse(label == "~Plat+",-freq, freq) )
```

```{r pyramid-gif, fig.width=12, fig.height=8}
pacman::p_load(tidyverse, ggpol, gganimate, gifski)

RegPyramid <- static.Region.Freq |>
  ggplot(aes(
    x = region,
    y = freq,
    fill = region
    )
    ) +
  geom_bar(stat = "identity") +
  geom_label(
    aes(y=freq,label = freq %>% scales::percent(accuracy = 0.1)),
    color="black",
    fill = "#f0f0f0",
    size = 3.5,
    hjust = 0.5,
    )  +
  scale_fill_manual("legend", values = list.levels$colorRegion.Balco) +
  theme(
    plot.background = element_rect(fill = "#f0f0f0", color = NA),
    panel.background = element_rect(fill = "#f0f0f0", color = NA),
    panel.border=element_blank(),

    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_line( size=.1, color="grey" ),
    panel.grid.minor.x = element_line( size=.1, color="grey" ),

    axis.title.y = element_blank(),
    axis.title.x = element_text( size = 16, face = "bold" ),
    axis.text.y = element_text(size = 12, color = "grey50" ),
    axis.text = element_text(size = 14),
    
    legend.position = "none",
    legend.key.size = unit(0.75, "cm"),
    legend.text = element_text( size = 15, face = "bold" ),
    
    plot.title  = element_text( size = 22, hjust = 0.5, face = "bold" ),
    plot.subtitle = element_text( size = 14, hjust = 0.5, face = "bold" ),
    plot.caption = element_text( size = 12, hjust = 0.5, face = "italic", color = "gray" )
    ) +
  coord_flip() +
  facet_share(
    ~label,
    dir = "h",
    scales = "free",
    reverse_num = TRUE,
    shrink = FALSE
    )
  
RegPyramid <- RegPyramid +
 labs(
      # title = "Regions Play Rate",
      subtitle = "number of times a region is included in a deck",
      y = "Play Rate",
      caption = glue::glue("{params$patch}
                         Ranked games from {params$start} UTC to {params$end} UTC
                         Metadata of games collected with RiotGames API")
     )
# RegPyramid

# animation
animRegPyramid <- RegPyramid +
  transition_states(
    time,
    transition_length = 2,
    state_length = 1
    ) +
  labs(title = paste0(params$patch,"- Region Play Rate: {closest_state} week")) +
  enter_fade() +
  exit_fade() +
  ease_aes('cubic-in-out')

# render
anim_save(animation = animRegPyramid,
          glue::glue("images/meta-report/{params$ind}-RegPyramid.gif"),
          # nframes = 100, fps = 20,
          width = 1200, height = 600,
          fps = 24,
          duration = 3
          )
```


::: {.panel}
### Table {.panel-name}

```{r print-tableFreq-gt}
Region.Freq.tbl <- Region.Freq |>
  select(-n,-icon,-factions) |>
  arrange(desc(freq)) |>
  gt( ) |>
  tab_header(
    title = "Region Play Rate",
    subtitle = "Relative Frequencies by Inclusion Rate of a Region"
  ) |>
  tab_spanner(
    label = "Shard",
    columns = c(americas, asia, europe)
  ) |>
  fmt_percent(
    columns = c(2:5),
    decimals = 2
  ) |>
  cols_align(
    align = "left",
    columns = 1
  ) |>
  cols_align(
    align = "center",
    columns = c(2:5)
  ) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = 1,
    )
  ) |>
  cols_label(
    region   = md("**Region**"),
    freq     = md("**Freq**"),
    americas = md("**America**"),
    asia     = md("**Asia**"),
    europe   = md("**Europe**")
  ) |>
   tab_options(
    table.background.color = "whitesmoke",
    table.font.color = "black",
    table.font.color.light = "black"
   ) |>
  tab_source_note(
    source_note = glue::glue("{params$patch}
                             Ranked games from {params$start} UTC to {params$end} UTC
                             Metadata of games collected with RiotGames API")
    )

Region.Freq.tbl
```
:::
:::

<!-- Close Region 1 panelset -->
:::

## Play Rate by number of Cards

`r kableExtra::text_spec("Note:", color = "red")` currently all dual region cards have only their main region as possible value assigned. The same problem also apply to the card's inclusion rates.

::: {.l-page}
```{r process-tableFreq_byCard}
Regions.Freq.byCards <- LoR.Melt.Master.RMD |>
  select( starts_with( "Card") ) %>%
  map_df(.,~str_sub(.x, start=3,end=4) ) %>%
  mutate_all(~fct_recode(.,!!!recodeRegShort)) |>
  unlist(use.names = FALSE) |> 
  tabyl(show_na = F) |> 
  rename_all(~c("region","n","freq")) |> 
  mutate(region := as.character(region))
  
setorderv(Regions.Freq.byCards, c("region"), c(1))

# Regions.Freq.byCards <- as.tibble(Regions.Freq.byCards)
Regions.Freq.byCards$freq <- round(Regions.Freq.byCards$freq,4)
Regions.Freq.byCards$icon <- data_regions$iconsPath

Regions.Freq.byCards.Server <- LoR.Melt.Master.RMD |>
  select( starts_with( "Card") ) %>%
  map_df(.,~str_sub(.x, start=3,end=4) ) %>%
  mutate_all(~fct_recode(.,!!!recodeRegShort)) |>
  add_column(server = LoR.Melt.Master.RMD$server ) |>
  melt(id.var=c("server")) |>
  select(value,server) |>
  tabyl(value,server, show_na = F) |>
  adorn_percentages("col")

Card.tableByRegPlot <- LoR.Melt.Master.RMD |>
  select( starts_with( "Card") ) %>%
  map_df(.,~str_sub(.x, start=3,end=4) ) %>%
  mutate_all(~fct_recode(.,!!!recodeRegShort)) |>
  add_column(server = LoR.Melt.Master.RMD$server ) |>
  melt(id.var=c("server")) |>
  select(value,server) |> table() %>% prop.table(.,margin = 2) |> as.data.table()
```

::: {.panelset}
::: {.panel}
### Plot {.panel-name}

```{r plotRegion_byCards}
sxLabel_card <- format(Regions.Freq.byCards$freq*100,2)
dxLabel_card <- format(Regions.Freq.byCards$freq*100,2)
sxLabel_card <- ifelse(as.numeric(sxLabel_card) > 4,  sxLabel_card , "") |> as.numeric() |> {\(x) scales::number(x, accuracy = 0.01)}()
dxLabel_card <- ifelse(as.numeric(dxLabel_card) <= 4, dxLabel_card , "") |> as.numeric() |> {\(x) scales::number(x, accuracy = 0.01)}()

RegionByCards <- Regions.Freq.byCards |>
  ggplot(aes(x = reorder(region, freq), y = freq)) +
  geom_bar_pattern(
    aes(
      pattern_filename = region,
    ),
    stat            = 'identity',
    pattern         = 'image',
    pattern_type    = 'none',
    fill            = data_regions$colorRegion,
    colour          = 'black',
    pattern_scale   = -2,
    pattern_filter  = 'point',
    pattern_gravity = 'east'
  ) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "Region",
    y = "Play Rate",
    title = "Regions Play Rate",
    subtitle = "number of times a card within a region is included in a deck",
    caption = glue::glue("{params$patch}
                         Ranked games from {params$start} UTC to {params$end} UTC
                         Metadata of games collected with RiotGames API")
  ) +
  annotate(
    geom = 'text',
    color = "grey50",
    x = 1.0, 
    y = 0.15, 
    hjust = 0.5,
    label = glue::glue('n = {nGames}\nGini Index = {round(DescTools::Gini(Regions.Freq.byCards$freq,na.rm = T),3)}'), 
    fontface = 'bold'
    ) +
  coord_flip() +

  scale_pattern_filename_discrete(choices = data_regions$iconsPath) +
  scale_pattern_discrete(guide = guide_legend(nrow = 1)) +
  scale_fill_manual("legend", values = list.levels$data_regions$colorRegion) +
  # nome of the table
  scale_y_continuous(limits = c(0, round(max(Regions.Freq.byCards$freq+0.04 ),3) ),
                     breaks = seq(0,0.5,0.04),
                     expand = c(-0.001,0.02),
                     labels = scales::percent_format(accuracy = 1) ) +
  # geom_text(aes(label=format(freq*100,2)),
  #           hjust = 2, size = 5,position = position_dodge(width = 1)) +
  geom_text(aes(label=sxLabel_card),
            hjust = 2.5, size = 5,position = position_dodge(width = 1)) +
  geom_text(aes(label=dxLabel_card),
            hjust = -0.5, size = 5,position = position_dodge(width = 1)) +
  guides(fill = "none") +
  theme_539() +
  theme( legend.position = "none",
         axis.text = element_text(face = "bold", color = "grey50"),
         panel.grid.major.y = element_blank()
         )

RegionByCards
```
:::

::: {.panel}
### Table {.panel-name}

```{r print-tableFreq_byCard-gt}
Region.Freq.byCards.tbl <- Regions.Freq.byCards[,c("region","freq")] |>
  left_join( Regions.Freq.byCards.Server, by = c("region"="value") ) |>
  arrange(desc(freq)) |>
  gt( ) |>
  tab_header(
    title = "Region Play Rate",
    subtitle = "Relative Frequencies by number of times a Card within a Region is included in a Deck"
  ) |>
  tab_spanner(
    label = "Shard",
    columns = c(americas, asia, europe)
  ) |>
  fmt_percent(
    columns = c(2:5),
    decimals = 2
  ) |>
  cols_align(
    align = "left",
    columns = 1
  ) |>
  cols_align(
    align = "center",
    columns = c(2:5)
  ) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = 1,
    )
  ) |>
  cols_label(
    region   = md("**Region**"),
    freq     = md("**Freq**"),
    americas = md("**America**"),
    asia     = md("**Asia**"),
    europe   = md("**Europe**")
  ) |>
   tab_options(
    table.background.color = "whitesmoke",
    table.font.color = "black",
    table.font.color.light = "black"
   ) |>
  tab_source_note(
    source_note = glue::glue("{params$patch}
                             Ranked games from {params$start} UTC to {params$end} UTC
                             Metadata of games collected with RiotGames API")
    )

Region.Freq.byCards.tbl
```
:::
:::

<!-- Close Region 2 panelset -->
:::

# Champions Combinations

Note: I know I have to add some aggregations especially for Bandle (sorry Dr.LoR)

```{r gt-archetype}
tribble( 
  ~Deck, ~Source,
  "ASZ - Sivir Ionia", "Akshan/Sivir (IO/SH) or Sivir/Zed or Akshan/Sivir/Zed",
  "RubinBait - <Champ>", "Burn Deck using <Champ> to bait mulligan",
  "Dragons (DE/MT)", "(DE/MT) Decks with *at least* Shyvana and ASol",
  "SunDisc", "Mono Shurima with 1+ Sun Disc"
) |>
  gt() |>
  tab_header(
    title = glue::glue("Archetype ~Fix")
  ) |>
  gtExtras::gt_theme_nytimes() |>
  tab_options(
    table.background.color = "whitesmoke",
    table.font.color = "black",
    table.font.color.light = "black"
   )
```

```{r process-tableChampion}
CC.tableByReg <- LoR.Melt.Matches.RMD |>
  tabyl(playerDeck,server) |>
  adorn_percentages("col")

CC.table <- LoR.Melt.Matches.RMD |>
  tabyl(playerDeck, show_na = F) |>
  rename_all(~c("playerDeck","n","freq")) |>
  left_join(CC.tableByReg,by="playerDeck")
```

```{r process-tableChampion-new}
CC.table.New <- LoR.Melt.Master.RMD |>
  tabyl(playerDeck, show_na = F) |>
  rename_all(~c("playerDeck","n","freq")) |>
  left_join(LoR.Melt.Master.RMD |>
              tabyl(playerDeck,server) |>
              adorn_percentages("col"),by="playerDeck")
```

## Play Rates

::: {.l-page}
::: {.panelset}
::: {.panel}
### Plot {.panel-name}

```{r prepare-cc-dt}
nrowPlot <- 20

topDeck <- union(
  setDT(CC.table)[ order(-freq) ][1:nrowPlot,playerDeck],
  setDT(CC.table.New)[ order(-freq) ][1:nrowPlot,playerDeck]
)

ChampionCombo <- tibble( playerDeck = topDeck ) |>
  left_join(CC.table[,c("playerDeck","freq")], by ="playerDeck" ) |>
  left_join(CC.table.New[,c("playerDeck","freq")], by ="playerDeck" ) |>
  rename_all(~c("playerDeck","LastSeason","Current")) |>
  pivot_longer( cols = c("LastSeason","Current"),names_to = "master",values_to = "freq" )

```


```{r plot-Champion-PR}
# | fig.width=12,
# | fig.height=8

nrowPlot <- 20

# ChampionCombo.plot <- CC.table |>
#   arrange(desc(freq)) %>%
#   slice_head(.,n = 20) |>
  
ChampionCombo |>
  mutate( playerDeck = factor(playerDeck),
          playerDeck = fct_reorder(playerDeck, freq, mean, .desc = F ) ) |>
  ggplot(aes(x = playerDeck, y = freq, group = master, fill = master))  +
  geom_bar( stat = "identity", position=position_dodge(0.5), width=.5 ) +
  coord_flip() +
  # guides(fill = "none")  +
  theme_bw() +
  geom_text(
    aes(label=round(freq*100,2)),
    size = 3,
    face = "bold",
    color = "grey50",
    hjust = -0.5, size = 4,
    # vjust=-0.25
    # position = position_dodge(width = 1)
    position = position_dodge(0.9),
    ) +
  # scale_fill_manual("legend", values = list.levels$data_regions$colorRegion) +
  scale_y_continuous(
    limits = c(0, round(max(CC.table$freq+0.04 ),3) ),
    breaks = seq(0,0.20,0.02),
    labels = scales::percent_format(accuracy = 1) ) +
  annotate(geom="text", x=3, y=0.05, col="black",label = paste("n =",nGames,"\n"," cumulative frequence \n ",
                                                               paste0(CC.table |> arrange(desc(freq)) %>% slice_head(.,n = 20) |> select(freq) |> sum() %>% round(.,4)*100 ,"%") )
           ) +
  theme_539() +
  labs(x = "Champions",
       y = "Play Rate",
       title = "Champions Combination Play Rates",
       subtitle = glue::glue("Play-Rates of the top {nrowPlot} most played combination of champions/regions"),
       caption = glue::glue("{params$patch}
                            Ranked games from {params$start} UTC to {params$end} UTC
                            Decks are chosen from the union of top {nrowPlot} from Last-Season Masters and Current resulting in {length(topDeck)} displayed
                            Metadata of games collected with RiotGames API")
       ) +
  theme( 
    # legend.position = "none",
    axis.text = element_text(size = 9, face = "bold", color = "grey25", family = "Helvetica"),
    panel.grid.major.y = element_blank(),
    plot.title = element_text(face = "bold", size = 12, hjust = 0.6),
    axis.title.x = element_text(face = "bold"),
    axis.title.y = element_text(face = "bold"),
    legend.position = c(0.8,0.1)
    )

ggsave(glue::glue("./images/meta-report/{params$ind}-topPlayrate.png"))
```
:::

::: {.panel}
### from Last-Season Master {.panel-name}

```{r table-Champion-PR-old}
CC.table |>
  arrange(desc(freq)) |>
  # filter(nGames>100) |>
  select(playerDeck,freq,americas,asia,europe) |>
  reactable(
    bordered = TRUE,
    highlight = TRUE,
    striped = TRUE,
    searchable = TRUE,
    compact = TRUE, # compact the table height
    fullWidth = TRUE, # don't fill the page
    defaultPageSize = 20,
    wrap = TRUE,
    defaultColDef = colDef(
      style = list(fontFamily = "Helvetica", fontSize = "13px"), align = "center"
      # minWidth = 120,
      ),
    columns = list(
      playerDeck = colDef(name = "Champions",minWidth = 120, style = list(fontSize = "11px", fontWeight = "bold", color="black") ),
      freq     = colDef(name = "Play Rate",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") ),
      americas = colDef(name = "America",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") ),
      asia     = colDef(name = "Asia",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") ),
      europe   = colDef(name = "Europe",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") )
      )
    ) |>
  reactablefmtr::add_source(element_text(glue::glue("Data from Last-Season Master Only.
                                                    Source: Source: Metadata of games collected with RiotGames API")), background_color = "whitesmoke", font_family = "Chivo")
```
:::

::: {.panel}
### from Current Master {.panel-name}

```{r table-Champion-PR-new}
CC.table.New |>
  arrange(desc(freq)) |>
  # filter(nGames>100) |>
  select(playerDeck,freq,americas,asia,europe) |>
  reactable(
    bordered = TRUE,
    highlight = TRUE,
    striped = TRUE,
    searchable = TRUE,
    compact = TRUE, # compact the table height
    fullWidth = TRUE, # don't fill the page
    defaultPageSize = 20,
    wrap = TRUE,
    defaultColDef = colDef(
      style = list(fontFamily = "Helvetica", fontSize = "13px"), align = "center"
      # minWidth = 120,
      ),
    columns = list(
      playerDeck = colDef(name = "Champions",minWidth = 120, style = list(fontSize = "11px", fontWeight = "bold", color="black") ),
      freq     = colDef(name = "Play Rate",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") ),
      americas = colDef(name = "America",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") ),
      asia     = colDef(name = "Asia",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") ),
      europe   = colDef(name = "Europe",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") )
      )
    ) |>
  reactablefmtr::add_source(element_text(glue::glue("Data from Current Master Only.
                                                    Source: Source: Metadata of games collected with RiotGames API")), background_color = "whitesmoke", font_family = "Chivo")
```
:::

:::

<!-- Close CC lay Rate panelset -->
:::

## Day by Day

Highlisting the top10 most played decks (at the moment of the last game played).

```{r champion-freq-by-date}
m = 10

Champion.deck.daily <- LoR.Melt.Master.RMD |>
  rename("champions"="playerDeck") |>
  arrange(game_start_time_utc) |>
  select(game_start_time_utc,champions) |>
  mutate( num_cc = factor(champions) |> as.numeric() ) |>
  as.data.table() |>
  {\(x) x[ , cumFreq := (cumsum(num_cc)/num_cc)/.I , by=champions ]}() |>
  select(!num_cc) |>
  mutate( champions = factor(champions) |> fct_infreq() )

fct_values <- LoR.Melt.Matches.RMD |>
  # mutate( top5 = fct_lump(champions, n = m, w = tot, ties.method = "max") ) |>
 mutate( top5 = fct_lump_n(playerDeck,n = m) |> fct_infreq() ) |>
 pull(top5) |> levels()
```

```{r plot-date-by-date, fig.width=12, fig.height=8}
meta_evo <- ggplot(
   # The ggplot object has associated the data for the highlighted countries
  data = Champion.deck.daily |> filter(champions %in% fct_values[-1]),
  aes(game_start_time_utc, cumFreq, group = champions)
  ) +
  ## Lines for the non-highlighted countries
  geom_line(
    data = Champion.deck.daily |> filter(champions %!in% fct_values[-1]),
    color = "grey75",
    size = .6,
    alpha = .5
  ) +
  ## Lines for the highlighted countries.
  # It's important to put them after the grey lines
  # so the colored ones are on top
  geom_line(
    aes(color = champions),
    size = .9
  ) +
  # geom_text(aes(label=champions,color = champions))
  geom_label_repel(
    data = Champion.deck.daily |> filter(champions %in% fct_values[-1]) |> group_by(champions) |> slice_max(game_start_time_utc,n=1) |> distinct(game_start_time_utc,champions,.keep_all = T),
    aes(label=str_to_upper(champions),color = champions),
    # aes(color = champions, label = champions),
    family = "Helvetica",
    # fontface = "bold",
    size = 3.5,
    direction = "y",
    xlim = c(as.POSIXct(max(Champion.deck.daily$game_start_time_utc) + hours(12)), NA),
    force = 3,
    hjust = 1,
    segment.size = .7,
    segment.alpha = .5,
    segment.linetype = "dotted",
    box.padding = .4,
    segment.curvature = -0.1,
    segment.ncp = 3,
    segment.angle = 15,
    # bg.color = "grey50",
    bg.color = "grey50",
    # bg.color = "whitesmoke",
    fill = "#f0f0f0",
    label.padding = 0,
    label.size = 0
  ) +
  scale_x_datetime(
    # expand = c(0.02,0.01),
    date_minor_breaks = "1 day",
    limits = c(as.POSIXct(params$start, tz="UTC"), as.POSIXct(params$end, tz="UTC")+hours(23))
    # limits = c(as.POSIXct(params$start, tz="UTC"), as.POSIXct(params$end, tz="UTC"))
  )  +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0,.20),
    breaks = seq(0,.20,0.04),
    labels = scales::percent_format(accuracy = 1) # glue::glue("{format(seq(0, 0.20, by = 0.05), nsmall = 2)}%")
  ) +
  scale_color_manual(
    values = c(rcartocolor::carto_pal(n = 10, name = "Vivid")[1:10-1], "grey50")
  ) +
  labs(x = "Date",
       y = "PlayRate",
       title = "Evolution of Play Rate over time",
       caption = glue::glue("{params$patch}
                            Ranked games from {params$start} UTC to {params$end} UTC
                            Metadata of games collected with RiotGames API")
  ) +
  theme_539() +
  theme( legend.position = "none",
         axis.text = element_text(size = 10, face = "bold", color = "grey50")
         )

meta_evo

ggsave(glue::glue("./images/meta-report/{params$ind}-playrate-daybyday.png"))
```

## Win Rates

Tie games are excluded / only games from 'Old' Master

```{r get-muWR}
MUtbl <- LoR.Melt.Matches.RMD |>
  filter(game_outcome!="tie") |>
  select( playerDeck,opponentDeck,game_outcome,server ) |>
  group_by(playerDeck,opponentDeck) |>
  summarise( muWin   = sum(game_outcome=="win"),
             muGames = n(),
             muWR=mean(game_outcome=="win") ) |>
  as.data.table() |>
  {\(x) x[ ,c("LCI","UCI") := binom.confint(muWin,muGames,0.95,methods="exact")[5:6] ] }() |>
  mutate( 
    okCI:=(!between(0.50,LCI,UCI)),
    direction:=ifelse(muWR>0.50,"POS","NEG"),
    CI = glue("({percent(LCI,accuracy = 0.1)} - {percent(UCI,accuracy = 0.1)})" )
    )
```

```{r process-winRate}
WR.DT <- LoR.Melt.Matches.RMD |>
  filter(game_outcome!="tie") |>
  select( playerDeck,opponentDeck,game_outcome ) |>
  group_by(playerDeck) |>
  summarise( nWin   = sum(game_outcome=="win"),
             nGames = n(),
             WR=mean(game_outcome=="win")
            ) |>
  ungroup() |>
  mutate( playrate = nGames/sum(nGames) )

WR.DT.Reg <- LoR.Melt.Matches.RMD |>
  filter(game_outcome!="tie") |>
  select( playerDeck,opponentDeck,game_outcome,server ) |>
  group_by(server,playerDeck) |>
  summarise(
    nWin   = sum(game_outcome=="win"),
    nGames = n(),
    WR=mean(game_outcome=="win"),
    ) |>
  ungroup() |>
  group_by(server) |>
  mutate( sumGames = sum(nGames), regPlayrate = nGames/sumGames ) |>
  left_join(WR.DT[,c("playerDeck","playrate")],by="playerDeck") 
```

::: {.l-page}
::: {.panelset}
::: {.panel}
### Meta Decks {.panel-name}

Win rates of the most played combination of champions. Play Rate \>= 1% in at least one of the servers.

```{r print-tableWinRate}
WR.DT.Reg |>
  arrange(desc(playrate)) |>
  filter(playrate >= 0.01) |>
  arrange(desc(playrate)) |>
  relocate(playerDeck,WR,nWin,nGames,regPlayrate,server) |>
  reactable(
    groupBy = "playerDeck",
    bordered = TRUE,
    # wrap = FALSE,
    highlight = TRUE,
    striped = TRUE,
    # filterable = TRUE,
    defaultSorted = list(nGames = "desc"),
    defaultColDef = colDef(
      # header = function(value) str_to_title(value),
      #  cell = function(value) format(value, nsmall = 1),
      align = "center",
      minWidth = 120
      # headerStyle = list(background = "steelblue",color="white")
      ),
    columns = list(
      playerDeck = colDef(name = "Champions",minWidth = 250),
      server = colDef(name = "Server", aggregate = "unique",minWidth = 120),
      nWin   = colDef(name = "#Win", aggregate = "sum"),
      nGames = colDef(name = "#Games", aggregate = "sum"),
      WR     = colDef(name = "WinRate", aggregate = JS(
        "function(values, rows) {
        var totalWin = 0
        var totalGames = 0
        rows.forEach(function(row) {
        totalWin   += row['nWin']
        totalGames += row['nGames']
        })
        return totalWin / totalGames
        }"
        ),format = colFormat(percent = TRUE,digits = 1),
        ),
      regPlayrate   = colDef(name = "Play Rate",
                             aggregate = JS("function(values, rows) {
                                            var total = 0;
                                            var n = 0;
                                            rows.forEach(function(row) {
                                            total += row['playrate']
                                            n += 1
                                            })
                                            return total/n
                                            }"),
                             format = colFormat(percent = TRUE,digits = 1)),
      sumGames   = colDef(show=F),
      playrate   = colDef(show=F)
      )
    )
```
:::

::: {.panel}
### Underdog {.panel-name}

Top Win rates of the top10 best performing least played combination of champions. Play rate $\in$ [0.1%,1%)[^1]

```{r print-under-tableWinRate}
WR.DT |>
  filter( nGames >= 50 & WR >= 0.50 & playrate >= 0.001 & playrate < 0.01) |>
  slice_max(WR,n = 10) |>
  relocate(playerDeck,WR,nWin,nGames,playrate) |>
  arrange(desc(WR)) |>
  reactable(
    # searchable = TRUE,
    bordered = TRUE,
    # wrap = FALSE,
    highlight = TRUE,
    striped = TRUE,
    # filterable = TRUE,
    defaultColDef = colDef(
      # header = function(value) str_to_title(value),
      #  cell = function(value) format(value, nsmall = 1),
      align = "center",
      minWidth = 120,
      headerStyle = list(background = "steelblue",color="white")
      ),
    columns = list(
      playerDeck = colDef(name = "Champions",minWidth = 250),
      nWin   = colDef(name = "#Win"),
      nGames = colDef(name = "#Games"),
      WR     = colDef(name = "WinRate",format = colFormat(percent = TRUE,digits = 1) ),
      playrate   = colDef(name = "Play Rate",format = colFormat(percent = TRUE,digits = 1))
      )
    )
```
:::
:::

<!-- Close Win Rate panelset -->
:::

[^1]: Min number of games 50, during the times a meta/ladder just changed.

# Match Ups

`r kableExtra::text_spec("Note:", color = "red")`: only games from Last-Season Master

Regarding MU, this is not the most accurate estimation you can get from my data. If you want a better picture of the current meta it would be better to look at the dedicated MU-page where I use all "Ranked" games with the current sets of buffs and nerfs. While one may object I don't account for optimizations and differences in skills acquired during the weeks, the overall number of games / sample size makes them a better source of information. So, in case, please refer to the [MU - page](https://www.llorr-stats.com/static/mu.html) for a better "meta-investigation".

```{r get-WR-Top10}
mu <- 15

TopCC <- CC.table |> 
  arrange(desc(freq)) |> 
  {\(x) slice_head(x,n = mu)}() |> 
  select(playerDeck) |> 
  pull()

WRTopCC <- tibble::tibble( 
  playerDeck = rep(TopCC,each=mu),
  opponentDeck = rep(TopCC,mu)
  ) |>
  left_join(MUtbl, by = c("playerDeck","opponentDeck"))
```

```{r}
MUtbl.new <- tibble::tibble( 
  playerDeck = rep(TopCC,each=mu),
  opponentDeck = rep(TopCC,mu)
  ) |> 
  left_join( LoR.Melt.Master.RMD |>
  filter( playerDeck %in% TopCC & opponentDeck %in% TopCC ) |>
  filter(game_outcome!="tie") |>
  select( playerDeck,opponentDeck,game_outcome,server ) |>
  group_by(playerDeck,opponentDeck) |>
  summarise( muWin   = sum(game_outcome=="win"),
             muGames = n(),
             muWR=mean(game_outcome=="win") ) |>
  as.data.table(), by = c("playerDeck","opponentDeck")) |>
  mutate( muWR = replace(muWR, muGames < 30, NA ) )
  # {\(x) x[, c("LCI","UCI") := binom.confint(muWin,muGames,0.95,methods="exact")[5:6] ] }() |>
  # {\(x) x[, okCI:=(!between(0.50,LCI,UCI)) ]  }() |>
  # {\(x) x[, direction:=ifelse(muWR>0.50,"POS","NEG")  ]   }() |>
  # mutate( CI := glue("({percent(LCI,accuracy = 0.1)} - {percent(UCI,accuracy = 0.1)})" ) )
  # {\(x)   }()
```

::: {.l-page}
::: {.panelset}
::: {.panel}
## Match-up Grid {.panel-name}

The win rates on the grid are among the `r mu` most played champion combination.
The upper value is from all the Last-Season Masters, the bottom one only from the current Current Masters. MU with less than 30 games are not included.

```{r}
grid <- matrix(WRTopCC$muWR, nrow = mu, ncol = mu, byrow = T)
diag(grid) <- NA
colnames(grid) <- TopCC

grid.plus <- matrix(MUtbl.new$muWR, nrow = mu, ncol = mu, byrow = T)
diag(grid.plus) <- NA
colnames(grid.plus) <- sprintf("%s.v2",TopCC)
grid.plus <- grid.plus |>
  as.data.table()

grid.all <- cbind(grid,grid.plus)
```

```{r gt-grid,fig.width=12, fig.height=10}
MUgrid.gt <- grid.all |>
  as.data.table() |>
  add_column( name = colnames(grid),.before = 1 ) |>
  rename(" "=1) |>
  gt() |>
  gtExtras::gt_color_rows(2:(params$nGrid+1),
                # palette = c("#D73027", "white", "#1A9850" ),
                palette = c("red", "white", "green"),
                use_paletteer = F,
                domain = c(0,1) ) |>
  fmt_percent(
    columns = -1,
    decimals = 1
  )

for (i in 1:params$nGrid ) {
  MUgrid.gt <- MUgrid.gt |>
    cols_merge(
      columns = c(i+1,params$nGrid+i+1),
      hide_columns = (params$nGrid+i+1),
      # pattern = "{1}&mdash;{2}"
      ) |> 
    text_transform(
      locations = cells_body(
        columns = (i+1)
        ),
      fn = function(x){
        percent <- word(x, 1)
        frac <- word(x, -1)
        glue::glue(
          #595959 #grey35 / #7f7f7f #grey50
          "<div style='line-height:12px'><span style='font-weight:bold;color:#595959;font-variant:small-caps;font-size:14px'>{percent}</div>
           <div style='line-height:10px'><span style='color:#7f7f7f;font-size:10px'>({frac})</span></div>"
        )
        }
      )
  
}

MUgrid.gt.final <- MUgrid.gt |>
  cols_align(
    align = "center",
    columns = -1
  ) |>
  tab_options(
    data_row.padding = px(3.5),
    table.font.size = px(12)
  ) |>
  cols_width(
    -1 ~ px(90),
     1 ~ px(120),
    # everything() ~ px(90)
  ) |>
  opt_table_font(
    font = "Chivo"
  ) |>
  tab_source_note(
  source_note = md(glue::glue("The upper value is from Last-Season Masters while the bottom value is from New Masters. 
                              MU with less than 30 games are not included.
                              Order of the Archetypes based on the playrate over the last 7 days from the last-update from Plat+ (change to Master once the ladder is more populated).
                              Source: Metadata of games collected with RiotGames API")
  ))

MUgrid.gt.final |>
  tab_options(
    table.background.color = "whitesmoke",
    data_row.padding = px(5),
    table.font.size = px(13),
    column_labels.font.size = px(10)
  ) |>
  cols_width(
    -1 ~ px(90),
     1 ~ px(150),
    # everything() ~ px(100)
  )

gtsave(MUgrid.gt.final,glue::glue("./images/meta-report/{params$ind}-mugrid-gt.png"), vwidth = 1500, vheight = 1000) |> invisible()
```

```{r}
downloadthis::download_this(
  .data = MUgrid.gt.final,
  # path = system.file("assets/css/all.min.css", package = "downloadthis"),
  button_label = "Download MU grid as .png",
  button_type = "primary",
  has_icon = TRUE,
  icon = "fa fa-save",
  self_contained = FALSE
)
```
:::

::: {.panel}
## Match-up Table {.panel-name}

```{r reactable-tbl}
require(htmltools)
require(crosstalk)

#'Quick link for a MUtbl for testing
#'##################################
# file.MU.DT   <- list.files(path = file.path("C:","LlorR","data","clean" ), pattern = "MUtbl_", full.names = T) |> max()
# MUtbl <- fread(file.MU.DT, header = T, na.strings = c("", NA))

# The fs object will inject css into your page.
# if (requireNamespace("crosstalk", quietly = TRUE)) {
data <- crosstalk::SharedData$new(MUtbl |>
                       filter(muGames>=100) |>
                       select(-LCI,-UCI,-okCI,-direction))

bscols(
  widths = c(3, 9),
  list(
    crosstalk::filter_select("playerDeck", "Player", data, ~playerDeck),
    crosstalk::filter_select("opponentDeck", "Opponent", data, ~opponentDeck),
    crosstalk::filter_slider("muWin",   "#Win", data, ~muWin, width = "100%",step = 50,min = 0),
    crosstalk::filter_slider("muGames", "#Games", data, ~muGames, width = "100%",step = 100,min = 0),
    crosstalk::filter_slider("muWR", "WinRate", data, ~muWR, width = "100%",step=0.01,min = 0,max = 1)
  ),
  reactable(data,
            bordered = TRUE,
            highlight = TRUE,
            striped = TRUE,
            searchable = TRUE,
            defaultSorted = list(muGames = "desc"),
            # filterable = TRUE,
             defaultColDef = colDef(
              style = list(fontWeight = 500, color = "black",
                       fontFamily = "Work Sans, sans-serif", fontSize = "11px"),
              align = "center",
              minWidth = 120,
              headerStyle = list(background = "steelblue",color="white")
            ),
            columns = list(
              playerDeck   = colDef(name = "Player",minWidth = 120),
              opponentDeck = colDef(name = "Opponent"  ,minWidth = 120),
              muWin    = colDef(name = "#Win", style = list( fontSize = "15px") ),
              muGames  = colDef(name = "#Games", style = list( fontSize = "15px")),
              muWR     = colDef(name = "WinRate",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "15px") ),
              CI       = colDef(name = "CI",minWidth = 120, style = list(fontSize = "13px"))
              )
    )
  )
```
:::
:::

<!-- Close MU panelset -->
:::

# Deck of the week {.tabset .tabset-fade .tabset-pills}

Of course this week I want to highlight Jayce but there are too many decks with him, which to choose? Let's do all of them!

I actually wanted to choose something with Noxus... (those who knows, knows) but too bad.

As there are too many decks I restricted the data to decks which has been played for at least 10 games across the players.

```{r deck-structure-prepare}
# brks <- c(0.50,0.55,0.60,0.65,0.70,0.75,0.80,0.85,0.90,0.95)
# clrs = colorRampPalette( c("white","steelblue") )(length(brks)+1)
# deck_color_generator <- scales::col_numeric(c("white", "white","green"), domain = NULL)

make_color_pal <- function(colors, bias = 1) {
  get_color <- colorRamp(colors, bias = bias)
  function(x) rgb(get_color(x), maxColorValue = 255)
}

good_color <- make_color_pal(c("white", "white", "#9bc2e6"))
```

::: {.l-page}
::: {.panelset}
::: {.panel}

## Jayce's waifu/husbando (decks with at least 10 games)

```{r deckweek, layout="l-page"}
deck.of.week <- "Jayce"

whichDecks <- LoR.Melt.Matches.RMD |>
  filter( str_detect(playerDeck,"Jayce") ) |>
  tabyl(deck_code) |>
  filter(n >= 10) |>
  pull(deck_code)

SubDeck_deck_code <- LoR.Melt.Matches.RMD |>
  filter( deck_code %in% whichDecks ) |>
  pull(deck_code)
  # filter(playerDeck == deck.of.week ) |>

data <- get_deck_structure_2(SubDeck_deck_code)

data |>
  reactable(
    bordered = TRUE,
    highlight = TRUE,
    searchable = TRUE,
    compact = TRUE, # compact the table height
    fullWidth = T, # don't fill the page
    defaultPageSize = 20,
    wrap = TRUE,
    # filterable = TRUE,
    defaultColDef = colDef(
      style = function(value) {
        if (!is.numeric(value)) return()
        # normalized <- (value - min(nottem)) / (max(nottem) - min(nottem))
        # good_color(0.8)
        color <- good_color(value)
        list(background = color,fontFamily = "Helvetica", fontSize = "14px")
        },
      # format = colFormat(digits = 1),
      # fontSize = "15px",
      headerStyle = list(background = "whitesmoke",color="black", align = "center"),
      align = "center",
      minWidth = 120
      ),
    columns = list(
      name     = colDef(name = "Card",minWidth = 120, style = list( fontWeight = "bold", fontFamily = "Helvetica", fontSize = "13px" ), align = "left" ),
      playrate = colDef(name = "PlayRate", format = colFormat(percent = TRUE,digits = 1) ),
      `3`      = colDef(name = "3",format = colFormat(percent = TRUE,digits = 1) ),
      `2`      = colDef(name = "2",format = colFormat(percent = TRUE,digits = 1) ),
      `1`      = colDef(name = "1",format = colFormat(percent = TRUE,digits = 1) )
      ),
    columnGroups = list(
      colGroup(name = glue::glue("{deck.of.week}"), columns = c("name"), headerStyle = list(background = "whitesmoke",color="black", align = "center") ),
      colGroup(name = glue::glue("Playrate (N: {length(SubDeck_deck_code)})"), columns = c("playrate","3","2","1"),headerStyle = list(background = "whitesmoke",color="black", align = "center"))
      )
    )
```
:::

::: {.panel}
## Deckcodes

```{r}
deckCodeTbl  <- LoR.Melt.Matches.RMD |>
  # filter( playerDeck == deck.of.week ) |>
  filter( deck_code %in% whichDecks ) |>
  mutate( server = str_to_title(server) ) |>
  group_by(server,playerDeck,deck_code ) |>
  summarise( n = n() ) |>
  slice_max(n, n = 2,with_ties = F) |>
  ungroup() |>
  mutate( deck_code = glue::glue("<a href='https://runeterra.ar/decks/code/{deck_code}'>{deck_code}</a>") )
```

```{r print-deck-code-tbl, layout="l-page"}
#' Contained in lor_costants
# urlruneterraAR <- "https://runeterra.ar/"
# urlrank <- "Main/Lor/Rank/"
# urldeck <- "decks/code/"

deckCodeTbl |>
  reactable(
    groupBy = c("playerDeck","server"),
    bordered = TRUE,
    highlight = TRUE,
    searchable = TRUE,
    compact = TRUE, # compact the table height
    fullWidth = T, # don't fill the page
    # defaultPageSize = 20,
    pagination = FALSE,
    wrap = TRUE,
    # filterable = TRUE,
    defaultColDef = colDef(
      style = list(fontFamily = "Helvetica", fontSize = "12px"),
      align = "center",
      minWidth = 120,
      ),
    columns = list(
      deck_code = colDef(name = "DeckCode", minWidth = 750, style = list( fontSize = 9 ), html = TRUE ),
      # deck_code = colDef(name = "DeckCode", cell = function(value, index) {
      #   # Render as a link
      #   url <- glue::glue("{urlruneterraAR}{urldeck}{value}")
      #   htmltools::tags$a(href = url, target = "_blank", as.character(value))
      #   },minWidth = 400, style = list(fontsize = 11) ),
      server = colDef(name = "Server",minWidth = 150),
      playerDeck = colDef(name = "Archetype",minWidth = 150),
      n     = colDef(name = "Games" )
      ),
    rowStyle = JS("function(rowInfo) {
                  if (rowInfo.level > 0) {
                  return { background: 'whitesmoke', borderLeft: '2px solid #ffa62d' }
                  } else {
                  return { borderLeft: '2px solid whitesmoke' }
                  }
                  }"),
    defaultExpanded = T
    )
```
:::

> How to read the table: <br> - Play rate: How often a card is included in this class of decks / the table is order by this column. <br> - 3/2/1 is the relative and absolute frequency of the number of copies in the decks that plays them <br> - Frequencies from 50% to 100% are colored from shades of green to white to identify more easily the highest values
:::

<!-- Close Deck Structure panelset -->
:::

# LoR-Meta Index (LMI)

-   **Tier0** with LMI \>= 97.5

-   **Tier1** with LMI $\in$ [85,97.5)

-   **Tier2** with LMI $\in$ [60,85)

-   **Tier3 or lower** with LMI \< 60

> The LMI [^2] [^3] is an Index I developed to measure the performance of decks in the metagame. For those who are familiar with basic statistical concept I wrote a document to explain the theory behind it: , it's very similar to [vicioussyndicate](https://www.vicioussyndicate.com) (vS) Meta Score from their data reaper report. The score of each deck ***is not*** just their "strength", it takes in consideration both play rates and win rates that's why I prefer to say it measure the "performance". The values range from 0 to 100 and the higher the value, the higher is the performance.

::: {.l-page}
::::: {.panelset}
::: {.panel}
## Static version

```{r lmi}
LMI.DT <- WR.DT |>
  filter( nGames > 200 ) |>
  # filter( playrate > 0.01 ) |>
  mutate( PR_ind    = scale_quantile(playrate) ) |>
  mutate( WR_ind    = scale_quantile(WR) ) |>
  rowwise() |>
  mutate( LMI = harm.mean(c_across(ends_with("ind")) ),
          tooltip = glue("Deck {playerDeck}
                         LMI {round(LMI*100,1)}
                         WinRate {scales::percent(WR,accuracy = 0.1)}
                         PlayRate {scales::percent(playrate,accuracy = 0.1)}") ) |>
  ungroup() |> 
  mutate(tier = case_when( 
     LMI >= 0.975 ~ "Tier0",
     0.85 <= LMI & LMI < 0.975 ~ "Tier1",
     0.60 <= LMI & LMI < 0.85 ~ "Tier2",
     LMI < 0.60 ~ "Tier3 or lower"
    ) 
  )

# LMI = map2_dbl(.x =PR_ind,.y =WR_ind, ~harm.mean(c(.x,.y) )  ),
#     tooltip = pmap( list(playerDeck,LMI,WR,playrate), ~glue("Deck {..1}
#                                                             LMI {round(..2*100,1)}
#                                                             WinRate {scales::percent(..3,accuracy = 0.1)}
#                                                             PlayRate {scales::percent(..4,accuracy = 0.1)}"))
```

```{r lmi-png, fig.height=8, fig.width=12}
LMI.plot <- LMI.DT |>
  slice_max(LMI,n = 15,with_ties = F) |>
  mutate( tooltip = glue("{playerDeck}
                         LMI {round(LMI*100,1)}
                         WinRate {scales::percent(WR,accuracy = 0.1)}
                         PlayRate {scales::percent(playrate,accuracy = 0.1)}
                         #Games {nGames}") ) |>
  mutate_if(is.numeric, funs(round(., 4)) ) |>
  mutate( LMI = LMI*100 ) |>
  ungroup() |>
  ggplot( aes(x=WR_ind, y=PR_ind, size = LMI, color = tier, text=tooltip)) +
  geom_point(alpha=0.6) +
  scale_size(range = c(1, 15), name="LMI") +
  theme_539() +
  geom_label_repel( 
    aes(label=tooltip),
    family = "Roboto",
    color = "grey40",
    fontface = "bold",
    size = 3,
    fill = NA,
    vjust = "outward",
    label.padding = unit(0.8, "mm"),
    label.size = unit(0.25, "mm"),
    label.r = unit(0.5, "mm"),
    min.segment.length = 0,
    segment.linetype = 2,
    segment.color = 'grey50'
  ) + 
  guides(colour = guide_legend(override.aes = list(size=10)),
         size = FALSE ) +
  theme( legend.position = "top",
         legend.background = element_blank(),
         legend.title = element_text(size=9, lineheight = 1.3),
         legend.justification = "right"
         ) +
  labs(
    title = "Top15 Deck Peformances",
    subtitle = "Deck's Peformances by highest value of LMI",
    x = "Win Index",
    y = "Freq Index",
    caption = element_text(glue::glue("{params$patch}
                                      Ranked games from {params$start} UTC to {params$end} UTC
                                      Metadata of games collected with RiotGames API
                                      LMI computed with the basic version which use PlayRate and WinRate. Additional Decks performances in the metareport"))
  )

LMI.plot

ggsave(glue::glue("./images/meta-report/{params$ind}-LMI.png"))
```
:::

::: {.panel}
## Interactive Version

```{r lmi-plotly}
fig <- LMI.DT |>
  slice_max(LMI,n = 50,with_ties = F) %>%
  mutate_if(is.numeric, funs(round(., 4)) ) |>
  ggplot( aes(x=WR_ind, y=PR_ind, size = LMI^2, color = tier, text=tooltip)) +
  geom_point(alpha=0.6) +
  scale_size(range = c(1, 15), name="LMI") + 
  theme_minimal() +
  labs( 
    x = "WR Index",
    y = "Freq Index",
    title = "LoR-Meta Index (LMI)\nhovering over a circle will display a deck values",
    caption = "top50 highest LMI values, with a min amount of 200 games."
    )

ggplotly(fig, tooltip="text")
```
:::
:::::
:::

[^2]: [LMI - Early Theory](https://llorr-stats.com/analysis/lmi/)

[^3]: [LMI - Adding a Ban Index](https://www.llorr-stats.com/analysis/lmi-02-tentative-expansion/)

# Win Marathons Leaders

Top3 Players (or more in case of ties) from each server that had the highest amount of consecutive wins with the same archetype. The provided deckcode is the one played in the last win found.

```{r win-marathon, layout="l-page"}
gtWinning <- setDT(LoR.Melt.Matches.RMD)[order(game_start_time_utc)][, counter := rowid(rleid(game_outcome)), by=c("playerID","playerDeck") ][ game_outcome == "win" ] |>
  # filter( server=="asia" & playerID == "Ryo 6192" & playerDeck ==	"Senna / Veigar (BC/SI)" )
  group_by(playerID) |>
  slice_max(counter,n=1) |>
  ungroup() |>
  group_by(server) |>
  slice_max(counter,n=3) |>
  left_join(LoR.Account.RMD[ ,c("RiotID","gameName") ]|>distinct(RiotID,.keep_all = T), by =c("playerID"="RiotID") ) |>
  mutate( server = str_to_title(server) ) |>
  group_by(server) |>
  mutate( ranking = rank(-counter,ties.method = "min" ) ) |>
  ungroup() |>
  mutate(
    counter_icon = dplyr::case_when(
      ranking == 1 ~ "trophy",
      ranking == 2 ~ "medal",
      ranking == 3 ~ "minus",
      TRUE ~ "other"
      ),
    icon = map(.x = counter_icon, ~fontawesome::fa(.x)),
    icon = map2(.x = counter, .y = icon, ~md(glue::glue("{.x} {.y}")) ),
    
    link = sprintf('<div><span style ="color:grey50;font-size:10px"><p><a href = "%s">%s</a></span></div>', glue::glue("{urlruneterraAR}{urldeck}{deck_code}"), deck_code),
    link = map(link, gt::html)
    # style ="font-weight:bold;color:grey;font-size:10px
  ) |>
  select(server,gameName,icon,playerDeck,link) |>
  gt(groupname_col = "server") |>
  cols_align(
    align = "left",
    columns = everything()
  ) |>
  gtExtras::gt_theme_538() |>
  tab_header(
    title = md(glue::glue("{fontawesome::fa('star')} Top3 Biggest Win Streak by Server {fontawesome::fa('star')}")),
    subtitle = "Cumulative wins with the same Archetype"
  ) |> 
  cols_width(vars(icon) ~ px(30)) %>% 
  #Original changes as above.
  cols_label(
    gameName = "Player",
    icon = "Result",
    playerDeck = "Archetype",
    link = "Deck Code"
  ) |>
  tab_source_note(
    source_note = glue("Games from all Master are collected each hour adding up to the last 20 matches.
                       Unlikely but possible to miss games in case of high frequency games.
                       Metadata of games collected with RiotGames API")
    ) |>
  opt_all_caps() |>
  opt_table_font(
    font = list(
      google_font("Chivo"),
      default_fonts()
    )
  ) |>
  cols_width(vars(icon) ~ px(150),
             vars(link) ~ px(400)) |>
  tab_options(
    # table.font.color = "black",
    # table.font.color.light = "black",
    column_labels.border.top.width = px(3),
    column_labels.border.top.color = "white",
    table.border.top.color = "white",
    table.border.bottom.color = "white",
    data_row.padding = px(3),
    source_notes.font.size = 12,
    heading.align = "left",
    table.font.size = px(12L),
    # Adjust grouped rows to make them stand out
    row_group.background.color = "grey"
    ) |>
  tab_style(
    style = cell_text(size = "small"),
    locations = cells_body(
      columns = vars(
        "playerDeck","link"
        )
      )
    )

gtWinning |>
 tab_options(
    table.background.color = "whitesmoke",
    table.font.color = "black",
    table.font.color.light = "black"
   )

gtsave(gtWinning, glue::glue("./images/meta-report/{params$ind}-topWin.png")   ) |> invisible()
```

# Cards Presence

```{r process-UniqueCards}
Card.Subset <- LoR.Melt.Matches.RMD |>
  select( starts_with( "Card" ) )

allCards            <- unlist(apply(Card.Subset, 1, unique),use.names = F)
TableAllCards       <- table(allCards)
RegionShortAllCards <- str_sub(names(TableAllCards),3,4)
TableCardsDT        <- data.table(TableAllCards)
setnames(TableCardsDT,old = "allCards",new = "card")

TableCardsDT[ ,region    := str_sub(card,3,4) ]
TableCardsDT[ ,regionID  := fct_recode(region,!!!recodeRegPosition) ]
TableCardsDT[ ,nGamesReg := Region.Freq$n[as.numeric(as.character(regionID))] ]
# Region.Freq contain the frequencies of appearence of each region in the decks
TableCardsDT[ ,p.byReg   := round(N/nGamesReg,3) ]
# Frequence of a card appearing in a deck within its own region

TableCardsDT[ ,card    := str_replace_all(card, set_names(LoR.Card$name, LoR.Card$cardCode)) ]
TableCardsDT[ ,region  := str_replace_all(region, set_names(data_regions$nameRef, data_regions$abbreviation)) ]
```

::: {.l-page}
::::: {.panelset}
::: {.panel}

## Play Rate {.panel-name}

It seems that not even Twin Disciple can beat Sharsight

```{r print-CardsTable-1}
MostPlayed <- TableCardsDT |>
  arrange(desc(p.byReg)) |>
  rename_all(~c("Card","# Decks with that card ","Region","RegionID","Games of X Region","Play Rate")) |>
  select(c(1,3,6,2)) |>
  datatable(rownames = FALSE) |>
  formatStyle('Card', fontWeight = 'bold') |>
  formatStyle('Play Rate', fontWeight = 'bold') |>
  formatStyle(
    'Region',
    target = 'row',
    backgroundColor = styleEqual(data_regions$nameRef, data_regions$colorRegion)
  ) |>
  formatPercentage('Play Rate', 1)
  # formatStyle('Card',  color = 'red', backgroundColor = 'orange', fontWeight = 'bold')

MostPlayed
```
:::

::: {.panel}
## Top 3 Play Rates by Region {.panel-name}

```{r print-CardsTable-3}
TopPlayed.PbyReg <- TableCardsDT |>
  group_by(region) |>
  arrange(desc(p.byReg)) |>
  top_n(3) |>
  arrange(region) |>
  rename_all(~c("Card","N","Region","RegionID","Games of X Region","Play Rate")) |>
  select(c(1,3,6,2,5)) |>
  datatable(rownames = FALSE, options = list(
    searching = FALSE,
    lengthChange = FALSE,
    pageLength = 4*9,
    info = FALSE)) |>
  formatStyle('Card', fontWeight = 'bold') |>
  formatStyle('Play Rate', fontWeight = 'bold') |>
  formatStyle(
    'Region',
    target = 'row',
    backgroundColor = styleEqual(data_regions$nameRef, data_regions$colorRegion)
  ) |>
  formatPercentage('Play Rate', 1)

TopPlayed.PbyReg
```
:::

::: {.panel}
## Forgotten Cards {.panel-name}

Cards that couldn't find place even in a meme deck.

```{r missingCards}
missingCards <- LoR.Card$cardCode[LoR.Card$cardCode %!in% names(TableAllCards)]

data.table(
  Card = LoR.Card$name[LoR.Card$cardCode %in% missingCards],
  Code = missingCards,
  Region = str_sub(missingCards,3,4) ) |>
  group_by(Region) |>
  mutate(n = row_number(),
         l = n() ) |>
  ungroup() |>
  arrange(desc(l)) |>
  select(-l,-Code) |>
  pivot_wider( names_from = n, values_from = Card  ) |>
  mutate(across(everything(), .fns = ~replace_na(.,""))) |>
  t() |>
  as.data.table() |>
  {\(x) rename_all(x, ~unlist(x[1,],use.names = F ) )  }() |>
  slice(-1) |>
  # gt() |>
  # gtExtras::gt_theme_538()
  reactable(
    bordered = TRUE,
    highlight = TRUE,
    wrap = T,
    sortable = F,
    searchable = TRUE,
    defaultPageSize = 15,
    style = list(fontFamily = "Chivo", fontSize = "12px"),
    # minRows = 10,
    # columns = list(
    #   BC = colDef( style = list ( background = data_regions$colorRegion[1], fontWeight = "bold", color  = "#404040" ) ),
    #   BW = colDef( style = list ( background = data_regions$colorRegion[2], fontWeight = "bold", color  = "#404040" ) ),
    #   DE = colDef( style = list ( background = data_regions$colorRegion[3], fontWeight = "bold", color  = "#404040" ) ),
    #   FR = colDef( style = list ( background = data_regions$colorRegion[4], fontWeight = "bold", color  = "#404040" ) ),
    #   IO = colDef( style = list ( background = data_regions$colorRegion[5], fontWeight = "bold", color  = "#404040" ) ),
    #   MT = colDef( style = list ( background = data_regions$colorRegion[6], fontWeight = "bold", color  = "white" ) ),
    #   NX = colDef( style = list ( background = data_regions$colorRegion[7], fontWeight = "bold", color  = "#404040" ) ),
    #   PZ = colDef( style = list ( background = data_regions$colorRegion[8], fontWeight = "bold", color  = "#404040" ) ),
    #   SI = colDef( style = list ( background = data_regions$colorRegion[9], fontWeight = "bold", color  = "#E5E5E5" ) ), #grey90
    #   SH = colDef( style = list ( background = data_regions$colorRegion[10], fontWeight = "bold", color = "#404040" ) )
    # ),
    defaultColDef = colDef( minWidth = 125 ) 
  )
```
:::
:::::
:::

<!-- Close Card Presence panelset -->

```{r twitter-meta, echo = FALSE}
metathis::meta() |>
  metathis::meta_description(
    glue::glue("{params$patch} - {params$description}")
  ) |> 
  metathis::meta_viewport() |> 
  metathis::meta_social(
    title = params$title,
    url = "https://www.llorr-stats.com/",
    image = params$cardlurl,
    og_type = "website",
    og_author = "Legna",
    twitter_card_type = "summary",
    twitter_creator = "@Maou_Legna"
  )
```

# Legal bla bla

This content was created under Riot Games 'Legal Jibber Jabber' policy using assets owned by Riot Games. Riot Games does not endorse or sponsor this project.
