---
params:
  ind: "027"
  patch: "Patch 2.17 - Week 1"
  title: "THE META REPORT NAME IS TOO LONG, TOO DAMN LONG (n°27)"
  description: "Patch next week. So that Sion won't dominate anymore... So that Sion won't dominate anymore, right?"
  cardlurl: "https://dd.b.pvp.net/latest/set5/en_us/img/cards/05BC116.png"
  prev:  "2021-09-29 21:00:00" #UTC tz / 'current' previous week start
  start: "2021-10-06 21:00:00" #UTC tz / 'current' week start
  end:   "2021-10-13 21:00:00" #UTC tz / 'current' week end
  skip:  3000000  # ~ Patch 2.16

title: | 
  `r params$title`
description: |
  `r params$patch` - `r params$description`
base_url: https://www.llorr-stats.com
preview: |
  `r params$cardlurl`
author:
  - name: Valentino (Legna) Vazzoler
date: 10-06-2021
output:
 distill::distill_article:
    toc: true
    toc_float: true
    toc_depth: 3
    self_contained: false
citation: false
draft: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE,
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  comment = NA,
  R.options = list(width = 140,
                   digits.secs=6),
  dev.args = list(bg = 'transparent'), # make graphics with transparent background
  fig.align = 'center',
  fig.width=12,
  fig.height=8,
  engine.path = list(
    python = 'C:/anaconda/'   # -> use_python("C:/anaconda/")
  ),
  #'distill options
  layout="l-body-outset",
  preview=FALSE
)

#' R Option
options(scipen = 999)
source(file.path("C:","LlorR","scripts","lor_main.R" ))
xaringanExtra::use_panelset()
```

```{r panelset-style}
xaringanExtra::style_panelset_tabs(
  font_family = "Helvetica",
  active_foreground = "white",
  hover_foreground = "black",
  hover_border_color = "black",
  active_background = "#007fff"
  )
```

```{r raw-data}
# skip.dt <-fread(file.path("C:","LlorR","data","raw","skip_row.csv")  )
# skip.dt

#' load gameDT
#'############
file.DT <- file.path("C:","LlorR","data","raw","LoR_MatchDT.csv")
header        <- fread(file.DT, header = FALSE, na.strings = c("",NA), nrows = 1, stringsAsFactors = FALSE)
LoR.Match.RMD <- fread(file.DT, header = FALSE, na.strings = c("",NA), skip = params$skip )
colnames(LoR.Match.RMD) <- unlist(header,use.names = F)

#' load Account
#'#############
LoR.Account.RMD <- fread(file.path("C:","LlorR","data","raw","LoR_ACCOUNT.csv"),
                         header=T, na.strings = c("",NA), encoding = 'UTF-8') |>
  mutate( RiotID = glue("{gameName}#{tagLine}") )

#' load DeckDT
#'############
LoR.Deck        <- fread(file.path("C:","LlorR","data","raw","LoR_DECK.csv"),na.strings = c("",NA))
```

```{r archetype-fix}
#' Limit the Deck DT to make the fixes much faster
deck_filter <- LoR.Match.RMD |>
  #' Base filters
  filter( game_type=="Ranked" ) |>
  filter( game_start_time_utc > as.POSIXct(params$start, tz = "UTC") ) |>
  select(deck_code_1,deck_code_2) |>
  pivot_longer( cols = contains("deck_code"),values_to = "decks" ) |>
  filter(decks!="") |>
  distinct(decks)

LoR.Deck <- LoR.Deck[deck_code %in% deck_filter$decks]

#' Archetype-Fix
#'##############
source(file.path("C:","LlorR","scripts","functions","lor_archetype.R"))
```

```{r prepare-data}
#' Melt tbl
#'#########
LoR.Melt.Matches.RMD <- LoR.Match.RMD |>
  filter( game_type=="Ranked" ) |>
  filter( game_start_time_utc > as.POSIXct(params$start, tz = "UTC") ) |>
  select( -ends_with("_3"),-ends_with("_4")  ) |>
  left_join(LoR.Deck[,.(deck_code,playerDeck_1=archetype)],  by=c("deck_code_1"="deck_code")) |>
  left_join(LoR.Deck[,.(deck_code,opponentDeck_1=archetype)],by=c("deck_code_2"="deck_code")) |>
  rename( playerPuuid_1 = puuid_1, playerPuuid_2 = puuid_2 ) |>
  mutate( playerDeck_2 = opponentDeck_1, opponentDeck_2 = playerDeck_1, opponentPuuid_1 = playerPuuid_2, opponentPuuid_2 = playerPuuid_1 ) |>
  pivot_longer(cols = c(ends_with("_1"),ends_with("_2")),
               names_to = c(".value"),
               names_pattern = "(.*)_[0-9]"
               ) |>
  #' finish 'process' data
  left_join(LoR.Account.RMD[,.(puuid,playerID=RiotID)]   ,by=c("playerPuuid"="puuid")) |>
  left_join(LoR.Account.RMD[,.(puuid,opponentID=RiotID)] ,by=c("opponentPuuid"="puuid")) |>
  left_join(LoR.Deck |> select(!archetype),by=c("deck_code","factions"))
```

# Data

```{r account-info}
masterEU   <- LoR.Account.RMD |> filter(activeShard=="europe"   & master=="master") |> distinct(gameName,tagLine) |> count() |> pull()
masterNA   <- LoR.Account.RMD |> filter(activeShard=="americas" & master=="master") |> distinct(gameName,tagLine) |> count() |> pull()
masterASIA <- LoR.Account.RMD |> filter(activeShard=="asia"     & master=="master") |> distinct(gameName,tagLine) |> count() |> pull()

namesList.EU.RMD   <- lor_leaderboard("europe")$name
namesList.NA.RMD   <- lor_leaderboard("americas")$name
namesList.ASIA.RMD <- lor_leaderboard("asia")$name
```

```{r nGames-data}
minrow_live <- min(which(LoR.Match.RMD[,game_start_time_utc >= as.POSIXct(params$start)]))
maxrow_live <- max(which(LoR.Match.RMD[,game_start_time_utc  < as.POSIXct(params$end)]  ))

max_time <- LoR.Match.RMD |>
  filter( game_start_time_utc >= as.POSIXct(params$start, tz = "UTC") & game_start_time_utc < as.POSIXct(params$end, tz = "UTC") & game_type=="Ranked") |>
  slice_max(game_start_time_utc) |> 
  pull(game_start_time_utc) |>
  format(format = "%Y-%m-%d %H:%M:%S")

nGames <- LoR.Match.RMD |>
  filter( game_start_time_utc >= as.POSIXct(params$start, tz = "UTC") & game_start_time_utc < as.POSIXct(params$end, tz = "UTC") & game_type=="Ranked") |>
  tabyl(game_type) |>
  filter( game_type=="Ranked" ) |>
  pull(n)
```

Number of (Ranked) matches analyzed **`r format(nGames,scientific = F)`** or **`r format(nGames*2,scientific = F)`** games.

Last Update: `r format(Sys.time(),format = "%Y-%m-%d %H:%M")` 

`r kableExtra::text_spec("Note :", color = "red")` following my recent analysis the following decks:

* Akshan / Sivir (IO/SH)

* Sivir / Zed

* Akshan / Sivir / Zed

Have been aggregated into a single archetype: "ASZ - Sivir Ionia"

In addition a quick fix to account for the Rubin-baits (burn decks that pretend to be other archetypes) decks have been applied and they are called:

* RubinBait - Draven / Ezreal

* RubinBait - Draven / Sion

* RubinBait - Caitlyn / Draven - not make from Rubin but same logic

```{r table-nGames-data, layout="l-body"}
tbl1 <- LoR.Match.RMD |>
  #' Stay only 'among' the row with the games in the time-frame I want
  ####################################################################
  slice(minrow_live:maxrow_live) |>
  #' Extrapolate Friendly and 'to Scrap' matches
  ##############################################
  mutate( game_type = case_when(
    status==404   ~ "Friendly",
    is.na(status) ~ "to Scrap",
    TRUE ~ as.character(game_type)
    )) |>
  #' Give to the new game_types a game_start_time_utc among the timeframe on interest
  #' so it can be used a filter without worrying about other parameter like status and so on
  ##########################################################################################
  mutate( game_start_time_utc = replace( game_start_time_utc, game_type %in% c("Friendly","to Scrap"),  as.POSIXct(params$start, tz = "UTC")+days(3) ) ) |>
  filter( game_start_time_utc >= as.POSIXct(params$start, tz = "UTC") & game_start_time_utc < as.POSIXct(params$end, tz = "UTC") ) |>
  mutate( game_type = fct_other(factor(game_type),keep = c("Ranked","Friendly","to Scrap")) |> fct_infreq() ) |>
  select(Status=game_type,Server=server) |>
  #' Create tbl
  #############
  tbl_summary()


tbl2 <- LoR.Match.RMD |>
  filter( game_start_time_utc >= as.POSIXct(params$start, tz = "UTC") & game_start_time_utc < as.POSIXct(params$end, tz = "UTC") ) |>
  filter( game_type == "Ranked" ) |>
  select(Server=server) |>
  tbl_summary()
  
nGames_tbl <- tbl_merge( 
    tbls = list(tbl1, tbl2),
    tab_spanner = c("**All Games**", "**Ranked**")
  ) |>
  modify_footnote(
    update = stat_0_1 ~
      md(glue::glue("Metadata from Friendly Matches (that aren't Bo3) is not recoverable, \n the value may not be perfect since I lack the starting time of the game. The amount of Games to still scrap is also an estimation based on the 'position' of the game" ))
  ) |>
  # modify_header(label ~ "**Variable**") |>
  bold_labels() |>
  as_gt() |>
  tab_header(
    title = glue::glue("{params$patch} - by the Numbers")
  ) |>
  tab_footnote(
    footnote = md(glue::glue("Max datetime recovered: {max_time} UTC from {params$start} to {params$end} UTC" )),
    locations = cells_title(groups = c("subtitle"))
    ) |>
  tab_footnote(
    footnote = md(glue::glue("EU Master playerDecks in the ladder: {length(namesList.EU.RMD)} while number of possible Master playerDecks recovered is: {masterEU} \n
                              NA Master playerDecks in the ladder: {length(namesList.NA.RMD)} while number of possible Master playerDecks recovered is: {masterNA} \n
                              ASIA Master playerDecks in the ladder: {length(namesList.ASIA.RMD)} while number of possible Master playerDecks recovered is: {masterASIA}" )),
    locations = cells_title(groups = c("subtitle"))
  ) |>
  tab_options(data_row.padding = px(1.2))
  
nGames_tbl |>
 tab_options(
    table.background.color = "transparent",
    table.font.color = "black",
    table.font.color.light = "black"
   )

# gtsave(nGames_tbl,"images/rep_data.png")
```

# Regions

## Play Rate
::: l-body-outset

```{r process-tableFreq}
Region.Freq <- LoR.Melt.Matches.RMD |>
  select(factions) |>
  separate_rows(factions,sep=",") |>
  tabyl(factions,show_na=F) |>
  tibble() |> 
  rename_all(~c("region","n","freq")) |>
  mutate( region = map_chr(.x = region, ~str_remove_all(.x, paste(c("_Name","faction_", ""), collapse = "|") ) ) ) |>
  add_column(icon = data_regions$iconsPath)

Region.Freq.Server <- LoR.Melt.Matches.RMD |>
  select(server,factions) |>
  separate_rows(factions,sep=",") |>
  tabyl(factions,server, show_na = F) |>
  adorn_percentages("col") |>
  mutate( region = map_chr(.x = factions, ~str_remove_all(.x, paste(c("_Name","faction_", ""), collapse = "|") ) ) )

Region.Freq <- full_join(Region.Freq,Region.Freq.Server,by="region")
```

::::: {.panelset}
::: {.panel}

### Plot {.panel-name}

```{r plot-Region}
# remotes::install_github("olihawkins/pilot")
# library(pilot)

sxLabel_card <- format(Region.Freq$freq*100,2)
dxLabel_card <- format(Region.Freq$freq*100,2)
sxLabel_card <- ifelse(as.numeric(sxLabel_card) > 4,  sxLabel_card , "") |> as.numeric() |> {\(x) scales::number(x, accuracy = 0.01)}()
dxLabel_card <- ifelse(as.numeric(dxLabel_card) <= 4, dxLabel_card , "") |> as.numeric() |> {\(x) scales::number(x, accuracy = 0.01)}()

RegionByRegion <- Region.Freq |>
  ggplot(aes(x = reorder(region, freq), y = freq)) +
  geom_bar(stat="identity") +
  geom_bar_pattern(
    aes(
      pattern_filename = region,
    ),
    stat            = 'identity',
    pattern         = 'image',
    pattern_type    = 'none',
    fill            = data_regions$colorRegion,
    colour          = 'black',
    pattern_scale   = -2,
    pattern_filter  = 'point',
    pattern_gravity = 'east'
  ) +
  # theme_void() +
  labs(
    x = "Region",
    y = "Play Rate",
    title = "Regions Play Rate",
    subtitle = "number of times a region is included in a deck",
    caption = glue::glue("{params$patch}
                         Ranked games from {params$start} UTC to {params$end} UTC.
                         Metadata of games collected with RiotGames API")
    ) +
  annotate(
    geom = 'text', 
    color = "grey50",
    x = 1.0, 
    y = 0.15, 
    hjust = 0.5,
    label = glue::glue('n = {nGames}\nGini Index = {round(DescTools::Gini(Region.Freq$freq,na.rm = T),3)}'), 
    fontface = 'bold') +
  coord_flip() +
  scale_pattern_filename_discrete(choices = data_regions$iconsPath ) +
  scale_pattern_discrete(guide = guide_legend(nrow = 1)) +
  scale_fill_manual("legend", values = data_regions$colorRegion) +
  scale_y_continuous(limits = c(0, round(max(Region.Freq$freq+0.04 ),3) ),
                     breaks = seq(0,0.5,0.04),
                     expand = c(-0.001,0.02),
                     labels = scales::percent_format(accuracy = 1) ) +
  guides(fill = "none") +
  #' Adding the text of the frequencies
  geom_text(aes(label = sxLabel_card), hjust = 2.5, size = 5,position = position_dodge(width = 1)) +
  geom_text(aes(label = dxLabel_card), hjust = -0.5, size = 5,position = position_dodge(width = 1)) +
  theme_539() +
  theme( 
    legend.position = "none",
    axis.text = element_text(face = "bold", color = "grey50"),
    panel.grid.major.y = element_blank()
    )
  
RegionByRegion
```

The Gini Index is a measure of heterogeneity so, in this case and in simpler terms, how much the play rates are similar. The Index goes (when normalized like here) $in$ [0,1] and it's equal to 1 when there's a single value with 100% play rate or 0 when all play rates are equal. Of course a Gini Index of 1 needs to be avoided but it's not like the aim should be 0. As said, it's just to add some additional tools.

:::

::: {.panel}
### Table {.panel-name}

```{r print-tableFreq-gt}
Region.Freq.tbl <- Region.Freq |>
  select(-n,-icon,-factions) |>
  arrange(desc(freq)) |>
  gt( ) |>
  tab_header(
    title = "Region Play Rate",
    subtitle = "Relative Frequencies by Inclusion Rate of a Region"
  ) |>
  tab_spanner(
    label = "Shard",
    columns = c(americas, asia, europe)
  ) |>
  fmt_percent(
    columns = c(2:5),
    decimals = 2
  ) |>
  cols_align(
    align = "left",
    columns = 1
  ) |>
  cols_align(
    align = "center",
    columns = c(2:5)
  ) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = 1,
    )
  ) |>
  cols_label(
    region   = md("**Region**"),
    freq     = md("**Freq**"),
    americas = md("**America**"),
    asia     = md("**Asia**"),
    europe   = md("**Europe**")
  ) |>
   tab_options(
    table.background.color = "transparent",
    table.font.color = "black",
    table.font.color.light = "black"
   ) |>
  tab_source_note(
    source_note = glue::glue("{params$patch}
                             Ranked games from {params$start} UTC to {params$end} UTC.
                             Metadata of games collected with RiotGames API")
    )

Region.Freq.tbl

# Region.Freq.tbl <- gtsave(
#     "images/reg_freq.png",
# )
```
:::
:::::
<!-- Close Region 1 panelset -->
:::

## Play Rate by number of Cards

`r kableExtra::text_spec("Note:", color = "red")` currently all dual region cards have only their main region as possible value assigned. The same problem also apply to the card's inclusion rates, with Lulu being the most notable case affected by this.

::: l-body-outset

```{r process-tableFreq_byCard}
Card.Subset <- LoR.Melt.Matches.RMD |>
  select( starts_with( "Card" ) )

Regions.Freq.byCards <- LoR.Melt.Matches.RMD |>
  select( starts_with( "Card") ) %>%
  map_df(.,~str_sub(.x, start=3,end=4) ) %>%
  mutate_all(~fct_recode(.,!!!recodeRegShort)) |>
  unlist(use.names = FALSE) |> 
  tabyl(show_na = F) |> 
  rename_all(~c("region","n","freq")) |> 
  mutate(region := as.character(region))
  
setorderv(Regions.Freq.byCards, c("region"), c(1))

# Regions.Freq.byCards <- as.tibble(Regions.Freq.byCards)
Regions.Freq.byCards$freq <- round(Regions.Freq.byCards$freq,4)
Regions.Freq.byCards$icon <- data_regions$iconsPath

Regions.Freq.byCards.Server <- LoR.Melt.Matches.RMD |>
  select( starts_with( "Card") ) %>%
  map_df(.,~str_sub(.x, start=3,end=4) ) %>%
  mutate_all(~fct_recode(.,!!!recodeRegShort)) |>
  add_column(server = LoR.Melt.Matches.RMD$server ) |>
  melt(id.var=c("server")) |>
  select(value,server) |>
  tabyl(value,server, show_na = F) |>
  adorn_percentages("col")

Card.tableByRegPlot <- LoR.Melt.Matches.RMD |>
  select( starts_with( "Card") ) %>%
  map_df(.,~str_sub(.x, start=3,end=4) ) %>%
  mutate_all(~fct_recode(.,!!!recodeRegShort)) |>
  add_column(server = LoR.Melt.Matches.RMD$server ) |>
  melt(id.var=c("server")) |>
  select(value,server) |> table() %>% prop.table(.,margin = 2) |> as.data.table()
```

::::: {.panelset}
::: {.panel}
### Plot {.panel-name}

```{r plotRegion_byCards}
sxLabel_card <- format(Regions.Freq.byCards$freq*100,2)
dxLabel_card <- format(Regions.Freq.byCards$freq*100,2)
sxLabel_card <- ifelse(as.numeric(sxLabel_card) > 4,  sxLabel_card , "") |> as.numeric() |> {\(x) scales::number(x, accuracy = 0.01)}()
dxLabel_card <- ifelse(as.numeric(dxLabel_card) <= 4, dxLabel_card , "") |> as.numeric() |> {\(x) scales::number(x, accuracy = 0.01)}()

RegionByCards <- Regions.Freq.byCards |>
  ggplot(aes(x = reorder(region, freq), y = freq)) +
  geom_bar_pattern(
    aes(
      pattern_filename = region,
    ),
    stat            = 'identity',
    pattern         = 'image',
    pattern_type    = 'none',
    fill            = data_regions$colorRegion,
    colour          = 'black',
    pattern_scale   = -2,
    pattern_filter  = 'point',
    pattern_gravity = 'east'
  ) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(
    x = "Region",
    y = "Play Rate",
    title = "Regions Play Rate",
    subtitle = "number of times a card within a region is included in a deck",
    caption = glue::glue("{params$patch}
                         Ranked games from {params$start} UTC to {params$end} UTC.
                         Metadata of games collected with RiotGames API")
  ) +
  annotate(
    geom = 'text',
    color = "grey50",
    x = 1.0, 
    y = 0.15, 
    hjust = 0.5,
    label = glue::glue('n = {nGames}\nGini Index = {round(DescTools::Gini(Regions.Freq.byCards$freq,na.rm = T),3)}'), 
    fontface = 'bold'
    ) +
  coord_flip() +

  scale_pattern_filename_discrete(choices = data_regions$iconsPath) +
  scale_pattern_discrete(guide = guide_legend(nrow = 1)) +
  scale_fill_manual("legend", values = list.levels$data_regions$colorRegion) +
  # nome of the table
  scale_y_continuous(limits = c(0, round(max(Regions.Freq.byCards$freq+0.04 ),3) ),
                     breaks = seq(0,0.5,0.04),
                     expand = c(-0.001,0.02),
                     labels = scales::percent_format(accuracy = 1) ) +
  # geom_text(aes(label=format(freq*100,2)),
  #           hjust = 2, size = 5,position = position_dodge(width = 1)) +
  geom_text(aes(label=sxLabel_card),
            hjust = 2.5, size = 5,position = position_dodge(width = 1)) +
  geom_text(aes(label=dxLabel_card),
            hjust = -0.5, size = 5,position = position_dodge(width = 1)) +
  guides(fill = "none") +
  theme_539() +
  theme( legend.position = "none",
         axis.text = element_text(face = "bold", color = "grey50"),
         panel.grid.major.y = element_blank()
         )

RegionByCards
```

:::

::: {.panel}
### Table {.panel-name}

```{r print-tableFreq_byCard-gt}
Region.Freq.byCards.tbl <- Regions.Freq.byCards[,c("region","freq")] |>
  left_join( Regions.Freq.byCards.Server, by = c("region"="value") ) |>
  arrange(desc(freq)) |>
  gt( ) |>
  tab_header(
    title = "Region Play Rate",
    subtitle = "Relative Frequencies by number of times a Card within a Region is included in a Deck"
  ) |>
  tab_spanner(
    label = "Shard",
    columns = c(americas, asia, europe)
  ) |>
  fmt_percent(
    columns = c(2:5),
    decimals = 2
  ) |>
  cols_align(
    align = "left",
    columns = 1
  ) |>
  cols_align(
    align = "center",
    columns = c(2:5)
  ) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = 1,
    )
  ) |>
  cols_label(
    region   = md("**Region**"),
    freq     = md("**Freq**"),
    americas = md("**America**"),
    asia     = md("**Asia**"),
    europe   = md("**Europe**")
  ) |>
  tab_source_note(
    source_note = glue::glue("{params$patch}
                             Ranked games from {params$start} UTC to {params$end} UTC.
                             Metadata of games collected with RiotGames API")
    ) |>
   tab_options(
    table.background.color = "transparent",
    table.font.color = "black",
    table.font.color.light = "black"
   )

Region.Freq.byCards.tbl

# Region.Freq.tbl <- gtsave(
#     "images/reg_freq.png",
# )
```
:::
:::::
<!-- Close Region 2 panelset -->
:::

# Champions Combinations

```{r process-tableChampion}
CC.tableByReg <- LoR.Melt.Matches.RMD |>
  tabyl(playerDeck,server) |>
  adorn_percentages("col")

CC.table <- LoR.Melt.Matches.RMD |>
  tabyl(playerDeck, show_na = F) |>
  rename_all(~c("playerDeck","n","freq")) |>
  left_join(CC.tableByReg,by="playerDeck")
```

## Play Rates

::: l-body-outset

::::: {.panelset}
::: {.panel}
### Plot {.panel-name}

```{r plot-Champion-PR}
nrowPlot <- 20

ChampionCombo.plot <- CC.table |>
  arrange(desc(freq)) %>%
  slice_head(.,n = 20) |>
  ggplot(aes(x = reorder(playerDeck, freq), y = freq))  +

  geom_bar( stat = "identity",fill="steelblue" ) +
  coord_flip() +
  guides(fill = "none")  +
  theme_bw() +
  geom_text(
    aes(label=round(freq*100,2),size = 5),
    face = "bold",
    color = "grey50",
    hjust = -0.5, size = 4,
    # vjust=-0.25
    # position = position_dodge(width = 1)
    position = position_dodge(0.9),
    ) +
  # scale_fill_manual("legend", values = list.levels$data_regions$colorRegion) +
  scale_y_continuous(limits = c(0, round(max(CC.table$freq+0.04 ),3) ),
                     breaks = seq(0,0.20,0.02),
                     expand = c(-0.001,0.02),
                     labels = scales::percent_format(accuracy = 1) ) +

  theme( plot.title = element_text(face = "bold", size = 12, hjust = 0.6),
         axis.title.x = element_text(face = "bold"),
         axis.title.y = element_text(face = "bold"),
         legend.position = "none") +
  annotate(geom="text", x=3, y=0.08, col="black",label = paste("n =",nGames,"\n"," cumulative frequence \n ",
                                                               paste0(CC.table |> arrange(desc(freq)) %>% slice_head(.,n = 20) |> select(freq) |> sum() %>% round(.,4)*100 ,"%") )
           ) +
  theme_539() +
  labs(x = "Champions",
       y = "Play Rate",
       title = "Champions Combination Play Rates",
       subtitle = glue::glue("Play-Rates of the top {nrowPlot} most played combination of champions/regions"),
       caption = glue::glue("{params$patch}
                            Ranked games from {params$start} UTC to {params$end} UTC.
                            Metadata of games collected with RiotGames API")
       ) +
  theme( 
    legend.position = "none",
    axis.text = element_text(size = 10, face = "bold", color = "grey25", family = "Helvetica"),
    panel.grid.major.y = element_blank()
    )

ChampionCombo.plot
```
:::

::: {.panel}
### Table {.panel-name}

```{r table-Champion-PR}
CC.table |>
  arrange(desc(freq)) |>
  # filter(nGames>100) |>
  select(playerDeck,freq,americas,asia,europe) |>
  reactable(
    bordered = TRUE,
    highlight = TRUE,
    striped = TRUE,
    searchable = TRUE,
    compact = TRUE, # compact the table height
    fullWidth = TRUE, # don't fill the page
    defaultPageSize = 20,
    wrap = TRUE,
    defaultColDef = colDef(
      style = list(fontFamily = "Helvetica", fontSize = "13px"), align = "center"
      # minWidth = 120,
      ),
    columns = list(
      playerDeck = colDef(name = "Champions",minWidth = 120, style = list(fontSize = "11px", fontWeight = "bold", color="black") ),
      freq     = colDef(name = "Play Rate",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") ),
      americas = colDef(name = "America",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") ),
      asia     = colDef(name = "Asia",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") ),
      europe   = colDef(name = "Europe",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") )
      )
    )

```
:::
:::::
<!-- Close CC lay Rate panelset -->
:::

## Day by Day

Highlisting the top10 most played decks (at the moment of the last game played).

```{r champion-freq-by-date}
m = 10

Champion.deck.daily <- LoR.Melt.Matches.RMD |>
  rename("champions"="playerDeck") |>
  arrange(game_start_time_utc) |>
  select(game_start_time_utc,champions) |>
  mutate( num_cc = factor(champions) |> as.numeric() ) |>
  as.data.table() |>
  {\(x) x[ , cumFreq := (cumsum(num_cc)/num_cc)/.I , by=champions ]}() |>
  select(!num_cc) |>
  mutate( champions = factor(champions) |> fct_infreq() )

fct_values <- LoR.Melt.Matches.RMD |>
  # mutate( top5 = fct_lump(champions, n = m, w = tot, ties.method = "max") ) |>
 mutate( top5 = fct_lump_n(playerDeck,n = m) |> fct_infreq() ) |>
 pull(top5) |> levels()
```

```{r plot-date-by-date}
meta_evo <- ggplot(
   # The ggplot object has associated the data for the highlighted countries
  data = Champion.deck.daily |> filter(champions %in% fct_values[-1]),
  aes(game_start_time_utc, cumFreq, group = champions)
  ) +
  ## Lines for the non-highlighted countries
  geom_line(
    data = Champion.deck.daily |> filter(champions %!in% fct_values[-1]),
    color = "grey75",
    size = .6,
    alpha = .5
  ) +
  ## Lines for the highlighted countries.
  # It's important to put them after the grey lines
  # so the colored ones are on top
  geom_line(
    aes(color = champions),
    size = .9
  ) +
  # geom_text(aes(label=champions,color = champions))
  geom_label_repel(
    data = Champion.deck.daily |> filter(champions %in% fct_values[-1]) |> group_by(champions) |> slice_max(game_start_time_utc,n=1) |> distinct(game_start_time_utc,champions,.keep_all = T),
    aes(label=str_to_upper(champions),color = champions),
    # aes(color = champions, label = champions),
    family = "Helvetica",
    # fontface = "bold",
    size = 3.5,
    direction = "y",
    xlim = c(as.POSIXct(max(Champion.deck.daily$game_start_time_utc) + hours(12)), NA),
    force = 3,
    hjust = 1,
    segment.size = .7,
    segment.alpha = .5,
    segment.linetype = "dotted",
    box.padding = .4,
    segment.curvature = -0.1,
    segment.ncp = 3,
    segment.angle = 15,
    bg.color = "grey50"
  ) +
  scale_x_datetime(
    # expand = c(0.02,0.01),
    date_minor_breaks = "1 day",
    limits = c(as.POSIXct(params$start, tz="UTC"), as.POSIXct(params$end, tz="UTC")+hours(23))
    # limits = c(as.POSIXct(params$start, tz="UTC"), as.POSIXct(params$end, tz="UTC"))
  )  +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0,0.15),
    breaks = seq(0,0.15,0.02),
    labels = scales::percent_format(accuracy = 1) # glue::glue("{format(seq(0, 0.20, by = 0.05), nsmall = 2)}%")
  ) +
  scale_color_manual(
    values = c(rcartocolor::carto_pal(n = 10, name = "Vivid")[1:10-1], "grey50")
  ) +
  labs(x = "Date",
       y = "PlayRate",
       title = "Evolution of Play Rate over time",
       caption = glue::glue("{params$patch}
                            Ranked games from {params$start} UTC to {params$end} UTC.
                            Metadata of games collected with RiotGames API")
  ) +
  theme_539() +
  theme( legend.position = "none",
         axis.text = element_text(size = 10, face = "bold", color = "grey50")
         )

meta_evo

ggsave(glue::glue("./images/meta-report/{params$ind}-playrate-daybyday.png"))
```

## Win Rates

Tie games are excluded

```{r get-muWR}
MUtbl <- LoR.Melt.Matches.RMD |>
  filter(game_outcome!="tie") |>
  select( playerDeck,opponentDeck,game_outcome,server ) |>
  group_by(playerDeck,opponentDeck) |>
  summarise( muWin   = sum(game_outcome=="win"),
             muGames = n(),
             muWR=mean(game_outcome=="win") ) |>
  as.data.table()

MUtbl[, c("LCI","UCI") := binom.confint(muWin,muGames,0.95,methods="exact")[5:6] ]
MUtbl[, okCI:=(!between(0.50,LCI,UCI)) ]
MUtbl[, direction:=ifelse(muWR>0.50,"POS","NEG")  ]

MUtbl <- MUtbl |>
  mutate( CI := glue("({percent(LCI,accuracy = 0.1)} - {percent(UCI,accuracy = 0.1)})" ) )
```

```{r process-winRate}
WR.DT <- LoR.Melt.Matches.RMD |>
  filter(game_outcome!="tie") |>
  select( playerDeck,opponentDeck,game_outcome ) |>
  group_by(playerDeck) |>
  summarise( nWin   = sum(game_outcome=="win"),
             nGames = n(),
             WR=mean(game_outcome=="win")
            ) |>
  ungroup() |>
  mutate( playrate = nGames/sum(nGames) )

WR.DT.Reg <- LoR.Melt.Matches.RMD |>
  filter(game_outcome!="tie") |>
  select( playerDeck,opponentDeck,game_outcome,server ) |>
  group_by(server,playerDeck) |>
  summarise(
    nWin   = sum(game_outcome=="win"),
    nGames = n(),
    WR=mean(game_outcome=="win"),
    ) |>
  ungroup() |>
  group_by(server) |>
  mutate( sumGames = sum(nGames), regPlayrate = nGames/sumGames ) |>
  left_join(WR.DT[,c("playerDeck","playrate")],by="playerDeck") 
```
::: l-body-outset

::::: {.panelset}
::: {.panel}
### Meta Decks {.panel-name}

Win rates of the most played combination of champions. Play Rate \>= 1% in at least one of the servers.

```{r print-tableWinRate}
WR.DT.Reg |>
  arrange(desc(playrate)) |>
  filter(playrate >= 0.01) |>
  arrange(desc(playrate)) |>
  relocate(playerDeck,WR,nWin,nGames,regPlayrate,server) |>
  reactable(
    groupBy = "playerDeck",
    bordered = TRUE,
    # wrap = FALSE,
    highlight = TRUE,
    striped = TRUE,
    # filterable = TRUE,
    defaultSorted = list(nGames = "desc"),
    defaultColDef = colDef(
      # header = function(value) str_to_title(value),
      #  cell = function(value) format(value, nsmall = 1),
      align = "center",
      minWidth = 120
      # headerStyle = list(background = "steelblue",color="white")
      ),
    columns = list(
      playerDeck = colDef(name = "Champions",minWidth = 250),
      server = colDef(name = "Server", aggregate = "unique",minWidth = 120),
      nWin   = colDef(name = "#Win", aggregate = "sum"),
      nGames = colDef(name = "#Games", aggregate = "sum"),
      WR     = colDef(name = "WinRate", aggregate = JS(
        "function(values, rows) {
        var totalWin = 0
        var totalGames = 0
        rows.forEach(function(row) {
        totalWin   += row['nWin']
        totalGames += row['nGames']
        })
        return totalWin / totalGames
        }"
        ),format = colFormat(percent = TRUE,digits = 1),
        ),
      regPlayrate   = colDef(name = "Play Rate",
                             aggregate = JS("function(values, rows) {
                                            var total = 0;
                                            var n = 0;
                                            rows.forEach(function(row) {
                                            total += row['playrate']
                                            n += 1
                                            })
                                            return total/n
                                            }"),
                             format = colFormat(percent = TRUE,digits = 1)),
      sumGames   = colDef(show=F),
      playrate   = colDef(show=F)
      )
    )
```
:::

::: {.panel}
### Underdog {.panel-name}

Top Win rates of the top10 best performing least played combination of champions. Play rate $\in$ [0.1%,1%)[^2]

[^2]: Min number of games 50, during the times a meta/ladder just changed.

```{r print-under-tableWinRate}
WR.DT |>
  filter( nGames >= 50 & WR >= 0.50 & playrate >= 0.001 & playrate < 0.01) |>
  slice_max(WR,n = 10) |>
  relocate(playerDeck,WR,nWin,nGames,playrate) |>
  arrange(desc(WR)) |>
  reactable(
    # searchable = TRUE,
    bordered = TRUE,
    # wrap = FALSE,
    highlight = TRUE,
    striped = TRUE,
    # filterable = TRUE,
    defaultColDef = colDef(
      # header = function(value) str_to_title(value),
      #  cell = function(value) format(value, nsmall = 1),
      align = "center",
      minWidth = 120,
      headerStyle = list(background = "steelblue",color="white")
      ),
    columns = list(
      playerDeck = colDef(name = "Champions",minWidth = 250),
      nWin   = colDef(name = "#Win"),
      nGames = colDef(name = "#Games"),
      WR     = colDef(name = "WinRate",format = colFormat(percent = TRUE,digits = 1) ),
      playrate   = colDef(name = "Play Rate",format = colFormat(percent = TRUE,digits = 1))
      )
    )
```
:::
:::::
<!-- Close Win Rate panelset -->
:::

# Match Ups

`r kableExtra::text_spec("Note :", color = "red")` Regarding MU, this is not the most accurate estimation you can get from my data. If you want a better picture of the current meta it would be better to look at the dedicated MU-page where I use all "Ranked" games with the current sets of buffs and nerfs. While one may object I don't account for optimizations and differences in skills acquired during the weeks, the overall number of games / sample size makes them a better source of information. So, in case, pls refer to the [MU - page](https://www.llorr-stats.com/static/mu.html) for a better "meta-investigation".

```{r get-WR-Top10}
mu <- 15

TopCC <- CC.table |> 
  arrange(desc(freq)) |> 
  {\(x) slice_head(x,n = mu)}() |> 
  select(playerDeck) |> 
  pull()

WRTop10 <- MUtbl[ playerDeck %in% TopCC & opponentDeck %in% TopCC, ]
WRTop10 <- setorderv(WRTop10, c("playerDeck","opponentDeck"), c(1,1))
```

::: l-page
::::: {.panelset}
::: {.panel}

## Match-up Grid {.panel-name}

The win rates on the grid are among the `r mu` most played champion combination.

```{r prepare-flex}
require(flextable)
require(officer)

big_border   = fp_border(color="darkgray", width = 2)
small_border = fp_border(color="gray", width = 1)

dummy_fun <- function(x){
  ifelse( !is.na(x),sprintf( "%.0f%%", x*100 ),NA )
}
```

```{r prepare-flex-grid}
grid <- matrix(WRTop10$muWR, nrow = mu, ncol = mu, byrow = T)
diag(grid) <- NA

colnames(grid) <- TopCC
colourer <- col_numeric(
  palette = c(
    "#D73027", # red
    # "#f9ccac", # red/orange
    "white",
    # "#e3eaa7", # green
    "#1A9850" # darker green
    ),
  domain = c(0, 1))

funs <- setNames(rep(list(dummy_fun), mu), TopCC)
```

```{r print-flex}
ft <- grid |> 
  as_tibble() |>
  # mutate(across(everything(),~scales::percent(.x, accuracy = 0.1 ))) |>
  add_column(TopCC,.before = TopCC[1]) |>
  rename("MatchUps"="TopCC") |>
  flextable::flextable( ) |> 
  theme_vanilla( ) |>
  # theme_booktabs(bold_header = TRUE) |> 
  flextable::align(align = "center", part = "all") |>
  flextable::bg(
    bg = colourer,
    j = ~ . -MatchUps,
    part = "body") |>
  {\(x) border_remove(x = x)}() |>
  border_outer(part="all", border = big_border ) |>
  border_inner_h(part="all", border = small_border ) |>
  border_inner_v(part="all", border = small_border ) |>
  set_formatter(values = funs) |>
  fontsize(size = 8, part = "header") |>
  fontsize(j=1, size = 8) |>
  bg(part = "header", bg = "white"  ) |>
  bg(j = 1, bg = "white"  ) |>
  autofit()

ft
```
:::

::: {.panel}
## Match-up Table {.panel-name}

```{r reactable-tbl}
require(reactable)
require(htmltools)
require(crosstalk)

#'Quick link for a MUtbl for testing
#'##################################
# file.MU.DT   <- list.files(path = file.path("C:","LlorR","data","clean" ), pattern = "MUtbl_", full.names = T) |> max()
# MUtbl <- fread(file.MU.DT, header = T, na.strings = c("", NA))

# The fs object will inject css into your page.
# if (requireNamespace("crosstalk", quietly = TRUE)) {
data <- crosstalk::SharedData$new(MUtbl |>
                       filter(muGames>=100) |>
                       select(-LCI,-UCI,-okCI,-direction))

bscols(
  widths = c(3, 9),
  list(
    crosstalk::filter_select("playerDeck", "Player", data, ~playerDeck),
    crosstalk::filter_select("opponentDeck", "Opponent", data, ~opponentDeck),
    crosstalk::filter_slider("muWin",   "#Win", data, ~muWin, width = "100%",step = 50,min = 0),
    crosstalk::filter_slider("muGames", "#Games", data, ~muGames, width = "100%",step = 100,min = 0),
    crosstalk::filter_slider("muWR", "WinRate", data, ~muWR, width = "100%",step=0.01,min = 0,max = 1)
  ),
  reactable(data,
            bordered = TRUE,
            highlight = TRUE,
            striped = TRUE,
            searchable = TRUE,
            # filterable = TRUE,
             defaultColDef = colDef(
              style = list(fontWeight = 500, color = "black",
                       fontFamily = "Work Sans, sans-serif", fontSize = "11px"),
              align = "center",
              minWidth = 120,
              headerStyle = list(background = "steelblue",color="white")
            ),
            columns = list(
              playerDeck   = colDef(name = "Player",minWidth = 120),
              opponentDeck = colDef(name = "Opponent"  ,minWidth = 120),
              muWin    = colDef(name = "#Win", style = list( fontSize = "15px") ),
              muGames  = colDef(name = "#Games", style = list( fontSize = "15px")),
              muWR     = colDef(name = "WinRate",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "15px") ),
              CI       = colDef(name = "CI",minWidth = 120, style = list(fontSize = "13px"))
              )
    )
  )
```
:::
:::::
<!-- Close MU panelset -->
:::

# Decks of the week {.tabset .tabset-fade .tabset-pills}

Another week another way to abuse Bandle

```{r deck-structure-prepare}
# brks <- c(0.50,0.55,0.60,0.65,0.70,0.75,0.80,0.85,0.90,0.95)
# clrs = colorRampPalette( c("white","steelblue") )(length(brks)+1)

deck_color_generator <- scales::col_numeric(c("white", "white","green"), domain = NULL)

make_color_pal <- function(colors, bias = 1) {
  get_color <- colorRamp(colors, bias = bias)
  function(x) rgb(get_color(x), maxColorValue = 255)
}

good_color <- make_color_pal(c("white", "white", "#9bc2e6"))
```

::: l-page

::::: {.panelset}
::: {.panel}
## Sivir/Tristana (BC/SH)

```{r deckweek, layout="l-page"}
deck.of.week <- "Sivir/Tristana (BC/SH)"

SubDeck_deck_code <- LoR.Melt.Matches.RMD |>
  filter(playerDeck == deck.of.week ) |>
  pull(deck_code)

data <- get_deck_structure_2(SubDeck_deck_code)

data |>
  reactable(
    bordered = TRUE,
    highlight = TRUE,
    searchable = TRUE,
    compact = TRUE, # compact the table height
    fullWidth = T, # don't fill the page
    defaultPageSize = 20,
    wrap = TRUE,
    # filterable = TRUE,
    defaultColDef = colDef(
      style = function(value) {
        if (!is.numeric(value)) return()
        # normalized <- (value - min(nottem)) / (max(nottem) - min(nottem))
        # good_color(0.8)
        color <- good_color(value)
        list(background = color,fontFamily = "Helvetica", fontSize = "14px")
        },
      # format = colFormat(digits = 1),
      # fontSize = "15px",
      headerStyle = list(background = "whitesmoke",color="black", align = "center"),
      align = "center",
      minWidth = 120
      ),
    columns = list(
      name     = colDef(name = "Card",minWidth = 120, style = list( fontWeight = "bold", fontFamily = "Helvetica", fontSize = "13px" ), align = "left" ),
      playrate = colDef(name = "PlayRate", format = colFormat(percent = TRUE,digits = 1) ),
      `3`      = colDef(name = "3",format = colFormat(percent = TRUE,digits = 1) ),
      `2`      = colDef(name = "2",format = colFormat(percent = TRUE,digits = 1) ),
      `1`      = colDef(name = "1",format = colFormat(percent = TRUE,digits = 1) )
      ),
    columnGroups = list(
      colGroup(name = glue::glue("{deck.of.week}"), columns = c("name"), headerStyle = list(background = "whitesmoke",color="black", align = "center") ),
      colGroup(name = glue::glue("Playrate (N: {length(SubDeck_deck_code)})"), columns = c("playrate","3","2","1"),headerStyle = list(background = "whitesmoke",color="black", align = "center"))
      )
    )
```
:::

::: {.panel}
## Deckcodes

```{r}
deckCodeTbl  <- LoR.Melt.Matches.RMD |>
  filter( playerDeck == deck.of.week ) |>
  mutate( server = str_to_title(server) ) |>
  group_by(server,playerDeck,deck_code ) |>
  summarise( n = n() ) |>
  slice_max(n, n = 2,with_ties = F) |>
  ungroup()
```

```{r print-deck-code-tbl, layout="l-page"}
#' Contained in lor_costants
# urlruneterraAR <- "https://runeterra.ar/"
# urlrank <- "Main/Lor/Rank/"
# urldeck <- "decks/code/"

deckCodeTbl |>
  reactable(
    groupBy = c("playerDeck","server"),
    bordered = TRUE,
    highlight = TRUE,
    searchable = TRUE,
    compact = TRUE, # compact the table height
    fullWidth = T, # don't fill the page
    # defaultPageSize = 20,
    pagination = FALSE,
    wrap = TRUE,
    # filterable = TRUE,
    defaultColDef = colDef(
      style = list(background = color,fontFamily = "Helvetica", fontSize = "14px"),
      align = "center",
      minWidth = 120
      ) ,
    columns = list(
      deck_code = colDef(name = "DeckCode", cell = function(value, index) {
        # Render as a link
        url <- glue::glue("{urlruneterraAR}{urldeck}{value}")
        htmltools::tags$a(href = url, target = "_blank", as.character(value))
        },minWidth = 400, style = list(fontsize = "8px") ),
      server = colDef(name = "Server",minWidth = 150),
      playerDeck = colDef(name = "Archetype",minWidth = 150),
      n     = colDef(name = "Games" )
      ),
    rowStyle = JS("function(rowInfo) {
                  if (rowInfo.level > 0) {
                  return { background: 'whitesmoke', borderLeft: '2px solid #ffa62d' }
                  } else {
                  return { borderLeft: '2px solid transparent' }
                  }
                  }"),
    defaultExpanded = T
    )
```
:::

> How to read the table: <br> - Play rate: How often a card is included in this class of decks / the table is order by this column. <br> - 3/2/1 is the relative and absolute frequency of the number of copies in the decks that plays them <br> - Frequencies from 50% to 100% are colored from shades of green to white to identify more easily the highest values

:::::
<!-- Close Deck Structure panelset -->
:::

# LoR-Meta Index (LMI)

`r kableExtra::text_spec("New:", color = "red")` added a Tier classification of decks based on their LMI value. This is more experimental and not as strict as a result of one of my analysis (in this case it's a first glimpse to the distribution of the LMI values). The classification is as follows:

- **Tier0** with LMI >= 97.5

- **Tier1** with LMI $\in$ [85,97.5)

- **Tier2** with LMI $\in$ [60,85)

- **Tier3 or lower** with LMI < 60

This method will be improved in the next weeks, maybe adding the ban rate which can be extracted from Gauntlet and Bo3 Friendly Matches.

`r kableExtra::text_spec("Note:", color = "red")`Hovering over a circle will display a deck values.

> The LMI [^3] [^4] is an Index I developed to measure the performance of decks in the metagame. For those who are familiar with basic statistical concept I wrote a document to explain the theory behind it: , it's very similar to [vicioussyndicate](https://www.vicioussyndicate.com) (vS) Meta Score from their data reaper report. The score of each deck ***is not*** just their "strength", it takes in consideration both play rates and win rates that's why I prefer to say it measure the "performance". The values range from 0 to 100 and the higher the value, the higher is the performance.

[^3]: [LMI - Early Theory](https://llorr-stats.com/analysis/lmi/)

[^4]: [LMI - Adding a Ban Index](https://www.llorr-stats.com/analysis/lmi-02-tentative-expansion/)

```{r lmi, layout="l-page"}
LMI.DT <- WR.DT |>
  filter( nGames > 200 ) |>
  # filter( playrate > 0.01 ) |>
  mutate( PR_ind    = scale_quantile(playrate) ) |>
  mutate( WR_ind    = scale_quantile(WR) ) |>
  rowwise() |>
  mutate( LMI = harm.mean(c_across(ends_with("ind")) ),
          tooltip = glue("Deck {playerDeck}
                         LMI {round(LMI*100,1)}
                         WinRate {scales::percent(WR,accuracy = 0.1)}
                         PlayRate {scales::percent(playrate,accuracy = 0.1)}") ) |>
  ungroup() |> 
  mutate(tier = case_when( 
     LMI >= 0.975 ~ "Tier0",
     0.85 <= LMI & LMI < 0.975 ~ "Tier1",
     0.60 <= LMI & LMI < 0.85 ~ "Tier2",
     LMI < 0.60 ~ "Tier3 or lower"
    ) 
  )
```


```{r lmi-png, fig.height=8, fig.width=12, include=FALSE, layout="l-page"}
LMI.DT |>
  slice_max(LMI,n = 15,with_ties = F) |>
  mutate( tooltip = glue("{playerDeck}
                         LMI {round(LMI*100,1)}
                         WinRate {scales::percent(WR,accuracy = 0.1)}
                         PlayRate {scales::percent(playrate,accuracy = 0.1)}
                         #Games {nGames}") ) |>
  mutate_if(is.numeric, funs(round(., 4)) ) |>
  mutate( LMI = LMI*100 ) |>
  ungroup() |>
  ggplot( aes(x=WR_ind, y=PR_ind, size = LMI, color = tier, text=tooltip)) +
  geom_point(alpha=0.6) +
  scale_size(range = c(1, 15), name="LMI") +
  theme_539() +
  geom_label_repel( 
    aes(label=tooltip),
    family = "Roboto",
    color = "grey40",
    fontface = "bold",
    size = 3,
    fill = NA,
    vjust = "outward",
    label.padding = unit(0.8, "mm"),
    label.size = unit(0.25, "mm"),
    label.r = unit(0.5, "mm"),
    min.segment.length = 0,
    segment.linetype = 2,
    segment.color = 'grey50'
  ) + 
  guides(colour = guide_legend(override.aes = list(size=10)),
         size = FALSE ) +
  theme( legend.position = "top",
         legend.background = element_blank(),
         legend.title = element_text(size=9, lineheight = 1.3),
         legend.justification = "right"
         ) +
  labs(
    title = "Top15 Deck Peformances",
    subtitle = "HighTop15 Deck Peformances",
    x = "Win Index",
    y = "Freq Index",
    caption = element_text(glue::glue("{params$patch}
                                      Ranked games from {params$start} UTC to {params$end} UTC.
                                      Metadata of games collected with RiotGames API
                                      LMI computed with the basic version which use PlayRate and WinRate. Additional Decks performances in the metareport"))
  )

ggsave(glue::glue("./images/meta-report/{params$ind}-LMI.png"))
```


```{r lmi-plotly, layout="l-page"}
fig <- LMI.DT |>
  slice_max(LMI,n = 50,with_ties = F) %>%
  mutate_if(is.numeric, funs(round(., 4)) ) |>
  ggplot( aes(x=WR_ind, y=PR_ind, size = LMI^2, color = tier, text=tooltip)) +
  geom_point(alpha=0.6) +
  scale_size(range = c(1, 15), name="LMI") + 
  theme_minimal() +
  labs( 
    x = "WR Index",
    y = "Freq Index",
    title = "LoR-Meta Index (LMI)",
    caption = "top50 highest LMI values, with a min amount of 100 games."
    )

ggplotly(fig, tooltip="text")
```

# Win Marathons Leaders

`r kableExtra::text_spec("New:", color = "red")` Top3 Players (or more in case of ties) from each server that had the highest amount of consecutive wins with the same archetype. The provided deckcode is the one played in the last win found.

```{r win-marathon, layout="l-page"}
gtWinning <- setDT(LoR.Melt.Matches.RMD)[order(game_start_time_utc)][, counter := rowid(rleid(game_outcome)), by=c("playerID","playerDeck") ][ game_outcome == "win" ] |>
  # filter( server=="asia" & playerID == "Ryo 6192" & playerDeck ==	"Senna / Veigar (BC/SI)" )
  group_by(playerID) |>
  slice_max(counter,n=1) |>
  ungroup() |>
  group_by(server) |>
  slice_max(counter,n=3) |>
  left_join(LoR.Account.RMD[ ,c("RiotID","gameName") ]|>distinct(RiotID,.keep_all = T), by =c("playerID"="RiotID") ) |>
  mutate( server = str_to_title(server) ) |>
  group_by(server) |>
  mutate( ranking = rank(-counter,ties.method = "min" ) ) |>
  ungroup() |>
  mutate(
    counter_icon = dplyr::case_when(
      ranking == 1 ~ "trophy",
      ranking == 2 ~ "medal",
      ranking == 3 ~ "minus",
      TRUE ~ "other"
      ),
    icon = map(.x = counter_icon, ~fontawesome::fa(.x)),
    icon = map2(.x = counter, .y = icon, ~md(glue::glue("{.x} {.y}")) ),
    
    link = sprintf('<div><span style ="color:grey50;font-size:10px"><p><a href = "%s">%s</a></span></div>', glue::glue("{urlruneterraAR}{urldeck}{deck_code}"), deck_code),
    link = map(link, gt::html)
    # style ="font-weight:bold;color:grey;font-size:10px
  ) |>
  select(server,gameName,icon,playerDeck,link) |>
  gt(groupname_col = "server") |>
  cols_align(
    align = "left",
    columns = everything()
  ) |>
  gtExtras::gt_theme_538() |>
  tab_header(
    title = md(glue::glue("{fontawesome::fa('star')} Top3 Biggest Win Streak by Server {fontawesome::fa('star')}")),
    subtitle = "Cumulative wins with the same Archetype"
  ) |> 
  cols_width(vars(icon) ~ px(30)) %>% 
  #Original changes as above.
  cols_label(
    gameName = "Player",
    icon = "Result",
    playerDeck = "Archetype",
    link = "Deck Code"
  ) |>
  tab_source_note(
    source_note = glue("Games from all Master are collected each hour adding up to the last 20 matches.
                       Unlikely but possible to miss games in case of high frequency games.
                       Metadata of games collected with RiotGames API")
    ) |>
  opt_all_caps() |>
  opt_table_font(
    font = list(
      google_font("Chivo"),
      default_fonts()
    )
  ) |>
  cols_width(vars(icon) ~ px(150),
             vars(link) ~ px(400)) |>
  tab_options(
    # table.font.color = "black",
    # table.font.color.light = "black",
    column_labels.border.top.width = px(3),
    column_labels.border.top.color = "transparent",
    table.border.top.color = "transparent",
    table.border.bottom.color = "transparent",
    data_row.padding = px(3),
    source_notes.font.size = 12,
    heading.align = "left",
    table.font.size = px(12L),
    # Adjust grouped rows to make them stand out
    row_group.background.color = "grey"
    ) |>
  tab_style(
    style = cell_text(size = "small"),
    locations = cells_body(
      columns = vars(
        "playerDeck","link"
        )
      )
    ) |>
  gtsave(
    glue::glue("./images/meta-report/{params$ind}-topWin.png")
    # path = tempdir()
  )
```

# Cards Presence

```{r process-UniqueCards}
allCards            <- unlist(apply(Card.Subset, 1, unique),use.names = F)
TableAllCards       <- table(allCards)
RegionShortAllCards <- str_sub(names(TableAllCards),3,4)
TableCardsDT        <- data.table(TableAllCards)
setnames(TableCardsDT,old = "allCards",new = "card")

TableCardsDT[ ,region    := str_sub(card,3,4) ]
TableCardsDT[ ,regionID  := fct_recode(region,!!!recodeRegPosition) ]
TableCardsDT[ ,nGamesReg := Region.Freq$n[as.numeric(as.character(regionID))] ]
# Region.Freq contain the frequencies of appearence of each region in the decks
TableCardsDT[ ,p.byReg   := round(N/nGamesReg,3) ]
# Frequence of a card appearing in a deck within its own region

TableCardsDT[ ,card    := str_replace_all(card, set_names(LoR.Card$name, LoR.Card$cardCode)) ]
TableCardsDT[ ,region  := str_replace_all(region, set_names(data_regions$nameRef, data_regions$abbreviation)) ]
```
::::: {.panelset}
::: {.panel}
## Play Rate {.panel-name}

It seems that not even Twin Disciple can beat Sharsight

```{r print-CardsTable-1}
MostPlayed <- TableCardsDT |>
  arrange(desc(p.byReg)) |>
  rename_all(~c("Card","# Decks with that card ","Region","RegionID","Games of X Region","Play Rate")) |>
  select(c(1,3,6,2)) |>
  datatable(rownames = FALSE) |>
  formatStyle('Card', fontWeight = 'bold') |>
  formatStyle('Play Rate', fontWeight = 'bold') |>
  formatStyle('Play Rate', fontWeight = 'bold') |> formatStyle(
    'Region',
    target = 'row',
    backgroundColor = styleEqual(data_regions$nameRef, data_regions$colorRegion)
  ) |>
  formatPercentage('Play Rate', 1)
  # formatStyle('Card',  color = 'red', backgroundColor = 'orange', fontWeight = 'bold')

MostPlayed
```
:::

::: {.panel}
## Top 3 Play Rates by Region {.panel-name}

```{r print-CardsTable-3}
TopPlayed.PbyReg <- TableCardsDT |>
  group_by(region) |>
  arrange(desc(p.byReg)) |>
  top_n(3) |>
  arrange(region) |>
  rename_all(~c("Card","N","Region","RegionID","Games of X Region","Play Rate")) |>
  select(c(1,3,6,2,5)) |>
  datatable(rownames = FALSE, options = list(
    searching = FALSE,
    lengthChange = FALSE,
    pageLength = 4*9,
    info = FALSE)) |>
  formatStyle('Card', fontWeight = 'bold') |>
  formatStyle('Play Rate', fontWeight = 'bold') |>
  formatStyle('Play Rate', fontWeight = 'bold') |> formatStyle(
    'Region',
    target = 'row',
    backgroundColor = styleEqual(data_regions$nameRef, data_regions$colorRegion)
  ) |>
  formatPercentage('Play Rate', 1)

TopPlayed.PbyReg
```
:::

::: {.panel}
## Forgotten Cards {.panel-name}

Cards that couldn't find place even in a meme deck.

```{r missingCards, results='asis'}
missingCards <- LoR.Card$cardCode[LoR.Card$cardCode %!in% names(TableAllCards)]

missingCards.DT <- data.table(
  Card = LoR.Card$name[LoR.Card$cardCode %in% missingCards],
  Code = missingCards,
  Region = str_sub(missingCards,3,4)
  )

missingTable <- t(missingCards.DT[,c(1,3)] |>
              group_by(Region) |>
              mutate(n = row_number()) |>
              spread(n, Card) |>
              mutate(across(everything(), .fns = ~replace_na(.,""))) |>
              mutate(Region = fct_relevel(Region,!!!list.levels$regionShort) )  
              ) |>
              # setnames(.,list.levels$factions.clean) |>
  kable("html", escape = F ) |>
  # kable("html", escape = F, col.names = missColNames ) |>
  kable_styling(bootstrap_options = c("hover"))

row.names(missingTable) <- NULL
missingTable
```
:::
:::::
<!-- Close Card Presence panelset -->

```{r twitter-meta, echo = FALSE}
metathis::meta() |>
  metathis::meta_description(
    glue::glue("{params$patch} - {params$description}")
  ) |> 
  metathis::meta_viewport() |> 
  metathis::meta_social(
    title = params$title,
    url = "https://www.llorr-stats.com/",
    image = params$cardurl,
    image_alt = "BandleMayor",
    og_type = "website",
    og_author = "Legna",
    twitter_card_type = "summary",
    twitter_creator = "@Maou_Legna"
  )
```

# Legal bla bla {.unnumbered}

This content was created under Riot Games' "Legal Jibber Jabber" policy using assets owned by Riot Games. Riot Games does not endorse or sponsor this project.