---
params:
  ind: "SkillCap"
  title: "From Curve to Gap. On difference of win-rates at different ranks"
  description: ""
title: | 
  `r params$title`
description: |
  `r params$description`
# preview: 
base_url: https://www.llorr-stats.com
author:
  - name: Valentino (Legna) Vazzoler
date: 11-10-2021
output:
 distill::distill_article:
    toc: true
    toc_float: true
    toc_depth: 3
    self_contained: false
citation: false
# bibliography: references.bib
draft: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo       = FALSE,
  eval       = TRUE,
  warning    = FALSE,
  error      = FALSE,
  message    = FALSE,
  comment    = NA,
  R.options  = list(width = 140, digits.secs=6),
  dev.args   = list(bg = 'whitesmoke'),
  fig.align  = 'center',
  fig.width  = 12,
  fig.height = 8,
  # fig.path   = "figures/prefix-"
  fig.path   = glue::glue("images/{params$ind}-"),
  layout     = "l-page",
  preview    = TRUE
)

# R Option
# options(scipen = 999)
source(file.path("C:","LlorR","scripts","lor_main.R" ))
source(file.path("C:","LlorR","scripts","functions","lor_constants.R"))
source(file.path("C:","LlorR","scripts","functions","lor_functions.R"))
xaringanExtra::use_panelset()
```

```{r panelset-style}
xaringanExtra::style_panelset_tabs(
  font_family        = "Helvetica",
  active_foreground  = "white",
  hover_foreground   = "black",
  hover_border_color = "black",
  active_background  = "#007fff"
  )
```

```{r twitter-meta, echo = FALSE}
metathis::meta() |>
  metathis::meta_description(params$description) |>
  metathis::meta_viewport() |>
  metathis::meta_social(
    title = params$title,
    url = "https://www.llorr-stats.com/",
    image = "",
    image_alt = "",
    og_type = "website",
    og_author = "Legna",
    twitter_card_type = "summary",
    twitter_creator = "@Maou_Legna"
  )
```

# Introduction

When talking in any discussion about any competitive activity a recurring concept that is likely to be bought up.

Skill is a commonly recurring factor bought up in any discussion revolving a competitive activity, be it a sport, a game or anything else

While we usually have a clear idea of the meaning of the *skill* concept, skill is by itself, from a measuring perspective by itself is an ill-defined term similarly to the concept of intelligence.

Be it Legends of Runeterra (LoR), Hearthstone (HS), Magic the Gathering (MtG) or simply any other game, skill is often used a explain the differences between players. To explain a result, skill alongside match-ups, are probably the most

In a previous article <ref> we discussed the concept of mastery-curve to illustrate the potential relationship between effort spent on a deck in number of games with it.

The Mastery-Curve can give an indication of the *skill* a deck may require to be played, but the method fall short to provide an easy to digest difference between group of players.

In this article we try to explore the concept of Skill-Cap explained by [ZachO](https://twitter.com/ZachODR){.uri}

define the theory behind it and try to replicate in our own way the concept for LoR in a measure we define as **Skill-Cap Gap** (SCG).

> Disclaimer: The definition and methodology by which the Skill-cap is defined by Zach.O is merely obtained by reading and listening to the media where he talked about it and that we found. We couldn't reach him for confirmation so it's possible that something is lacking.

# Measuring the Skill-Cap

## The Wrong Way

```{r vS-example}
# weight of the decks at each rank
W <- matrix(c(0.30,0.70,
              0.55,0.45,
              0.60,0.40),nrow = 3,byrow = T) 

# WR of each deck
P <- c(0.60,0.44)
W %*% P

n = c(20000,5000,2000)
rank_levels <- c("platinum","diamond","master")

# if I wanted to give the final win rate and obtain the probabilites of each MU  
# p <- limSolve::Solve(a, b)
# inva <- MASS::ginv(a)
# inva %*% b

# data <- tibble(outcome = NA_integer_)[0,]
example <- tibble(outcome = NA_integer_,
                  mu = NA_character_,
                  rank = NA_character_ )[0,]

# 'simulate the meta'
set.seed(123)
for (i in seq_len(NROW(W)) ) {
  
  print(i)
  
  outcome <- c(#win (P1) of MU1 at rank i
    rep(1,n[i]*W[i,1]*P[1]),
    #loss (1-P1) of MU1 at rank i
    rep(0,n[i]*W[i,1]*(1-P[1])),
    #win (P2) of MU2 at rank i
    rep(1,n[i]*W[i,2]*P[2]),
    #loss (1-P2) of MU2 at rank i
    rep(0,n[i]*W[i,2]*(1-P[2]))
  )
  
  # sim <- c(
  #   # MU-1
  #   sample(x = c(1,0),size = n[i]*W[i,1],replace = T,prob = c(P[1],1-P[1]) ),
  #   # MU-2 # example the 60% presence of MU2 with it's win rate of 40/60
  #   sample(x = c(1,0),size = n[i]*W[i,2],replace = T,prob = c(P[2],1-P[2]) )
  # )
  
  mu <- c(rep("MU1",n[i]*W[i,1]),
          rep("MU2",n[i]*W[i,2]) )
  
  example <- example |>
    add_row(outcome = outcome,rank = rank_levels[i],mu = mu)

}

example <- example |>
  mutate(rank = factor(rank,levels = rank_levels,labels = str_to_title(rank_levels),ordered = T))

# scales::percent(mean(example$outcome),accuracy = 0.01)
# example |>
#   group_by(rank) |>
#   summarise(wr = mean(outcome))
```

In games with a ladder/rank system a common question is if there is any difference in skill between X at one particular rank vs another rank of choice.

Let us take Hearthstone as an example: if we want to say that at top 1000 Legends players are more proficient than Diamond players with a certain deck a common approach would be to compare such deck win rate (WR) across those ranks and assume the difference in win rate can be explained by the difference in skill by the players.

**WRONG**

That would be one of the basic errors when doing such kind of analysis.

We created an example to illustrate what can easily go wrong:

We start by having a deck with a crude win rate of `r scales::percent(mean(example$outcome),accuracy = 0.01)`

Assuming that the numbers of games collected is large enough it would be possible to assume that the deck has an almost coin-toss win rate but more toward the losing side.

While looking at these results the high ranked players may have some doubts about the results as they are sure that overall the decks has a positive win-rate.

As the data is collected at different ranks platinum,diamond and master rank we obtain the stratified win-rate:

```{r wr-by-rank, fig.width  = 6, fig.height = 4}
example |>
  group_by(rank) |>
  summarise(wr = mean(outcome)) |>
  ggplot(aes(x = rank,y = wr)) +
  geom_point() +
  geom_line(group = 1) +
  scale_y_continuous(
    limits = c(0.40,0.55),
    labels = scales::percent_format(accuracy = 1)
  ) +
  geom_text(
    aes(label=round(wr*100,2)),colour = "grey50",size = 4,
    vjust = -1, hjust = -0.5
  ) +
  labs(title = "Win Rate by Rank",x = "Rank",y="WinRate") +
  theme_Publication()
```

The result is now coherent with the high level players and indeed the deck has a different WR at different ranks.

It would be very easy to assume that the differences in WR is to assign to the difference in skills of the players. The higher the rank the better are the players to pilot a deck.

In this example the *meta* is defined by a simple case two different match ups (let's ignore if it's feasible or not)

What follows is again the stratified win rate by rank but also by each different match ups.

```{r wr-by-rank-mu, fig.width  = 10, fig.height = 8}
example |>
  group_by(rank,mu) |>
  summarise(wr = mean(outcome)) |>
  ggplot(aes(x = rank,y = wr, group=mu, fill=mu, color=mu)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(
    # limits = c(0.40,0.60),
    labels = scales::percent_format(accuracy = 1)
  ) +
  geom_text(
    aes(label=round(wr*100,2)),
    size = 4, face = "bold", color = "grey50", vjust = -1, hjust = -0.5
  ) +
  labs(title = "Win Rate by Rank",subtitle = "Results by Rank AND Match Ups",x = "Rank",y="WinRate") +
  theme_Publication() +
  guides(color = guide_legend(title = "Match Up"), fill = "none", color = "none")
```

We can see that ... It's possible to notice that the win rate was actually constant at each rank And that the explanation is to found elsewhere.

As this is a very easy example, the only remaining factor which could be the cause of the differences is by the variation in play rates of the two match ups at each rank

```{r gt-meta}
example |>
  mutate(mu = factor(mu, levels = c("MU1","MU2"),labels = c("MatchUp1","MatchUp2") ) ) |>
  tbl_cross(
    row = rank,
    col = mu,
    percent = "row",
    label = list(rank ~ "Player Rank", mu ~ "Match Up")
  )
```

## The Vicious (Syndicate) Way

Trying to evaluate the differences in skills in a CG, in a certain meta at different ranks is no easy task.

Assuming it was possible to collect all information a game played it would be still hard to control for all possible confounding variable

Even if it was possible to create the perfect experiment it would be hard to track all the confounding variables

Human factors that are not collectable. Of course it's possible to make some assumption, proxy but overall

In the Hearthstone community Zach.O has discussed several times [^1] [^2] about skill-cap of decks at different ranks.

[^1]: [Invenglobal Interview](https://www.invenglobal.com/articles/15634/vs-zacho-grandmasters-are-not-immune-to-making-poor-judgment-calls-like-running-safety-inspector-in-paladin){.uri}
[^2]: Data Reaper Podcast: Ep.62 / Ep.64

In his podcast, Zach, while discussing with Hat on the skill-testing of "Garrote Contact Rogue" deck, goes more in detail about the skill-cap concept:

> ... and I look at the difference between Top Legends and DiamondI-IV. I look at the disparities in MU, not looking at <unclear> because sometimes the fields is going to influence a deck winrates at different brackets. Because, you know if the fields is more favourable, that can contributes to the deck's win rate. But, when I try to eliminate all other factors, and look at the disparities, just the MU disparities based of skill... ^[Data Reaper Podcast: Ep.62 28:55]

Other keys references from the discussion are some key references like:

> A 2/3% win rate improvement is already big

And similarly

> A 3-4% is extremely high skill cap

<!-- The projection of the skill curve is so high, there is reason to believe it can add a couple more percentages at the very top of the ladder, because the scaling in insane -->

In addition, also worth to remember is said by both Zach and Hat:

> Zach: Data is not blind to skill. Data can very much identify skill if it doesn't appear in the data... it's probably a fairy tail

> Hat: (taling about the player influence) If something is only good at top100, that mean that the best players in the world are playing a mediocre deck and off-setting for that Because the very best players in the world, will absolutely make anything look good

As we mentioned in the introduction the methodology is only inferred from the sources mentioned and wrote in the footnotes.

It's highly possible that Zach uses a more complex methodology compared to the one we will present as they have access to a bigger pool of variables and so being able to control for a bigger number of confounders. Still, the core concept should still remain similar.

Now, let us extract the key points from the discussion:

- Sometimes the fields is going to influence a deck win-rates at different brackets because if the fields is more favourable, that contributes to the deck's win rate.

This is the play-rate issue mentioned in our example.

Even small differences in the meta can vastly change the overall performance of a deck.

This is also a concept that we introduced in one of our earliest analysis on [Matching and Propensity Score](https://www.llorr-stats.com/analysis/matching-win-rate){.uri}

- Measuring the Skill-Cap by looking at the differences between Top Legends/Diamond I-IV after removing all other factors and seeing the disparity in MU

This is the key point which along side the previous one should explain the core methodology.

The crude difference in win-rate of a deck d between two rank i,j is:

$WR(d)_i - WR(d)_j$

But the definition of skill-cap provided by Zach use as unit of choice if the difference in win-rates among match-ups.

$S(d)_{i,j} = f( MU(d)_{i,1} - MU(d)_{j,1}, ...,  MU(d)_{i,i} - MU(d)_{j,i}, ..., MU(d)_{i,n} - MU(d)_{j,n} ) = f( MU(d)_{i,n} - MU(d)_{j,n} ) \forall n \in 1:N  $ where n is every deck facing the chosen deck d.

Here we assume that the function of the differences in win-rates among match-ups is simply the expected value as it's probably the most appropriate yet simple choice for the result we are aiming for.

$S(d)_{i,j} = \frac{1}{N} \sum_{k} ( MU(d)_{i,k} - MU(d)_{j,k} )$

but because of the linearity properties of the mean we can write it as

$S(d)_{i,j} = \frac{1}{N} \sum_{k} MU(d)_{i,k} - \frac{1}{N} \sum_{k} MU(d)_{j,k} = \overline{MU(d)_i} - \overline{MU(d)_j}$

with $\overline{MU(d)}$ the mean win-rates of the deck d

and instead of using the two difference of two crude win-rates we use the difference of two mean win-rates.

This approach is simple and yet would solve the *field problem* mentioned before.

Before we goes a bit more deep into the theory we must point out a possible problem with using the differences in match-ups win-rates: the shared meta.

Assuming $N_i$ different decks are being played at rank i and $N_j$ are being played at rank j, unless $N_i = N_j$ the comparison at different ranks will only be limited to the shared decks that are being played at each different ranks. In addition decks with a really poor sample size in one of the meta will have to be excluded too.

Assuming the two meta at different ranks differ a lot the skill-cap obtained will only reflect a certain percentage of both meta limiting as such the internal validity.

How much of the shared meta issue is excluded probably depends also by each card game.

In HS and MtG for example, because of rotations and power-creeps (HS) the pool of possible decks is more limited and sort of guided.

On the contrary, in card games like YuGiOh and LoR with all cards ever released being playable (ban list aside) there is the chance of having to exclude a significant percentage of each meta.

With a more developed archetype-definition and ability to define the similarity between decks a possible solution would be the use of data from other available data from decks in a similar concept to the one 
we defined in the [matching introduction](https://www.llorr-stats.com/analysis/matching-win-rate/) we did before.

# Theory and methods




## Standardisation


# Laveraging the Shuriman devert

```{r raw-data}
# # load DeckDT
# LoR.Deck.RMD       <- fread(file.path("C:","LlorR","data","raw","LoR_DECK.csv"),na.strings = c("",NA))
# 
# # load Games DT
# LoR.Account.RMD <- list.files(path = file.path("C:", "LlorR", "data", "raw"), pattern = glue("^(.*)ACCOUNT(.*)csv$"), full.names = T) |>
#   map_dfr(data.table::fread,colClasses = "character",header = T, na.strings = c("", NA), encoding = "UTF-8") |>
#   mutate(activeShard = if_else(activeShard %in% c("sea","asia"),"apac",activeShard) ) |>
#   mutate(RiotID = glue::glue("{gameName}#{tagLine}")) |>
#   distinct(puuid,.keep_all = T)
# 
# # load Seasonal
# LoR.Seasonal.DT.RMD <- list.files(path = file.path("C:", "LlorR", "data", "raw","games"), pattern = glue("^(.*)Seasonal(.*)csv$"), full.names = T) |>
#   map_dfr(data.table::fread,header = T, na.strings = c("", NA), encoding = "UTF-8") |>
#   mutate(server = if_else(server %in% c("sea","asia"),"apac",server) )
# 
# # load Temp DT
# LoR.Temp.DT.RMD <- list.files(path = file.path("C:", "LlorR", "data", "raw","games"), pattern = glue("^(.*)Temp_DT_S12(.*)csv$"), full.names = T) |>
#   map_dfr(data.table::fread,header = T, na.strings = c("", NA), encoding = "UTF-8") |>
#   mutate(server = if_else(server %in% c("sea","asia"),"apac",server) )
# 
# # load Games DT
# LoR.Match.DT.RMD <- list.files(path = file.path("C:", "LlorR", "data", "raw"), pattern = glue("^(.*)Match_DT_S12(.*)csv$"), full.names = T) |>
#   str_subset(pattern = "Keys",negate = T) |>
#   map_dfr(data.table::fread,header = T, na.strings = c("", NA), encoding = "UTF-8") |>
#   mutate(server = if_else(server %in% c("sea","asia"),"apac",server) )
# 
# # load Games DT
# LoR.Diamond.DT.RMD <- list.files(path = file.path("C:", "LlorR", "data", "raw"), pattern = glue("^(.*)Diamond_DT_S12(.*)csv$"), full.names = T) |>
#   str_subset(pattern = "Keys",negate = T) |>
#   map_dfr(data.table::fread,header = T, na.strings = c("", NA), encoding = "UTF-8") |>
#   mutate(server = if_else(server %in% c("sea","asia"),"apac",server) )
```

```{r players-select}
# LoR.Seasonal.DT.RMD |>
#   # filter(game_version == max(game_version) ) |>
#   filter(game_version == "live_3_01_12" ) |>
#   select(match_key,starts_with("puuid")) |>
#   pivot_longer(-match_key,values_to = "puuid") |>
#   distinct(puuid) |>
#   pull() -> puuid_seasonal
```

```{r temp}
# LoR.Melt.Temp.RMD <- LoR.Temp.DT.RMD |>
#   filter(game_mode == "Constructed") |>
#   filter(game_start_time_utc >= as_datetime("2022-02-16 19:00:00") ) |>
#   select(-contains("factions")) |>
#   rename(playerPuuid_1 = puuid_1, playerPuuid_2 = puuid_2 ) |>
#   mutate(opponentPuuid_1 = playerPuuid_2, opponentPuuid_2 = playerPuuid_1 ) |>
#   mutate(opponent_deck_code_1 = deck_code_2, opponent_deck_code_2 = deck_code_1 ) |>
#   pivot_longer(cols = c(ends_with("_1"),ends_with("_2")),
#                names_to = c(".value"),
#                names_pattern = "(.*)_[0-9]"
#                ) |>
#   as.data.table() |>
#   # Add Deck data
#   left_join(LoR.Deck.RMD, by="deck_code") |>
#   rename(playerDeck=archetype) |>
#   left_join(
#     LoR.Deck.RMD[,.(deck_code,opponentDeck=archetype)],
#     by=c("opponent_deck_code"="deck_code")) |>
#   # Add Player data
#   left_join(LoR.Account.RMD[,.(puuid,playerID=RiotID)]   ,by=c("playerPuuid"="puuid")) |>
#   left_join(LoR.Account.RMD[,.(puuid,opponentID=RiotID)] ,by=c("opponentPuuid"="puuid"))
# 
# LoR.Melt.Diamond.RMD <- LoR.Diamond.DT.RMD |>
#   filter(game_mode == "Constructed") |>
#   filter(game_start_time_utc >= as_datetime("2022-02-16 19:00:00") ) |>
#   select(-contains("factions")) |>
#   rename(playerPuuid_1 = puuid_1, playerPuuid_2 = puuid_2 ) |>
#   mutate(opponentPuuid_1 = playerPuuid_2, opponentPuuid_2 = playerPuuid_1 ) |>
#   mutate(opponent_deck_code_1 = deck_code_2, opponent_deck_code_2 = deck_code_1 ) |>
#   pivot_longer(cols = c(ends_with("_1"),ends_with("_2")),
#                names_to = c(".value"),
#                names_pattern = "(.*)_[0-9]"
#                ) |>
#   as.data.table() |>
#   # Add Deck data
#   left_join(LoR.Deck.RMD, by="deck_code") |>
#   rename(playerDeck=archetype) |>
#   left_join(
#     LoR.Deck.RMD[,.(deck_code,opponentDeck=archetype)],
#     by=c("opponent_deck_code"="deck_code")) |>
#   # Add Player data
#   left_join(LoR.Account.RMD[,.(puuid,playerID=RiotID)]   ,by=c("playerPuuid"="puuid")) |>
#   left_join(LoR.Account.RMD[,.(puuid,opponentID=RiotID)] ,by=c("opponentPuuid"="puuid"))
# 
# LoR.Melt.Master.RMD <- LoR.Match.DT.RMD |>
#   filter(game_mode == "Constructed") |>
#   filter(game_start_time_utc >= as_datetime("2022-02-16 19:00:00") ) |>
#   select(-contains("factions")) |>
#   rename(playerPuuid_1 = puuid_1, playerPuuid_2 = puuid_2 ) |>
#   mutate(opponentPuuid_1 = playerPuuid_2, opponentPuuid_2 = playerPuuid_1 ) |>
#   mutate(opponent_deck_code_1 = deck_code_2, opponent_deck_code_2 = deck_code_1 ) |>
#   pivot_longer(cols = c(ends_with("_1"),ends_with("_2")),
#                names_to = c(".value"),
#                names_pattern = "(.*)_[0-9]"
#                ) |>
#   as.data.table() |>
#   # Add Deck data
#   left_join(LoR.Deck.RMD, by="deck_code") |>
#   rename(playerDeck=archetype) |>
#   left_join(
#     LoR.Deck.RMD[,.(deck_code,opponentDeck=archetype)],
#     by=c("opponent_deck_code"="deck_code")) |>
#   # Add Player data
#   left_join(LoR.Account.RMD[,.(puuid,playerID=RiotID)]   ,by=c("playerPuuid"="puuid")) |>
#   left_join(LoR.Account.RMD[,.(puuid,opponentID=RiotID)] ,by=c("opponentPuuid"="puuid"))
```

```{r melt-data}
# LoR.Melt.Games.RMD <- LoR.Temp.DT.RMD |>
#   bind_rows(LoR.Match.DT.RMD) |>
#   bind_rows(LoR.Diamond.DT.RMD) |>
#   filter(game_mode == "Constructed") |>
#   filter(puuid_1 %in% puuid_seasonal | puuid_2 %in% puuid_seasonal) |>
#   distinct(match_key,.keep_all = T) |>
#   filter(game_start_time_utc >= as_datetime("2022-02-16 19:00:00") ) |>
#   # filter(game_type == "Ranked") |>
#   select(-contains("factions")) |>
#   rename(playerPuuid_1 = puuid_1, playerPuuid_2 = puuid_2 ) |>
#   mutate(opponentPuuid_1 = playerPuuid_2, opponentPuuid_2 = playerPuuid_1 ) |>
#   mutate(opponent_deck_code_1 = deck_code_2, opponent_deck_code_2 = deck_code_1 ) |>
#   pivot_longer(cols = c(ends_with("_1"),ends_with("_2")),
#                names_to = c(".value"),
#                names_pattern = "(.*)_[0-9]"
#                ) |>
#   as.data.table() |>
#   # Add Deck data
#   left_join(LoR.Deck.RMD, by="deck_code") |>
#   rename(playerDeck=archetype) |>
#   left_join(
#     LoR.Deck.RMD[,.(deck_code,opponentDeck=archetype)],
#     by=c("opponent_deck_code"="deck_code")) |>
#   # Add Player data
#   left_join(LoR.Account.RMD[,.(puuid,playerID=RiotID)]   ,by=c("playerPuuid"="puuid")) |>
#   left_join(LoR.Account.RMD[,.(puuid,opponentID=RiotID)] ,by=c("opponentPuuid"="puuid"))
```

```{r}
# nMU <- 30
# 
# MasterOnly <- LoR.Melt.Master.RMD |>
#   anti_join(LoR.Melt.Diamond.RMD,by = c("match_key","playerPuuid"))
# 
# DiamondOnly <- LoR.Melt.Diamond.RMD |>
#   anti_join(LoR.Melt.Master.RMD,by = c("match_key","playerPuuid"))
# 
# MasterOnly |>
#   bind_rows(DiamondOnly) |>
#   count(playerDeck) |>
#   slice_max(n,n=nMU) |>
#   pull(playerDeck) -> decks_top
# 
# # # only decks with at least 100 games
# # MU_Master |>
# #   filter(playerDeck == deck) |>
# #   filter(muGames >= 100) |>
# #   pull(opponentDeck) -> deck_min_100
# 
# MU_Master <-  MasterOnly |>
#   match_ups() |>
#   filter(playerDeck %in% decks_top & opponentDeck %in% decks_top) |>
#   filter(playerDeck != opponentDeck) |>
#   add_column(rank = "master")
# 
# MU_Diamond <- DiamondOnly |>
#   match_ups() |>
#   filter(playerDeck %in% decks_top & opponentDeck %in% decks_top) |>
#   filter(playerDeck != opponentDeck)  |>
#   add_column(rank = "diamond")
```

```{r darkness, fig.width  = 12, fig.height = 8}
# 
# deck  <- "Senna/Veigar"
# decks <- decks_top[1:20]
# # decks <- deck_min_100
# 
# MU_Master |>
#   filter(playerDeck==deck) |>
#   filter(opponentDeck %in% decks) |>
#   rename(muMaster=muWR) |>
#   mutate(w = muGames/sum(muGames)) |>
#   select(1,2,5,last_col()) |>
#   left_join(
#     MU_Diamond |>
#       filter(playerDeck==deck) |>
#       filter(opponentDeck %in% decks) |>
#       rename(muDiamond=muWR) |>
#       mutate(w = muGames/sum(muGames)) |>
#       select(1,2,5),
#       # select(1,2,5,last_col()),
#     by = c("playerDeck","opponentDeck")
#   ) |>
#   mutate(opponentDeck = factor(opponentDeck, levels = decks, ordered = TRUE) ) |>
#   arrange(opponentDeck) |>
#   mutate(diffMU = muMaster-muDiamond) |>
#   # pull(diffMU) -> vec_diff
#   mutate(mean_diffMU = cummean(diffMU)) |>
#   select(opponentDeck,mean_diffMU) |>
#   mutate(wr_label=scales::percent(mean_diffMU,accuracy = 0.1) ) -> diffDT
# 
# 
# 
# MU_Master |>
#   bind_rows(MU_Diamond) |>
#   filter(playerDeck==deck) |>
#   filter(opponentDeck %in% decks) |>
#   mutate(opponentDeck = factor(opponentDeck, levels = decks, ordered = TRUE) ) |>
#   mutate(rank = factor(rank, levels = c("master","diamond"), ordered = TRUE) ) |>
#   # mutate(opponentDeck = fct_reorder(opponentDeck, muGames, .desc = TRUE) ) |>
#   ggplot() +
#   geom_errorbar(aes(x=opponentDeck,ymin=LCI,ymax=UCI,color=rank),
#                 position = position_dodge(0.3),width = 0.2) +
#   geom_point(aes(x=opponentDeck,y=muWR,color = rank), position = position_dodge(0.3)) +
#   geom_line(data=diffDT,aes(x=opponentDeck,y=mean_diffMU*10,group = 1), size=1.2,linetype=2, color="darkviolet") +
#   geom_label_repel(
#     data=diffDT,aes(x=opponentDeck,y=mean_diffMU*10,label=wr_label,group = 1),
#     family = "Helvetica",fontface = "bold", size = 3.5, direction = "y", force = 3, hjust = 1, segment.size = .7, segment.alpha = .5, segment.linetype = "dotted", box.padding = .4,
#     segment.curvature = -0.1, segment.ncp = 3, segment.angle = 15, fill = "#f0f0f0", label.padding = 0, label.size = 0
#   ) +
#   expand_limits(y=0) +
#   scale_y_continuous(
#     breaks=seq(0,1,0.25),
#     # Add a second axis and specify its features
#     labels = scales::percent_format(accuracy = 1),
#     sec.axis =  dup_axis(trans=~./10,breaks = seq(0,0.1,0.02), name="Win Rate difference")
#   ) +
#   labs(title = glue::glue("{deck} Skill-Cap Gap Plot"),
#        subtitle = "Difference in Win-Rates",
#        caption = "Left Y-axis are the win-rates") +
#   theme_Publication() +
#   theme(axis.text.x = element_text(angle = 60, vjust = 0.85, hjust=1, size = 10)) +
#   scale_colour_Publication()
```

```{r lurk, fig.width  = 12, fig.height = 8}
# 
# deck  <- "Pyke/Rek'Sai"
# decks <- decks_top[1:20]
# # decks <- deck_min_100
# 
# MU_Master |>
#   filter(playerDeck==deck) |>
#   filter(opponentDeck %in% decks) |>
#   rename(muMaster=muWR) |>
#   mutate(w = muGames/sum(muGames)) |>
#   select(1,2,5,last_col()) |>
#   left_join(
#     MU_Diamond |>
#       filter(playerDeck==deck) |>
#       filter(opponentDeck %in% decks) |>
#       rename(muDiamond=muWR) |>
#       mutate(w = muGames/sum(muGames)) |>
#       select(1,2,5),
#       # select(1,2,5,last_col()),
#     by = c("playerDeck","opponentDeck")
#   ) |>
#   mutate(opponentDeck = factor(opponentDeck, levels = decks, ordered = TRUE) ) |>
#   arrange(opponentDeck) |>
#   mutate(diffMU = muMaster-muDiamond) |>
#   # pull(diffMU) -> vec_diff
#   mutate(mean_diffMU = cummean(diffMU)) |>
#   select(opponentDeck,mean_diffMU) |>
#   mutate(wr_label=scales::percent(mean_diffMU,accuracy = 0.1) ) -> diffDT
# 
# 
# 
# MU_Master |>
#   bind_rows(MU_Diamond) |>
#   filter(playerDeck==deck) |>
#   filter(opponentDeck %in% decks) |>
#   mutate(opponentDeck = factor(opponentDeck, levels = decks, ordered = TRUE) ) |>
#   mutate(rank = factor(rank, levels = c("master","diamond"), ordered = TRUE) ) |>
#   # mutate(opponentDeck = fct_reorder(opponentDeck, muGames, .desc = TRUE) ) |>
#   ggplot() +
#   geom_errorbar(aes(x=opponentDeck,ymin=LCI,ymax=UCI,color=rank),
#                 position = position_dodge(0.3),width = 0.2) +
#   geom_point(aes(x=opponentDeck,y=muWR,color = rank), position = position_dodge(0.3)) +
#   geom_line(data=diffDT,aes(x=opponentDeck,y=mean_diffMU*10,group = 1), size=1.2,linetype=2, color="darkviolet") +
#   geom_label_repel(
#     data=diffDT,aes(x=opponentDeck,y=mean_diffMU*10,label=wr_label,group = 1),
#     family = "Helvetica",fontface = "bold", size = 3.5, direction = "y", force = 3, hjust = 1, segment.size = .7, segment.alpha = .5, segment.linetype = "dotted", box.padding = .4,
#     segment.curvature = -0.1, segment.ncp = 3, segment.angle = 15, fill = "#f0f0f0", label.padding = 0, label.size = 0
#   ) +
#   expand_limits(y=0) +
#   scale_y_continuous(
#     breaks=seq(0,1,0.25),
#     # Add a second axis and specify its features
#     labels = scales::percent_format(accuracy = 1),
#     sec.axis =  dup_axis(trans=~./10,breaks = seq(0,0.1,0.02), name="Win Rate difference")
#   ) +
#   labs(title = glue::glue("{deck} Skill-Cap Gap Plot"),
#        subtitle = "Difference in Win-Rates",
#        caption = "Left Y-axis are the win-rates") +
#   theme_Publication() +
#   theme(axis.text.x = element_text(angle = 60, vjust = 0.85, hjust=1, size = 10)) +
#   scale_colour_Publication()
```

```{r war-on-yuumi, fig.width  = 12, fig.height = 8}
# 
# deck  <- decks_top[3]
# decks <- decks_top[4:20]
# # decks <- deck_min_100
# 
# MU_Master |>
#   filter(playerDeck==deck) |>
#   filter(opponentDeck %in% decks) |>
#   rename(muMaster=muWR) |>
#   mutate(w = muGames/sum(muGames)) |>
#   select(1,2,5,last_col()) |>
#   left_join(
#     MU_Diamond |>
#       filter(playerDeck==deck) |>
#       filter(opponentDeck %in% decks) |>
#       rename(muDiamond=muWR) |>
#       mutate(w = muGames/sum(muGames)) |>
#       select(1,2,5),
#       # select(1,2,5,last_col()),
#     by = c("playerDeck","opponentDeck")
#   ) |>
#   mutate(opponentDeck = factor(opponentDeck, levels = decks, ordered = TRUE) ) |>
#   arrange(opponentDeck) |>
#   mutate(diffMU = muMaster-muDiamond) |>
#   # pull(diffMU) -> vec_diff
#   mutate(mean_diffMU = cummean(diffMU)) |>
#   select(opponentDeck,mean_diffMU) |>
#   mutate(wr_label=scales::percent(mean_diffMU,accuracy = 0.1) ) -> diffDT
# 
# 
# 
# MU_Master |>
#   bind_rows(MU_Diamond) |>
#   filter(playerDeck==deck) |>
#   filter(opponentDeck %in% decks) |>
#   mutate(opponentDeck = factor(opponentDeck, levels = decks, ordered = TRUE) ) |>
#   mutate(rank = factor(rank, levels = c("master","diamond"), ordered = TRUE) ) |>
#   # mutate(opponentDeck = fct_reorder(opponentDeck, muGames, .desc = TRUE) ) |>
#   ggplot() +
#   geom_errorbar(aes(x=opponentDeck,ymin=LCI,ymax=UCI,color=rank),
#                 position = position_dodge(0.3),width = 0.2) +
#   geom_point(aes(x=opponentDeck,y=muWR,color = rank), position = position_dodge(0.3)) +
#   geom_line(data=diffDT,aes(x=opponentDeck,y=mean_diffMU*10,group = 1), size=1.2,linetype=2, color="darkviolet") +
#   geom_label_repel(
#     data=diffDT,aes(x=opponentDeck,y=mean_diffMU*10,label=wr_label,group = 1),
#     family = "Helvetica",fontface = "bold", size = 3.5, direction = "y", force = 3, hjust = 1, segment.size = .7, segment.alpha = .5, segment.linetype = "dotted", box.padding = .4,
#     segment.curvature = -0.1, segment.ncp = 3, segment.angle = 15, fill = "#f0f0f0", label.padding = 0, label.size = 0
#   ) +
#   expand_limits(y=0) +
#   scale_y_continuous(
#     breaks=seq(0,1,0.25),
#     # Add a second axis and specify its features
#     labels = scales::percent_format(accuracy = 1),
#     sec.axis =  dup_axis(trans=~./10,breaks = seq(0,0.1,0.02), name="Win Rate difference")
#   ) +
#   labs(title = glue::glue("{deck} Skill-Cap Gap Plot"),
#        subtitle = "Difference in Win-Rates",
#        caption = "Left Y-axis are the win-rates") +
#   theme_Publication() +
#   theme(axis.text.x = element_text(angle = 60, vjust = 0.85, hjust=1, size = 10)) +
#   scale_colour_Publication()
```

# Legal bla bla

This content was created under Riot Games' "Legal Jibber Jabber" policy using assets owned by Riot Games. Riot Games does not endorse or sponsor this project.
