---
title: "Meta & Decks (from Patch 3.8 WorldWalker)"
author: "by Legna"
base_url: https://www.llorr-stats.com
output:
  flexdashboard::flex_dashboard:
    navbar:
      - { icon: "fa-trophy", text: "MatchUps", href: "https://www.llorr-stats.com/static/mu.html", align: right }
      - { icon: "fa-home", href: "https://www.llorr-stats.com", align: right }
    orientation: row
    vertical_layout: fill
params:
  start:   "2022-05-25 18:00:00"
  end:     "2022-12-31 18:00:00"
  min_mu_games: 10  # min number of games for a MU
  last_season: "S13"
  max_top_pr:  12 # meta evolution decks
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo       = FALSE, 
  eval       = TRUE, 
  warning    = FALSE, 
  error      = FALSE, 
  message    = FALSE, 
  comment    = NA, 
  R.options  = list(width = 140, digits.secs=6), 
  dev.args   = list(bg = 'whitesmoke'), 
  fig.align  = 'center', 
  fig.width  = 12, 
  fig.height = 8, 
  fig.path   = glue::glue("images/"), 
  layout     = "l-page", 
  preview    = TRUE
)

#' R Option
options(scipen = 999)
source(file.path("C:", "LlorR", "scripts", "lor_main.R"))
source(file.path("C:", "LlorR", "scripts", "functions", "lor_constants.R"))
source(file.path("C:", "LlorR", "scripts", "functions", "lor_functions.R"))
xaringanExtra::use_panelset()
```

```{r constants}
# Precalculate user score colors to be used for custom cell rendering
get_score_color <- function(score) {
  blue_pal <- function(x) rgb(colorRamp(c("#9fc7df", "#416ea4"))(x), maxColorValue = 255)
  normalized <- score/100
  blue_pal(normalized)
}

last_update_box <- flexdashboard::valueBox(
  Sys.Date(), 
  caption = glue::glue("Last Update / Usually done around 5:00 UTC / 7:00 CET"), 
  icon = "fa-clock", 
  color = "#1A9850"
)

seq_date <- seq(lubridate::as_datetime(params$start), floor_date(lubridate::now(), unit = "day")+hours(18) , "day") #
```

```{r load-data}
# load DeckDT
LoR_Deck_RMD       <- fread(file.path("C:", "LlorR", "data", "raw", "LoR_DECK.csv"), na.strings = c("", NA), colClasses = "character")

# load Games DT
LoR_Match_DT_RMD <- list.files(path = file.path("C:", "LlorR", "data", "raw"), pattern = glue("^(.*)Temp_DT_{params$last_season}(.*)csv$"), full.names = T) |>
  str_subset(pattern = "Keys", negate = T) |>
  map_dfr(data.table::fread, header = T, na.strings = c("", NA), encoding = "UTF-8") |>
  mutate(server = if_else(server %in% c("sea", "asia"), "apac", server) )

LoR_Account_RMD <- list.files(path = file.path("C:", "LlorR", "data", "raw"), pattern = glue("^(.*)ACCOUNT(.*)csv$"), full.names = T) |>
  map_dfr(data.table::fread, colClasses = "character", header = T, na.strings = c("", NA), encoding = "UTF-8") |>
  mutate(activeShard = if_else(activeShard %in% c("sea", "asia"), "apac", activeShard) ) |>
  mutate(RiotID = glue::glue("{gameName}#{tagLine}")) |>
  # to be safe
  distinct(puuid, .keep_all = T)
```

```{r deck-fix}
# LoR_Deck_RMD <- archetype_pretty(LoR_Deck_RMD)
LoR_Deck_RMD <- update_and_save_deck(LoR_Deck_RMD,LoR_Match_DT_RMD)
LoR_Deck_RMD[ !is.na(archetype_pretty), archetype:=archetype_pretty ]
```

```{r prepara-data}
LoR_Melt_Matches_RMD <- LoR_Match_DT_RMD |>
  filter(game_type == "Ranked"  ) |>
  filter(game_start_time_utc %within% interval(lubridate::as_datetime(params$start), lubridate::as_datetime(params$end)) ) |>
  melt_match(LoR_Deck_RMD,LoR_Account_RMD)
```

# Stats (last 7days) {data-icon="fa-table"}

## Row

### Decks Performances

```{r stats-7days}
meta_7days <- reactable_meta(LoR_Melt_Matches_RMD,7)
meta_7days$meta_table
```

## Row {data-heigth="150"}

### Number of Games

```{r}
flexdashboard::valueBox(glue::glue("{meta_7days$nGames} Games"), 
                        caption = glue::glue("Number of Ranked Games - by (prev) Seasonal Players"), 
                        icon = "fa-table", 
                        color = "#a88b32")
```

### Number of Meta Decks

```{r}
flexdashboard::valueBox(glue::glue("{length(meta_7days$fct_meta)} Meta Decks"), 
                        caption = glue::glue("Decks with PlayRate with at least 1%"), 
                        icon = "fa-trophy", 
                        color = "#65c0a9")
```

### Number of Underdog Decks

```{r}
flexdashboard::valueBox(glue::glue("{length(meta_7days$fct_underdog)} Underdog Decks"), 
                        caption = glue::glue("Decks with positive WR and PR in 0.1% to 1%"), 
                        icon = "fa-dog", 
                        color = "#ff7f24")
```

### Last-Update

```{r}
last_update_box
```

# Stats (whole patch) {data-icon="fa-table"}

## Row

### Decks Performances

```{r stats-all}
meta_all <- reactable_meta(LoR_Melt_Matches_RMD)
meta_all$meta_table
```

## Row {data-heigth="150"}

### Number of Games

```{r value-games}
nGames <- NROW(LoR_Melt_Matches_RMD)

flexdashboard::valueBox(glue::glue("{meta_all$nGames} Games"), 
                        caption = glue::glue("Number of Ranked Games - by Seasonal Players"), 
                        icon = "fa-table", 
                        color = "#a88b32")
```

### Number of Meta Decks

```{r value-meta}
flexdashboard::valueBox(glue::glue("{length(meta_all$fct_meta)} Meta Decks"), 
                        caption = glue::glue("Decks with PlayRate with at least 1%"), 
                        icon = "fa-trophy", 
                        color = "#65c0a9")
```

### Number of Underdog Decks

```{r value-underdog}
flexdashboard::valueBox(glue::glue("{length(meta_all$fct_underdog)} Underdog Decks"), 
                        caption = glue::glue("Decks with positive WR and PR in 0.1% to 1%"), 
                        icon = "fa-dog", 
                        color = "#ff7f24")
```

### Last Update

```{r}
last_update_box
```

# Fresh Stats (last 24 hours) {data-icon="fa-table"}

```{r}
LoR_Melt_24hrs <- LoR_Melt_Matches_RMD |>
  filter(game_start_time_utc %within% interval(today()+hours(18)-days(2), today()+hours(18)-days(1)) ) |>
  distinct(match_key, playerPuuid, .keep_all = T)
```

## Row

### Previous Day

```{r 24hrs-process-winRate}
WR_tbl_24h <- LoR_Melt_24hrs |>
  win_rates(details = T, server = F) |>
  filter(playerDeck %!in% c(meta_7days$fct_meta, meta_all$fct_meta, meta_7days$fct_underdog, meta_all$fct_underdog) ) |>
  filter(WR > 0.5 ) |>
  slice_max(nGames, n = 50, with_ties = F) |>
  select(-lower, -upper)

deck_code_tbl_24hrs  <- LoR_Melt_24hrs |>
  filter(playerDeck %in% c(WR_tbl_24h$playerDeck) ) |>
  mutate(playerDeck = factor(playerDeck, ordered = TRUE, 
                              levels = c(WR_tbl_24h$playerDeck) )
         ) |>
  group_by(server, playerDeck, deck_code ) |>
  summarise( n = n() ) |>
  group_by(playerDeck) |>
  slice_max(n, n = 10) |>
  ungroup() |>
  mutate(link = glue::glue("<a href='https://runeterra.ar/decks/code/{deck_code}'>{deck_code}</a>"), 
         server = str_to_title(server) ) |>
  select(playerDeck, n, link, server)
```


```{r 24hrs-react-winRate}
with_tooltip <- function(value, tooltip) {
  htmltools::tags$abbr(style = "text-decoration: underline; text-decoration-style: dotted; cursor: help", 
            title = tooltip, value)
}

WR_tbl_24h |>
  reactable(
    # groupBy = "playerDeck", 
    searchable = TRUE, 
    bordered = TRUE, 
    # wrap = FALSE, 
    highlight = TRUE, 
    striped = TRUE, 
    pagination = FALSE, 
    fullWidth = T, 
    # defaultSorted = list(LMI = "desc"), 
    defaultColDef = colDef(
      align = "center", 
      minWidth = 100, 
      # headerStyle = list(background = "steelblue", color="white")
    ), 
    details = function(index) {
      # index = 1
      deckdata <- deck_code_tbl_24hrs[ deck_code_tbl_24hrs$playerDeck == WR_tbl_24h$playerDeck[index], ]
      reactable(
        deckdata, 
        fullWidth = F, 
        defaultColDef = colDef(
          style = list( fontSize = 13 ), 
          html = TRUE
          ), 
        theme = reactableTheme( headerStyle = list(background = "red", color="white", fontSize = 13 ) ), 
        columns = list(
          n = colDef(name = "#Games", minWidth = 75 ), 
          link = colDef(name = "DeckCode - Most played lists", minWidth = 750, style = list( fontSize = 9 ) ), 
          # playerDeck = colDef(name = "Archetype", minWidth = 150 ), 
          playerDeck = colDef(show = F), 
          server = colDef(name = "Server", minWidth = 100 )
          ) )}, 
    columns = list(
      playerDeck = colDef(name = "Archetype", minWidth = 250, align = "left", header = with_tooltip("Archetype", "I still have to decide what to display here, so for now I'll simply but the decks with at least 10 games, before WR that did't appear in the other sections (whole-Patch and 7days).")), 
      nWin   = colDef(name = "#Win"), 
      nGames = colDef(name = "#Games"), 
      playrate = colDef(name = "PlayRate", format = colFormat(percent = TRUE, digits = 1) ), 
      type = colDef(name = "Type"), 
      # LMI = colDef(name = "LMI"), 
      tier = colDef(name = "Tier", minWidth = 200, align = "left"), 
      CI = colDef(name = "Conf.Interval", minWidth = 200, align = "center"), 
      WR = colDef(name = "WinRate", format = colFormat(percent = TRUE, digits = 1) )
    )

  )
```

## Row {data-heigth="150"}

### Time Frame

```{r}
flexdashboard::valueBox(glue::glue("24 Hours Time Frame"), 
                        caption = glue::glue("from {Sys.Date()+hours(18)-days(2)} to {Sys.Date()+hours(18)-days(1)}"), 
                        icon = "fa-clock", 
                        # color = "lightgreen"
                        color = "red")
```


### Last Update

```{r}
last_update_box
```

# Meta-Evolution {data-icon="fa-chart-line"}

## Row {data-heigth="750"}

### Graph

```{r meta-evo-temp}
#| fig.width=20, 
#| fig.height=8

hourly_meta_plot <- plot_hourly_meta_deck(data = LoR_Melt_Matches_RMD, max_top_pr = params$max_top_pr)

hourly_meta_plot

hourly_meta_plot <- plot_hourly_meta_deck(data = LoR_Melt_Matches_RMD, prev_days = 3, max_top_pr = params$max_top_pr)

hourly_meta_plot

ggsave(filename = "images/meta-evo-area-temp.png", plot = hourly_meta_plot, width = 12, height = 8) |> invisible()
```

```{r meta-evo-line}
#| fig.width=20, 
#| fig.height=8

hourly_meta_lines <- plot_playrate_by_time(data = LoR_Melt_Matches_RMD,prev_days = 7,max_top_pr = params$max_top_pr)

hourly_meta_lines

ggsave(filename = "images/meta-evo-line-temp.png", plot = hourly_meta_plot, width = 12, height = 8) |> invisible()
```

## Row {data-heigth="150"}

### Number of Players

```{r value-player-base}
flexdashboard::valueBox(glue::glue("{LoR_Account_RMD[seasonal=='seasonal', .N]}"), 
                        caption = glue::glue("Seasonal Players"), 
                        icon = "fa-medal", 
                        color = "#65c0a9")
```

### Last Update

```{r}
last_update_box
```

# Downloads and Informations {data-orientation="columns" data-icon="fa-info-circle"}

## Column {data-width="450"}

### Archetypes Guide

current aggregations applied to archetypes (Champions+Regions)

```{r archetype}
tbl_archetype
```

## Column {data-width="550"}

### LMI - Tiers

```{r info-gt-lmi}
tribble( 
  ~Tier, ~Note, 
  "Best Choice ~ T0", "with LMI >= 97.5", 
  "Good ~T1", "with LMI in [85, 97.5)", 
  "Could do better ~T2", "with LMI in [50, 85)", 
  "Meh, either bad or not played/ignored ~T3", "with LMI < 50"
  ) |>
  gt() |>
  tab_header(
    title = glue::glue("LMI Tiers")
  ) |>
  gtExtras::gt_theme_nytimes()
```

### Donwload

```{r}
downloadthis::download_file(
  path = file.path("images/meta-evo-temp.png"), 
  # path = system.file("assets/css/all.min.css", package = "downloadthis"), 
  button_label = "Download PlayRates over time as .png", 
  button_type = "primary", 
  has_icon = TRUE, 
  icon = "fa fa-save", 
  self_contained = FALSE
)
```


### General info

When I refer to games it's always refering a single playerDeck. So, if I have the information of 1 match it's equivalent to 2 games.

#### Credits

<!-- Special thanks to Trinathan and bA1ance for the recent support (ᐛ)ᕗ  -->
