---
title: "Meta & Decks (from Patch 3.21 - The Darkin Saga - World Ender)"
author: "by Legna"
base_url: https://www.llorr-stats.com
output:
  flexdashboard::flex_dashboard:
    theme:
      bg: "#101010"
      fg: "#FDF7F7"
      primary: "#ED7979"
    navbar:
      - { icon: "fa-trophy", text: "MatchUps", href: "https://www.llorr-stats.com/static/mu.html", align: right }
      - { icon: "fa-home", href: "https://www.llorr-stats.com", align: right }
    orientation: row
    vertical_layout: fill
params:
  start:    "2022-11-09 18:00:00"
  end:      "2024-11-09 18:00:00"
  min_mu_games: 10 # min number of games for a MU
  max_top_pr:   12  # meta evolution decks
  last_season: "S17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo       = FALSE, 
  eval       = TRUE, 
  warning    = FALSE, 
  error      = FALSE, 
  message    = FALSE, 
  comment    = NA, 
  R.options  = list(width = 140, digits.secs=6), 
  dev.args   = list(bg = 'whitesmoke'), 
  fig.align  = 'center', 
  fig.width  = 12, 
  fig.height = 8, 
  fig.path   = glue::glue("images/"), 
  layout     = "l-page", 
  preview    = TRUE
)

source(file.path("C:", "LlorR", "scripts", "lor_main.R"))
source(file.path("C:", "LlorR", "scripts", "functions", "lor_functions.R"))
# source(file.path("C:", "LlorR", "scripts", "functions", "lor_constants.R"))
xaringanExtra::use_panelset()
```

```{css}
.value-box {
  height: 100px;
}
```

```{r constants}
last_update_box <- flexdashboard::valueBox(
  Sys.Date(), 
  caption = glue::glue("Last Update / Usually done around 5:00 UTC / 7:00 CET"), 
  icon = "fa-clock", 
  color = "#1A9850"
)

seq_date <- seq(lubridate::as_datetime(params$start), floor_date(lubridate::now(), unit = "day")+hours(18) , "day") #
```

```{r load-data}
meta_7days <- readr::read_rds(file = file.path("C:", "LlorR", "data", "clean","meta_week.rds") )
meta_all   <- readr::read_rds(file = file.path("C:", "LlorR", "data", "clean","meta_all.rds") )

summary_info <- readr::read_rds(file = file.path("C:", "LlorR", "data", "clean","summary_info.rds") )

hourly_master_plot <- readr::read_rds( file = file.path("C:", "LlorR", "data", "clean","hourly_master_plot.rds") )
hourly_master_line <- readr::read_rds( file = file.path("C:", "LlorR", "data", "clean","hourly_master_line.rds") )
hourly_diamond_plot <- readr::read_rds( file = file.path("C:", "LlorR", "data", "clean","hourly_diamond_plot.rds") )
hourly_diamond_line <- readr::read_rds( file = file.path("C:", "LlorR", "data", "clean","hourly_diamond_line.rds") )

LoR_Melt_24hrs <- data.table::fread(
  file = file.path("C:", "LlorR", "data", "clean","ranked_24hrs.csv"),
  header = T, na.strings = c("", NA), encoding = "UTF-8"
)
```

Stats (last 7days) {data-icon="fa-table" data-orientation=rows}
================================

Row {data-heigth="125"}
-----------------------------------------------------------------------

### Number of Games

```{r}
flexdashboard::valueBox(glue::glue("{meta_7days$nGames} Games"), 
                        caption = glue::glue("Number of Ranked Games - Master"), 
                        icon = "fa-table", 
                        color = "#a88b32")
```

### Number of Meta Decks

```{r}
flexdashboard::valueBox(glue::glue("{length(meta_7days$fct_meta)} Meta Decks"), 
                        caption = glue::glue("Decks with PlayRate with at least 1%"), 
                        icon = "fa-trophy", 
                        color = "#65c0a9")
```

### Number of Underdog Decks

```{r}
flexdashboard::valueBox(glue::glue("{length(meta_7days$fct_underdog)} Underdog Decks"), 
                        caption = glue::glue("Decks with positive WR and PR in 0.1% to 1%"), 
                        icon = "fa-dog", 
                        color = "#ff7f24")
```

### Last-Update

```{r}
last_update_box
```

Row {data-heigth="875"}
-----------------------------------------------------------------------

### Decks Performances

```{r}
meta_7days$meta_table
```

Meta-Evolution {data-icon="fa-chart-line"}
================================

Row {data-heigth="125"}
-----------------------------------------------------------------------

### Master

```{r value-player-master}
flexdashboard::valueBox(value = summary_info$nMaster,
                        caption = glue::glue("Master Players"), 
                        icon = "fa-medal", 
                        color = "#65c0a9")
```

### Diamond

```{r value-player-diamond}
flexdashboard::valueBox(value = summary_info$nDiamond, 
                        caption = glue::glue("HighDiamond Players"), 
                        icon = "fa-diamond", 
                        color = "#ff7f24")
```

### Last Update

```{r}
last_update_box
```

Row {.tabset}
-----------------------------------------------------------------------

### Master

```{r meta-evo-master, fig.width=20, fig.height=8}
hourly_master_plot + hourly_master_line
```

### Diamond

```{r meta-evo-diamond, fig.width=20, fig.height=8}
hourly_diamond_plot + hourly_diamond_line
```

Stats (whole patch) {data-icon="fa-table"}
================================

Row 
-----------------------------------------------------------------------

### Number of Games

```{r value-games}
flexdashboard::valueBox(glue::glue("{meta_all$nGames} Games"), 
                        caption = glue::glue("Number of Ranked Games - by Master players"), 
                        icon = "fa-table", 
                        color = "#a88b32")
```

### Number of Meta Decks

```{r value-meta}
flexdashboard::valueBox(glue::glue("{length(meta_all$fct_meta)} Meta Decks"), 
                        caption = glue::glue("Decks with PlayRate with at least 1%"), 
                        icon = "fa-trophy", 
                        color = "#65c0a9")
```

### Number of Underdog Decks

```{r value-underdog}
flexdashboard::valueBox(glue::glue("{length(meta_all$fct_underdog)} Underdog Decks"), 
                        caption = glue::glue("Decks with positive WR and PR in 0.1% to 1%"), 
                        icon = "fa-dog", 
                        color = "#ff7f24")
```

### Last Update

```{r}
last_update_box
```

Row {data-heigth="875"}
-----------------------------------------------------------------------

### Decks Performances

```{r stats-all}
meta_all$meta_table
```

Fresh Stats (last 24 hours) {data-icon="fa-table"}
================================

Row {data-heigth="125"}
-----------------------------------------------------------------------

### Time Frame

```{r}
flexdashboard::valueBox(glue::glue("24 Hours Time Frame"), 
                        caption = glue::glue("from {Sys.Date()+hours(18)-days(2)} to {Sys.Date()+hours(18)-days(1)}"), 
                        icon = "fa-clock", 
                        # color = "lightgreen"
                        color = "red")
```


### Last Update

```{r}
last_update_box
```

Row {data-heigth="875"}
-----------------------------------------------------------------------

### Previous Day

```{r 24hrs-process-winRate}
if (NROW(LoR_Melt_24hrs)>0) {
  
  WR_tbl_24h <- LoR_Melt_24hrs |>
  win_rates(details = T, server = F) |>
  filter(playerDeck %!in% c(meta_7days$fct_meta, meta_all$fct_meta, meta_7days$fct_underdog, meta_all$fct_underdog) ) |>
  filter(WR > 0.5 ) |>
  slice_max(nGames, n = 50, with_ties = F) |>
  select(-lower, -upper)

deck_code_tbl_24hrs  <- LoR_Melt_24hrs |>
  filter(playerDeck %in% c(WR_tbl_24h$playerDeck) ) |>
  mutate(playerDeck = factor(playerDeck, ordered = TRUE, 
                              levels = c(WR_tbl_24h$playerDeck) )
         ) |>
  group_by(server, playerDeck, deck_code ) |>
  summarise( n = n() ) |>
  group_by(playerDeck) |>
  slice_max(n, n = 10) |>
  ungroup() |>
  mutate(link = glue::glue("<a href='https://runeterra.ar/decks/code/{deck_code}'>{deck_code}</a>"), 
         server = str_to_title(server) ) |>
  select(playerDeck, n, link, server)
  
with_tooltip <- function(value, tooltip) {
  htmltools::tags$abbr(style = "text-decoration: underline; text-decoration-style: dotted; cursor: help", 
            title = tooltip, value)
}

WR_tbl_24h |>
  reactable(
    # groupBy = "playerDeck", 
    searchable = TRUE, 
    bordered = TRUE, 
    # wrap = FALSE, 
    highlight = TRUE, 
    striped = TRUE, 
    pagination = FALSE, 
    fullWidth = T, 
    # defaultSorted = list(LMI = "desc"), 
    defaultColDef = colDef(
      align = "center", 
      minWidth = 100, 
      # headerStyle = list(background = "steelblue", color="white")
    ), 
    details = function(index) {
      # index = 1
      deckdata <- deck_code_tbl_24hrs[ deck_code_tbl_24hrs$playerDeck == WR_tbl_24h$playerDeck[index], ]
      reactable(
        deckdata, 
        fullWidth = F, 
        defaultColDef = colDef(
          style = list( fontSize = 13 ), 
          html = TRUE
          ), 
        theme = reactableTheme(
          headerStyle = list(background = "red", color="white", fontSize = 13), 
          rowStyle = list(height = "45px")
        ), 
        columns = list(
          n = colDef(name = "#Games", minWidth = 75 ), 
          link = colDef(name = "DeckCode - Most played lists", minWidth = 750, style = list( fontSize = 9 ) ), 
          # playerDeck = colDef(name = "Archetype", minWidth = 150 ), 
          playerDeck = colDef(show = F), 
          server = colDef(name = "Server", minWidth = 100 )
          ) )}, 
    columns = list(
      playerDeck = colDef(name = "Archetype", minWidth = 250, align = "left", header = with_tooltip("Archetype", "I still have to decide what to display here, so for now I'll simply but the decks with at least 10 games, before WR that did't appear in the other sections (whole-Patch and 7days).")), 
      nWin   = colDef(name = "#Win"), 
      nGames = colDef(name = "#Games"), 
      playrate = colDef(name = "PlayRate", format = colFormat(percent = TRUE, digits = 1) ), 
      type = colDef(name = "Type"), 
      # LMI = colDef(name = "LMI"), 
      tier = colDef(name = "Tier", minWidth = 200, align = "left"), 
      CI = colDef(name = "Conf.Interval", minWidth = 200, align = "center"), 
      WR = colDef(name = "WinRate", format = colFormat(percent = TRUE, digits = 1) )
    )

  )

}
```

Downloads and Informations {data-orientation="columns" data-icon="fa-info-circle"}
================================

Column {data-width="450"}
-----------------------------------------------------------------------

### Archetypes Guide

current aggregations applied to archetypes (Champions+Regions)

```{r archetype}
tbl_archetype
```

Column {data-width="550"}
-----------------------------------------------------------------------

### LMI - Tiers

```{r info-gt-lmi}
tribble( 
  ~Tier, ~Note, 
  "Best Choice ~ T0", "with LMI >= 97.5", 
  "Good ~T1", "with LMI in [85, 97.5)", 
  "Could do better ~T2", "with LMI in [50, 85)", 
  "Meh, either bad or not played/ignored ~T3", "with LMI < 50"
  ) |>
  gt() |>
  tab_header(
    title = glue::glue("LMI Tiers")
  ) |>
  gtExtras::gt_theme_nytimes()
```

### General info

When I refer to games it's always refering a single playerDeck. So, if I have the information of 1 match it's equivalent to 2 games.
