---
params:
  ind: "S2021-08-14"
  # patch: "Patch 2.17 - Week 1"
  title: "THE SEASONAL REPORT IS VAST (n°2)"
  description: "Seasonal Tournament - Beyond the Bandlewood - Open Rounds"
  cardlurl: "https://dd.b.pvp.net/latest/set5/en_us/img/cards/05BC116-full.png"
  seasonalDate: "2021-10-09"
  # prev:  "2021-10-02 21:00:00" #UTC tz / 'current' previous week start
  # start: "2021-10-09 21:00:00" #UTC tz / 'current' week start
  # end:   "2021-10-13 21:00:00" #UTC tz / 'current' week end
  skip:  3200000  # ~ Patch 2.16

title: | 
  `r params$title`
description: |
  `r params$description`
base_url: https://www.llorr-stats.com
preview: |
  `r params$cardlurl`
author:
  - name: Valentino (Legna) Vazzoler
date: 10-08-2021
output:
 distill::distill_article:
    toc: true
    toc_float: true
    toc_depth: 3
    self_contained: false
citation: false
draft: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  eval = TRUE,
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  comment = NA,
  R.options = list(width = 140,
                   digits.secs=6),
  dev.args = list(bg = 'transparent'), # make graphics with transparent background
  fig.align = 'center',
  fig.width=12,
  fig.height=8,
  engine.path = list(
    python = 'C:/anaconda/'   # -> use_python("C:/anaconda/")
  ),
  #'distill options
  layout="l-page",
  preview=FALSE
)

#' R Option
options(scipen = 999)
source(file.path("C:","LlorR","scripts","lor_main.R" ))
xaringanExtra::use_panelset()

require(grid)
require(cowplot)
```

```{r panelset-style}
xaringanExtra::style_panelset_tabs(
  font_family = "Helvetica",
  active_foreground = "white",
  hover_foreground = "black",
  hover_border_color = "black",
  active_background = "#007fff"
  )
```

```{r create-TimeBlcok}
timeBlock.1.start <- ymd_hms(glue::glue("{params$seasonalDate} 11:55:00")) + lubridate::minutes(5)
timeBlock.2.start <- ymd_hms(glue::glue("{params$seasonalDate} 13:00:00")) + lubridate::minutes(5)
timeBlock.3.start <- ymd_hms(glue::glue("{params$seasonalDate} 14:05:00")) + lubridate::minutes(5)
timeBlock.4.start <- ymd_hms(glue::glue("{params$seasonalDate} 15:10:00")) + lubridate::minutes(5)
timeBlock.5.start <- ymd_hms(glue::glue("{params$seasonalDate} 16:15:00")) + lubridate::minutes(5)
# 30 min break
timeBlock.6.start <- ymd_hms(glue::glue("{params$seasonalDate} 17:45:00")) + lubridate::minutes(5)
timeBlock.7.start <- ymd_hms(glue::glue("{params$seasonalDate} 18:50:00")) + lubridate::minutes(5)
timeBlock.8.start <- ymd_hms(glue::glue("{params$seasonalDate} 19:55:00")) + lubridate::minutes(5)
timeBlock.9.start <- ymd_hms(glue::glue("{params$seasonalDate} 21:00:00")) + lubridate::minutes(5)

timeBlock.1.end <- ymd_hms(glue::glue("{params$seasonalDate} 11:55:00")) + lubridate::minutes(5) + lubridate::minutes(60)
timeBlock.2.end <- ymd_hms(glue::glue("{params$seasonalDate} 13:00:00")) + lubridate::minutes(5) + lubridate::minutes(60)
timeBlock.3.end <- ymd_hms(glue::glue("{params$seasonalDate} 14:05:00")) + lubridate::minutes(5) + lubridate::minutes(60)
timeBlock.4.end <- ymd_hms(glue::glue("{params$seasonalDate} 15:10:00")) + lubridate::minutes(5) + lubridate::minutes(60)
timeBlock.5.end <- ymd_hms(glue::glue("{params$seasonalDate} 16:15:00")) + lubridate::minutes(5) + lubridate::minutes(60)
# 30 min break
timeBlock.6.end <- ymd_hms(glue::glue("{params$seasonalDate} 17:45:00")) + lubridate::minutes(5) + lubridate::minutes(60)
timeBlock.7.end <- ymd_hms(glue::glue("{params$seasonalDate} 18:50:00")) + lubridate::minutes(5) + lubridate::minutes(60)
timeBlock.8.end <- ymd_hms(glue::glue("{params$seasonalDate} 19:55:00")) + lubridate::minutes(5) + lubridate::minutes(60)
timeBlock.9.end <- ymd_hms(glue::glue("{params$seasonalDate} 21:00:00")) + lubridate::minutes(5) + lubridate::minutes(60)
```

```{r raw-data}
# skip.dt <-fread(file.path("C:","LlorR","data","raw","skip_row.csv")  )
# skip.dt

#' load gameDT
#'############
file.DT <- file.path("C:","LlorR","data","raw","LoR_MatchDT.csv")
header        <- fread(file.DT, header = FALSE, na.strings = c("",NA), nrows = 1, stringsAsFactors = FALSE)
LoR.Match.RMD <- fread(file.DT, header = FALSE, na.strings = c("",NA), skip = params$skip )
colnames(LoR.Match.RMD) <- unlist(header,use.names = F)

#' load Seasonal DB
#'############
# LoR.Seasonal <- fread(file.path("C:","LlorR","data","raw","LoR_Seasonal.csv"), header = T, na.strings = c("",NA) )[ game_start_time_utc >= with_tz(force_tz(timeBlock.1.start,"Japan"),"UTC") , ]
LoR.Seasonal <- fread(file.path("C:","LlorR","data","raw","LoR_SeasonalDT.csv"), header = T, na.strings = c("",NA) ) |>
  filter( game_mode == "SeasonalTournamentLobby"  ) |>
  filter( game_start_time_utc >= with_tz(force_tz(timeBlock.1.start,"Japan"),"UTC") &
            game_start_time_utc < (with_tz(force_tz(timeBlock.1.start,"Japan"),"UTC")+lubridate::days(2)) )

#' load Account
#'#############
LoR.Account.RMD <- fread(file.path("C:","LlorR","data","raw","LoR_ACCOUNT.csv"),
                         header=T, na.strings = c("",NA), encoding = 'UTF-8') |>
  mutate( RiotID = sprintf("%s#%s",gameName,tagLine) )

#' load DeckDT
#'############
LoR.Deck        <- fread(file.path("C:","LlorR","data","raw","LoR_DECK.csv"),na.strings = c("",NA))
```

```{r archetype-fix}
#' Limit the Deck DT to make the fixes much faster
deck_filter <- rbind(LoR.Match.RMD,
                     LoR.Seasonal) |>
  filter( game_start_time_utc >= (with_tz(force_tz(timeBlock.1.start,"Japan"),"UTC")-lubridate::days(7)) & game_start_time_utc < (with_tz(force_tz(timeBlock.1.start,"Japan"),"UTC")+days(2)) ) |>
  #' Base filters
  filter( game_type=="Ranked" | game_mode == "SeasonalTournamentLobby" ) |>
  select(deck_code_1,deck_code_2) |>
  pivot_longer( cols = contains("deck_code"),values_to = "decks" ) |>
  filter(decks!="") |>
  distinct(decks)

LoR.Deck <- LoR.Deck[deck_code %in% deck_filter$decks]

#' Archetype-Fix
#'##############
source(file.path("C:","LlorR","scripts","functions","lor_archetype.R"))
```

```{r prepare-seasonal-data}
#' Melt tbl
#'#########
LoR.Melt.Seasonal <- LoR.Seasonal |>
  select( -ends_with("_3"),-ends_with("_4")  ) |>
  left_join(LoR.Deck[,.(deck_code,playerDeck_1=archetype)],  by=c("deck_code_1"="deck_code")) |>
  left_join(LoR.Deck[,.(deck_code,opponentDeck_1=archetype)],by=c("deck_code_2"="deck_code")) |>
  rename( playerPuuid_1 = puuid_1, playerPuuid_2 = puuid_2 ) |>
  mutate( playerDeck_2 = opponentDeck_1, opponentDeck_2 = playerDeck_1, opponentPuuid_1 = playerPuuid_2, opponentPuuid_2 = playerPuuid_1 ) |>
  pivot_longer(cols = c(ends_with("_1"),ends_with("_2")),
               names_to = c(".value"),
               names_pattern = "(.*)_[0-9]"
               ) |>
  #' finish 'process' data
  left_join(LoR.Account.RMD[,.(puuid,playergameName=gameName,playerID=RiotID)]   ,by=c("playerPuuid"="puuid")) |>
  left_join(LoR.Account.RMD[,.(puuid,opponentgameName=gameName,opponentID=RiotID)] ,by=c("opponentPuuid"="puuid")) |>
  left_join(LoR.Deck |> select(!archetype),by=c("deck_code","factions")) |>
  as.data.table()

```

```{r prepare-ladder-data}
#' Melt tbl
#'#########
LoR.Melt.Matches.RMD <- LoR.Match.RMD |>
  filter( game_type=="Ranked" ) |>
  filter( game_start_time_utc >= (with_tz(force_tz(timeBlock.1.start,"Japan"),"UTC")-lubridate::days(7)) & game_start_time_utc < with_tz(force_tz(timeBlock.1.start,"Japan"),"UTC") ) |>
  select( -ends_with("_3"),-ends_with("_4")  ) |>
  left_join(LoR.Deck[,.(deck_code,playerDeck_1=archetype)],  by=c("deck_code_1"="deck_code")) |>
  left_join(LoR.Deck[,.(deck_code,opponentDeck_1=archetype)],by=c("deck_code_2"="deck_code")) |>
  rename( playerPuuid_1 = puuid_1, playerPuuid_2 = puuid_2 ) |>
  mutate( playerDeck_2 = opponentDeck_1, opponentDeck_2 = playerDeck_1, opponentPuuid_1 = playerPuuid_2, opponentPuuid_2 = playerPuuid_1 ) |>
  pivot_longer(cols = c(ends_with("_1"),ends_with("_2")),
               names_to = c(".value"),
               names_pattern = "(.*)_[0-9]"
               ) |>
  #' finish 'process' data
  left_join(LoR.Account.RMD[,.(puuid,playerID=RiotID)]   ,by=c("playerPuuid"="puuid")) |>
  left_join(LoR.Account.RMD[,.(puuid,opponentID=RiotID)] ,by=c("opponentPuuid"="puuid")) |>
  left_join(LoR.Deck |> select(!archetype),by=c("deck_code","factions")) |>
  as.data.table()
```

```{r}
# LoR.Melt.Seasonal[ is.na(playerDeck), .N ]
# LoR.Melt.Matches.RMD[ is.na(playerDeck), .N ]
```


```{r create-lineUp-DT}
LineUp.DT <- LoR.Melt.Seasonal |>
  group_by(playerID,playergameName,server) |>
  summarise( listDeck=list(unique(playerDeck)),listCode=list(unique(deck_code)) ) |>
  ungroup()

LineUp.DT <- LineUp.DT |>
  group_by( playerID ) |>
  summarise( map_df(.x = listCode, .f = ~assignLineUp(.x) )) |>
  ungroup() |>
  right_join(LineUp.DT, by = "playerID") |>
  #' quality filter
  filter( !is.na(deck_1) ) |>
  rename("code_1"="deck_1","code_2"="deck_2","code_3"="deck_3" ) |>
  left_join( LoR.Deck |>select(deck_code,deck_1=archetype),by=c("code_1"="deck_code") ) |>
  left_join( LoR.Deck |>select(deck_code,deck_2=archetype),by=c("code_2"="deck_code") ) |>
  left_join( LoR.Deck |>select(deck_code,deck_3=archetype),by=c("code_3"="deck_code") ) |>
  #' quality filter
  filter( !is.na(deck_1) ) |>
  mutate(LU = purrr::pmap_chr(list(x = deck_1,y = deck_2,z = deck_3), ~  glue::glue_collapse(na.omit(sort(c(..1,..2,..3))), sep = " - ")   )  )
```

```{r ompute-MU-ladder}
#' playrates by presence in a LineUp, not games played
playRates.byLU <- LineUp.DT |>
  select(contains("deck_")) |>
  unlist(use.names = F) |>
  {\(x) tabyl(x,show_na = F)}() |>
  arrange(desc(n))  |>
  #' account for the presence of 3 decks
  mutate(percent = 3*percent ) |>
  rename( 'playerDeck'=1 )

#' WR tbl
#'#######
WR.DT <- LoR.Melt.Seasonal |>
  filter(game_outcome!="tie") |>
  group_by(playerDeck,factions) |>
  summarise(
    nWin   = sum(game_outcome=="win"),
    nGames = n(),
    WR=mean(game_outcome=="win")
  ) |> 
  ungroup() |>
  # mutate( factions = str_remove_all(factions, pattern = paste(c("_Name","faction_"), collapse = "|")) ) |>
  left_join(playRates.byLU, by="playerDeck" ) |>
  rename( "playrate"="percent" )

# DT[, .(agra = sum(a), agrb = mean(b)), by=category]
# WR.DT <- LoR.Melt.Seasonal[game_outcome!="tie", 
#                            .( nWin = sum(game_outcome=="win"),
#                               nGames = .N,
#                               WR=mean(game_outcome=="win") ), by=.(playerDeck,factions)][playRates.byLU, on = 'playerDeck']

#' MU tbl the date is already filtered
#'####################################
MUtbl <- LoR.Melt.Seasonal |>
  filter( game_outcome != "tie" ) |>
  select( playerDeck,opponentDeck,game_outcome,server,factions ) |>
  group_by(playerDeck,opponentDeck) |>
  summarise(
    muWin   = sum(game_outcome=="win"),
    muGames = n(),
    muWR=mean(game_outcome=="win")
    ) |>
  ungroup() |>
  mutate( CI   = map2_df(.x=muWin,.y = muGames, .f = ~binom::binom.confint(.x,.y,0.95,methods="exact")[,c("lower","upper")] ) ) |>
  chop(CI) |>
  unnest(CI) |>
  mutate( okCI = map2_lgl(.x = lower,.y = upper, ~ !between(0.50,.x,.y) ) ) |>
  mutate( direction = ifelse(muWR>0.50,"POS","NEG") ) |>
  mutate( direction = replace(direction,direction==0.50,"TIE") ) |>
  mutate( CI := glue::glue("({scales::percent(lower,accuracy = 0.1)}-{scales::percent(upper,accuracy = 0.1)})" ) ) |>
  left_join(WR.DT[,c("playerDeck","playrate")],by="playerDeck")
```

```{r compute-MU}
#' WR tbl
#'#######
ladder.WR.DT <- LoR.Melt.Matches.RMD |>
  filter(game_outcome!="tie") |>
  group_by(playerDeck,factions) |>
  summarise( 
    nWin   = sum(game_outcome=="win"),
    nGames = n(),
    WR=mean(game_outcome=="win")
  ) |>
  ungroup() |>
  mutate( playrate = nGames/sum(nGames) )

#' MU tbl the date is already filtered
#'####################################
ladder.MUtbl <- LoR.Melt.Matches.RMD |>
  filter( game_outcome != "tie" ) |>
  select( playerDeck,opponentDeck,game_outcome,server,factions ) |>
  group_by(playerDeck,opponentDeck) |>
  summarise(
    muWin   = sum(game_outcome=="win"),
    muGames = n(),
    muWR=mean(game_outcome=="win")
    ) |>
  ungroup() |>
  mutate( CI   = map2_df(.x=muWin,.y = muGames, .f = ~binom::binom.confint(.x,.y,0.95,methods="exact")[,c("lower","upper")] ) ) |>
  chop(CI) |>
  unnest(CI) |>
  mutate( okCI = map2_lgl(.x = lower,.y = upper, ~ !between(0.50,.x,.y) ) ) |>
  mutate( direction = ifelse(muWR>0.50,"POS","NEG") ) |>
  mutate( direction = replace(direction,direction==0.50,"TIE") ) |>
  mutate( CI := glue::glue("({scales::percent(lower,accuracy = 0.1)}-{scales::percent(upper,accuracy = 0.1)})" ) ) |>
  left_join(WR.DT[,c("playerDeck","playrate")],by="playerDeck")
```
# Data

```{r account-info}
nSeasonal = LoR.Melt.Seasonal |>
  group_by(server) |>
  distinct(playerID) |>
  count() |>
  as.data.table()

# nSeasonal
```

Number of (Ranked) matches analyzed **`r format(NROW(LoR.Seasonal),scientific = F)`** or **`r format(NROW(LoR.Melt.Seasonal),scientific = F)`** games.

Last Update: `r format(Sys.time(),format = "%Y-%m-%d %H:%M")` 

`r kableExtra::text_spec("Note :", color = "red")` following my recent analysis the following decks:

* Akshan / Sivir (IO/SH)

* Sivir / Zed

* Akshan / Sivir / Zed

Have been aggregated into a single archetype: "ASZ - Sivir Ionia"

In addition a quick fix to account for the Rubin-baits (burn decks that pretend to be other archetypes) decks have been applied and they are called:

* RubinBait - Draven / Ezreal

* RubinBait - Draven / Sion

* RubinBait - Caitlyn / Draven - not make from Rubin but same logic

```{r create-gt-summary}
gtSeasonal <- tibble( server = c("asia","europe","americas"),
        players = c(glue::glue("{ifelse(length(nSeasonal[server=='asia',n])==0,0,nSeasonal[server=='asia',n])}/(?)"),
                    glue::glue("{ifelse(length(nSeasonal[server=='europe',n])==0,0,nSeasonal[server=='europe',n])}/1024(?)"),
                    glue::glue("{ifelse(length(nSeasonal[server=='americas',n])==0,0,nSeasonal[server=='americas',n])}/1024(?)"))
        ) |>
  left_join(LoR.Melt.Seasonal |>
              group_by(server) |>
              summarize( n = n() ), by = "server" ) |>
  mutate( server = str_to_title(server) ) |>
  gt() |>
  cols_label(
    server   = md("**Server**"),
    players  = md("**Players**"),
    n = md("**Games**")
    
  ) |>
  tab_header(
    title = "Seasonal Open Rounds - by the Numbers",
    subtitle = glue::glue("Players coverage reached regarding the {params$description}")
  ) |>
  tab_source_note(
    source_note = glue::glue("Source: Source: Metadata of games collected with RiotGames API")
    ) |>
  gtExtras::gt_theme_538() |>
  tab_options(
    table.background.color = "transparent",
    table.font.color = "black",
    table.font.color.light = "black"
   )

gtsave(gtSeasonal,glue::glue("./images/seasonal/{params$ind}-coverage-player.png") ) |> invisible()
 
gtSeasonal |>
 tab_options(
    table.background.color = "transparent",
    table.font.color = "black",
    table.font.color.light = "black"
   )

# gtSeasonal
```

```{r compute-games-asia}
Game.Result.ASIA <- LoR.Melt.Seasonal |>
  filter( server=="asia" ) |>
  # As the players and opponents plays each other only in a single match group them and the min of their game_start can identify the round they are playing in
  group_by( playerID,opponentID,server ) |>
  mutate(   timeBlock = min(game_start_time_utc) |> {\(x) as_datetime(x, tz="UTC")}() ) |>
  group_by(  playerID,opponentID,server,timeBlock ) |>
  arrange( timeBlock ) |>
  summarise( result = paste(game_outcome,collapse = "," ), ldeck  = list(playerDeck) ) |>
  arrange( playerID, timeBlock ) |>
  # Identify the round with the official schedule
  mutate( round = case_when(
    # Japan Standard Time is 9 hours ahead of Universal Time Coordinated
    # JST = UTC - 9hrs
    timeBlock > with_tz(force_tz(timeBlock.1.start,"Japan"),"UTC") & timeBlock <= with_tz(force_tz(timeBlock.1.end,"Japan"),"UTC") ~ 1, # 11:55
    timeBlock > with_tz(force_tz(timeBlock.2.start,"Japan"),"UTC") & timeBlock <= with_tz(force_tz(timeBlock.2.end,"Japan"),"UTC") ~ 2, # 13:00
    timeBlock > with_tz(force_tz(timeBlock.3.start,"Japan"),"UTC") & timeBlock <= with_tz(force_tz(timeBlock.3.end,"Japan"),"UTC") ~ 3, # 14:05
    timeBlock > with_tz(force_tz(timeBlock.4.start,"Japan"),"UTC") & timeBlock <= with_tz(force_tz(timeBlock.4.end,"Japan"),"UTC") ~ 4, # 15:10
    timeBlock > with_tz(force_tz(timeBlock.5.start,"Japan"),"UTC") & timeBlock <= with_tz(force_tz(timeBlock.5.end,"Japan"),"UTC") ~ 5, # 16:15
    
    timeBlock > with_tz(force_tz(timeBlock.6.start,"Japan"),"UTC") & timeBlock <= with_tz(force_tz(timeBlock.6.end,"Japan"),"UTC") ~ 6, # 17:45
    timeBlock > with_tz(force_tz(timeBlock.7.start,"Japan"),"UTC") & timeBlock <= with_tz(force_tz(timeBlock.7.end,"Japan"),"UTC") ~ 7, # 18:50
    timeBlock > with_tz(force_tz(timeBlock.8.start,"Japan"),"UTC") & timeBlock <= with_tz(force_tz(timeBlock.8.end,"Japan"),"UTC") ~ 8, # 19:55
    timeBlock > with_tz(force_tz(timeBlock.9.start,"Japan"),"UTC") ~ 9, # 21:00
    )
  ) |>
  # number of won games in the match
  mutate( nWin = str_count(result,"win") ) |>
  # is the match won?
  mutate( matchWin = ifelse(nWin==2,1,0) ) |>
  ungroup() |>
  group_by(playerID) |>
  # sum of ALL matches won
  mutate( cumWin = cumsum(nWin)) |>
  # sum of ALL games won
  mutate( cumMatchWin = cumsum(matchWin)) |>
  ungroup() |>
  {\(x)
  left_join(
  tibble( playerID = rep( LineUp.DT |>filter(server=="asia") |>pull(playerID),each=9),
          round  = rep(seq(1,9,1), times = (LineUp.DT |>filter(server=="asia") |>NROW())  ),
          server = "asia"),
  x, by = c("playerID","round","server"))}() |>
  relocate(round, .after = server) |>
  left_join(LineUp.DT,by=c("server","playerID")) |>
  mutate( ban = map2_chr(.x = listDeck, .y = ldeck, ~(setdiff(unlist(.x),unlist(.y) )) |> {\(x) ifelse(length(x)==1,x,NA)}() )  ) 
```

```{r compute-games-europe}
Game.Result.EU <- LoR.Melt.Seasonal |>
  filter( server=="europe" ) |>
  # As the players and opponents plays each other only in a single match group them and the min of their game_start can identify the round they are playing in
  group_by(  playerID,opponentID,server ) |>
  mutate(   timeBlock = min(game_start_time_utc) |> {\(x) as_datetime(x, tz="UTC")}() ) |>
  group_by(  playerID,opponentID,server,timeBlock ) |>
  arrange( timeBlock ) |>
  summarise( result = paste(game_outcome,collapse = "," ), ldeck  = list(playerDeck) ) |>
  arrange( playerID, timeBlock ) |>
  # Identify the round with the official schedule
  mutate( round = case_when(
    # Japan Standard Time is 9 hours ahead of Universal Time Coordinated
    # JST = UTC - 9hrs
    timeBlock > with_tz(force_tz(timeBlock.1.start,"CET"),"UTC") & timeBlock <= with_tz(force_tz(timeBlock.1.end,"CET"),"UTC") ~ 1, # 11:55
    timeBlock > (with_tz(force_tz(timeBlock.2.start,"CET"),"UTC")+minutes(90)) & timeBlock <= (with_tz(force_tz(timeBlock.2.end,"CET"),"UTC")+minutes(90)) ~ 2, # 13:00
    timeBlock > (with_tz(force_tz(timeBlock.3.start,"CET"),"UTC")+minutes(105)) & timeBlock <= (with_tz(force_tz(timeBlock.3.end,"CET"),"UTC")+minutes(105)) ~ 3, # 14:05
    timeBlock > (with_tz(force_tz(timeBlock.4.start,"CET"),"UTC")+minutes(105)) & timeBlock <= (with_tz(force_tz(timeBlock.4.end,"CET"),"UTC")+minutes(105)) ~ 4, # 15:10
    timeBlock > (with_tz(force_tz(timeBlock.5.start,"CET"),"UTC")+minutes(105)) & timeBlock <= (with_tz(force_tz(timeBlock.5.end,"CET"),"UTC")+minutes(105)) ~ 5, # 16:15
    
    timeBlock > (with_tz(force_tz(timeBlock.6.start,"CET"),"UTC")+minutes(105)) & timeBlock <= (with_tz(force_tz(timeBlock.6.end,"CET"),"UTC")+minutes(105)) ~ 6, # 17:45
    timeBlock > (with_tz(force_tz(timeBlock.7.start,"CET"),"UTC")+minutes(105)) & timeBlock <= (with_tz(force_tz(timeBlock.7.end,"CET"),"UTC")+minutes(105)) ~ 7, # 18:50
    timeBlock > (with_tz(force_tz(timeBlock.8.start,"CET"),"UTC")+minutes(105)) & timeBlock <= (with_tz(force_tz(timeBlock.8.end,"CET"),"UTC")+minutes(105)) ~ 8, # 19:55
    timeBlock > (with_tz(force_tz(timeBlock.9.start,"CET"),"UTC")+minutes(105)) ~ 9, # 21:00
    )
  ) |>
  # number of won games in the match
  mutate( nWin = str_count(result,"win") ) |>
  # is the match won?
  mutate( matchWin = ifelse(nWin==2,1,0) ) |>
  ungroup() |>
  group_by(playerID) |>
  # sum of ALL matches won
  mutate( cumWin = cumsum(nWin)) |>
  # sum of ALL games won
  mutate( cumMatchWin = cumsum(matchWin)) |>
  ungroup() |>
  left_join(
  tibble( playerID = rep( LineUp.DT |>filter(server=="europe") |>pull(playerID),each=9),
          round  = rep(seq(1,9,1), times = (LineUp.DT |>filter(server=="europe") |>NROW())  ),
          server = "europe"),
  ., by = c("playerID","round","server")) |>
  relocate(round, .after = server) |>
  left_join(LineUp.DT,by=c("server","playerID")) |>
  mutate( ban = map2_chr(.x = listDeck, .y = ldeck, ~(setdiff(unlist(.x),unlist(.y) )) |> {\(x) ifelse(length(x)==1,x,NA)}() )  ) 
```

```{r compute-games-americas}
# with_tz(force_tz(timeBlock.1.start,"US/Central"),"UTC")
Game.Result.NA <- LoR.Melt.Seasonal |>
  filter( server=="americas" ) |>
  # As the players and opponents plays each other only in a single match group them and the min of their game_start can identify the round they are playing in
  group_by(  playerID,opponentID,server ) |>
  mutate(   timeBlock = min(game_start_time_utc) |> {\(x) as_datetime(x, tz="UTC")}() ) |>
  group_by(  playerID,opponentID,server,timeBlock ) |>
  arrange( timeBlock ) |>
  summarise( result = paste(game_outcome,collapse = "," ), ldeck  = list(playerDeck) ) |>
  arrange( playerID, timeBlock ) |>
  # ungroup() |>
  # group_by(playerID) |>
  # mutate( rounds = n() ) |>
  # ungroup() |>
  # filter( rounds == 9)
  # Identify the round with the official schedule
  mutate( round = case_when(
    timeBlock > with_tz(force_tz(timeBlock.1.start,"US/Central"),"UTC") & timeBlock <= with_tz(force_tz(timeBlock.1.end,"US/Central"),"UTC") ~ 1, # 11:55
    timeBlock > with_tz(force_tz(timeBlock.2.start,"US/Central"),"UTC") & timeBlock <= with_tz(force_tz(timeBlock.2.end,"US/Central"),"UTC") ~ 2, # 13:00
    timeBlock > with_tz(force_tz(timeBlock.3.start,"US/Central"),"UTC") & timeBlock <= with_tz(force_tz(timeBlock.3.end,"US/Central"),"UTC") ~ 3, # 14:05
    timeBlock > with_tz(force_tz(timeBlock.4.start,"US/Central"),"UTC") & timeBlock <= with_tz(force_tz(timeBlock.4.end,"US/Central"),"UTC") ~ 4, # 15:10
    timeBlock > with_tz(force_tz(timeBlock.5.start,"US/Central"),"UTC") & timeBlock <= with_tz(force_tz(timeBlock.5.end,"US/Central"),"UTC") ~ 5, # 16:15
    
    timeBlock > with_tz(force_tz(timeBlock.6.start,"US/Central"),"UTC") & timeBlock <= with_tz(force_tz(timeBlock.6.end,"US/Central"),"UTC") ~ 6, # 17:45
    timeBlock > (with_tz(force_tz(timeBlock.7.start,"US/Central"),"UTC")+minutes(85)) & (timeBlock <= with_tz(force_tz(timeBlock.7.end,"US/Central"),"UTC")+minutes(85)) ~ 7, # 18:50
    timeBlock > (with_tz(force_tz(timeBlock.8.start,"US/Central"),"UTC")+minutes(85)) & (timeBlock <= with_tz(force_tz(timeBlock.8.end,"US/Central"),"UTC")+minutes(85)) ~ 8, # 19:55
    timeBlock > (with_tz(force_tz(timeBlock.9.start,"US/Central"),"UTC")+minutes(85)) ~ 9, # 21:00
    )
  ) |>
  # number of won games in the match
  mutate( nWin = str_count(result,"win") ) |>
  # is the match won?
  mutate( matchWin = ifelse(nWin==2,1,0) ) |>
  ungroup() |>
  group_by(playerID) |>
  # sum of ALL matches won
  mutate( cumWin = cumsum(nWin)) |>
  # sum of ALL games won
  mutate( cumMatchWin = cumsum(matchWin)) |>
  ungroup() |>
  left_join(
  tibble( playerID = rep( LineUp.DT |>filter(server=="americas") |>pull(playerID),each=9),
          round  = rep(seq(1,9,1), times = (LineUp.DT |>filter(server=="americas") |>NROW()) ),
          server = "americas" ),
  ., by = c("playerID","round","server")) |>
  relocate(round, .after = server) |>
  left_join(LineUp.DT,by=c("server","playerID")) |>
  mutate( ban = map2_chr(.x = listDeck, .y = ldeck, ~(setdiff(unlist(.x),unlist(.y) )) |> {\(x) ifelse(length(x)==1,x,NA)}() )  ) 
```

```{r create-file}
Game.Result.all  <- rbind(Game.Result.ASIA,Game.Result.EU,Game.Result.NA)

# Game.Result.all |>
#   filter( !is.na(opponentID) ) |>
#   tabyl(round)

# Game.Result.all |>
#   .[, sapply(., class) != "list"] |>
#   fwrite(file.path("C:","LlorR","data","clean","Seasonal_2021_xx.csv"))
```

```{r table-ban}
#' all deck for bans
deckForBan <- LoR.Melt.Seasonal |> 
  distinct(playerDeck) |>
  pull() |> sort()
        
#' create Ban DT      
################
ban.tbl <- Game.Result.all |>
  group_by( ban ) |>
  #' effective ban for each deck
  count(ban) |>
  filter( !is.na(ban) )

ban.DT <- tibble( deck = deckForBan ) |>
  left_join(ban.tbl |> select(deck = ban,nBan=n) ,by = "deck") |>
  as.data.table() |>
  #' compute the max Ban
  mutate( maxBan = map_int(
    .x = deck,
    .f = function(.x) { 
      whichLU <- Game.Result.all |>
        filter( deck_1 == .x | deck_2 == .x | deck_3 == .x ) |>
        pull(LU)
      
      Game.Result.all |>
        filter( LU %in% whichLU ) |>
        filter( !is.na(ban) ) |>
        NROW()
      
      } ) )

WR.DT <- ban.DT |>  
  # start with ban.DT as it contains the list of all decks that theoretically can appears
  # add the games data
  left_join(WR.DT,by=c("deck"="playerDeck")) |>
  # if there are NA it's decks that have not being played
  mutate( 
    # since the number of ban considers all the cases with ban information it is some to impute 0
    across(c(nBan,nWin, nGames,playrate), ~replace_na(.x, 0)),
    meanBan = nBan/maxBan,
    meanBan = replace_na(meanBan, 0)
    ) |>
  left_join(ladder.WR.DT |> select(deck=playerDeck,lplayrate=playrate,lWR=WR),by=c("deck"))
```

```{r compute-LMI}
# skimr::skim(full.ban.DT$nGames)
LMI.DT <- WR.DT |>
  drop_na() |>
  # arrange(desc(nGames)) |>
  slice_max(nGames, n = 50) |>
  # filter( nGames >= 50 ) |>
  #' noramlize variables
  mutate(
    PR_ind = scale_quantile(playrate),
    WR_ind = scale_quantile(WR),
    lWR_ind = scale_quantile(lWR),
    meanBan_ind = scale_quantile(meanBan)
    ) |>
  mutate( 
    #' ladder with seasonal WR
    WIN_ind    = map2_dbl(.x = WR_ind, .y = lWR_ind, ~weighted.mean(x = c(.x,.y),w = c(0.5,0.5) )) ,
    WIN_ind = scale_quantile(WIN_ind),
    #' WR with ban
    str_dim = map2_dbl(.x = WIN_ind, .y = meanBan_ind, ~weighted.mean(x = c(.x,.y),w = c(0.5,0.5) )),
    str_dim = scale_quantile(str_dim),
    #' strength dim with freq dim
    LMI = map2_dbl(.x = str_dim, .y = PR_ind, ~weighted.mean(x = c(.x,.y),w = c(0.5,0.5) )),
    LMI = scale_quantile(LMI),
    #' tooltips
    tooltip = glue::glue("{deck}
                         LMI {round(LMI*100,1)}
                         WinRate {scales::percent(WR,accuracy = 0.1)}
                         PlayRate {scales::percent(playrate,accuracy = 0.1)}
                         BanRate {scales::percent(meanBan,accuracy = 0.1)}"),
    tooltip_mini = glue::glue("{deck}
                              LMI {round(LMI*100,1)}")
  ) |>
  mutate(tier = case_when( 
     LMI >= 0.975 ~ "Tier0",
     0.85 <= LMI & LMI < 0.975 ~ "Tier1",
     0.60 <= LMI & LMI < 0.90 ~ "Tier2",
     LMI < 0.60 ~ "Tier3"
     # LMI < 03.0 ~ "Tier4 or lower",
    ) 
  )
```

::: {.l-page}
::::: {.panelset}

::: {.panel}
### Missing Games {.panel-name}

The following data is related to the the number of games missing to recreate a match.So when I could only collect either a win or a loss or both a win and a loss but not the remaining game. **It is not** the total number of missing games as it doesn't account for the cases where I lack all games but that value can't be known as it's impossible to know whenever the round was played or not.

During the partial results is the graph is lacking I recovered all games I could up until that moment.

```{r plot-missing-match-games, fig.cap="Uncomplete Matches Distribution", fig.subcap="Absolute frequencies"}
if ( 
  Game.Result.all |>
    filter( result %in% c("win","loss" ) | result %in% c("win,loss","loss,win" ) ) |>
  count() > 0
  ) {

Game.Result.all |>
  filter( result %in% c("win","loss" ) | result %in% c("win,loss","loss,win" ) ) |> # | is.na(result)
  # group_by(server) |>
  tabyl(round,server) |>
  pivot_longer(cols = -round,
               names_to = "server"
               ) |>
  mutate(round = factor(round)) |>
  mutate( server = str_to_title(server) ) |>
  # rename_all(~str_to_title(.)) |>
  ggplot(aes(round,value,fill=server)) +
    geom_bar(position="dodge",stat = "identity") +
    labs(x = "Round",
         y = "#Games",
         title = "Incomplete-Match Distribution by Round",
         subtitle = "number of games missing for the complete information of a match by server",
         caption = element_text(glue::glue("{params$description}
                                           The number refer to the number of games missing to recreate a match so when I could only collect either a win or a loss or both a win and a loss but not the remaining game") )) +
  theme_539() +
    scale_y_continuous(breaks = seq(0,1000,2))
  
}
```
:::

::: {.panel}
### Matches Coverage {.panel-name}

```{r}
gtMatch <-Game.Result.all |>
  select(round,server) |>
  gtsummary::tbl_summary( 
    by = "server",
    statistic = list(all_categorical() ~ "{n}")
    ) |>
  modify_header(
    update = list(
      label ~ "",
      stat_1 ~ "**America**",
      stat_2 ~ "**Asia**",
      stat_3 ~ "**Europe**"
    )
  ) |>
  as_gt() |>
  cols_align(
    align = "center",
    columns = everything()
  ) |>
  tab_header(
    title = "Seasonal Open Rounds - by the Numbers",
    subtitle = glue::glue("Match coverage reached regarding the {params$description}")
  ) |>
  tab_source_note(
    source_note = glue::glue("Source: Source: Metadata of games collected with RiotGames API")
    ) |>
  gtExtras::gt_theme_538()

# gtMatch <- Game.Result.all |>
#   filter( !is.na(opponentID) ) |>
#   count(round,server) |>
#   mutate( n = map2_chr( .x = n, .y = server, ~glue("{.x}/{nSeasonal[server==.y,n]}") ) ) |>
#   gt(groupname_col = "server") |>
#   cols_label(
#     round   = md("**Round**"),
#     # server   = md("**Server**"),
#     n = md("**Matches**")
#   ) |>
#   tab_header(
#     title = "Seasonal Open Rounds - by the Numbers",
#     subtitle = glue::glue("Match coverage reached regarding the {params$description}")
#   ) |>
#   tab_source_note(
#     source_note = glue::glue("Source: Source: Metadata of games collected with RiotGames API")
#     ) |>
#   gtExtras::gt_theme_538() |>
#   cols_align(
#     align = "left",
#     columns = everything()
#   ) 

gtsave(gtMatch, glue::glue("./images/seasonal/{params$ind}-coverage-match.png") ) |> invisible()

gtMatch |>
 tab_options(
    table.background.color = "transparent",
    table.font.color = "black",
    table.font.color.light = "black"
   )

# gtMatch
```
:::
:::::
:::

----

# Decks

As this is the Seasonal Tournament let's start with the decks/archetype informations

This is also the moment of the meta where the classification *Archetype = Champion+Region* shows its biggest limitation as there are an increase in *tech champions* (usually in single copy)

::: {.l-page}
::::: {.panelset}
::: {.panel}
### Single Decks Stats {.panel-name}

```{r react-deck}
react.LU.Stat <- left_join(
LineUp.DT |>
  select(contains("deck_")) |>
  {\(x) unlist(x,use.names = F)}() |>
  {\(x) tabyl(x,show_na = F)}() |>
  arrange(desc(n))  |>
  #' account for the presence of 3 decks
  mutate(percent = 3*percent ) |>
  rename( 'deck'=1 ),
LineUp.DT  |>
  select(contains("deck_")) |>
  filter(!is.na(deck_3)) |>
  select(contains("deck")) |>
  {\(x) unlist(x,use.names = F)}() |>
  {\(x) tabyl(x,show_na = F)}() |>
  arrange(desc(n))  |>
  #' account for the presence of 3 decks
  mutate(percent = 3*percent ) |>
  rename( 'deck'=1,"n_full"="n","percent_full"="percent" ),
by="deck"
) |>
  left_join( WR.DT[,c("deck","WR","meanBan","lplayrate","lWR")], by = "deck" ) |>
  mutate( diffLadder = WR-lWR ) |>
  relocate( diffLadder, .after = "meanBan" ) |>
  select(-lWR) |>
  reactable(
    theme = reactablefmtr::fivethirtyeight(),
    bordered = TRUE,
    highlight = TRUE,
    searchable = TRUE,
    compact = TRUE, # compact the table
    # fullWidth = FALSE, # don't fill the page
    defaultPageSize = 15,
    defaultColDef = colDef(
      style = list(fontWeight = 500, color = "black",
                   fontFamily = "Work Sans, sans-serif", fontSize = "12px"),
      align = "center",
      # minWidth = 100,
      headerStyle = list(background = "steelblue",color="white",fontFamily = "Work Sans, sans-serif", fontSize = "14px" )
      ),
    columnGroups = list(
      colGroup(name = "All-Data", columns = c("n", "percent")),
      colGroup(name = "only full Line-Ups", columns = c("n_full", "percent_full"))
      ),
    columns = list(
      deck         = colDef(name = "Archetype", style = list(fontWeight = "bold",color = "black",fontFamily = "Work Sans, sans-serif", fontSize = "13px"), minWidth = 200,align = "left" ),
      n            = colDef(name = "N", footer = function(values) sprintf("%.0f", sum(values,na.rm = T)), minWidth = 80),
      n_full       = colDef(name = "N",footer = function(values) sprintf("%.0f", sum(values,na.rm = T)), minWidth = 80),
      
      percent      = colDef(name = "PlayRate",format = colFormat(percent = TRUE,digits = 2), minWidth = 100),
      percent_full = colDef(name = "PlayRate",format = colFormat(percent = TRUE,digits = 2), minWidth = 100 ),
      
      WR        = colDef(name = "WinRate",format = colFormat(percent = TRUE,digits = 2), minWidth = 100),
      diffLadder= colDef(name = "WinRate diff \n vs Ladder",format = colFormat(percent = TRUE,digits = 2), minWidth = 100),
      meanBan   = colDef(name = "BanRate",format = colFormat(percent = TRUE,digits = 2), minWidth = 100),
      lplayrate = colDef(name = "ladder\nPlayRate",format = colFormat(percent = TRUE,digits = 2), minWidth = 100)
      
      )
    ) |>
  reactablefmtr::add_title("Deck's Stats", background_color = "transparent", font_family = "Helvetica") |>
  reactablefmtr::add_subtitle(params$description, background_color = "transparent", font_family = "Roboto") |>
  reactablefmtr::add_source(glue::glue("Relative frequencies from all data or only lineUps with full information
                                       Source: Metadata of games collected with RiotGames API"), background_color = "transparent", font_family = "Chivo")
  
react.LU.Stat |>
  reactablefmtr::save_reactable(glue::glue("./images/seasonal/{params$ind}-deck.png"))

react.LU.Stat
```

- **Ban Rate**: ratio between the number of bans and the number of matches of a deck.

\begin{equation}

BanRate = \frac{\#ban}{\#match}

\end{equation}

Example: 2 Line-Ups contained a Teemo/Ezreal deck, both played all 9 matches and Teemo/Ezreal was banned respectively 3 and 6 times; the ban rate would be $\frac{(3+6)}{(9+9)} = 50\%$

- **PlayRate**:  ratio between the number of times a deck appears among all lineUps (both including or not incomplete lineUps data) and the number of all decks in all lineUps.

:::

::: {.panel}
### Full Line-Ups {.panel-name}

```{r react-LineUps}
react.LU.Full <- LineUp.DT |>
  filter( !is.na(deck_3) ) |>
  tabyl(LU,show_na = F) |>
  arrange(desc(n))  |>
  # adorn_pct_formatting() |>
  rename('LU'=1) |>
  left_join(
    LineUp.DT |>
      select(contains("deck"),LU) |>
      filter(!is.na(deck_3)),
    by="LU"
    ) |>
  distinct(LU,.keep_all = T) |>
  select(percent,n,LU,deck_1,deck_2,deck_3 ) |>
  reactable(
    theme = reactablefmtr::fivethirtyeight(),
    bordered = TRUE,
    highlight = TRUE,
    searchable = TRUE,
    compact = TRUE, # compact the table
    # fullWidth = FALSE, # don't fill the page
    defaultPageSize = 15,
    defaultColDef = colDef(
      style = list(fontWeight = 500, color = "black",
                   fontFamily = "Work Sans, sans-serif", fontSize = "12px"),
      # header = function(value) str_to_title(value),
      #  cell = function(value) format(value, nsmall = 1),
      align = "center",
      headerStyle = list(background = "steelblue",color="white",fontFamily = "Work Sans, sans-serif", fontSize = "14px" )
      ),
    columns = list(
      n = colDef(name="N", footer = function(values) sprintf("%.0f", sum(values))),
      percent = colDef(name="Percent", format = colFormat(percent = TRUE, digits = 2), footer = function(values) sprintf("%.2f", sum(values))  ),
      deck_1 = colDef(name = "Deck 1", style = list(color = "red", fontFamily = "Work Sans, sans-serif", fontSize = "12px"  ) ),
      deck_2 = colDef(name = "Deck 2", style = list(color = "green", fontFamily = "Work Sans, sans-serif", fontSize = "12px") ),
      deck_3 = colDef(name = "Deck 3", style = list(color = "blue", fontFamily = "Work Sans, sans-serif", fontSize = "12px" ) ),
      LU = colDef(name = "Line Up", style = list(fontWeight = "bold", fontFamily = "Work Sans, sans-serif", fontSize = "12px" ) )
      )
    ) |>
  reactablefmtr::add_title("LineUp's Playrates", background_color = "transparent", font_family = "Helvetica") |>
  reactablefmtr::add_subtitle(params$description, background_color = "transparent", font_family = "Roboto") |>
  reactablefmtr::add_source(element_text(glue::glue("Data from only full Line-Ups.
                                                    Source: Source: Metadata of games collected with RiotGames API")), background_color = "transparent", font_family = "Chivo")

react.LU.Full |>
  reactablefmtr::save_reactable(glue::glue("./images/seasonal/{params$ind}-LU.png"))

react.LU.Full
```
:::
:::::
:::

------------------------------------------------------------------------

# LMI

- **Tier0** with LMI >= 97.5

- **Tier1** with LMI $\in$ [85,97.5)

- **Tier2** with LMI $\in$ [60,85)

- **Tier3 or lower** with LMI < 60

`r kableExtra::text_spec("Note:", color = "red")` Hovering over a circle will display a deck values.

> The LMI [^1] [^2] is an Index I developed to measure the performance of decks in the metagame. For those who are familiar with basic statistical concept I wrote a document to explain the theory behind it: , it's very similar to [vicioussyndicate](https://www.vicioussyndicate.com) (vS) Meta Score from their data reaper report. The score of each deck ***is not*** just their "strength", it takes in consideration both play rates and win rates that's why I prefer to say it measure the "performance". The values range from 0 to 100 and the higher the value, the higher is the performance.

[^1]: [LMI - Early Theory](https://llorr-stats.com/analysis/lmi/)

[^2]: [LMI - Adding a Ban Index](https://www.llorr-stats.com/analysis/lmi-02-tentative-expansion/)

```{r lmi-png, layout="l-page", fig.width=12,fig.height=8}
LMI.DT |>
  slice_max(LMI,n = 15,with_ties = F) |>
  # mutate( tooltip = glue("{deck}
  #                        LMI {round(LMI*100,1)}
  #                        WinRate {scales::percent(WR,accuracy = 0.1)}
  #                        PlayRate {scales::percent(playrate,accuracy = 0.1)}
  #                        #Games {nGames}") ) |>
  mutate_if(is.numeric, funs(round(., 4)) ) |>
  mutate( LMI = LMI*100 ) |>
  ungroup() |>
  ggplot( aes(x=WR_ind, y=PR_ind, size = LMI, color = tier, text=tooltip)) +
  geom_point(alpha=0.6) +
  scale_size(range = c(5, 15), name="LMI") +
  theme_539() +
  geom_label_repel( 
    aes(label=tooltip),
    family = "Roboto",
    color = "grey40",
    fontface = "bold",
    size = 3,
    fill = NA,
    vjust = "outward",
    label.padding = unit(0.8, "mm"),
    label.size = unit(0.25, "mm"),
    label.r = unit(0.5, "mm"),
    min.segment.length = 0,
    segment.linetype = 2,
    segment.color = 'grey50'
    # nudge_y = 0
  ) + 
  guides(colour = guide_legend(override.aes = list(size=10)),
         size = FALSE ) +
  theme( legend.position = "top",
         legend.background = element_blank(),
         legend.title = element_text(size=9, lineheight = 1.3),
         legend.justification = "right"
         ) +
  labs(
    title = "Top15 Deck Peformances",
    subtitle = "Deck's Peformances of the top15 best decks by highest value of LMI",
    x = "Win Index",
    y = "Freq Index",
    caption = element_text(glue::glue("{params$description}
                                      LMI computed with the improved version which included banrate and ladder win rates
                                      Source: Source: Metadata of games collected with RiotGames API"))
  )
  # xlim( 0,1 ) +
  # ylim( 0,1 )

ggsave(glue::glue("./images/seasonal/{params$ind}-LMI.png"))
```

```{r lmi-plotly, layout="l-page"}
fig <- LMI.DT |>
  slice_max(LMI,n = 50, with_ties = F) %>%
  mutate_if(is.numeric, funs(round(., 4)) ) |>
  ggplot( aes(x=WR_ind, y=PR_ind, size = LMI^2, color = tier, text=tooltip)) +
  geom_point(alpha=0.6) +
  scale_size(range = c(5, 15), name="LMI") + 
  theme_minimal() +
  labs( 
    x = "WR Index",
    y = "Freq Index",
    title = "LoR-Meta Index (LMI) / only complete informatio / max top50 deck / min 50 games",
    subtitle = "Deck's Peformances of the top15 best decks by highest value of LMI",
    caption = element_text(glue::glue("{params$description}
                                      Max top50 decks
                                      LMI computed with the improved version which included banrate and ladder win rates
                                      Source: Source: Metadata of games collected with RiotGames API"))
    )

ggplotly(fig, tooltip="text")
```

------------------------------------------------------------------------

# Regions

<!-- Some basic data regarding the regions play-rates / the values are  -->

## Play Rate

```{r process-tableFreq}
Region.Freq <- LineUp.DT |>
  select(contains("deck_"),contains("code_") ) |>
  pivot_longer(
    cols = c(contains("deck_"),contains("code_")),
    names_to=c(".value", "index"),
    names_sep = "_"
    ) |>
  drop_na() |>
  left_join(LoR.Deck[,.(deck_code,factions)], by=c("code"="deck_code")) |>
  select(factions) |>
  separate_rows(factions,sep=",") |>
  mutate( factions = map_chr(.x = factions, ~str_remove_all(.x, paste(c("_Name","faction_", ""), collapse = "|") ) ) ) |>
  tabyl(factions,show_na=F) |>
  tibble() |> 
  rename_all(~c("region","n","freq")) |>
  left_join(data_regions, by =c("region"="nameRef")) |>
  select(-factions)


Region.Freq.Server <- LineUp.DT |>
  select(server,contains("deck_"),contains("code_") ) |>
  pivot_longer(
    cols = c(contains("deck_"),contains("code_")),
    names_to=c(".value", "index"),
    names_sep = "_"
    ) |>
  drop_na() |>
  left_join(LoR.Deck[,.(deck_code,factions)], by=c("code"="deck_code")) |>
  mutate( factions = map_chr(.x = factions, ~str_remove_all(.x, paste(c("_Name","faction_", ""), collapse = "|") ) ) ) |>
  select(server,factions) |>
  separate_rows(factions,sep=",") |>
  tabyl(factions,server, show_na = F) |>
  adorn_percentages("col") |>
  mutate( region = map_chr(.x = factions, ~str_remove_all(.x, paste(c("_Name","faction_", ""), collapse = "|") ) ) ) |>
  select(-factions)

Region.Freq <- full_join(Region.Freq,Region.Freq.Server,by="region") |>
  mutate( 
    sxLabel_card = format(freq*100,2),
    sxLabel_card = ifelse(as.numeric(sxLabel_card) > 4,  sxLabel_card , "") |> as.numeric() |> {\(x) scales::number(x, accuracy = 0.01)}(),
    dxLabel_card = format(freq*100,2),
    dxLabel_card = ifelse(as.numeric(dxLabel_card) <= 4, dxLabel_card , "") |> as.numeric() |> {\(x) scales::number(x, accuracy = 0.01)}()
    )
```

::: l-page
::::: {.panelset}
::: {.panel}
### Plot {.panel-name}

```{r plot-Region, fig.width=12,fig.height=8}
RegionByRegion <- Region.Freq |>
  ggplot(aes(x = reorder(region, freq), y = freq)) +
  geom_bar(stat="identity") +
  geom_bar_pattern(
    aes(
      pattern_filename = region,
    ),
    stat            = 'identity',
    pattern         = 'image',
    pattern_type    = 'none',
    fill            = Region.Freq$colorRegion,
    colour          = 'black',
    pattern_scale   = -2,
    pattern_filter  = 'point',
    pattern_gravity = 'east'
  ) +
  scale_pattern_filename_discrete(choices = Region.Freq$iconsPath ) +
  # scale_pattern_discrete(guide = guide_legend(nrow = 1)) +
  annotate(
    geom = 'text',
    color = "grey50",
    x = 1.0,
    y = 0.15,
    hjust = 0.5,
    label = glue::glue('n = {NROW(LoR.Melt.Seasonal)}\nGini Index = {round(DescTools::Gini(Region.Freq$freq,na.rm = T),3)}'),
    fontface = 'bold') +
  coord_flip() +

  scale_fill_manual("legend", values = Region.Freq$colorRegion) +
  scale_y_continuous(limits = c(0, round(max(Region.Freq$freq+0.04 ),3) ),
                     breaks = seq(0,0.5,0.04),
                     expand = c(-0.001,0.02),
                     labels = scales::percent_format(accuracy = 1) ) +
  guides(fill = "none") +
  #' Adding the text of the frequencies
  geom_text(aes(label = Region.Freq$sxLabel_card), hjust = 2.5, size = 5,position = position_dodge(width = 1)) +
  geom_text(aes(label = Region.Freq$dxLabel_card), hjust = -0.5, size = 5,position = position_dodge(width = 1)) +
  theme_539() +
  theme(
    legend.position = "none",
    axis.text = element_text(face = "bold", color = "grey50"),
    panel.grid.major.y = element_blank()
    ) +
  labs(
    x = "Region",
    y = "Play Rate",
    title = "Regions Play Rate",
    subtitle = "number of times a region is included in a deck",
    caption = element_text(glue::glue("{params$description}
                                      Source: Metadata of games collected with RiotGames API"))
    )

RegionByRegion

ggsave(glue::glue("./images/seasonal/{params$ind}-RegionPR.png"))
```

The Gini Index is a measure of heterogeneity so, in this case and in simpler terms, how much the play rates are similar. The Index goes (when normalized like here) $in$ [0,1] and it's equal to 1 when there's a single value with 100% play rate or 0 when all play rates are equal. Of course a Gini Index of 1 needs to be avoided but it's not like the aim should be 0. As said, it's just to add some additional tools.
:::

::: {.panel}
### Table {.panel-name}

```{r print-tableFreq-gt}
Region.Freq.tbl <- Region.Freq |>
  select(region,freq,americas,asia,europe) |>
  arrange(desc(freq)) |>
  gt() |>
  tab_header(
    title = "Region Play Rate",
    subtitle = "Relative Frequencies by Inclusion Rate of a Region"
  ) |>
  tab_spanner(
    label = "Shard",
    columns = c(americas, asia, europe)
  ) |>
  fmt_percent(
    columns = c(2:5),
    decimals = 2
  ) |>
  cols_label(
    region   = md("**Region**"),
    freq     = md("**Freq**"),
    americas = md("**America**"),
    asia     = md("**Asia**"),
    europe   = md("**Europe**")
  ) |>
  tab_source_note(
    source_note = glue::glue("Source: Source: Metadata of games collected with RiotGames API")
    ) |>
  gtExtras::gt_theme_538() |>
  tab_options(
   table.background.color = "transparent",
   table.font.color = "black",
   table.font.color.light = "black"
  )

Region.Freq.tbl
```
:::
:::::
:::

# Top Player(?) Champions of Choice

This section is done before the release of the official top32 list from Riot.

- For the *Asia shard* it displays those who reached at least 7 matches wins (not counting bye)

- For the *America and Europe shard* it displays those who reached at least 8 matches wins (not counting bye)

When partial results are being published, it's not limited to the top32 but the current highest performing players collected at that point. As there are "Bye" that I can't track the final results will never be perfect. [^3]

[^3]: Pls Rito add a method to let us know of this kind of tournaments data.

```{r compute-top-32-data}
# Data from those who reached the highest amoutn of Match Win
top32tbl <- Game.Result.all |>
  select(playerID,cumMatchWin,server) |>
  group_by(server) |>
  filter( (server == "asia" & cumMatchWin >= 7) | (server != "asia" & cumMatchWin >= 8) ) |>
  # slice_max(cumMatchWin, n = 3,with_ties = T) |>
  left_join( LoR.Account.RMD[,c("gameName","RiotID")],
             by=c("playerID"="RiotID")
  ) |>
  arrange(server,desc(cumMatchWin)) |>
  distinct(gameName,.keep_all = T) |>
  left_join(LineUp.DT,by=c("playerID","server") )
  

# count the number of times a champion is present in a deck
# grouped by region
#'#########
top32tbl.CC <- top32tbl |>
  pivot_longer(
    cols = contains("code_"),values_to = "deck_code") |>
  select(server,deck_code) |>
  # for partial results
  filter( !is.na(deck_code) ) |>
  mutate( CC = map_chr(.x = deck_code, ~get_champion_from_code(.x) )) |>
  separate_rows(CC,sep = "/") |>
  group_by(server) |>
  count(CC) |>
  ungroup() |>
  arrange(desc(n),CC) |>
  rename("name"="CC")
```

::: l-page
::::: {.panelset}
::: {.panel}
### ASIA {.panel-name}

```{r create-top32-ASIA, fig.height=8, fig.width=12}
#' flextable for the champions which were used a single time
ft.top32tbl.CC.ASIA <- top32tbl.CC |>
  filter(server == "asia")  |>
  filter(n %in% 1:2) |>
  select(-server) |>
  rename_all(~c("Champion","N")) |>
  flextable::flextable() |>
  flextable::as_raster()

#' base plot
ggtop32.ASIA <- top32tbl.CC  |>
  filter(server=="asia") |>
  filter(n > 2) |>
  left_join(LoR.Set|>select(name,regionRef),by=c("name") ) |>
  
  mutate(img = map_chr(.x = name, ~getCardCode(.x) )) |>
  mutate(img = map_chr(.x = img, ~card_url_path(.x,full=F) )) |>
  left_join( data_regions, by = c("regionRef") ) |>
  
  ggplot(aes(reorder(name, n),n,fill=regionRef)) +
  geom_bar(position="dodge",stat = "identity", color = "black") +
  scale_y_continuous(breaks = seq(0,60,2), sec.axis = sec_axis(~(./(as.data.table(top32tbl)[ ,.N, by=server][server=="asia",N]))*100, name = "PlayRate (%)",breaks = seq(0,100,20))) +
  ggimage::geom_image(aes(x = name, image = img), y = 0, size = 0.05,inherit.aes = FALSE) +
  coord_flip() +
  scale_fill_manual("legend", values = set_names(data_regions$colorRegion, data_regions$regionRef  ) ) +
  theme_539() +
  labs( x = "Champion",
        y = "#Decks",
        title = "Champions' Play Rate - ASIA",
        subtitle = "Champions presence based by the number of decks that included them / playrate",
        caption = element_text(
          glue::glue("Number of players: {as.data.table(top32tbl)[ ,.N, by=server][server=='asia',N]}
                     The top players are selected from those with at least 7 matches won, not counting bye
                     The list doesn't include all top32 so obtained without Riot official data
                     Source: Source: Metadata of games collected with RiotGames API" )
          )) +
  theme(
    legend.position = "none",
    axis.text = element_text(face = "bold", color = "grey50"),
    panel.grid.major.y = element_blank()
  )

#' unite the plot and table
cowplot::plot_grid(
  ggtop32.ASIA,
  ggplot() +
    theme_539() +
    annotation_custom(grid::rasterGrob(ft.top32tbl.CC.ASIA), xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf), nrow = 1, ncol = 2, rel_widths = c(4, 1) )

ggsave(glue::glue("./images/seasonal/{params$ind}-champ-top-Asia.png"))
```
:::

::: {.panel}
### EU {.panel-name}

```{r plot-top32-EU}
#' flextable for the champions which were used a single time
ft.top32tbl.CC.EU <- top32tbl.CC |>
  filter(server == "europe")  |>
  filter(n %in% 1:2) |>
  select(-server) |>
  rename_all(~c("Champion","N")) |>
  flextable::flextable() |>
  flextable::as_raster()

#' base plot
ggtop32.EU <- top32tbl.CC  |>
  filter(server=="europe") |>
  filter(n > 2) |>
  left_join(LoR.Set|>select(name,regionRef),by=c("name") ) |>
  
  mutate(img = map_chr(.x = name, ~getCardCode(.x) )) |>
  mutate(img = map_chr(.x = img, ~card_url_path(.x,full=F) )) |>
  left_join( data_regions, by = c("regionRef") ) |>
  
  ggplot(aes(reorder(name, n),n,fill=regionRef)) +
  geom_bar(position="dodge",stat = "identity", color = "black") +
  scale_y_continuous(breaks = seq(0,60,2), sec.axis = sec_axis(~(./(as.data.table(top32tbl)[ ,.N, by=server][server=="europe",N]))*100, name = "PlayRate (%)",breaks = seq(0,100,20))) +
  ggimage::geom_image(aes(x = name, image = img), y = 0, size = 0.050,inherit.aes = FALSE) +
  coord_flip() +
  scale_fill_manual("legend", values = set_names(data_regions$colorRegion, data_regions$regionRef  ) ) +
  theme_539() +
  labs( x = "Champion",
        y = "#Decks",
        title = "Champions' Play Rate - EU",
        subtitle = "Champions presence based by the number of decks that included them / playrate",
        caption = element_text(
          glue::glue("Number of players: {as.data.table(top32tbl)[ ,.N, by=server][server=='europe',N]}
                     The top players are selected from those with at least 8 matches won, not counting bye
                     The list doesn't include all top32 so obtained without Riot official data
                     Source: Source: Metadata of games collected with RiotGames API" )
          )) +
  theme(
    legend.position = "none",
    axis.text = element_text(face = "bold", color = "grey50"),
    panel.grid.major.y = element_blank()
  )

#' unite the plot and table
cowplot::plot_grid(ggtop32.EU, ggplot() +
                     theme_void() +
                     annotation_custom(grid::rasterGrob(ft.top32tbl.CC.EU), xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf), nrow = 1, ncol = 2, rel_widths = c(4, 1) )

ggsave(glue::glue("./images/seasonal/{params$ind}-champ-top-EU.png"))
```
:::

::: {.panel}
### NA {.panel-name}

```{r plot-top32-NA}
ft.top32tbl.CC.EU <- top32tbl.CC |>
  filter(server == "americas")  |>
  filter(n %in% 1:2) |>
  select(-server) |>
  rename_all(~c("Champion","N")) |>
  flextable::flextable() |>
  flextable::as_raster()

#' base plot
ggtop32.NA <- top32tbl.CC  |>
  filter(server=="americas") |>
  filter(n > 2) |>
  left_join(LoR.Set|>select(name,regionRef),by=c("name") ) |>
  
  mutate(img = map_chr(.x = name, ~getCardCode(.x) )) |>
  mutate(img = map_chr(.x = img, ~card_url_path(.x,full=F) )) |>
  left_join( data_regions, by = c("regionRef") ) |>
  
  ggplot(aes(reorder(name, n),n,fill=regionRef)) +
  geom_bar(position="dodge",stat = "identity", color = "black") +
  scale_y_continuous(breaks = seq(0,60,2), sec.axis = sec_axis(~(./(as.data.table(top32tbl)[ ,.N, by=server][server=="americas",N]))*100, name = "PlayRate (%)",breaks = seq(0,100,20))) +
  ggimage::geom_image(aes(x = name, image = img), y = 0, size = 0.0750,inherit.aes = FALSE) +
  coord_flip() +
  scale_fill_manual("legend", values = set_names(data_regions$colorRegion, data_regions$regionRef  ) ) +
  theme_539() +
  labs( x = "Champion",
        y = "#Decks",
        title = "Champions' Play Rate - NA",
        subtitle = "Champions presence based by the number of decks that included them / playrate",
        caption = element_text(
          glue::glue("Number of players: {as.data.table(top32tbl)[ ,.N, by=server][server=='americas',N]}
                     The top players are selected from those with at least 8 matches won, not counting bye
                     The list doesn't include all top32 so obtained without Riot official data
                     Source: Source: Metadata of games collected with RiotGames API" )
          )) +
  theme(
    legend.position = "none",
    axis.text = element_text(face = "bold", color = "grey50"),
    panel.grid.major.y = element_blank()
  )

#' unite the plot and table
cowplot::plot_grid(ggtop32.NA, ggplot() +
                     theme_void() +
                     annotation_custom(grid::rasterGrob(ft.top32tbl.CC.EU), xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf), nrow = 1, ncol = 2, rel_widths = c(4, 1) )

ggsave(glue::glue("./images/seasonal/{params$ind}-champ-top-NA.png"))
```
:::

::: {.panel}
### Table - All Server & Deckcodes {.panel-name}

Remember that as I can't collect "bye" the true top list may differ buy a lot.

```{r react-top32}
react.LU.top32 <- top32tbl |>
  # filter( server == "asia" ) |>
  select(gameName,cumMatchWin,LU,contains("deck_"),contains("code_") ) |>
  pivot_longer(
    cols = c(contains("deck_"),contains("code_")),
    names_to=c(".value", "index"),
    names_sep = "_") |>
  relocate(LU,.after = code) |>
  select(-index) |>
  reactable(
    theme = reactablefmtr::fivethirtyeight(),
    groupBy = c("server","cumMatchWin","gameName"),
    bordered = TRUE,
    highlight = TRUE,
    searchable = TRUE,
    compact = TRUE, # compact the table
    # fullWidth = FALSE, # don't fill the page
    defaultPageSize = 10,
    defaultSorted = c("cumMatchWin"),
    defaultSortOrder = "desc",
    defaultColDef = colDef(
      style = list(fontWeight = 500, color = "black",
                   fontFamily = "Helvetica", fontSize = "12px"),
      align = "left",
      headerStyle = list(background = "steelblue",color="white",fontFamily = "Work Sans, sans-serif", fontSize = "14px" )
      ),
    columns = list(
      LU = colDef( show = F ),
      deck = colDef(name = "Deck",minWidth = 200 ),
      # code = colDef( show = F ),
      code = colDef(name = "DeckCode", cell = function(value, index) {
        # Render as a link
        if (!is.na(value) ) {
          url <- glue::glue("{urlruneterraAR}{urldeck}{value}")
          htmltools::tags$a(href = url, target = "_blank", as.character(value))
        } } ,minWidth = 600, style = list(fontSize = "9px") ),
      cumMatchWin = colDef(name = "#Matches Wins", aggregate = "unique",defaultSortOrder = "desc")
      ),
    rowStyle = JS("function(rowInfo) {
                  if (rowInfo.level > 0) {
                  return { background: 'whitesmoke', borderLeft: '2px solid #ffa62d' }
                  } else {
                  return { borderLeft: '2px solid transparent' }
                  }
                  }"),
    defaultExpanded = T
    ) |>
  reactablefmtr::add_title("Top Players' Deckcodes", background_color = "transparent", font_family = "Helvetica") |>
  reactablefmtr::add_subtitle(params$description, background_color = "transparent", font_family = "Roboto") |>
  reactablefmtr::add_source(glue::glue("Source: Source: Metadata of games collected with RiotGames API"), background_color = "transparent", font_family = "Chivo")

react.LU.top32 |>
  reactablefmtr::save_reactable(glue::glue("./images/seasonal/{params$ind}-top32.png"))

react.LU.top32
```
:::
:::::

:::

------------------------------------------------------------------------

# The Meta and the Seasonal

This Seasonal was much more "predictable" than what I expected. Probably because of the less try-harding many players approached the tournament simply with the "strongest" decks as they would in the ladder.

::: {.l-page}
::::: {.panelset}
::: {.panel}
### Playrate vs Ladder {.panel-name}

```{r compute-cor, fig.width=12,fig.height=8}
CC.tableByReg.S <- LineUp.DT |>
  select(server,contains("deck_")) |>
  pivot_longer( cols = c(contains("deck_")) ) |>
  select(server,deck=value) |>
  drop_na() |>
  tabyl(deck,server) |>
  adorn_percentages("col")

CC.table.S <- LineUp.DT |>
  select(contains("deck_")) |>
  pivot_longer( cols = c(contains("deck_")) ) |>
  select(deck=value) |>
  drop_na() |>
  tabyl(deck) |>
  arrange(desc(n)) |>
  mutate( percent = 3*percent ) |>
  left_join(CC.tableByReg.S,by="deck")

# CC.tableByReg.S <- LoR.Melt.Seasonal |>
#   tabyl(playerDeck,server) |>
#   adorn_percentages("col")

#' take the top30 from Seasonal
# CC.table.S <- LoR.Melt.Seasonal |>
#   tabyl(playerDeck, show_na = F) |>
#   rename_all(~c("playerDeck","n","freq")) |>
#   arrange(desc(n)) |>
#   slice_head(n = 30) |>
#   left_join(CC.tableByReg.S,by="playerDeck")

CC.tableByReg <- LoR.Melt.Matches.RMD |>
  tabyl(playerDeck,server) |>
  adorn_percentages("col")

CC.table <- LoR.Melt.Matches.RMD |>
  tabyl(playerDeck) |>
  rename_all(~c("playerDeck","n","freq")) |>
  arrange(desc(n)) |>
  slice_head(n = 30) |>
  left_join(CC.tableByReg,by="playerDeck")

#' create table for graph
CC.table.S |>
  rename(playerDeck=deck) |>
  select(-n) |>
  pivot_longer(
    cols = -playerDeck,values_to = "seasonal",names_to = "server"
    ) |>
  left_join(
    CC.table |>
      select(-n) |>
      pivot_longer(
        cols = -playerDeck,values_to = "ladder",names_to = "server"),
    by=c("playerDeck","server")
    ) |>
  drop_na() |>
  as.data.table() %>%
  .[ , correlation := cor(seasonal,ladder), by = server ] |>
  distinct(server,correlation) |>
  mutate( 
    server = replace(server, server=="freq", "all"),
    server = str_to_title(server),
    correlation = round(correlation,3)
    ) |>
  rename_all(~toupper(.)) -> tb

df <- tibble(x = 0.01, y = 0.17, tb = list(tb ))

tt <- ttheme_default(
         # Use hjust and x to left justify the text
         # Alternate the row fill colours
                 core = list(
                   # fg_params=list(hjust = 1, x=1),
                   fg_params=list(fontface=3),
                   # bg_params=list(fill=c("yellow", "pink")),
                   bg_params = list(fill = blues9[4:1], col=NA)
                   ),

         # Change column header to white text and red background
                 colhead = list(
                   fg_params=list(col="grey25"),
                   bg_params=list(fill=blues9[4])
                   )
 )

#' create graph
CC.table.S |>
  rename(playerDeck=deck) |>
  select(-n) |>
  pivot_longer(
    cols = -playerDeck,values_to = "seasonal",names_to = "server"
    ) |>
  left_join(
    CC.table |>
      select(-n) |>
      pivot_longer(
        cols = -playerDeck ,values_to = "ladder",names_to = "server"),
    by=c("playerDeck","server")
    ) |>
  drop_na() |>
  as.data.table() %>%
  .[ , corrPR := cor(seasonal,ladder), by = server ] |>
  # filter( server == "europe" ) |>
  # pull(seasonal) |> sd()
  mutate( server = str_to_title(server) ) |>
  mutate( server = replace(server,server=="Freq","All") ) %>%
  ggplot( aes(ladder,seasonal,color=server)) +
  geom_point() +
  stat_smooth(method="lm",se=FALSE) +
  # ggpubr::stat_regline_equation(aes(label = ..rr.label..),size=5,show.legend = FALSE) +
  geom_table(data = df, 
             aes(x = x, y = y, label = tb),
             table.theme = tt,
             size = 3, colour = "darkblue",
             stat = "fmt_tb"
             ) + 
  # facet_wrap(~server) +
  geom_abline(intercept = 0, alpha=0.8, color = "grey75") +
  labs(
    x = "Ladder Play Rate",
    y = "Seasonal Play Rate",
    title = "Comparison of Play Rates",
    subtitle = "Top30 PlayRate decks - Comparing Ladder and Tournament PlayRates",
    caption = element_text(
      glue::glue("Playrates from {(with_tz(force_tz(timeBlock.1.start,'Japan'),'UTC')-lubridate::days(7))} to {with_tz(force_tz(timeBlock.1.start,'Japan'),'UTC')}, one week before the start of the earliest Seasonal start (the Asian shard)
                 Colored lines are fitted values with a univariate linear model for each Shard
                 Gray line is the diagonal for the first quadrant
                 PlayRate at the tournament obtained by inclusion rates among all LineUps
                 Source: Metadata of games collected with RiotGames API") ) ) +
  xlim( 0, 0.20 ) +
  ylim( 0, 0.20 ) +
  theme_539()
  
ggsave("./images/seasonal/{params$ind}-PRcor.png")
```

:::

:::::
:::

```{r twitter-meta, echo = FALSE}
metathis::meta() |>
  metathis::meta_description(
    glue::glue("{params$description}")
  ) |> 
  metathis::meta_viewport() |> 
  metathis::meta_social(
    title = params$title,
    url = "https://www.llorr-stats.com/",
    image = params$cardlurl,
    image_alt = "BandleMayor",
    og_type = "website",
    og_author = "Legna",
    twitter_card_type = "summary",
    twitter_creator = "@Maou_Legna"
  )
```

# Legal bla bla

This content was created under Riot Games 'Legal Jibber Jabber' policy using assets owned by Riot Games. Riot Games does not endorse or sponsor this project.