---
params:
  title: "CI?! What is a Confidence Interval?"
  description: "A little guide to understanding and use/read them."

title: | 
  `r params$title`
description: |
  `r params$description`
base_url: https://www.llorr-stats.com
author: Valentino (Legna) Vazzoler
date: 2022-06-11
output:
 distill::distill_article:
    toc: true
    toc_float: true
    toc_depth: 3
    self_contained: false
citation: false
# bibliography: references.bib
draft: TRUE
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo       = FALSE,
  eval       = TRUE,
  warning    = FALSE,
  error      = FALSE,
  message    = FALSE,
  comment    = NA,
  R.options  = list(width = 140, digits.secs=6),
  dev.args   = list(bg = 'whitesmoke'),
  fig.align  = 'center',
  fig.width  = 12,
  fig.height = 8,
  # fig.path   = "figures/prefix-"
  fig.path   = glue::glue("images/{params$ind}-"),
  layout     = "l-page",
  preview    = TRUE
)

# R Option
# options(scipen = 999)
source(file.path("C:","LlorR","scripts","lor_main.R" ))
# source(file.path("C:","LlorR","scripts","functions","lor_constants.R"))
source(file.path("C:","LlorR","scripts","functions","lor_functions.R"))
xaringanExtra::use_panelset()
```

```{r panelset-style}
xaringanExtra::style_panelset_tabs(
  font_family        = "Helvetica",
  active_foreground  = "white",
  hover_foreground   = "black",
  hover_border_color = "black",
  active_background  = "#007fff"
  )
```

```{r twitter-meta, echo = FALSE}
metathis::meta() |>
  metathis::meta_description(params$description) |>
  metathis::meta_viewport() |>
  metathis::meta_social(
    title = params$title,
    url = "https://www.llorr-stats.com/",
    image = "",
    image_alt = "",
    og_type = "website",
    og_author = "Legna",
    twitter_card_type = "summary",
    twitter_creator = "@Maou_Legna"
  )
```

# Introduction



# A bit of theory

We can't access the population so we take samples
There will be variation across samples
There will be sampling errors
We go crazy for sampling and we takes lots of sampling and we takes the means for each samples and plot the distribution of the means
the particular sample we have may not have have the population values
but the sampling distribution will give us the population value
the sampling deviation will give us that
the sampling deviation should be narrows and the standard deviation of the sampling distribution is the standard error

An interval such as that across a large number of samples we contains the population values
How wide should the interval be to contains the population value a lot of times
we take a sample and decide to use it

1.96*SE

The estimate and its interval may or may not contain the true population value
across a lot of sample if were to set the limits around the estimate around 1.96*SE
we are going to hit the population value 95% of SAMPLES

Each bar is a sample that

Intervals that contains the true population value of the paramter in 95% ifsamples

NO - It's an interval i'm 95% confident that the population estimate falls within the interval 
it's an interval where there is a 95% probability that contains the population value!
Hyper no! it's either 1 or 0 but you don't know which
They do not reflect confidence in the value of the population parameter


Assuming that this sample is one of the 95% that yields a confidence interval containing the true value of the parameter 

For every standard deviation change of the paramter we have an increase of the effect


```{r}
# broom::tidy(model)
# # modelbased::estimate_means(lm,fixed=var_name)
# 
# car::Anova(model, type=3)
# 
# ggplot2::autoplot(model,which=c(1,2,3,4), colour="#5c97bf", alpha = 0.5, size = 1) + theme_minimal()
# 
# robust::lmRob()
# 
# parameters::model_parameters(model, robust=TRUE, vcov.type="HC4")
```



In statistics, a sampling distribution or finite-sample distribution is the probability distribution of a given random-sample-based statistic
Wikipedia

# Definition


# Example
