---
params:
  ind: "MR042"
  patch: "Patch 3.00 - Week 3"
  title: "THE META REPORT NAME IS TOO LONG, TOO DAMN LONG (n°42)"
  description: "Rise of the AlPACa"
  cardlurl: "https://dd.b.pvp.net/latest/set1/en_us/img/cards/01NX051-full.png"
  start: "2022-01-19 18:00:00" #UTC tz / 'current' week start
  end:   "2022-01-26 18:00:00" #UTC tz / 'current' week end
  nGrid: 10

title: | 
  `r params$title`
description: |
  `r params$patch` - `r params$description`
base_url: https://www.llorr-stats.com
preview: |
  `r params$cardlurl`
author:
  - name: Valentino (Legna) Vazzoler
date: 01-01-1986
output:
 distill::distill_article:
    toc: true
    toc_float: true
    toc_depth: 3
    self_contained: false
citation: TRUE
draft: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo       = FALSE,
  eval       = TRUE,
  warning    = FALSE,
  error      = FALSE,
  message    = FALSE,
  comment    = NA,
  R.options  = list(width = 140, digits.secs=6),
  dev.args   = list(bg = 'whitesmoke'),
  fig.align  = 'center',
  fig.width  = 12,
  fig.height = 8,
  # fig.path   = "figures/prefix-"
  fig.path   = glue::glue("images/{params$ind}-"),
  layout     = "l-page",
  preview    = TRUE
)

#' R Option
options(scipen = 999)
source(file.path("C:","LlorR","scripts","lor_main.R" ))
source(file.path("C:","LlorR","scripts","functions","lor_constants.R"))
source(file.path("C:","LlorR","scripts","functions","lor_functions.R"))
xaringanExtra::use_panelset()
```

```{r panelset-style}
xaringanExtra::style_panelset_tabs(
  font_family        = "Helvetica",
  active_foreground  = "white",
  hover_foreground   = "black",
  hover_border_color = "black",
  active_background  = "#007fff"
  )
```

```{r constant}
general.caption <- glue::glue("{params$patch}
                              Ranked games from {params$start} UTC to {params$end} UTC
                              Source: Metadata of games collected with RiotGames API
                              Last Update: {now(tzone='UTC')}")
```

```{r raw-data}
# load Master
LoR.Match.DT.RMD    <- fread(file.path("C:","LlorR","data","raw","LoR_MatchDT_S11.csv"), header = T, na.strings = c("", NA))

# load Diamond
LoR.Diamond.DT.RMD  <- fread(file.path("C:","LlorR","data","raw","LoR_DiamondDT_S11.csv"), header = T, na.strings = c("", NA))

# load Account
LoR.Account.RMD <- fread(file.path("C:","LlorR","data","raw","LoR_ACCOUNT.csv"),header=T, na.strings = c("",NA), encoding = 'UTF-8') |>
  mutate( RiotID = sprintf("%s#%s",gameName,tagLine) )

# load Deck
LoR.Deck.RMD    <- fread(file.path("C:","LlorR","data","raw","LoR_DECK.csv"),colClasses = "character", header = T, na.strings = c("", NA))
```

```{r archetype-fix}
# Limit the Deck DT to make the fixes much faster
deck_filter <- do.call("rbind", mget(ls(pattern="\\.DT.RMD$")) ) |>
  # filter( game_start_time_utc > as.POSIXct(params$start, tz = "UTC") ) |>
  select(deck_code_1,deck_code_2) |>
  pivot_longer( cols = contains("deck_code"),values_to = "decks" ) |>
  filter(decks!="") |>
  distinct(decks)

LoR.Deck.RMD <- LoR.Deck.RMD[deck_code %in% deck_filter$decks]
source(file.path("C:","LlorR","scripts","functions","lor_archetype_rmd.R"))
LoR.Deck.RMD[ !is.na(archetype_pretty), archetype:=archetype_pretty ]
```

```{r account-info}
masterEU <- fread(file.path("C:","LlorR","data","raw","account","LoR_Master_S11_EU.csv"), header = T, na.strings = c("", NA), encoding = "UTF-8") |>
  filter(time <= as.POSIXct(params$end,"UTC"))

masterNA <- fread(file.path("C:","LlorR","data","raw","account","LoR_Master_S11_NA.csv"), header = T, na.strings = c("", NA), encoding = "UTF-8") |>
  filter(time <= as.POSIXct(params$end,"UTC"))

masterAPAC <- fread(file.path("C:","LlorR","data","raw","account","LoR_Master_S11_APAC.csv"), header = T, na.strings = c("", NA), encoding = "UTF-8") |>
  filter(time <= as.POSIXct(params$end,"UTC"))

namesList.EU.RMD   <- masterEU[ !is.na(puuid), .N ]
namesList.NA.RMD   <- masterNA[ !is.na(puuid), .N ]
namesList.APAC.RMD <- masterAPAC[ !is.na(puuid), .N ]
```

```{r prepare-data-master}
# Melt tbl
LoR.Melt.Master.RMD <- LoR.Match.DT.RMD |>
  filter( game_type == "Ranked"  ) |>
  filter( game_start_time_utc %within% interval(as.POSIXct(params$start,"UTC"),as.POSIXct(params$end,"UTC")) ) |>
  rename( playerPuuid_1 = puuid_1, playerPuuid_2 = puuid_2 ) |>
  mutate( opponentPuuid_1 = playerPuuid_2, opponentPuuid_2 = playerPuuid_1 ) |>
  mutate( opponent_deck_code_1 = deck_code_2, opponent_deck_code_2 = deck_code_1 ) |>
  pivot_longer(cols = c(ends_with("_1"),ends_with("_2")),
               names_to = c(".value"),
               names_pattern = "(.*)_[0-9]"
               ) |>
  as.data.table() |>
  # Add Deck data
  select(-factions) |>
  left_join(LoR.Deck.RMD, by="deck_code") |>
  rename(playerDeck=archetype) |>
  left_join(
    LoR.Deck.RMD[,.(deck_code,opponentDeck=archetype)],
    by=c("opponent_deck_code"="deck_code")) |>
  # Add Player data
  left_join(LoR.Account.RMD[,.(puuid,playerID=RiotID)]   ,by=c("playerPuuid"="puuid")) |>
  left_join(LoR.Account.RMD[,.(puuid,opponentID=RiotID)] ,by=c("opponentPuuid"="puuid"))
```

```{r prepare-data-diamond}
# Melt tbl
LoR.Melt.Diamond.RMD <- LoR.Diamond.DT.RMD |>
  filter( game_type == "Ranked"  ) |>
  filter( game_start_time_utc %within% interval(as.POSIXct(params$start,"UTC"),as.POSIXct(params$end,"UTC")) ) |>
  rename( playerPuuid_1 = puuid_1, playerPuuid_2 = puuid_2 ) |>
  mutate( opponentPuuid_1 = playerPuuid_2, opponentPuuid_2 = playerPuuid_1 ) |>
  mutate( opponent_deck_code_1 = deck_code_2, opponent_deck_code_2 = deck_code_1 ) |>
  pivot_longer(cols = c(ends_with("_1"),ends_with("_2")),
               names_to = c(".value"),
               names_pattern = "(.*)_[0-9]"
               ) |>
  as.data.table() |>
  # Add Deck data
  select(-factions) |>
  left_join(LoR.Deck.RMD, by="deck_code") |>
  rename(playerDeck=archetype) |>
  left_join(
    LoR.Deck.RMD[,.(deck_code,opponentDeck=archetype)],
    by=c("opponent_deck_code"="deck_code")) |>
  # Add Player data
  left_join(LoR.Account.RMD[,.(puuid,playerID=RiotID)]   ,by=c("playerPuuid"="puuid")) |>
  left_join(LoR.Account.RMD[,.(puuid,opponentID=RiotID)] ,by=c("opponentPuuid"="puuid"))
```

```{r check-value}
if (any(c(LoR.Melt.Master.RMD[  is.na(playerID), .N ],
          LoR.Melt.Diamond.RMD[ is.na(playerID), .N ],
          # LoR.Melt.Diamond.RMD[ is.na(playerDeck),  ]
          LoR.Melt.Diamond.RMD[ is.na(playerDeck), .N ],
          LoR.Melt.Master.RMD[  is.na(playerDeck), .N ]
          ))!=0) paste("If you are seeing this message something is wrong and the code must be fixed")
```
# Data

```{r}
#| layout="l-body"
LoR.Account.RMD |>
  filter(master=="diamond" |
           (master=="master" & gameName %in% masterEU$gameName & activeShard=="europe") |
           (master=="master" & gameName %in% masterNA$gameName & activeShard=="americas") |
           (master=="master" & gameName %in% masterAPAC$gameName & activeShard=="apac")
  ) |>
  select(activeShard,rank=master) |>
  mutate(rank = factor(rank, levels = c("master","diamond"), labels = c("Master","HighDiamond") ) ) |>
  tbl_summary(by = activeShard) |>
  as_gt() |>
  gtExtras::gt_theme_538() |>
  tab_header(
    title = glue::glue("{params$patch} / Players Info")
  ) |>
  tab_source_note(source_note = md(general.caption)) |>
  tab_options(
    data_row.padding = px(1.2),
    table.background.color = "whitesmoke",
    table.font.color = "black",
    table.font.color.light = "black"
   )
```

```{r nGames-data}
max_time <- do.call("rbind", mget( ls(pattern="\\.DT.RMD$") ) ) |>
  slice_max(game_start_time_utc,n=1,with_ties = F) |> 
  pull(game_start_time_utc) |>
  format(format = "%Y-%m-%d %H:%M:%S")
  
merge.tbl.master  <- table_bythenumbers(LoR.Match.DT.RMD)
merge.tbl.diamond <- table_bythenumbers(LoR.Diamond.DT.RMD)

nGames.Master  <- LoR.Melt.Master.RMD[,.N]
nGames.Diamond <- LoR.Melt.Diamond.RMD[,.N]
```

Number of (Ranked) matches analysed **`r format(nGames.Master/2,scientific = F)`** or **`r format(nGames.Master,scientific = F)`** games. / **Master** Players

Number of (Ranked) matches analysed **`r format(nGames.Diamond/2,scientific = F)`** or **`r format(nGames.Diamond,scientific = F)`** games. / **~HighDiamond** Players

Last Update: `r format(Sys.time(),format = "%Y-%m-%d %H:%M")`

```{r table-nGames-data}
#| layout="l-body"
nGames_tbl <- tbl_merge( 
  tbls = list(merge.tbl.master,merge.tbl.diamond),
    tab_spanner = c("**Master**", "**~HighDiamond**")
  ) |>
  modify_footnote(
    update = label ~
      md(glue::glue("Metadata from Friendly Matches (that aren't Bo3) is not recoverable, \n the value may not be perfect since I lack the starting time of the game. The amount of Games to still scrap is also an estimation based on the 'position' of the game" ))
  ) |> # show_header_names()
  modify_footnote(
    # row_type, variable, var_label
    update = contains("stat_") ~
      md(glue::glue("n(%) took from the number of matches. When the data is analysed the size is double since we account each different player" ))
  ) |>
  # modify_header(label ~ "**Variable**") |>
  bold_labels() |>
  as_gt() |>
  tab_header(
    title = glue::glue("{params$patch} - by the Numbers")
  ) |>
  tab_footnote(
    footnote = md(glue::glue("Max datetime recovered: {max_time} UTC from {params$start} to {params$end} UTC" )),
    locations = cells_title(groups = c("title"))
    ) |>
  tab_footnote(
    footnote = md(glue::glue(
      "EU Master {masterEU[,.N]}/{masterEU[!is.na(puuid),.N]}
      NA Master {masterNA[,.N]}/{masterNA[!is.na(puuid),.N]}
      APAC Master {masterAPAC[,.N]}/{masterAPAC[!is.na(puuid),.N]}"
      )),
    locations = cells_column_spanners(spanners = everything())
  ) 

nGames_tbl |> #
  tab_options(
    data_row.padding = px(1.2),
    table.background.color = "whitesmoke",
    table.font.color = "black",
    table.font.color.light = "black"
   )

gtsave(nGames_tbl, glue::glue("images/{params$ind}-bytheNumbers.png")) |> invisible()
```

# Regions

## Play Rate

```{r compute-region-freq}
Region.Freq <- freq_by_faction(LoR.Melt.Master.RMD)
```

::: {.l-page}
::::: {.panelset}

::: {.panel}
### Plot {.panel-name}

```{r reg-freq-plot}
#| fig.width=12,
#| fig.height=8

plot_freq(
  Region.Freq,
  nGames.Master,
  subtitle = "number of times a region is included in a deck",
  caption = general.caption
  )
```

The Gini Index is a measure of heterogeneity so, in this case and in simpler terms, how much the play rates are similar. The Index goes (when normalized like here) $in$ [0,1] and it's equal to 1 when there's a single value with 100% play rate or 0 when all play rates are equal. Of course a Gini Index of 1 needs to be avoided but it's not like the aim should be 0. As said, it's just to add some additional tools.
:::

::: {.panel}
### Table {.panel-name}

```{r}
table_freq_gt(Region.Freq) |>
  tab_header(
    title    = "Region Play Rate",
    subtitle = "Relative Frequencies by Inclusion Rate of a Region"
  ) |>
  tab_source_note( source_note = general.caption ) 
```
:::

:::::
:::

## Play Rate by number of Cards

```{r compute-region-freq-bycards}
Region.Freq.byCards <- freq_by_cards(LoR.Melt.Master.RMD)
```

::: {.l-page}
::::: {.panelset}

::: {.panel}
### Plot {.panel-name}

```{r reg-freq-bycards-plot}
#| fig.width=12,
#| fig.height=8
plot_freq(
  Region.Freq.byCards,
  nGames.Master,
  subtitle = "number of times a card within a region is included in a deck",
  # caption = general.caption
  caption = glue::glue("{params$patch}
                       Ranked games from {params$start} UTC to {params$end} UTC - Master Rank
                       DualRegions cards are counted based by the region that matters in the deck
                       Source: Metadata of games collected with RiotGames API
                       Last Update: {now(tzone='UTC')}")
  )
```
:::

::: {.panel}
### Table {.panel-name}

```{r}
table_freq_gt(Region.Freq.byCards) |>
  tab_header(
    title    = "Region Play Rate",
    subtitle = "Relative Frequencies by number of times a Card within a Region is included in a Deck"
  ) |>
  tab_source_note( source_note = general.caption )
```
:::
:::::
:::

# Champions Combinations

```{r process-tableChampion}
CC.table.Master <- LoR.Melt.Master.RMD |>
  tabyl(playerDeck, show_na = F) |>
  left_join(LoR.Melt.Master.RMD |>
              tabyl(playerDeck,server) |>
              adorn_percentages("col"),by="playerDeck") |>
  as.data.table()

CC.table.Diamond <- LoR.Melt.Diamond.RMD |>
  tabyl(playerDeck, show_na = F) |>
  left_join(LoR.Melt.Diamond.RMD |>
              tabyl(playerDeck,server) |>
              adorn_percentages("col"),by="playerDeck") |>
  as.data.table()
```

## Play Rates

::: {.l-page}
::::: {.panelset}
::: {.panel}
### Plot {.panel-name}

```{r prepare-cc-dt}
nrowPlot <- 20

topDeck <- union(
  CC.table.Master[ order(-percent) ][1:nrowPlot,playerDeck],
  CC.table.Diamond[ order(-percent) ][1:nrowPlot,playerDeck]
)

ChampionCombo <- tibble( playerDeck = topDeck ) |>
  left_join(CC.table.Master[,c("playerDeck","percent")], by ="playerDeck" ) |>
  left_join(CC.table.Diamond[,c("playerDeck","percent")], by ="playerDeck" ) |>
  rename_all(~c("playerDeck","Master","Diamond")) |>
  pivot_longer( cols = c("Master","Diamond"),names_to = "master",values_to = "freq" )
```


```{r champion-playrate-plot}
#| fig.width=12,
#| fig.height=8

nrowPlot <- 20

ChampionCombo |>
  mutate( playerDeck = factor(playerDeck),
          playerDeck = fct_reorder(playerDeck, freq, mean, .desc = F ) ) |>
  ggplot(aes(x = playerDeck, y = freq, group = master, fill = master))  +
  geom_bar( stat = "identity", position=position_dodge(0.5), width=.5 ) +
  coord_flip() +
  # guides(fill = "none")  +
  theme_bw() +
  geom_text(
    aes(label=round(freq*100,2)),
    size = 3,
    face = "bold",
    color = "grey50",
    hjust = -0.5, size = 4,
    position = position_dodge(0.9),
    ) +
  scale_y_continuous(
    limits = c(0, round(max(ChampionCombo$freq+0.04 ),3) ),
    breaks = seq(0,0.20,0.02),
    labels = scales::percent_format(accuracy = 1) ) +
  annotate(geom="text", x=3, y=0.05, col="black",label = paste("n =",nGames.Master,"\n"," cumulative frequence \n ",
                                                               paste0(CC.table.Master |> slice_max(percent,n = 20) |> select(percent) |> sum() %>% round(.,4)*100 ,"%") )
           ) +
  theme_539() +
  labs(x = "Champions",
       y = "Play Rate",
       title = "Champions Combination Play Rates",
       subtitle = glue::glue("Play-Rates of the top {nrowPlot} most played combination of champions/regions"),
       caption = glue::glue("{params$patch}
                            Ranked games from {params$start} UTC to {params$end} UTC
                            Decks are chosen from the union of top {nrowPlot} from Last-Seasononal player and ~HighDiamond resulting in {length(topDeck)} displayed
                            Source: Metadata of games collected with RiotGames API
                            Last Update: {now(tzone='UTC')}")
       ) +
  theme( 
    # legend.position = "none",
    axis.text = element_text(size = 9, face = "bold", color = "grey25", family = "Helvetica"),
    panel.grid.major.y = element_blank(),
    plot.title = element_text(face = "bold", size = 12, hjust = 0.6),
    axis.title.x = element_text(face = "bold"),
    axis.title.y = element_text(face = "bold"),
    legend.position = c(0.8,0.1)
    )
```
:::

::: {.panel}
### from Master {.panel-name}

```{r table-Champion-PR-old}
CC.table.Master |>
  rename(freq = percent) |>
  arrange(desc(freq)) |>
  # filter(nGames>100) |>
  select(playerDeck,freq,americas,apac,europe) |>
  reactable(
    bordered = TRUE,
    highlight = TRUE,
    striped = TRUE,
    searchable = TRUE,
    compact = TRUE, # compact the table height
    fullWidth = TRUE, # don't fill the page
    defaultPageSize = 20,
    wrap = TRUE,
    defaultColDef = colDef(
      style = list(fontFamily = "Helvetica", fontSize = "13px"), align = "center"
      # minWidth = 120,
      ),
    columns = list(
      playerDeck = colDef(name = "Champions",minWidth = 120, style = list(fontSize = "11px", fontWeight = "bold", color="black") ),
      freq     = colDef(name = "Play Rate",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") ),
      americas = colDef(name = "America",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") ),
      apac     = colDef(name = "Apac",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") ),
      europe   = colDef(name = "Europe",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") )
      )
    )
  # reactablefmtr::add_source(element_text(glue::glue("Data from Master Only.
  #                                                   Source: Metadata of games collected with RiotGames API.
  #                                                   Last Update: {now(tzone='UTC')}")), background_color = "whitesmoke", font_family = "Chivo")
```
:::

::: {.panel}
### from ~HighDiamond {.panel-name}

```{r table-Champion-PR-new}
CC.table.Diamond |>
  rename(freq = percent) |>
  arrange(desc(freq)) |>
  # filter(nGames>100) |>
  select(playerDeck,freq,americas,apac,europe) |>
  reactable(
    bordered = TRUE,
    highlight = TRUE,
    striped = TRUE,
    searchable = TRUE,
    compact = TRUE, # compact the table height
    fullWidth = TRUE, # don't fill the page
    defaultPageSize = 20,
    wrap = TRUE,
    defaultColDef = colDef(
      style = list(fontFamily = "Helvetica", fontSize = "13px"), align = "center"
      # minWidth = 120,
      ),
    columns = list(
      playerDeck = colDef(name = "Champions",minWidth = 120, style = list(fontSize = "11px", fontWeight = "bold", color="black") ),
      freq     = colDef(name = "Play Rate",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") ),
      americas = colDef(name = "America",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") ),
      apac     = colDef(name = "Apac",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") ),
      europe   = colDef(name = "Europe",format = colFormat(percent = TRUE,digits = 1), style = list( fontSize = "13px") )
      )
    )
  # reactablefmtr::add_source(element_text(glue::glue("Data from ~HighDiamond Only.
  #                                                   Source: Metadata of games collected with RiotGames API
  #                                                   Last Update: {now(tzone='UTC')}.")), background_color = "whitesmoke", font_family = "Chivo")
```
:::

:::::
:::

```{r twitter-meta}
#| echo=FALSE
metathis::meta() |>
  metathis::meta_description(
    glue::glue("{params$patch} - {params$description}")
  ) |>
  metathis::meta_viewport() |>
  metathis::meta_social(
    title = params$title,
    url = "https://www.llorr-stats.com/",
    image = params$cardlurl,
    og_type = "website",
    og_author = "Legna",
    twitter_card_type = "summary",
    twitter_creator = "@Maou_Legna"
  )
```

## Day by Day

Highlighting the play-rates of most played^[at the moment of the last game] decks over time.

::: {.l-page}
::::: {.panelset}

::: {.panel}
### Master {.panel-name}

```{r day-by-day-master}
#| fig.width=12,
#| fig.height=8

m = 12

Champion.deck.daily <- LoR.Melt.Master.RMD |>
  arrange(game_start_time_utc) |>
  select(game_start_time_utc,playerDeck) |>
  mutate(num_cc = factor(playerDeck) |> as.numeric() ) |>
  as.data.table() |>
  {\(x) x[ , cumFreq := (cumsum(num_cc)/num_cc)/.I , by=playerDeck ][ , n:=sum(num_cc), by=playerDeck ] }()
  # mutate(playerDeck = factor(playerDeck) |> fct_infreq() )

fct_values = Champion.deck.daily |>
  distinct(playerDeck,n) |>
  slice_max(n, n = m) |>
  pull(playerDeck)

plot_daily(
  Champion.deck.daily,
  decks = fct_values,
  title = "Evolution of Play Rate over time - Master",
  limit = .15 ) -> meta_evo

meta_evo
```
:::

::: {.panel}
### HighDiamond {.panel-name}

```{r day-by-day-diamond}
#| fig.width=12,
#| fig.height=8

m = 12

Champion.deck.daily <- LoR.Melt.Diamond.RMD |>
  arrange(game_start_time_utc) |>
  select(game_start_time_utc,playerDeck) |>
  mutate(num_cc = factor(playerDeck) |> as.numeric() ) |>
  as.data.table() |>
  {\(x) x[ , cumFreq := (cumsum(num_cc)/num_cc)/.I , by=playerDeck ][ , n:=sum(num_cc), by=playerDeck ] }()
  # mutate(playerDeck = factor(playerDeck) |> fct_infreq() )

fct_values = Champion.deck.daily |>
  distinct(playerDeck,n) |>
  slice_max(n, n = m) |>
  pull(playerDeck)

plot_daily(
  Champion.deck.daily,
  decks = fct_values,
  title = "Evolution of Play Rate over time - HighDiamond",
  limit = .15 ) -> meta_evo

meta_evo
```
:::

:::::
:::